### 2020-03-28 manuscript/manuscript.tex
Manuscript metadata, authors, etc.

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

\usepackage{float}
\restylefloat{table}

\journal{SoftwareX}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Untitled RadLib Paper}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Victoria B. Stephens}
\author{Sally Jensen}
\author{David O. Lignell\corref{cor1}}

\cortext[cor1]{Corresponding author. \ead{davidlignell@byu.edu}}

\address{Department of Chemical Engineering, Brigham Young University, Provo, UT 84602, United States}

\begin{abstract}
%% Text of abstract 
Ca. 100 words

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
radiative heat transfer \sep reacting flows

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}

Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & TODO 2.1 \\
\hline
C2 & Permanent link to code/repository used for this code version & $github.com/BYUignite/RadLib$ \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License   & TODO MIT license (MIT) \\
\hline
C5 & Code versioning system used & Git \\
\hline
C6 & Software code languages, tools, and services used & C++, Python 3 \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & TODO \\
\hline
C8 & If available Link to developer documentation/manual & TODO \\
\hline
C9 & Support email for questions & davidlignell@byu.edu \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\linenumbers

%% main text

The permanent link to code/repository or the zip archive should include the following requirements: 
\begin{itemize}
	\item TO DO: README.txt and LICENSE.txt.
	\item TO DO: Source code in a src/ directory, not the root of the repository.
	\item TO DO: Tag corresponding with the version of the software that is reviewed.
	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
\end{itemize}

\section{Motivation and significance}
\label{}

Introduce the scientific background and the motivation for developing the software. \cite{Lignell_2018}

Explain why the software is important, and describe the exact (scientific) problem(s) it solves.

Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.

Provide a description of the experimental setting (how does the user use the software?).

Introduce related work in literature (cite or list algorithms used, other software etc.).

\section{Software description}
\label{}

Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.

\subsection{Software Architecture}
\label{}

Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.

\subsection{Software Functionalities}
\label{}

Present the major functionalities of the software.

\subsection{Sample code snippets analysis (optional)}
\label{}

\section{Illustrative Examples}
\label{}

Provide at least one illustrative example to demonstrate the major functions.

Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel. (Please upload any video as a single supplementary file with your article. Only one MP4 formatted, with 50MB maximum size, video is possible per article. Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second. Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$. This tool will display your video exactly in the same way as it will appear on ScienceDirect.).

\section{Impact}
\label{}

\textbf{This is the main section of the article and the reviewers weight the description here appropriately}

Indicate in what way new research questions can be pursued as a result of the software (if any).

Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).

Indicate in what way the software has changed the daily practice of its users (if so).

Indicate how widespread the use of the software is within and outside the intended user group.

Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).

\section{Conclusions}
\label{}

Set out the conclusion of this original software publication.

\section{Conflict of Interest}
%Please select the appropriate text:
%
%Potential conflict of interest exists:
%We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work. The nature of potential conflict of interest is described below: [Describe conflict of interest]

%No conflict of interest exists:
We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.

\section*{Acknowledgements}
\label{}

This work was supported by the funding from the National Science Foundation under Grant Number CBET-1403403.

Special thanks to Vladimir P. Solovjov of Brigham Young University for his insights and assistance with model development.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References:

\bibliographystyle{elsarticle-num} 
\bibliography{references}

\section*{Current executable software version}
\label{}

Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
\hline
S1 & Current software version & TODO 2.1 \\
\hline
S2 & Permanent link to executables of this version  & TODO For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
\hline
S3 & Legal Software License & TODO MIT license (MIT) \\
\hline
S4 & Computing platforms/Operating Systems & Linux, OS X, Microsoft Windows\\
\hline
S5 & Installation requirements \& dependencies & TODO \\
\hline
S6 & If available, link to user manual - if formally published include a reference to the publication in the reference
    list & TODO For example: $http://mozart.github.io/documentation/$ \\
\hline
S7 & Support email for questions & davidlignell@byu.edu \\
\hline
\end{tabular}
\caption{Software metadata (optional)}
\label{} 
\end{table}

\end{document}
\endinput

### 2020-10-12 manuscript/manuscript.tex
Initial brain dump of paper text

@@
 
-\title{Untitled RadLib Paper}
+\title{RadLib: a radiative heat transfer model library for CFD}
 
@@
 Ca. 100 words
-
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-radiative heat transfer \sep reacting flows
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
+radiative heat transfer \sep reacting flows  \sep CFD
 \end{keyword}
@@
 \hline
-C3 & Code Ocean compute capsule & \\
+C3 & Code Ocean compute capsule & N/A \\
 \hline
-C4 & Legal Code License   & TODO MIT license (MIT) \\
+C4 & Legal Code License   & MIT license (MIT) \\
 \hline
@@
 
-%% main text
-
-The permanent link to code/repository or the zip archive should include the following requirements: 
-\begin{itemize}
-	\item TO DO: README.txt and LICENSE.txt.
-	\item TO DO: Source code in a src/ directory, not the root of the repository.
-	\item TO DO: Tag corresponding with the version of the software that is reviewed.
-	\item TO DO: Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
-\end{itemize}
+% TO DO
+% - update README
+% - tag software version
+% - decide on and generate documentation
 
 \section{Motivation and significance}
-\label{}
+\label{s:motivation}
 
-Introduce the scientific background and the motivation for developing the software. \cite{Lignell_2018}
+% Brain dump for first draft
+Why did we make this?
+Radiation is hard to deal with in CFD.
+It's complicated.
+You can't really get analytic solutions to practical problems.
+In lots of cases, that's fine because radiation can be safely neglected; it's not usually the dominant mode of heat transfer.
+However, we do combustion CFD.
+Radiation isn't always important to combustion problems, but when it is, simulations can get grossly inaccurate.
+So we need a nice way to account for radiation in our CFD simulations.
 
-Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
+When is radiation important to combustion simulations?
+In high-temperature systems, radiation can often be neglected in the beginning and middle of the simulation (assuming, say, a jet flame or a counterflow flame or something like that).
+At those times (which I'm going to call "early flame"), convective heat transfer dominates pretty heavily.
+However, radiation becomes more important for late-stage flame phenomena, either after some time has gone by (radiation time scales?), or physically high up in a flame where convection doesn't dominate as much as below, or just in areas that are relatively far away from the flame sheet itself where the reactions are happening.
+There's also soot, which involves radiation heavily, but soot particles are so big and slow that their time and length scales (and their radiative time scales) mean that radiation doesn't become important until late in the flame evolution.
 
-Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
+So what's the problem?
+Why hasn't this been done already?
+Radiation is complicated.
+So is combustion.
+Combustion in particular can be so complex that direct simulations are too computationally expensive for us to simulate configurations that are practical for engineering systems.
+Direct simulations are usually used as a research tool.
+Other modeling approaches exist (LES, ODT, etc.) that lower the computational cost and allow us to simulate practical things.
+So far so good.
 
-Provide a description of the experimental setting (how does the user use the software?).
+Radiation is a little like combustion in that its core mechanisms are complex, physically and mathematically.
+In addition, it's directional AND depends on the wavelength of the energy involved (other heat transfer doesn't have the wavelength dependence); its governing equations integrate over direction and wavelength, which makes things extra complicated.
+RADIATION GOVERNING EQUATIONS HERE.
+Convective heat transfer follows easy rules, but radiation doesn't.
+There are simple systems in which we can boil things down to analytic solutions, but most of the time, the simple equations don't apply, and that's often true in combustion systems where there are so many different length and time scales involved.
+The fundamental equations of radiative heat transfer are big and mathematically complex; they don't have analytic solutions except in the simplest geometries.
+So what do we do?
+One of two things.
+One, we do ray tracing (sometimes referred to as Monte Carlo simulations.
+These can be extremely accurate, but super computationally expensive.
+Essentially the equivalent of a direct numerical solution.
+Two, we simplify the the equations.
+We make assumptions.
+And so on.
+This is potentially less accurate, but more practical.
+By simplifying the fundamental governing equations, we create models that apply to various situations, systems, and geometries (i.e.
+black body assumptions, directional assumptions, etc.).
+There are models developed for CFD and specific combustion systems.
+These are the models that we've put into practice here in such a way that they're easy to apply to various systems.
+Modular organization for this purpose.
 
-Introduce related work in literature (cite or list algorithms used, other software etc.).
+So far there isn't an easy way to access and use radiation models.
+There are simple ones in Cantera (check this, there might not be any), but they make too many assumptions or don't work well for combustion or what have you.
+RadLib is a radiation library of models that you can apply to any simulation type, and we'd like to add it to Cantera, too.
+Basically, there isn't a reliable way to do radiation calculations in CFD simulations without coding the models yourself, which is extra hard because they're complicated and hard.
+So we've done it for you and put them in a library that easy for anyone to use.
+\cite{Lignell_2018}
+
+Models we're using:
+\begin{itemize}
+	\item planck mean (optically thin?)
+	\item two flux model (not sure if we even have this)
+	\item weighted sum of grey gases (CITE Bordbar and others)
+	\item SLW model (CITE Solovjov and others)
+\end{itemize}
+Discuss pros and cons of each model for combustion simulations?
+You still have to pick the right one for your simulation and situation.
+That discussion might fit better in software description section.
+See example section for comparisons of models.
+
+%Author guidelines for this section:
+%\begin{itemize}
+%	\item Introduce the scientific background and the motivation for developing the software. \cite{Lignell_2018}
+%	\item Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
+%	\item Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
+%	\item Provide a description of the experimental setting (how does the user use the software?).
+%	\item Introduce related work in literature (cite or list algorithms used, other software etc.).
+%\end{itemize}
 
 \section{Software description}
-\label{}
+\label{s:description}
 
-Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
+%Author guidelines for this section
+%\begin{itemize}
+%	\item Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
+%	\item  Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
+%	\item Present the major functionalities of the software.
+%\end{itemize}
+
+\subsection{Model descriptions}
+\label{s:models}
+
+You need two separate (but very related) models for any given case: one to get radiation absorption coefficients and one for the solution to the governing equations.
+The first can happen independently of anything else, but the second requires the first.
+You can sort of mix and match models, but usually we don't, so it's not presented that way in the software.
+
+\subsubsection{Planck Mean}
+\label{s:planckmean}
+
+\subsubsection{WSGG}
+\label{s:wsgg}
+
+\subsubsection{RCSLW}
+\label{s:RCSLW}
 
 \subsection{Software Architecture}
-\label{}
+\label{s:architechture}
 
-Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
+Object-oriented C++ class library. Examples folder contains sample driver scripts for using the library.
 
-\subsection{Software Functionalities}
-\label{}
-
-Present the major functionalities of the software.
-
-\subsection{Sample code snippets analysis (optional)}
-\label{}
+Python version somewhere? Corresponding examples?
 
 \section{Illustrative Examples}
-\label{}
+\label{s:Examples}
 
-Provide at least one illustrative example to demonstrate the major functions.
+Simple comparisons of each of these models as implemented to some ray-tracing results (equivalent to a direct numerical solution) to establish validity.
+Illustrates when to use various models and why you might choose one over another.
+Plots and discussion go here.
 
-Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.
-(Please upload any video as a single supplementary file with your article.
-Only one MP4 formatted, with 50MB maximum size, video is possible per article.
-Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second.
-Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$.
-This tool will display your video exactly in the same way as it will appear on ScienceDirect.).
+%Author guidelines for this section
+%\begin{itemize}
+%	\item Provide at least one illustrative example to demonstrate the major functions.
+%	\item Optional: you may include one explanatory video 
+%\end{itemize}
 
 \section{Impact}
-\label{}
+\label{s:impact}
 
-\textbf{This is the main section of the article and the reviewers weight the description here appropriately}
+As far as I'm aware, there isn't an easy way to incorporate radiative heat transfer into a CFD simulation.
+Most cases use optically thin assumption (which works in some cases, but not in others) or neglect radiation entirely (also applicable sometimes, but not always).
+Unfortunately, this means that when you simulation some configuration in which radiation might be important to the overall heat transfer, you won't get accurate simulation results.
+Furthermore, if your study is about something else entirely, your radiation model (or lack thereof) becomes a source of error that may be very difficult to separate from other sources of error in your simulation study (i.e.
+soot modeling studies).
+As of right now, if you want any detailed radiation treatment, you have to code it yourself, which is difficult and requires external validation.
 
-Indicate in what way new research questions can be pursued as a result of the software (if any).
+RadLib can make researchers' lives easier by providing a library of prevalidated radiation models that can be switched out with no difficulty.
+Additional models can be added easily using the provided modular framework.
+Researchers can even use Radlib as a tool for comparing models.
+No need to code multiple different complex radiation models yourself just to decide which one works best for your simulation.
+And no need to puzzle through the literature to figure our which model(s) might be best for your simulation, either; instead, you can test them yourself.
+It saves tons of time and effort that researchers can now put toward results rather than code or model development.
 
-Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
+By putting all these models side by side in a modular framework, RadLib also provides a structure on which new or altered radiation models can be tested against existing ones.
+Maybe more comparative studies can be done, especially for more complex simulation cases.
+We plan to add radiation models as appropriate to RadLib, too.
 
-Indicate in what way the software has changed the daily practice of its users (if so).
+RadLib opens up new horizons for CFD simulations, especially in combustion cases.
+It is designed such that it can be easily incorporated into existing research codes.
+Our group plans to use it with ODT [CITE OTHER SOFTWAREX PAPER HERE?] alongside soot model library (in development) to study late-flame phenomena such as soot oxidation, flame extinction, and soot-flame breakthrough.
+These topics in particular are difficult because they require accurate simulation data over a relatively long computational time in addition to good models for both soot chemistry (which is an active research area) and radiation heat transfer (which is the difficult part that RadLib can solve).
+Using RadLib for such studies allows us to separate and quantify sources of error that may occur due to various models, which is super difficult if you only have one model to work with or it hasn't been validated well.
 
-Indicate how widespread the use of the software is within and outside the intended user group.
+RadLib can also be used outside of combustion CFD research for anything involving radiative heat transfer.
+Potential research areas that could benefit include atmospheric and climate sciences, interstellar phenomena, improving efficiency of energy-producing processes, safety in chemical plant design, etc.
+We aren't experts in these areas, but radiative heat transfer is a universal phenomena that applies to any system or process that involves heat transfer.
 
-Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
+This software has not been used outside of the current research group, and it is not used in any commercial settings at this time.
+
+%Author guidelines for this section
+%\begin{itemize}
+%	\item \textbf{This is the main section of the article and the reviewers weight the description here appropriately}
+%	\item Indicate in what way new research questions can be pursued as a result of the software (if any).
+%	\item Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
+%	\item Indicate in what way the software has changed the daily practice of its users (if so).
+%	\item Indicate how widespread the use of the software is within and outside the intended user group.
+%	\item Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
+%\end{itemize}
 
@@
 
-This work was supported by the funding from the National Science Foundation under Grant Number CBET-1403403.
+This work was supported in part by the funding from the National Science Foundation under Grant Number CBET-1403403 and [INSERT SALLY FUNDING SOURCE HERE?].
 
@@
 \hline
-S3 & Legal Software License & TODO MIT license (MIT) \\
+S3 & Legal Software License & MIT license (MIT) \\
 \hline

### 2020-11-08 manuscript/manuscript.tex
Adding references, starting text on model descriptions

@@
 So we've done it for you and put them in a library that easy for anyone to use.
-\cite{Lignell_2018}
 
@@
 \begin{itemize}
-	\item planck mean (optically thin?)
-	\item two flux model (not sure if we even have this)
-	\item weighted sum of grey gases (CITE Bordbar and others)
-	\item SLW model (CITE Solovjov and others)
+	\item planck mean (optically thin?) with coefficients from TNF website \cite{Smith_2003}
+	\begin{itemize}
+		\item other references from TNF website: \cite{Grosshandler_1993,Frank_2000,Zhu_2002,Barlow_2001}
+	\end{itemize}
+	\item weighted sum of grey gases \cite{Bordbar_2014,Bordbar_2020}
+	\item RCSLW model \cite{Solovjov_2017}
+	\begin{itemize}
+		\item SLW model \cite{Solovjov_2001}
+		\item LCSLW \cite{Solovjov_2020}
+		\item "It is shown that the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases." \cite{Badger_2019}
+
+	\end{itemize}		
 \end{itemize}
@@
 %\begin{itemize}
-%	\item Introduce the scientific background and the motivation for developing the software. \cite{Lignell_2018}
+%	\item Introduce the scientific background and the motivation for developing the software. 
 %	\item Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
@@
 
-You need two separate (but very related) models for any given case: one to get radiation absorption coefficients and one for the solution to the governing equations.
-The first can happen independently of anything else, but the second requires the first.
-You can sort of mix and match models, but usually we don't, so it's not presented that way in the software.
+RadLib includes three radiation models of varying complexity.
+Each model consists of two parts: calculation of radiation absorption coefficients and solution of the radiative transfer equation.
+Radiation absorption coefficients are typically described by correlations relating species absorption coefficients to temperature [CHECK THIS].
+The radiative transfer equation (RTE) includes one or more gas species over which the radiative intensity or heat flux is calculated.
+In RadLib, four radiating gas species are used: H$_2$O, CO, CO$_2$, and CH$_4$.
+[also soot?]
 
-\subsubsection{Planck Mean}
+\subsubsection{Planck mean absorption coefficients}
 \label{s:planckmean}
 
-\subsubsection{WSGG}
+\subsubsection{Weighted sum of gray gases (WSGG)}
 \label{s:wsgg}
 
-\subsubsection{RCSLW}
+\subsubsection{Rank Correlated SLW (RCSLW) model}
 \label{s:RCSLW}
@@
 Plots and discussion go here.
-
-%Author guidelines for this section
-%\begin{itemize}
-%	\item Provide at least one illustrative example to demonstrate the major functions.
-%	\item Optional: you may include one explanatory video 
-%\end{itemize}
+Five example cases demonstrated with this code in both C++ and Python.
 
@@
 Most cases use optically thin assumption (which works in some cases, but not in others) or neglect radiation entirely (also applicable sometimes, but not always).
-Unfortunately, this means that when you simulation some configuration in which radiation might be important to the overall heat transfer, you won't get accurate simulation results.
+[Refer to TNF website radiation page here.] Unfortunately, this means that when you simulation some configuration in which radiation might be important to the overall heat transfer, you won't get accurate simulation results.
 Furthermore, if your study is about something else entirely, your radiation model (or lack thereof) becomes a source of error that may be very difficult to separate from other sources of error in your simulation study (i.e.
@@
 
-This work was supported in part by the funding from the National Science Foundation under Grant Number CBET-1403403 and [INSERT SALLY FUNDING SOURCE HERE?].
-
-Special thanks to Vladimir P. Solovjov of Brigham Young University for his insights and assistance with model development.
+The authors extend special thanks to Hadi Bordbar for assistance with the WSGG model and to Vladimir Solovjov and Brent Webb of Brigham Young University for their insights and assistance with the RCSLW model.
 

### 2020-11-10 manuscript/manuscript.tex
Adding text to WSGG section, various other edits

@@
 
-RadLib includes three radiation models of varying complexity.
-Each model consists of two parts: calculation of radiation absorption coefficients and solution of the radiative transfer equation.
-Radiation absorption coefficients are typically described by correlations relating species absorption coefficients to temperature [CHECK THIS].
-The radiative transfer equation (RTE) includes one or more gas species over which the radiative intensity or heat flux is calculated.
-In RadLib, four radiating gas species are used: H$_2$O, CO, CO$_2$, and CH$_4$.
-[also soot?]
+RadLib includes three models of varying complexity and accuracy to calculate the radiation absorption coefficients and their weighting factors for each gas considered by the model.
+Radiation absorption coefficients are typically calculated using correlations relating them local properties such as temperature, total pressure, or species partial pressure, depending on the model.
+Correlations come from curve fits to high-resolution radiation property databases.
+At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and, optionally, soot volume fraction in its calculation of absorption coefficients and weighting factors.
 
-\subsubsection{Planck mean absorption coefficients}
+Once the radiative absorption coefficients are calculated, they are then used to solve the radiative transfer equation (RTE), which depends on the simulation configuration and assumptions.
+Solving the RTE is not the focus of this software, but RadLib's example cases do employ a simple implicit trapezoid method solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
+[MORE DESCRIPTION OF SOLVER GOES HERE?]
+
+[OTHER THINGS THAT APPLY TO ALL MODELS GO HERE]
+
+[MAYBE INCLUDE SOME BASIC INFO ON LBL?]
+
+\subsubsection{Planck Mean absorption coefficients}
 \label{s:planckmean}
+
+When we refer to the Plank Mean model, what we're using is actually the Planck Mean absorption coefficients, calculated from the correlations given on the TNF workshop site \citep{Smith_2003}.
+Their correlations (temperature dependent) are based on the RADCAL model in \citep{Grosshandler_1993}.
+The TNF radiation model is also documented in \citep{Barlow_2001}.
+
+This model is commonly used because it's relatively simple, easy to implement, low in computational expense, and provides reasonably accurate results in many cases.
+
+Quote from TNF site page: "The characteristics of some flames selected for the workshop are such that a model based upon the assumption of optically thin radiative heat loss should yield reasonable accuracy.
+This has been demonstrated for the simple hydrogen jet flames \cite{Barlow_1999}.
+However, there is some evidence that the optically thin model significantly over predicts radiative losses from the CH4 flames in the TNF library, due to strong absorption by the 4.3-micron band of CO2 \cite{Frank_2000,Zhu_2002,Coelho_2002}." Basically, it works well for flames that are actually optically thin, but not so well for flames that aren't.
+This is especially true of sooting flames.
 
@@
 \label{s:wsgg}
+The basic assumption of weighted sum of gray gases (WSGG) models in general is that the non-gray behavior of gas mixtures, in this case H$_2$O and CO$_2$, can be modeled by a weighted sum of several gray gases and one transparent gas (which represents the spectral windows between absorption bands).
+RadLib uses the WSGG model presented by Bordbar et al.
+\citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}.
+RadLib, in accordance with the Bordbar et al.
+WSGG method cited above, uses a mixture of four gray gases and one transparent gas.
+Absorption coefficients are calculated by
+\begin{equation}
+	K_i=\sum_{k=0}^{4}d_{i,k}M_r^k,
+\end{equation}
+where $K_i$ is the absorption coefficient for species $i$, $d_{i,k}$ is a species-specific correlated model coefficient, and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$.
+The weight factors are calculated by
+\begin{equation}
+	a_i=\sum_{j=0}^{4}b_{i,j}T_r^j,
+\end{equation}
+where $a_i$ is the weighting factor for species $i$ and $T_r$ is a normalized temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The value of $b_{i,j}$ is calculated by 
+\begin{equation}
+	b_{i,j}=\sum_{k=0}^{4}C_{i,j}M_r^k,
+\end{equation}
+where $C_{i,j}$ is another correlated model coefficient and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$ as above.
 
@@
 
-Object-oriented C++ class library. Examples folder contains sample driver scripts for using the library.
+RadLib is an object-oriented C++ class library.
+
+Examples folder contains sample driver scripts for using the library.
 
@@
 
-Simple comparisons of each of these models as implemented to some ray-tracing results (equivalent to a direct numerical solution) to establish validity.
+Simple comparisons of each of these models to some ray-tracing results (equivalent to a direct numerical solution) to establish validity.
 Illustrates when to use various models and why you might choose one over another.
@@
 Five example cases demonstrated with this code in both C++ and Python.
+Compared to line-by-line calculations (essentially the radiation version of Monte Carlo).
 

### 2020-11-14 manuscript/manuscript.tex
adding examples to the paper

@@
 
-When we refer to the Plank Mean model, what we're using is actually the Planck Mean absorption coefficients, calculated from the correlations given on the TNF workshop site \citep{Smith_2003}.
+When we refer to the Plank Mean model, what we're using is actually the Planck Mean (PM) absorption coefficients, calculated from the correlations given on the TNF workshop site \citep{Smith_2003}.
 Their correlations (temperature dependent) are based on the RADCAL model in \citep{Grosshandler_1993}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Illustrative Examples}
@@
 
-Simple comparisons of each of these models to some ray-tracing results (equivalent to a direct numerical solution) to establish validity.
-Illustrates when to use various models and why you might choose one over another.
-Plots and discussion go here.
-Five example cases demonstrated with this code in both C++ and Python.
-Compared to line-by-line calculations (essentially the radiation version of Monte Carlo).
+Several examples are presented to illustrate the behavior of the models.
+The examples show heat flux $q$ or volumetric heat source $Q$ one one-dimensional configurations with varying gas compositions and temperatures.
+We compare the PM, WSGG, and RCSLW models for each example.
+The examples are taken from those presented by Solvojov et al., (2017) \cite{Solovjov_2017}, and Bordbar et al., 2020 \cite{Bordbar_2020}; the number corresponds to the example in the respective referece.
+A ray-tracing code is used to solve the radiative transport equation between two parallel plates.
+Table~\ref{t:examples} summarizes the cases.
+Example S1 is a hot slab next to a cold slab where the cold thickness varies; Example S2 is similar but isothermal with a \emph{thick} slab of high CO$_2$ next to a \emph{thin} slab of low CO$_2$ of varying thickness; Example S3 has parabolic temperature and H$_2$O profiles; Example S4 has a triangular temperature profile between equally-spaced isothermal regions; Example S5 is a half-sinusoid decreasing in temperature from 1500 to 500 K; and Example B3 has symmetric temperature and H$_2$O profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$).
+In each case, comparison is made to the line-by-line (LBL) data presented in the references.
+%
+\begin{table}
+    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2017}. All cases have $P=1$ atm, black walls.}
+    \label{t:examples}
+    \centering
+    \resizebox{\textwidth}{!}{
+    \begin{tabular}{c l l c c c}
+        \hline
+        Example & T(K)                           & $y_{H2O}$  $y_{CO2}$ (mole frac.)                     & L (m)   & $T_{walls}$ (K)\\
+        \hline
+        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$     & $y_{CO2}=0.1$, $y_{H2O}=0.2$                          & 0.5-2.5 & cold, cold     \\
+        S2 & T=1000                              & $y_{CO2}(x<0.5)=0.4$, $y_{CO2}(x>0.5)=0.1$            & 0.5-2.5 & cold, cold     \\
+           &                                     & $y_{H2O}=0.0$                                         &         &                \\
+        S3 & $T(x) = 4000x(L-x)/L^2 + 800$       & $y_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$                   & 1       & 800, 800       \\
+           &                                     & $y_{CO2}=0$                                           &         &                \\
+        S4 & middle third triangular to 2500     & $y_{H2O}=0.1$, $y_{CO2}=0$                            & 0.3     & 500, 500       \\
+        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$    & $y_{H2O}=0.1$, $y_{CO2}=0$                            & 2       & 1500, 500      \\
+        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$  & $y_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$         & 1       & 400, 400       \\
+           &                                     & $y_{CO2}=1-y_{H2O}$                                   &         &                \\
+        \hline
+    \end{tabular}
+    }
+\end{table}
+%
+
+The examples are provided with the radlib code and implemented in both C++ and Python.
+A Juptyer notebook is provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files.
+Python and Cython versions of the one-dimensional solver \texttt{parallel\_planes} are provided for convenience.
+
+These examples are not meant to be exhaustive, and details about the motivation of these examples and the behavior of the specific models is to be found in the respective references.
+The cases presented are intended to illustrate the use of the radiative library.
+While not shown  for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020}, so that these examples also serve as a validation of the implementation of the models.
+
+Figure~\ref{f:examples} shows comparative results for the different radiation models for these cases. 
+%
+\begin{figure}
+    \begin{center}
+    \begin{tabular}{c c}
+        Example S1 & Example S2 \\
+        \includegraphics[width=3 in]{ex_1.pdf} &
+        \includegraphics[width=3 in]{ex_2b.pdf} \\
+        Example S3 & Example S4 \\
+        \includegraphics[width=3 in]{ex_3a.pdf} &
+        \includegraphics[width=3 in]{ex_4a.pdf} \\
+        Example S5 & Example B3 \\
+        \includegraphics[width=3 in]{ex_5b.pdf} &
+        \includegraphics[width=3 in]{ex_6.pdf}
+    \end{tabular}
+    \caption{Results for examples summarized in Table~\ref{t:examples}.}
+    \label{f:examples}
+    \end{center}
+\end{figure}
+%
+In general, the PM model performs poorly compared to the WSSGG and RCSLW models.
+A notable exception is Example S4.
+In Example S2, the PM $q(L)/\sigma T^4$ is off scale at an essentially constant at a value of unity.
+The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m.
+Example S5 omits the PM model to more clealy show the behavior of the WSGG and RCSLW models.
+For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 at $x=0$ to a peak of 200 at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m.
+In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model.
+Example S5 shows the sensitivity of the RCSLW model to the number of gases used.
+When $n$ is increased to eight the RCSLW model improves to show nearly perfect agreement with the LBL data in Example S2.
+In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain.
+In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.
+
+% TODO: do the cost comparison  <13-11-20, dol> %
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-11-16 manuscript/manuscript.tex
Drafted text of software architecture section. Added flow chart figure. Various edits and additions to model descriptions.

--- 2020-11-10 manuscript/manuscript.tex
@@
 
-Models we're using:
-\begin{itemize}
-	\item planck mean (optically thin?) with coefficients from TNF website \cite{Smith_2003}
-	\begin{itemize}
-		\item other references from TNF website: \cite{Grosshandler_1993,Frank_2000,Zhu_2002,Barlow_2001}
-	\end{itemize}
-	\item weighted sum of grey gases \cite{Bordbar_2014,Bordbar_2020}
-	\item RCSLW model \cite{Solovjov_2017}
-	\begin{itemize}
-		\item SLW model \cite{Solovjov_2001}
-		\item LCSLW \cite{Solovjov_2020}
-		\item "It is shown that the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases." \cite{Badger_2019}
-
-	\end{itemize}		
-\end{itemize}
-Discuss pros and cons of each model for combustion simulations?
-You still have to pick the right one for your simulation and situation.
-That discussion might fit better in software description section.
-See example section for comparisons of models.
-
 %Author guidelines for this section:
@@
 
-\section{Software description}
-\label{s:description}
-
 %Author guidelines for this section
@@
 
-\subsection{Model descriptions}
+\section{Model descriptions}
 \label{s:models}
@@
 
-\subsubsection{Planck Mean absorption coefficients}
+\subsection{Planck Mean absorption coefficients}
 \label{s:planckmean}
@@
 
-\subsubsection{Weighted sum of gray gases (WSGG)}
+\subsection{Weighted sum of gray gases (WSGG)}
 \label{s:wsgg}
@@
 where $C_{i,j}$ is another correlated model coefficient and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$ as above.
+The model coefficients $d_{i,k}$ and $C_{i,j}$ can be found in the literature \citep{Bordbar_2014,Bordbar_2020}.
+RadLib uses the updated model coefficients from \citep{Bordbar_2020}, which extends the model presented in \citep{Bordbar_2014} to include all possible values of the H$_2$O-CO$_2$ molar ratio.
 
-\subsubsection{Rank Correlated SLW (RCSLW) model}
+\subsection{Rank Correlated SLW (RCSLW)}
 \label{s:RCSLW}
 
-\subsection{Software Architecture}
+The Spectral Line Weighted-sum-of-gray gases (SLW) model represents a family of global approaches to radiative heat transfer in high-temperature gases that also includes Absorption Distribution Function (ADF) and Full Spectrum $k$-distribution (FSK) models, all of which are based on the same fundamental principle in modeling the gas absorption spectrum \cite{Solovjov_2016}.
+In order to extend their spectral models from uniform conditions (isothermal, homogeneous gases) to nonuniform conditions (non-isothermal, non-homogeneous gases), these models take a reference approach in which local gas states are corrected relative to a reference state.
+Reference approaches, however, generally lack consistent reference states and can yield significant errors in cases with large spatial temperature gradients \cite{Solovjov_2017}.
+The Rank Correlated SLW (RCSLW) model is a unique extension of the generalized SLW model that does not require a specified gas reference state and preserves the emission term of the spectrally integrated RTE.
+Recent comparison of advanced SLW modeling approaches revealed that "the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases" \citep{Badger_2019}.
+A brief overview of the general SLW and RCSLW models will be given here; detailed discussion can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
+
+The radiative transfer equation (RTE) for an absorbing, emitting, and non-scattering medium along a given path length $s$ in a direction $\hat{\Omega}$ is given by 
+\begin{equation}
+	\frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b \eta},
+\end{equation}
+where $I_{\eta}$ is the radiative spectral intensity, $I_{b\eta}$ is the Planck spectral distribution of blackbody intensity, and $\kappa_{\eta}$ is the spectral absorption coefficient of the medium.
+Integrating with respect to wavenumber and subdividing the absorption cross-section into gray gases gives the SLW form of the RTE:
+\begin{equation}
+\label{e:RTE_SLW}
+	\frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n.
+\end{equation}
+Here, $n$ is the number of gray gases in the model and $I_j$ is the intensity of gray gas $j$.
+$\kappa_j$ is the gray gas absorption coefficient, which can be calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
+where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}.
+The gray gas weights corresponding to each absorption coefficient are given by $a_j=F(C_j)-F(C_{j-1})$, where $F(C_j)$ is the absorption line blackbody distribution function (ALBDF) for species $j$, calculated from the detailed absorption spectrum of that species.
+The absorption cross-sections are chosen with respect to a thermodynamic reference state, which makes generalized SLW methods reference approaches.
+Once Equation ~\ref{e:RTE_SLW} is solved for each gray gas species, to total radiative intensity $I$ can be calculated by summing the gray gas intensities:
+\begin{equation}
+	I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
+\end{equation}
+
+The Rank-Correlated SLW (RCSLW) model avoids specifying a reference state by relating thermodynamic states to one another instead.
+If two arbitrary absorption cross-sections define identical wavenumber intervals, the two cross-sections (neither of which is designated a reference cross-section) can be said to be rank-correlated.
+The inverse ALBDF, defined such that $C[F(C,\phi_g,T_b),\phi_g,T_b]=C$ and $F[C(F,\phi_g,T_b),\phi_g,T_b]=F$ for a given gas thermodynamic state $\phi_g$ and blackbody temperature $T_b$, is proven to have this property and can also be called the rank-correlated reordered absorption cross-sections \cite{Solovjov_2017}.
+As a result, the inverse ALBDF can be used to construct cross-section intervals for the RCSLW model that do not rely on a defined reference state or spectrum.
+RadLib's RCSLW model uses Method 1.2.2 as defined and recommended in \cite{Solovjov_2017}
+
+\section{Software Description}
 \label{s:architechture}
 
-RadLib is an object-oriented C++ class library.
+RadLib is an object-oriented C++ class library, including both C++ and Python interfaces.
+The RadLib package contains five subdirectories (upon initial download): \texttt{source} contains the RadLib source code; \texttt{build} contains installation files; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to generate code documentation with Doxygen (optional).
 
-Examples folder contains sample driver scripts for using the library.
+The \texttt{source} and \texttt{examples} directories are further divided into \texttt{C++} and \texttt{Python} subdirectories to differentiate between interfaces.
+There are three interface options for using this code: C++, Python, and Cython-wrapped Python.
+C++ interfaces are located within the \texttt{examples/c++} folder, while Python interfaces are located within the \texttt{examples/python} folder.
+When running examples with Python, the Cython-wrapped version is the default; to run the regular Python version without the Cython wrapper, edit the comments near the top of the example files (i.e \texttt{ex\textunderscore S1.py}).
+The C++ interface produces the fastest-running code, followed by the Cython-wrapped Python interface and then the regular Python interface.
+[INSERT RUNTIME COMPARISONS HERE]
 
-Python version somewhere? Corresponding examples?
+RadLib installation is automated with CMake.
+First, navigate to the \texttt{radlib/build} directory.
+If the user requires an installation location other than the default \texttt{radlib/installed} directory, edit the \texttt{user\textunderscore config} file before running CMake.
+To compile the package, run the command \texttt{cmake -C user\textunderscore config ../source}.
+Upon successful completion, run \texttt{make} and then \texttt{make install} to complete the process.
+The generated C++ library file is located at \texttt{radlib/installled/lib/libradlib.a}.
+
+Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces.
+The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry, making it a versatile tool for any simulation that requires radiative heat transfer, regardless of configuration.
+The interfaces, solver, and examples included with the library serve to illustrate its use and validate the implementation and results.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=\textwidth]{../figures/radlib_structure.pdf}
+	\end{center}
+	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
+\label{fig:flowchart}
+\end{figure}
 

### 2020-11-17 manuscript/manuscript.tex
Cleaned up motivation section

@@
 
-% Brain dump for first draft
-Why did we make this?
-Radiation is hard to deal with in CFD.
-It's complicated.
-You can't really get analytic solutions to practical problems.
-In lots of cases, that's fine because radiation can be safely neglected; it's not usually the dominant mode of heat transfer.
-However, we do combustion CFD.
-Radiation isn't always important to combustion problems, but when it is, simulations can get grossly inaccurate.
-So we need a nice way to account for radiation in our CFD simulations.
+Modeling radiative heat transfer, and particular radiation absorption coefficients, for CFD is complex and challenging.
+More specifically, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost.
+As a result, researchers typically manufacture configurations in which radiation can be safely ignored, which can lead to results inapplicable to practical systems, or use oversimplified models and assumptions, which can produce inaccurate results.
+Unfortunately, these approaches are neither rigorous nor applicable to real engineering systems.
 
-When is radiation important to combustion simulations?
-In high-temperature systems, radiation can often be neglected in the beginning and middle of the simulation (assuming, say, a jet flame or a counterflow flame or something like that).
-At those times (which I'm going to call "early flame"), convective heat transfer dominates pretty heavily.
-However, radiation becomes more important for late-stage flame phenomena, either after some time has gone by (radiation time scales?), or physically high up in a flame where convection doesn't dominate as much as below, or just in areas that are relatively far away from the flame sheet itself where the reactions are happening.
-There's also soot, which involves radiation heavily, but soot particles are so big and slow that their time and length scales (and their radiative time scales) mean that radiation doesn't become important until late in the flame evolution.
+In some cases, other modes of heat transfer dominate the system, and radiation can be safely neglected, but many practical engineering systems do not allow this.
+Simple jet flames, for example, demonstrate both possibilities: early in a flame's development, convection typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and cannot be simulated accurately without a radiation model.
 
-So what's the problem?
-Why hasn't this been done already?
-Radiation is complicated.
-So is combustion.
-Combustion in particular can be so complex that direct simulations are too computationally expensive for us to simulate configurations that are practical for engineering systems.
-Direct simulations are usually used as a research tool.
-Other modeling approaches exist (LES, ODT, etc.) that lower the computational cost and allow us to simulate practical things.
-So far so good.
+Like combustion, the core mechanisms of radiation are physically and mathematically complex.
+Unlike other modes of heat transfer, it is governed by a set of integro-differential equations that depend on both direction and wavelength.
+Only the simplest systems have analytic solutions, and most practical systems require a numerical solution.
+Ray tracing (Monte Carlo) solutions are very accurate but extremely computationally expensive, and often require high-performance computing resources to execute.
+Modeling assumptions are common and can reduce simulation cost at the expense of accuracy, depending on their validity for the system in question.
 
-Radiation is a little like combustion in that its core mechanisms are complex, physically and mathematically.
-In addition, it's directional AND depends on the wavelength of the energy involved (other heat transfer doesn't have the wavelength dependence); its governing equations integrate over direction and wavelength, which makes things extra complicated.
-RADIATION GOVERNING EQUATIONS HERE.
-Convective heat transfer follows easy rules, but radiation doesn't.
-There are simple systems in which we can boil things down to analytic solutions, but most of the time, the simple equations don't apply, and that's often true in combustion systems where there are so many different length and time scales involved.
-The fundamental equations of radiative heat transfer are big and mathematically complex; they don't have analytic solutions except in the simplest geometries.
-So what do we do?
-One of two things.
-One, we do ray tracing (sometimes referred to as Monte Carlo simulations.
-These can be extremely accurate, but super computationally expensive.
-Essentially the equivalent of a direct numerical solution.
-Two, we simplify the the equations.
-We make assumptions.
-And so on.
-This is potentially less accurate, but more practical.
-By simplifying the fundamental governing equations, we create models that apply to various situations, systems, and geometries (i.e.
-black body assumptions, directional assumptions, etc.).
-There are models developed for CFD and specific combustion systems.
-These are the models that we've put into practice here in such a way that they're easy to apply to various systems.
-Modular organization for this purpose.
-
-So far there isn't an easy way to access and use radiation models.
-There are simple ones in Cantera (check this, there might not be any), but they make too many assumptions or don't work well for combustion or what have you.
-RadLib is a radiation library of models that you can apply to any simulation type, and we'd like to add it to Cantera, too.
-Basically, there isn't a reliable way to do radiation calculations in CFD simulations without coding the models yourself, which is extra hard because they're complicated and hard.
-So we've done it for you and put them in a library that easy for anyone to use.
-
-%Author guidelines for this section:
-%\begin{itemize}
-% \item Introduce the scientific background and the motivation for developing the software. 
-% \item Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
-% \item Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
-% \item Provide a description of the experimental setting (how does the user use the software?).
-% \item Introduce related work in literature (cite or list algorithms used, other software etc.).
-%\end{itemize}
-
-%Author guidelines for this section
-%\begin{itemize}
-% \item Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
-% \item  Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
-% \item Present the major functionalities of the software.
-%\end{itemize}
+Currently, there is no convenient or easy-to-use access point for CFD radiation models.
+As such, we present RadLib, a modular library of radiation models that can be applied alongside various simulation tools.
+RadLib focuses on calculation of radiation absorption coefficients, often the most difficult and time-consuming portion of radiation calculations, which permits its use with various solvers.
+The models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.
 
@@
 
-When we refer to the Plank Mean model, what we're using is actually the Planck Mean (PM) absorption coefficients, calculated from the correlations given on the TNF workshop site \citep{Smith_2003}.
-Their correlations (temperature dependent) are based on the RADCAL model in \citep{Grosshandler_1993}.
+RadLib's simplest model uses Planck Mean absorption coefficients calculated from the correlations given on the TNF Workshop site \citep{Smith_2003}.
+The temperature-dependent correlations are based on the RADCAL model in \citep{Grosshandler_1993}.
 The TNF radiation model is also documented in \citep{Barlow_2001}.
 
-This model is commonly used because it's relatively simple, easy to implement, low in computational expense, and provides reasonably accurate results in many cases.
+Planck Mean absorption coefficients are commonly used to model radiation, especially in combustion systems, because the model is relatively easy to implement, computationally inexpensive, and reasonably accurate in many cases.
+The TNF Workshop correlations were developed for use with an optically thin radiation model, which assumes that radiation passes through a medium mostly undisturbed.
+In cases where the optically thin assumption applies, such as simple hydrogen jet flames, this model and the associated Planck Mean absorption coefficients can produce accurate results \citep{Barlow_1999}.
+In cases where the optically thin assumption is not reasonable, including many other combustion scenarios, this model does not produce accurate results.
+For example, it significantly overpredicts radiative losses from the TNF library's CH$_4$ flames \cite{Frank_2000,Zhu_2002,Coelho_2002}.
 
-Quote from TNF site page: "The characteristics of some flames selected for the workshop are such that a model based upon the assumption of optically thin radiative heat loss should yield reasonable accuracy.
-This has been demonstrated for the simple hydrogen jet flames \cite{Barlow_1999}.
-However, there is some evidence that the optically thin model significantly over predicts radiative losses from the CH4 flames in the TNF library, due to strong absorption by the 4.3-micron band of CO2 \cite{Frank_2000,Zhu_2002,Coelho_2002}." Basically, it works well for flames that are actually optically thin, but not so well for flames that aren't.
-This is especially true of sooting flames.
+Because RadLib does not specify case geometry or medium, there is no optically thin assumption inherent in its use of the Planck Mean absorption coefficients.
+However, the correlations were developed with the intention of use with an optically thin assumption, and, as a result, depend only on local temperature values.
+RadLib users must take care to consider these limitations before using this model.
 
@@
 
-RadLib is an object-oriented C++ class library, including both C++ and Python interfaces.
+RadLib is an object-oriented C++ class library that includes both C++ and Python interfaces.
 The RadLib package contains five subdirectories (upon initial download): \texttt{source} contains the RadLib source code; \texttt{build} contains installation files; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to generate code documentation with Doxygen (optional).
@@
 \begin{table}
-    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2017}. All cases have $P=1$ atm, black walls.}
+    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2020}. All cases have $P=1$ atm, black walls.}
     \label{t:examples}

### 2020-11-20 manuscript/manuscript.tex
Minor grammar edits to examples section

@@
 \hline
-C7 & Compilation requirements, operating environments \& dependencies & TODO \\
+C7 & Compilation requirements, operating environments \& dependencies & Python 3, Cython \\
 \hline
@@
 Several examples are presented to illustrate the behavior of the models.
-The examples show heat flux $q$ or volumetric heat source $Q$ one one-dimensional configurations with varying gas compositions and temperatures.
+The examples show heat flux $q$ or volumetric heat source $Q$ in one one-dimensional configurations with varying gas compositions and temperatures.
 We compare the PM, WSGG, and RCSLW models for each example.
-The examples are taken from those presented by Solvojov et al., (2017) \cite{Solovjov_2017}, and Bordbar et al., 2020 \cite{Bordbar_2020}; the number corresponds to the example in the respective referece.
+The examples correspond to those presented by Solvojov et al.
+(S) \cite{Solovjov_2017} and Bordbar et al.
+(B) \cite{Bordbar_2020}, and the number of each example corresponds to the example number in the respective reference.
 A ray-tracing code is used to solve the radiative transport equation between two parallel plates.
 Table~\ref{t:examples} summarizes the cases.
-Example S1 is a hot slab next to a cold slab where the cold thickness varies; Example S2 is similar but isothermal with a \emph{thick} slab of high CO$_2$ next to a \emph{thin} slab of low CO$_2$ of varying thickness; Example S3 has parabolic temperature and H$_2$O profiles; Example S4 has a triangular temperature profile between equally-spaced isothermal regions; Example S5 is a half-sinusoid decreasing in temperature from 1500 to 500 K; and Example B3 has symmetric temperature and H$_2$O profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$).
-In each case, comparison is made to the line-by-line (LBL) data presented in the references.
+Example S1 is a hot slab next to a cold slab where the cold slab's thickness varies; Example S2 is isothermal with a thick slab of high CO$_2$ next to a thin slab of low CO$_2$ with variable thickness; Example S3 uses parabolic temperature and H$_2$O mole fraction profiles; Example S4 has a triangular temperature profile between equally-spaced isothermal regions; Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K; and Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$).
+Each case is presented alongside the line-by-line (LBL) data presented in the references.
 %
 \begin{table}
-    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2020}. All cases have $P=1$ atm, black walls.}
+    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2020}. All cases use $P=1$ atm and black walls.}
     \label{t:examples}
@@
 
-The examples are provided with the radlib code and implemented in both C++ and Python.
+The examples are provided with the RadLib code and implemented in both C++ and Python.
 A Juptyer notebook is provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files.
-Python and Cython versions of the one-dimensional solver \texttt{parallel\_planes} are provided for convenience.
+Python and Cython versions of the one-dimensional solver \texttt{parallel\textunderscore planes.py} are provided for convenience.
 
-These examples are not meant to be exhaustive, and details about the motivation of these examples and the behavior of the specific models is to be found in the respective references.
-The cases presented are intended to illustrate the use of the radiative library.
-While not shown  for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020}, so that these examples also serve as a validation of the implementation of the models.
+These cases are intended to illustrate the use of the RadLib library and are not exhaustive.
+Details about these examples and their motivations can be found in their respective references.
+While ommitted here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020} such that these examples also serve as a validation of the implementation of the models.
 
@@
 The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m.
-Example S5 omits the PM model to more clealy show the behavior of the WSGG and RCSLW models.
+Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models.
 For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 at $x=0$ to a peak of 200 at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m.
@@
 \hline
-S5 & Installation requirements \& dependencies & TODO \\
+S5 & Installation requirements \& dependencies & Python 3, Cython \\
 \hline

### 2020-11-25 manuscript/manuscript.tex
Draft text of impact section, fixes to references

@@
 
-As far as I'm aware, there isn't an easy way to incorporate radiative heat transfer into a CFD simulation.
-Most cases use optically thin assumption (which works in some cases, but not in others) or neglect radiation entirely (also applicable sometimes, but not always).
-[Refer to TNF website radiation page here.] Unfortunately, this means that when you simulation some configuration in which radiation might be important to the overall heat transfer, you won't get accurate simulation results.
-Furthermore, if your study is about something else entirely, your radiation model (or lack thereof) becomes a source of error that may be very difficult to separate from other sources of error in your simulation study (i.e.
-soot modeling studies).
-As of right now, if you want any detailed radiation treatment, you have to code it yourself, which is difficult and requires external validation.
+Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs.
+Neglecting radiation or using simple models like the optically thin assumption is adequate for some cases with simple geometry or limited chemical reactions, but most simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results.
+In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error.
+Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.
 
-RadLib can make researchers' lives easier by providing a library of prevalidated radiation models that can be switched out with no difficulty.
-Additional models can be added easily using the provided modular framework.
-Researchers can even use Radlib as a tool for comparing models.
-No need to code multiple different complex radiation models yourself just to decide which one works best for your simulation.
-And no need to puzzle through the literature to figure our which model(s) might be best for your simulation, either; instead, you can test them yourself.
-It saves tons of time and effort that researchers can now put toward results rather than code or model development.
+RadLib makes researchers' work easier by consolidating various approaches into a modular library of interchangeable, prevalidated radiation models.
+Additionally, RadLib's modular framework is designed to easily accommodate new models as well, allowing researchers to compare new or existing models with very little overhead.
+Sometimes, it is not clear which radiation model may be the best fit for a particular simulation.
+When simulations are especially complex or computationally expensive, researchers may have to extrapolate from theory and literature to choose an appropriate radiation model rather than testing for their specific case.
+RadLib is designed to ease both of these obstacles by facilitating comparison between radiation models through a common interface and providing a practical means of testing various models without the restriction of prespecified geometry or case parameters.
+With RadLib, researchers can put more of their time and effort into useful results rather than code or model development.
 
-By putting all these models side by side in a modular framework, RadLib also provides a structure on which new or altered radiation models can be tested against existing ones.
-Maybe more comparative studies can be done, especially for more complex simulation cases.
-We plan to add radiation models as appropriate to RadLib, too.
-
-RadLib opens up new horizons for CFD simulations, especially in combustion cases.
-It is designed such that it can be easily incorporated into existing research codes.
-Our group plans to use it with ODT [CITE OTHER SOFTWAREX PAPER HERE?] alongside soot model library (in development) to study late-flame phenomena such as soot oxidation, flame extinction, and soot-flame breakthrough.
-These topics in particular are difficult because they require accurate simulation data over a relatively long computational time in addition to good models for both soot chemistry (which is an active research area) and radiation heat transfer (which is the difficult part that RadLib can solve).
-Using RadLib for such studies allows us to separate and quantify sources of error that may occur due to various models, which is super difficult if you only have one model to work with or it hasn't been validated well.
-
-RadLib can also be used outside of combustion CFD research for anything involving radiative heat transfer.
-Potential research areas that could benefit include atmospheric and climate sciences, interstellar phenomena, improving efficiency of energy-producing processes, safety in chemical plant design, etc.
-We aren't experts in these areas, but radiative heat transfer is a universal phenomena that applies to any system or process that involves heat transfer.
-
-This software has not been used outside of the current research group, and it is not used in any commercial settings at this time.
+Currently, RadLib is only used within the authors' research group, where it is applied to combustion CFD simulations using the One-Dimensional Turbulence (ODT) model \cite{Stephens_2020}, but its design and structure as a C++ library allows it to be incorporated easily into existing codes.
+It can be applied to  research questions in various other fields involving radiative heat transfer as well, including energy engineering or atmospheric and climate sciences.
+Radiation is a universal phenomenon, and RadLib can assist researchers in many areas with systems and processes that involve heat transfer.
 

### 2020-12-09 manuscript/manuscript.tex
Metadata, added author, minor latex file formatting

@@
 
+\usepackage{hyperref}
+
 \journal{SoftwareX}
@@
 \author{Sally Jensen}
+\author{Isaac Wheeler}
 \author{David O. Lignell\corref{cor1}}
@@
 
-\section*{Required Metadata}
-\label{}
-
-\section*{Current code version}
-\label{}
-
-Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.
-
 \begin{table}[H]
@@
 \hline
-\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
+\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
 \hline
@@
 \hline
-C2 & Permanent link to code/repository used for this code version & $github.com/BYUignite/RadLib$ \\
+C2 & Permanent link to code/repository used for this code version & $github.com/BYUignite/radlib$ \\
 \hline
-C3 & Code Ocean compute capsule & N/A \\
+C3 & Code Ocean compute capsule & (in review) \\
 \hline
@@
 \hline
-C7 & Compilation requirements, operating environments \& dependencies & Python 3, Cython \\
+C7 & Compilation requirements, operating environments \& dependencies & CMake, C++, Python 3, Cython \\
 \hline
@@
 \end{tabular}
-\caption{Code metadata (mandatory)}
+\caption{Code metadata.}
 \label{} 
@@
 % - decide on and generate documentation
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 RadLib's RCSLW model uses Method 1.2.2 as defined and recommended in \cite{Solovjov_2017}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conclusions}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Conflict of Interest}
-%Please select the appropriate text:
-%
-%Potential conflict of interest exists:
-%We wish to draw the attention of the Editor to the following facts, which may be considered as potential conflicts of interest, and to significant financial contributions to this work.
-The nature of potential conflict of interest is described below: [Describe conflict of interest]
 
-%No conflict of interest exists:
-We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
+There are no known conflicts of interest associated with this publication and there has been no significant financial support for     this work that could have influenced its outcome.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section*{Acknowledgements}
-\label{}
+\label{sec:acknowledgements}
 
@@
 
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %% \appendix
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% References:
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Current executable software version}
@@
 
-Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.
+%Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.
 
@@
 \hline
-\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
+\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Metadata} \\
 \hline
-S1 & Current software version & TODO 2.1 \\
+S1 & Current software version & 1.0 \\
 \hline
-S2 & Permanent link to executables of this version  & TODO For example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
+S2 & Permanent link to executables of this version  & \href{https://github.com/BYUignite/radlib}{https://github.com/BYUignite/radlib} \\
 \hline
@@
 \hline
-S5 & Installation requirements \& dependencies & Python 3, Cython \\
+S5 & Installation requirements \& dependencies & CMake, C++, Python 3, Cython \\
 \hline
 S6 & If available, link to user manual - if formally published include a reference to the publication in the reference
-    list & TODO For example: $http://mozart.github.io/documentation/$ \\
+    list & \href{https://github.com/BYUignite/radlib}{https://github.com/BYUignite/radlib} \\
 \hline
@@
 \end{tabular}
-\caption{Software metadata (optional)}
+\caption{Software metadata.}
 \label{} 

### 2020-12-15 manuscript/manuscript.tex
Introduction edits (see DOL email 12/9/20)

--- 2020-11-25 manuscript/manuscript.tex
@@
 Modeling radiative heat transfer, and particular radiation absorption coefficients, for CFD is complex and challenging.
-More specifically, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost.
-As a result, researchers typically manufacture configurations in which radiation can be safely ignored, which can lead to results inapplicable to practical systems, or use oversimplified models and assumptions, which can produce inaccurate results.
-Unfortunately, these approaches are neither rigorous nor applicable to real engineering systems.
+More specifically, combustion simulations, which can require many complex property models already, are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost.
+This can lead to simulations that use oversimplified radiation models, but in cases where radiation is significant relative to the other physical phenomena, oversimplified models can negatively impact the accuracy of simulation results.
+In some cases, radiative gains or losses are small compared to other sources, sinks, or modes of heat transfer, and radiation can be safely neglected, but many practical engineering systems do not allow this.
+For example, simple jet flames demonstrate both possibilities: early in a flame's development, turbulent mixing typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and are difficult to simulate accurately without a robust radiation model.
+These problems motivated development of the RadLib library, which provides a framework and uniform interface for radiation property models and implements three powerful models in C++ and Python, giving researchers easier and more convenient access to advanced radiation property models and a consistent framework for further model development.
 
-In some cases, other modes of heat transfer dominate the system, and radiation can be safely neglected, but many practical engineering systems do not allow this.
-Simple jet flames, for example, demonstrate both possibilities: early in a flame's development, convection typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and cannot be simulated accurately without a radiation model.
+The core mechanisms of radiative phenomena are physically and mathematically complex.
+Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
+Solving the RTE for a given system also requires information about the radiative properties of the materials and media involved, typically radiation absorption coefficients.
+Depending on the model, absorption coefficients can be dependent on a number of local system properties such as temperature, pressure, and gas composition.
+As a result, computational radiation solvers require two parts: first, a solution approach for the radiative transfer equations (RTE); and second, a radiation property model.
+RadLib addresses the second part by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
 
-Like combustion, the core mechanisms of radiation are physically and mathematically complex.
-Unlike other modes of heat transfer, it is governed by a set of integro-differential equations that depend on both direction and wavelength.
+%Like combustion, the core mechanisms of radiation are physically and mathematically complex.
+Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength.
 Only the simplest systems have analytic solutions, and most practical systems require a numerical solution.
-Ray tracing (Monte Carlo) solutions are very accurate but extremely computationally expensive, and often require high-performance computing resources to execute.
+Ray tracing solutions are very accurate but extremely computationally expensive, and often require high-performance computing resources to execute.
 Modeling assumptions are common and can reduce simulation cost at the expense of accuracy, depending on their validity for the system in question.
 
-Currently, there is no convenient or easy-to-use access point for CFD radiation models.
-As such, we present RadLib, a modular library of radiation models that can be applied alongside various simulation tools.
-RadLib focuses on calculation of radiation absorption coefficients, often the most difficult and time-consuming portion of radiation calculations, which permits its use with various solvers.
-The models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.
+With RadLib, we provide a convenient, easy-to-use access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
+RadLib is a modular C++ library with an optional Python interface used to compute the radiation properties of participating media, often the most difficult and time-consuming portion of radiation calculations.
+RadLib's current focus is calculating radiation absorption coefficients and weighting factors for use in global radiation models, but the flexible framework permits expansion to other radiative properties.
+Three models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.
 

### 2020-12-15 manuscript/manuscript.tex

@@
 Three models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-12-15 manuscript/manuscript.tex
Edits to model description sections. Some reorganization. (See DOL email 12/14/20)

@@
 
-RadLib includes three models of varying complexity and accuracy to calculate the radiation absorption coefficients and their weighting factors for each gas considered by the model.
-Radiation absorption coefficients are typically calculated using correlations relating them local properties such as temperature, total pressure, or species partial pressure, depending on the model.
+To give context to the following discussion of radiative individual property models, we include here a brief description of the radiative transfer equation (RTE).
+Along a given path length $s$ in a direction $\hat{\Omega}$, the general RTE  for an absorbing, emitting, and non-scattering medium is described by
+\begin{equation}
+	\label{e:RTE_general}
+	\frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b \eta},
+\end{equation}
+where $I_{\eta}$ is the radiative spectral intensity, $I_{b\eta}$ is the Planck spectral distribution of blackbody intensity, and $\kappa_{\eta}$ is the spectral absorption coefficient of the medium.
+Radiation property models such as those implemented by RadLib are used to calculate the absorption coefficients $\kappa_{\eta}$.
+From this point, various approximations can be made to simplify the solution process.
+For example, integrating with respect to wavenumber and subdividing the absorption cross-section into gray gases gives the spectral line-weighted (SLW) form of the RTE,
+\begin{equation}
+\label{e:RTE_SLW}
+	\frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
+\end{equation}
+where $n$ is the number of gray gases in the model, $I_j$ is the intensity of gray gas $j$, and $\kappa_j$ represents the gray gas absorption coefficient for gas $j$.
+When multiple gray gases are used to approximate the radiative properties, the total radiative intensity $I$ can be calculated by summing the individual gray gas intensities calculated with Equation \ref{e:RTE_SLW}:
+\begin{equation}
+	I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
+\end{equation}
+From there, the total radiative intensity can be used to calculate various radiative heat fluxes and, where appropriate, be incorporated into larger energy balances for a simulation.
+
+RadLib implements three models of varying complexity and accuracy to calculate the radiation absorption coefficients $\kappa$ and their weighting factors $a$ for each gas considered by the model.
+The absorption coefficients are typically calculated using correlations relating them local properties such as temperature, pressure, and composition.
 Correlations come from curve fits to high-resolution radiation property databases.
-At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and, optionally, soot volume fraction in its calculation of absorption coefficients and weighting factors.
+At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot in its calculation of absorption coefficients and weighting factors.
 
-Once the radiative absorption coefficients are calculated, they are then used to solve the radiative transfer equation (RTE), which depends on the simulation configuration and assumptions.
-Solving the RTE is not the focus of this software, but RadLib's example cases do employ a simple implicit trapezoid method solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
-[MORE DESCRIPTION OF SOLVER GOES HERE?]
+Once the radiative absorption coefficients are calculated, they can then be used to solve the RTE, which depends on the simulation configuration and assumptions.
+Solving the RTE is not the focus of this software, but RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
 
-[OTHER THINGS THAT APPLY TO ALL MODELS GO HERE]
-
-[MAYBE INCLUDE SOME BASIC INFO ON LBL?]
+%[OTHER THINGS THAT APPLY TO ALL MODELS GO HERE]
 
@@
 
-Planck Mean absorption coefficients are commonly used to model radiation, especially in combustion systems, because the model is relatively easy to implement, computationally inexpensive, and reasonably accurate in many cases.
-The TNF Workshop correlations were developed for use with an optically thin radiation model, which assumes that radiation passes through a medium mostly undisturbed.
+Planck Mean absorption coefficients are commonly used to model radiation, especially in combustion systems, because the model is relatively easy to implement, computationally inexpensive, and reasonably accurate in some cases.
+The Planck Mean model is most appropriate under optically thin conditions with relatively low radiative transfer relative to other heat sources such as reactive heat release rates.
 In cases where the optically thin assumption applies, such as simple hydrogen jet flames, this model and the associated Planck Mean absorption coefficients can produce accurate results \citep{Barlow_1999}.
-In cases where the optically thin assumption is not reasonable, including many other combustion scenarios, this model does not produce accurate results.
+In cases where the optically thin assumption is not reasonable, including many other combustion scenarios, the Planck Mean model does not produce accurate results.
 For example, it significantly overpredicts radiative losses from the TNF library's CH$_4$ flames \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-
-Because RadLib does not specify case geometry or medium, there is no optically thin assumption inherent in its use of the Planck Mean absorption coefficients.
-However, the correlations were developed with the intention of use with an optically thin assumption, and, as a result, depend only on local temperature values.
-RadLib users must take care to consider these limitations before using this model.
+The examples included with the code and illustrated in Section \ref{s:Examples} demonstrate the deficiencies of the Planck Mean model in comparison to the others included with RadLib.
 
@@
 The basic assumption of weighted sum of gray gases (WSGG) models in general is that the non-gray behavior of gas mixtures, in this case H$_2$O and CO$_2$, can be modeled by a weighted sum of several gray gases and one transparent gas (which represents the spectral windows between absorption bands).
-RadLib uses the WSGG model presented by Bordbar et al.
+RadLib implements the WSGG model presented by Bordbar et al.
 \citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}.
-RadLib, in accordance with the Bordbar et al.
-WSGG method cited above, uses a mixture of four gray gases and one transparent gas.
+It uses four gray gases and one transparent gas.
 Absorption coefficients are calculated by
@@
 The model coefficients $d_{i,k}$ and $C_{i,j}$ can be found in the literature \citep{Bordbar_2014,Bordbar_2020}.
-RadLib uses the updated model coefficients from \citep{Bordbar_2020}, which extends the model presented in \citep{Bordbar_2014} to include all possible values of the H$_2$O-CO$_2$ molar ratio.
+
+Previous WSGG versions and other property models often considered weighting factors as a function of temperature only and assumed a fixed molar ratio of H$_2$O and CO$_2$.
+This version includes dependence on both temperature and an arbitrary molar fraction ratio, increasing its accuracy and flexibility.
+RadLib uses the updated model coefficients from \citep{Bordbar_2020}, which extends the limited range of H$_2$O-CO$_2$ molar ratios originally presented in \citep{Bordbar_2014}.
 
@@
 
-The radiative transfer equation (RTE) for an absorbing, emitting, and non-scattering medium along a given path length $s$ in a direction $\hat{\Omega}$ is given by 
-\begin{equation}
-	\frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b \eta},
-\end{equation}
-where $I_{\eta}$ is the radiative spectral intensity, $I_{b\eta}$ is the Planck spectral distribution of blackbody intensity, and $\kappa_{\eta}$ is the spectral absorption coefficient of the medium.
-Integrating with respect to wavenumber and subdividing the absorption cross-section into gray gases gives the SLW form of the RTE:
-\begin{equation}
-\label{e:RTE_SLW}
-	\frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n.
-\end{equation}
-Here, $n$ is the number of gray gases in the model and $I_j$ is the intensity of gray gas $j$.
-$\kappa_j$ is the gray gas absorption coefficient, which can be calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
+The RCSLW model begins with the SLW form of the RTE, given by Equation \ref{e:RTE_SLW}. The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
 where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}.
-The gray gas weights corresponding to each absorption coefficient are given by $a_j=F(C_j)-F(C_{j-1})$, where $F(C_j)$ is the absorption line blackbody distribution function (ALBDF) for species $j$, calculated from the detailed absorption spectrum of that species.
-The absorption cross-sections are chosen with respect to a thermodynamic reference state, which makes generalized SLW methods reference approaches.
-Once Equation ~\ref{e:RTE_SLW} is solved for each gray gas species, to total radiative intensity $I$ can be calculated by summing the gray gas intensities:
-\begin{equation}
-	I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
-\end{equation}
-
+The gray gas weights $a_j$ corresponding to each absorption coefficient are given by $a_j=F(C_j)-F(C_{j-1})$, where $F(C_j)$ is the absorption line blackbody distribution function (ALBDF) for species $j$, calculated from the detailed absorption spectrum of that species.
+In general SLW methods, the absorption cross-sections are chosen with respect to a thermodynamic reference state, classifying them as reference approaches.
 The Rank-Correlated SLW (RCSLW) model avoids specifying a reference state by relating thermodynamic states to one another instead.
@@
 The inverse ALBDF, defined such that $C[F(C,\phi_g,T_b),\phi_g,T_b]=C$ and $F[C(F,\phi_g,T_b),\phi_g,T_b]=F$ for a given gas thermodynamic state $\phi_g$ and blackbody temperature $T_b$, is proven to have this property and can also be called the rank-correlated reordered absorption cross-sections \cite{Solovjov_2017}.
-As a result, the inverse ALBDF can be used to construct cross-section intervals for the RCSLW model that do not rely on a defined reference state or spectrum.
-RadLib's RCSLW model uses Method 1.2.2 as defined and recommended in \cite{Solovjov_2017}
+As a result, the inverse ALBDF can be used to construct cross-section intervals for the RCSLW model that do not rely on an arbitrary reference state or spectrum.
+RadLib's RCSLW model uses Method 1.2.2 as defined and recommended in \cite{Solovjov_2017}.
 

### 2020-12-16 manuscript/manuscript.tex
Minor notation fixes

@@
 \begin{equation}
- K_i=\sum_{k=0}^{4}d_{i,k}M_r^k,
+ \kappa_i=\sum_{k=0}^{4}d_{i,k}M_r^k,
 \end{equation}
-where $K_i$ is the absorption coefficient for species $i$, $d_{i,k}$ is a species-specific correlated model coefficient, and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$.
+where $\kappa_i$ is the absorption coefficient for gray gas species $i$, $d_{i,k}$ is a species-specific correlated model coefficient, and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$.
 The weight factors are calculated by

### 2020-12-16 manuscript/manuscript.tex
Added soot treatment subsection to model description

@@
 As a result, the inverse ALBDF can be used to construct cross-section intervals for the RCSLW model that do not rely on an arbitrary reference state or spectrum.
-RadLib's RCSLW model uses Method 1.2.2 as defined and recommended in \cite{Solovjov_2017}.
+ALBDFs for individual gray gases are multiplied together to obtain an overall ABLDF for the gas mixture \cite{Solovjov_2001}.
+RadLib's RCSLW model uses Method 1.2.2 as defined in and recommended by \cite{Solovjov_2017}.
+
+\subsection{Soot treatment}
+\label{s:soot}
+
+RadLib can also account for the radiative properties of soot in combustion environments.
+Soot particles are assumed to be unagglomerated spheres that absorb and emit radiation at all wavelengths such that their optical properties can be determined using the Rayleigh small particle limit.
+Radiation scattering may be neglected because unagglomerated soot particles in the Rayleigh regime are still small relative to the wavelength of infrared radiation in flames \cite{Brewster_1992,Solovjov_2001}.
+The spectral soot absorption coefficient is given by
+\begin{equation}
+\label{e:soot1}
+	\kappa_{\lambda}=C_0 \frac{f_v}{\lambda} , \; \; \; C_0 = \frac{36\pi n k}{(n^2-k^2+2)^2+4n^2k^2},
+\end{equation}
+where $n$ and $k$ are the real and imaginary parts of the soot complex index of refraction, respectively, and $f_v$ is the soot volume fraction \cite{Solovjov_2001,Modest_2013}.
+Various values for the refraction index have been proposed and applied to various scenarios \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}.
+RadLib uses the values $n=1.75$ and $k=1.03$ given in \cite{Williams_2007}, which result in a value of $C_0=7.03$, aligning nicely with the value $C_0=7.0$ suggested by \cite{Solovjov_2001}.
+Due to the simple $1/\lambda$ dependence and the suitably small difference between the mean absorption coefficients calculated for optically thin and optically thick cases, we can use one expression to calculate a spectral mean absorption coefficient for soot that applies to all optical regimes:
+\begin{equation}
+\label{e:soot2}
+	\kappa_{soot}=3.72\frac{f_vC_0T}{C_2},
+\end{equation}
+where $T$ is the temperature and $C_2=1.4388$ cm K is a Planck function constant \cite{Modest_2013}.
+
+In order to incorporate its radiative effects, soot is modeled as a pseudo-gas of its own and included alongside the existing gray gases.
+In the Planck Mean model, which models a gas mixture as one gray gas, the soot absorption coefficient calculated from Equation \ref{e:soot2} is simply added to the existing gas absorption coefficient.
+In the WSGG model, the soot absorption coefficient is similarly calculated from Equation \ref{e:soot2} but is then added to each of the gases separately.
+Because soot radiates across all wavelengths, its absorption coefficient is added to the values of all four gray gases and the transparent gas that represents the spectral gaps between absorption bands.
+Unlike the Planck Mean and WSGG models, the RCSLW model requires a spectrally dependent soot model.
+Instead of finding a mean soot absorption coefficient, we use Equation \ref{e:soot1} to define a soot absorption cross-section and ALBDF as detailed in \cite{Solovjov_2001}.
+The soot ALBDF can then be multiplied with the other gray gas ALBDFs to find the overall ALBDF for the gas-soot mixture.
 

### 2020-12-16 manuscript/manuscript.tex
Fixed missing subscript in WSGG equations

@@
 \begin{equation}
- b_{i,j}=\sum_{k=0}^{4}C_{i,j}M_r^k,
+ b_{i,j}=\sum_{k=0}^{4}C_{i,j,k}M_r^k,
 \end{equation}
-where $C_{i,j}$ is another correlated model coefficient and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$ as above.
-The model coefficients $d_{i,k}$ and $C_{i,j}$ can be found in the literature \citep{Bordbar_2014,Bordbar_2020}.
+where $C_{i,j,k}$ is another correlated model coefficient and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$ as above.
+The model coefficients $d_{i,k}$ and $C_{i,j,k}$ can be found in the literature \citep{Bordbar_2014,Bordbar_2020}.
 

### 2020-12-18 manuscript/manuscript.tex
DOL edits to introduction and section 2 (but not subsections yet)

@@
 \usepackage{lineno}
+\usepackage{amsmath}
 
@@
 
-Modeling radiative heat transfer, and particular radiation absorption coefficients, for CFD is complex and challenging.
-More specifically, combustion simulations, which can require many complex property models already, are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost.
+Modeling radiative heat transfer for CFD is complex and challenging.
+Combustion simulations, for example, which require many physics models, are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost.
 This can lead to simulations that use oversimplified radiation models, but in cases where radiation is significant relative to the other physical phenomena, oversimplified models can negatively impact the accuracy of simulation results.
-In some cases, radiative gains or losses are small compared to other sources, sinks, or modes of heat transfer, and radiation can be safely neglected, but many practical engineering systems do not allow this.
+In some cases, radiative gains or losses are small compared to other energy sources or heat transfer modes and radiation can be safely neglected, but many practical engineering systems do not allow this.
 For example, simple jet flames demonstrate both possibilities: early in a flame's development, turbulent mixing typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and are difficult to simulate accurately without a robust radiation model.
-These problems motivated development of the RadLib library, which provides a framework and uniform interface for radiation property models and implements three powerful models in C++ and Python, giving researchers easier and more convenient access to advanced radiation property models and a consistent framework for further model development.
+These problems motivated development of the RadLib library, which provides a framework and uniform interface for radiation property models and implements three powerful models in C++ and Python, giving researchers more convenient access to advanced radiation property models and a consistent framework for further model development.
 
@@
 Solving the RTE for a given system also requires information about the radiative properties of the materials and media involved, typically radiation absorption coefficients.
-Depending on the model, absorption coefficients can be dependent on a number of local system properties such as temperature, pressure, and gas composition.
+These absorption coefficients are dependent on a number of local system properties such as temperature, pressure, and gas composition.
 As a result, computational radiation solvers require two parts: first, a solution approach for the radiative transfer equations (RTE); and second, a radiation property model.
@@
 With RadLib, we provide a convenient, easy-to-use access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
-RadLib is a modular C++ library with an optional Python interface used to compute the radiation properties of participating media, often the most difficult and time-consuming portion of radiation calculations.
-RadLib's current focus is calculating radiation absorption coefficients and weighting factors for use in global radiation models, but the flexible framework permits expansion to other radiative properties.
-Three models are fully implemented and validated and all use a common interface, allowing researchers easy and convenient access to radiation modeling tools regardless of the field of application.
+RadLib is a modular C++ library with an optional Python interface used to compute the radiation properties of participating media, which can be a difficult and time-consuming portion of radiation calculations.
+RadLib's current focus is calculating radiation absorption coefficients and weighting factors for use in global radiation models, but the expansion to other radiative properties is possible.
+Three models are fully implemented and validated and use a common interface, allowing researchers convenient access to radiation modeling tools suitable for various applications.
 
@@
 
-To give context to the following discussion of radiative individual property models, we include here a brief description of the radiative transfer equation (RTE).
-Along a given path length $s$ in a direction $\hat{\Omega}$, the general RTE  for an absorbing, emitting, and non-scattering medium is described by
+The RTE for intensity $I$ in (unit) direction $\mathbf{s}$ for an absorbing, emitting, and non-scattering medium is described by
+%
 \begin{equation}
 	\label{e:RTE_general}
-	\frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b \eta},
+    \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
 \end{equation}
-where $I_{\eta}$ is the radiative spectral intensity, $I_{b\eta}$ is the Planck spectral distribution of blackbody intensity, and $\kappa_{\eta}$ is the spectral absorption coefficient of the medium.
+%
+where $I_{\eta}$ is the radiative spectral intensity, 
+%$I_{b\eta}$ is the Planck spectral distribution of blackbody intensity, 
+$I_{b\eta}$ is spectral blackbody intensity (or Planck function), 
+$\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a pathlength along direction $\mathbf{s}$.
 Radiation property models such as those implemented by RadLib are used to calculate the absorption coefficients $\kappa_{\eta}$.
-From this point, various approximations can be made to simplify the solution process.
-For example, integrating with respect to wavenumber and subdividing the absorption cross-section into gray gases gives the spectral line-weighted (SLW) form of the RTE,
-\begin{equation}
-\label{e:RTE_SLW}
+%
+The gas absorption spectrum is an extremely complex function consisting of millions of spectral lines (peaks) corresponding to quantum mechanical energy levels of the gas molecules.
+Direct solution of Eq.~(\ref{e:RTE_general}), involves so-called \emph{line-by-line} calculations that are computationally prohibitive for most practical calculations, and are used primarily for model validation.
+Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model \cite{Hottel_1967,Modest_2013}.
+For instance, integrating Eq.~(\ref{e:RTE_general}) over fixed spectral ranges $\eta_j$ and assuming gray (spectrally uniform) properties in each region $j$, (that is, in each \emph{gray gas} $j$), gives
+%
+\begin{equation} \label{e:RTE_wsgg}
 	\frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
 \end{equation}
-where $n$ is the number of gray gases in the model, $I_j$ is the intensity of gray gas $j$, and $\kappa_j$ represents the gray gas absorption coefficient for gas $j$.
-When multiple gray gases are used to approximate the radiative properties, the total radiative intensity $I$ can be calculated by summing the individual gray gas intensities calculated with Equation \ref{e:RTE_SLW}:
+%
+where $a_j$ is a weight factor defined as
+%
+\begin{align}
+    &a_j= \frac{\int_{\eta_j}I_{b,\eta}d\eta}{I_b},\\
+    &\sum_j a_j = 1.
+\end{align}
+%
+Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~(\ref{e:RTE_wsgg}) can be computed for each of the $n+1$ gray gases.
+Normally, the $j=0$ gas is considered as a clear gas and represents \emph{transparent windows} in the spectrum for which $\kappa_0=0$.
+The total radiative intensity $I$ is calculated by summing the individual gray gas intensities:
+%
 \begin{equation}
@@
 \end{equation}
-From there, the total radiative intensity can be used to calculate various radiative heat fluxes and, where appropriate, be incorporated into larger energy balances for a simulation.
+%
+In the above, $I$ is a function of direction $\mathbf{s}$. The heat flux vector $\mathbf{q}$ is found by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere:
+%
+\begin{equation}
+    \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
+\end{equation}
+%
+The volumetric radiative heat source is then 
+%
+\begin{equation}
+    Q = -\nabla\cdot\mathbf{q}.
+\end{equation}
+%
 
-RadLib implements three models of varying complexity and accuracy to calculate the radiation absorption coefficients $\kappa$ and their weighting factors $a$ for each gas considered by the model.
+RadLib currently implements three models of varying complexity and accuracy to calculate the radiation absorption coefficients $\kappa_j$ and their weight factors $a_j$ for each gas $j$.
 The absorption coefficients are typically calculated using correlations relating them local properties such as temperature, pressure, and composition.
 Correlations come from curve fits to high-resolution radiation property databases.
-At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot in its calculation of absorption coefficients and weighting factors.
+At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot.
 
-Once the radiative absorption coefficients are calculated, they can then be used to solve the RTE, which depends on the simulation configuration and assumptions.
-Solving the RTE is not the focus of this software, but RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
+While solving the RTE is not the focus of this software, RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
 
 %[OTHER THINGS THAT APPLY TO ALL MODELS GO HERE]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Weighted sum of gray gases (WSGG)}
 \label{s:wsgg}
+
 The basic assumption of weighted sum of gray gases (WSGG) models in general is that the non-gray behavior of gas mixtures, in this case H$_2$O and CO$_2$, can be modeled by a weighted sum of several gray gases and one transparent gas (which represents the spectral windows between absorption bands).
@@
 RadLib uses the updated model coefficients from \citep{Bordbar_2020}, which extends the limited range of H$_2$O-CO$_2$ molar ratios originally presented in \citep{Bordbar_2014}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-12-19 manuscript/manuscript.tex
Edits to model section, all except the RCSLW section; that's next

@@
 %% for the whole article with \linenumbers.
+
 \usepackage{lineno}
 \usepackage{amsmath}
+\usepackage{float}
+\usepackage[version=4]{mhchem}
+\usepackage{booktabs}
+\usepackage{siunitx}
 
-\usepackage{float}
 \restylefloat{table}
@@
 
-% TO DO
-% - update README
-% - tag software version
-% - decide on and generate documentation
+% TODO tag software version
 
@@
 
-\section{Motivation and significance}
-\label{s:motivation}
+\section{Motivation and significance} \label{s:motivation}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Model descriptions}
-\label{s:models}
+\section{Model descriptions} \label{s:models}
 
@@
 % 
-\begin{equation}
-	\label{e:RTE_general}
+\begin{linenomath}
+\begin{equation} \label{e:RTE_general}
     \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
 \end{equation}
+\end{linenomath}
 %
 where $I_{\eta}$ is the radiative spectral intensity, 
-%$I_{b\eta}$ is the Planck spectral distribution of blackbody intensity, 
 $I_{b\eta}$ is spectral blackbody intensity (or Planck function), 
@@
 %
+\begin{linenomath}
 \begin{equation} \label{e:RTE_wsgg}
@@
 \end{equation}
+\end{linenomath}
 %
@@
 %
+\begin{linenomath}
 \begin{align}
@@
 \end{align}
+\end{linenomath}
 %
@@
 %
+\begin{linenomath}
 \begin{equation}
@@
 RadLib's simplest model uses Planck Mean absorption coefficients calculated from the correlations given on the TNF Workshop site \citep{Smith_2003}.
-The temperature-dependent correlations are based on the RADCAL model in \citep{Grosshandler_1993}.
+The temperature-dependent correlations are based on the RADCAL model \citep{Grosshandler_1993}.
 The TNF radiation model is also documented in \citep{Barlow_2001}.
@@
 
-The basic assumption of weighted sum of gray gases (WSGG) models in general is that the non-gray behavior of gas mixtures, in this case H$_2$O and CO$_2$, can be modeled by a weighted sum of several gray gases and one transparent gas (which represents the spectral windows between absorption bands).
+The WSGG model was outlined in Sec.~\ref{s:models}.
 RadLib implements the WSGG model presented by Bordbar et al.
 \citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}.
-It uses four gray gases and one transparent gas.
+It uses four gray gases and one transparent gas, and considers gaseous species \ce{CO2} and \ce{H2O}.
+This version of the WSGG model has the advantage over some others in that it allows for arbitrary \ce{CO2} and \ce{H2O} compositions, increasing its accuracy and flexibility.
 Absorption coefficients are calculated by
+%
+\begin{linenomath}
 \begin{equation}
- \kappa_i=\sum_{k=0}^{4}d_{i,k}M_r^k,
+    \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
 \end{equation}
-where $\kappa_i$ is the absorption coefficient for gray gas species $i$, $d_{i,k}$ is a species-specific correlated model coefficient, and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$.
+\end{linenomath}
+%
+where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $y_{\mathrm{H_2O}}/y_{\mathrm{CO_2}}$.
 The weight factors are calculated by
+%
+\begin{linenomath}
 \begin{equation}
- a_i=\sum_{j=0}^{4}b_{i,j}T_r^j,
+    a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
 \end{equation}
-where $a_i$ is the weighting factor for species $i$ and $T_r$ is a normalized temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The value of $b_{i,j}$ is calculated by 
+\end{linenomath}
+%
+where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The value of $b_{i,j}$ is calculated by 
+%
+\begin{linenomath}
 \begin{equation}
- b_{i,j}=\sum_{k=0}^{4}C_{i,j,k}M_r^k,
+ b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
 \end{equation}
-where $C_{i,j,k}$ is another correlated model coefficient and $M_r$ is the molar ratio $Y_{\mathrm{H_2O}}/Y_{\mathrm{CO_2}}$ as above.
-The model coefficients $d_{i,k}$ and $C_{i,j,k}$ can be found in the literature \citep{Bordbar_2014,Bordbar_2020}.
+\end{linenomath}
+%
+where $C_{j,k,i}$ is another correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020}.
 
-Previous WSGG versions and other property models often considered weighting factors as a function of temperature only and assumed a fixed molar ratio of H$_2$O and CO$_2$.
-This version includes dependence on both temperature and an arbitrary molar fraction ratio, increasing its accuracy and flexibility.
-RadLib uses the updated model coefficients from \citep{Bordbar_2020}, which extends the limited range of H$_2$O-CO$_2$ molar ratios originally presented in \citep{Bordbar_2014}.
+The correlations provided in \cite{Bordbar_2014} are valid for $0.01\le M_r\le4$.
+In \cite{Bordbar_2020} this range was extended to arbitrary $M_r$ by interpolation of $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$, that is, for \ce{CO2}: interpolation between values at $M_r=0.01$ and pure \ce{CO2}; and for \ce{H2O}: interpolation between values at $M_r=4$ and pure \ce{H2O}.
 
@@
 
-The RCSLW model begins with the SLW form of the RTE, given by Equation \ref{e:RTE_SLW}. The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
+The RCSLW model begins with the SLW form of the RTE, given by Eq.~(\ref{e:RTE_SLW}). The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
 where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}.
@@
 
-\subsection{Soot treatment}
-\label{s:soot}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Soot treatment} \label{s:soot}
 
@@
 The spectral soot absorption coefficient is given by
+%
+\begin{linenomath}
 \begin{equation}
 \label{e:soot1}
-	\kappa_{\lambda}=C_0 \frac{f_v}{\lambda} , \; \; \; C_0 = \frac{36\pi n k}{(n^2-k^2+2)^2+4n^2k^2},
+	\kappa_{s,\eta}=C_0 f_v \eta, \; \; \; C_0 = \frac{36\pi n k}{(n^2-k^2+2)^2+4n^2k^2},
 \end{equation}
+\end{linenomath}
+%
 where $n$ and $k$ are the real and imaginary parts of the soot complex index of refraction, respectively, and $f_v$ is the soot volume fraction \cite{Solovjov_2001,Modest_2013}.
-Various values for the refraction index have been proposed and applied to various scenarios \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}.
-RadLib uses the values $n=1.75$ and $k=1.03$ given in \cite{Williams_2007}, which result in a value of $C_0=7.03$, aligning nicely with the value $C_0=7.0$ suggested by \cite{Solovjov_2001}.
-Due to the simple $1/\lambda$ dependence and the suitably small difference between the mean absorption coefficients calculated for optically thin and optically thick cases, we can use one expression to calculate a spectral mean absorption coefficient for soot that applies to all optical regimes:
+Various values for the refraction index have been proposed and applied \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}.
+% INSERT FIGURE SHOWING DIFFERENT MODELS
+RadLib uses the values $n=1.75$ and $k=1.03$ given in \cite{Williams_2007}, which result in a value of $C_0=7.03$, which is nearly the same as the value $C_0=7.0$ used in \cite{Solovjov_2001}. 
+The Planck mean and Rosseland mean soot absorption coefficients are given in \cite{Modest_2013} as $\kappa_s=3.83f_vC_0T/C_2$ and $\kappa_s=3.60f_vC_0T/C_2$, respectively.
+Due to the small difference between the coefficients in these two expressions, a mean value is suggested \cite{Felske_1977,Modest_2013}:
+%
+\begin{linenomath}
 \begin{equation}
@@
 \end{equation}
-where $T$ is the temperature and $C_2=1.4388$ cm K is a Planck function constant \cite{Modest_2013}.
+\end{linenomath}
+%
+where $T$ is the temperature and $C_2=0.014388$ \si{m.K} is a Planck function constant \cite{Modest_2013}.
 
-In order to incorporate its radiative effects, soot is modeled as a pseudo-gas of its own and included alongside the existing gray gases.
-In the Planck Mean model, which models a gas mixture as one gray gas, the soot absorption coefficient calculated from Equation \ref{e:soot2} is simply added to the existing gas absorption coefficient.
-In the WSGG model, the soot absorption coefficient is similarly calculated from Equation \ref{e:soot2} but is then added to each of the gases separately.
-Because soot radiates across all wavelengths, its absorption coefficient is added to the values of all four gray gases and the transparent gas that represents the spectral gaps between absorption bands.
-Unlike the Planck Mean and WSGG models, the RCSLW model requires a spectrally dependent soot model.
-Instead of finding a mean soot absorption coefficient, we use Equation \ref{e:soot1} to define a soot absorption cross-section and ALBDF as detailed in \cite{Solovjov_2001}.
-The soot ALBDF can then be multiplied with the other gray gas ALBDFs to find the overall ALBDF for the gas-soot mixture.
+In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~(\ref{e:soot2}) is added to the gas absorption coefficient.
+This gives $\kappa_s=1817f_vT$ \si{m^{-1}}.
+
+In the WSGG model, Bordbar suggested incorporating soot as follows \cite{Bordbar_personal}.
+The soot absorption coefficient is similarly calculated from Eq.~(\ref{e:soot2}) but is then added to each of the gases separately.
+Because soot radiates across all wavelengths, its absorption coefficient is added to the values of all four gray gases and the clear gas.
+The gas weights $a_j$ are not changed.
+This model yeilds the expected behavior for the soot-only and gas-only limits.
+
+The soot model used in the WSGG model can be applied to the RCSLW model as well.
+However, the formulation of the RCSLW model allows for a spectral soot treatment in the same manner as for the gas species~\cite{Solovjov_2001}.
+Calculation of the soot ALBDF is facilitated by the simple $\eta$ dependence of $\kappa_{s,\eta}$ in Eq.~(\ref{e:soot1}).
+The fraction of the black energy at wavenumbers below $\eta$ is computed directly using a series expansion from Chang and Rhee \cite{Chang_1984,Solovjov_2001}.
+The soot ALBDF is then included in the product of species ALBDFs to obtain the mixture ALBDF.
 
@@
 The interfaces, solver, and examples included with the library serve to illustrate its use and validate the implementation and results.
-
+%
 \begin{figure}
@@
 \end{figure}
+%
 

### 2020-12-19 manuscript/manuscript.tex
initial rcslw section

@@
 
-\subsection{Planck Mean absorption coefficients}
-\label{s:planckmean}
+\subsection{Planck Mean absorption coefficients} \label{s:planckmean}
 
@@
 
-\subsection{Weighted sum of gray gases (WSGG)}
-\label{s:wsgg}
+\subsection{Weighted sum of gray gases (WSGG)} \label{s:wsgg}
 
@@
 
-\subsection{Rank Correlated SLW (RCSLW)}
-\label{s:RCSLW}
+\subsection{Rank Correlated SLW (RCSLW)} \label{s:RCSLW}
 
-The Spectral Line Weighted-sum-of-gray gases (SLW) model represents a family of global approaches to radiative heat transfer in high-temperature gases that also includes Absorption Distribution Function (ADF) and Full Spectrum $k$-distribution (FSK) models, all of which are based on the same fundamental principle in modeling the gas absorption spectrum \cite{Solovjov_2016}.
+The Spectral Line Weighted-Sum-of-Gray Gases (SLW) model represents a family of global approaches to radiative heat transfer in high-temperature gases that also includes Absorption Distribution Function (ADF) and Full Spectrum $k$-distribution (FSK) models, all of which are based on the same fundamental principle in modeling the gas absorption spectrum \cite{Solovjov_2016}.
 In order to extend their spectral models from uniform conditions (isothermal, homogeneous gases) to nonuniform conditions (non-isothermal, non-homogeneous gases), these models take a reference approach in which local gas states are corrected relative to a reference state.
@@
 The Rank Correlated SLW (RCSLW) model is a unique extension of the generalized SLW model that does not require a specified gas reference state and preserves the emission term of the spectrally integrated RTE.
-Recent comparison of advanced SLW modeling approaches revealed that "the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases" \citep{Badger_2019}.
+%
+% TODO: what does this last phrase mean: preserves the emission...?
+%
+Recent comparison of advanced SLW modeling approaches revealed that ``the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases" \citep{Badger_2019}.
 A brief overview of the general SLW and RCSLW models will be given here; detailed discussion can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
 
-The RCSLW model begins with the SLW form of the RTE, given by Eq.~(\ref{e:RTE_SLW}). The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
-where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}.
+SLW models are similar to WSGG models but instead of integrating over simple sequential $\eta$ bands, spectral integration is done over wavenumbers in a given range of absorption cross section.
+So, in Eq.~(\ref{e:RTE_wsgg}), gas $j$ would refer to wavenumbers $\eta\in\Delta_j$ with $\Delta_j=\{\eta:\,\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$, using Solovjov's notation, where $C$ denotes absorption cross-section (where $\kappa=CN$, $N$ is molar density of the radiatively participating gas), and $\tilde{C}$ are supplemental cross sections defining interfaces between adjacent cross-section bands.
+
+If $\tilde{C}_j$ are known for all $j$, then $\kappa_j = N\sqrt{C_{j-1}C_j}$.
+The weights $a_j$ are computed using the absorption line blackbody distribution function (ALBDF), denoted $F$, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorbtion cross sections less than $C$: $F$ is a monotonically-increasing function of $C$, and depends on the thermodynamic state $\phi$, and the black temperature $T_b$ defining the Planck function: $F = F(C,\phi,T_b)$.
+The $a_j$ are then computed as
+%
+\begin{linenomath}
+\begin{equation}
+a_j = F(\tilde{C}_j,\phi, T) - F(\tilde{C}_{j-1}, \phi,T).
+\end{equation}
+\end{linenomath}
+%
+
+Equation~(\ref{e:RTE_wsgg}) assumes the $\Delta_j$ intervals are independent of spatial position, but care must be taken since $C(\eta)$ depends on the thermodynamic state, which does vary spatially.
+Hence, the fixed $\Delta_j$ imply a corresponding variation in $C_j$ and $\tilde{C}_j$.
+
+%The RCSLW model begins with the SLW form of the RTE, given by Eq.~(\ref{e:RTE_SLW}). The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
+%where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}.
 The gray gas weights $a_j$ corresponding to each absorption coefficient are given by $a_j=F(C_j)-F(C_{j-1})$, where $F(C_j)$ is the absorption line blackbody distribution function (ALBDF) for species $j$, calculated from the detailed absorption spectrum of that species.
@@
 
-\section{Software Description}
-\label{s:architechture}
+\section{Software Description} \label{s:architechture}
 
@@
 
-\section{Illustrative Examples}
-\label{s:Examples}
+\section{Illustrative Examples} \label{s:Examples}
 
@@
 
-\section{Impact}
-\label{s:impact}
+\section{Impact} \label{s:impact}
 
@@
 
-\section{Conclusions}
-\label{}
+\section{Conclusions} \label{s:conclusions}
 
@@
 
-\section{Conflict of Interest}
+\section{Conflict of Interest} \label{s:coi}
 
@@
 
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
+\section*{Acknowledgements} \label{sec:acknowledgements}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% References:
 
@@
 
-\section*{Current executable software version}
-\label{}
+\section*{Current executable software version} \label{s:current_software}
 

### 2020-12-19 manuscript/manuscript.tex
updating manuscript.tex, somehow changes dont seem to have propgated, so Im trying to fix it

@@
 The Rank Correlated SLW (RCSLW) model is a unique extension of the generalized SLW model that does not require a specified gas reference state and preserves the emission term of the spectrally integrated RTE.
-%
 % TODO: what does this last phrase mean: preserves the emission...?
@@
 Recent comparison of advanced SLW modeling approaches revealed that ``the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases" \citep{Badger_2019}.
-A brief overview of the general SLW and RCSLW models will be given here; detailed discussion can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
+A brief overview of the RCSLW model is given here; detailed discussion can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
+Solovjov et al.~\cite{Solovjov_2017} present a number of methods within a generalized framework, with method I.2.2 giving the best results. That is the method implemented and summarized here.
+%
 
-SLW models are similar to WSGG models but instead of integrating over simple sequential $\eta$ bands, spectral integration is done over wavenumbers in a given range of absorption cross section.
-So, in Eq.~(\ref{e:RTE_wsgg}), gas $j$ would refer to wavenumbers $\eta\in\Delta_j$ with $\Delta_j=\{\eta:\,\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$, using Solovjov's notation, where $C$ denotes absorption cross-section (where $\kappa=CN$, $N$ is molar density of the radiatively participating gas), and $\tilde{C}$ are supplemental cross sections defining interfaces between adjacent cross-section bands.
+SLW models are similar to WSGG models but instead of integrating over a given range of $\eta$, with sequential $\eta$ bands defining gray gases $j$, spectral integration is done over wavenumbers in a given range of absorption cross section, with sequential bands of cross-section defining the gray gases $j$.
+So, in Eq.~(\ref{e:RTE_wsgg}), gas $j$ would refer to wavenumbers $\eta\in\Delta_j$ with $\Delta_j=\{\eta:\,\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$, using Solovjov's notation, where $C$ denotes absorption cross-section (where $\kappa=CN$ and $N$ is molar density of the radiatively participating gas), and $\tilde{C}$ are supplemental cross sections defining interfaces between adjacent cross-section bands.
+This ensures that the gas is in fact gray in a given band, by definition, at least to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
+In contrast, in traditional WSGG approaches, the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
 
-If $\tilde{C}_j$ are known for all $j$, then $\kappa_j = N\sqrt{C_{j-1}C_j}$.
-The weights $a_j$ are computed using the absorption line blackbody distribution function (ALBDF), denoted $F$, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorbtion cross sections less than $C$: $F$ is a monotonically-increasing function of $C$, and depends on the thermodynamic state $\phi$, and the black temperature $T_b$ defining the Planck function: $F = F(C,\phi,T_b)$.
-The $a_j$ are then computed as
+The gas weights $a_j$, are the fraction of the blackbody emission from $\eta$ corresponding to a given cross-section band.
+This energy is computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections less than $C$:
+%
+\begin{linenomath}
+    \begin{equation} \label{e:albdf}
+    F(C,\phi,T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C(\eta,\phi)<C\}}E_b(\eta,T)d\eta,
+\end{equation}
+\end{linenomath}
+%
+so that
 %
@@
 %
+%todo: deal with T versus Tb in e:albdf and previous eqn.
+Note that $F$ varies between zero and one, and is monotonic in $C$, allowing calculation of the inverse $C(F,\phi,T_b)$.
 
-Equation~(\ref{e:RTE_wsgg}) assumes the $\Delta_j$ intervals are independent of spatial position, but care must be taken since $C(\eta)$ depends on the thermodynamic state, which does vary spatially.
-Hence, the fixed $\Delta_j$ imply a corresponding variation in $C_j$ and $\tilde{C}_j$.
+Equation~(\ref{e:RTE_wsgg}) assumes the sets $\Delta_j$ are independent of spatial position, but care must be taken since C depends on the thermodynamic state (denoted by vector $\phi$ with nominal components $T$, $P$, and $y_i$), which does vary spatially.
+That is, $C=C(\eta,\phi)$.
+Hence, the fixed $\Delta_j$ imply a corresponding variation in $C_j$ and $\tilde{C}_j$ from one spatial location to the next.
+
+The RCSLW model uses the notion of \emph{rank correlation} to account for this variation in the $C_j$, which in turn define the absorption coefficients $\kappa_j$.
+Solovjov defines two spectra arising from thermodynamic states $\phi_1$ and $\phi_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wave number sets $\Delta_1$ and $\Delta_2$ are equal, where $\Delta_1=\{\eta: C(\eta,\phi_1)<C(\hat{\eta},\phi_1)\}$, and $\Delta_2=\{\eta: C(\eta,\phi_2)<C(\hat{\eta},\phi_2)\}$.
+Note in Eq.~(\ref{e:albdf}), that $\phi$ determines $C$, which then determines the set of $\eta$ integrated over.
+But for a \emph{given} set $\eta$, e.g., $\Delta_1$, $F$ can be considered as $F(C,T)$.
+Hence, if $\Delta_1=\Delta_2$, then at a fixed reference black temperature $T_{ref}$, we have $F(C_1,\phi_1,T_{ref})=F(C_2,\phi_2,T_{ref})$.
+One can then compute the inverse to find $C_1$ at $\phi_1$ and $C_2$ at $\phi_2$ (i.e., values at two spatial positions) corresponding to the same wavenumber interval.
+
+In practice, for a given problem, a grid of $\tilde{F}_j$ points are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$.
+The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position can then be found by inversion: $C_j = C(F_j,\phi,T_{ref})$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$.
+$\kappa_j$ and $a_j$ can then be computed as noted above.
+%TODO verify this in terms of the quadrature.
 

### 2020-12-21 manuscript/manuscript.tex
tweeking the rcslw section. That will continue...

@@
 \usepackage{siunitx}
+\usepackage{bm}
 
@@
 \usepackage{hyperref}
+
+\newcommand{\BS}{\boldsymbol}
 
@@
 SLW models are similar to WSGG models but instead of integrating over a given range of $\eta$, with sequential $\eta$ bands defining gray gases $j$, spectral integration is done over wavenumbers in a given range of absorption cross section, with sequential bands of cross-section defining the gray gases $j$.
-So, in Eq.~(\ref{e:RTE_wsgg}), gas $j$ would refer to wavenumbers $\eta\in\Delta_j$ with $\Delta_j=\{\eta:\,\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$, using Solovjov's notation, where $C$ denotes absorption cross-section (where $\kappa=CN$ and $N$ is molar density of the radiatively participating gas), and $\tilde{C}$ are supplemental cross sections defining interfaces between adjacent cross-section bands.
-This ensures that the gas is in fact gray in a given band, by definition, at least to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
+So, in Eq.~(\ref{e:RTE_wsgg}), gas $j$ would refer to wavenumbers in set $\Delta_j=\{\eta:\,\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$, using Solovjov's notation, where $C$ denotes absorption cross-section, and $\tilde{C}$ are supplemental cross sections defining interfaces between adjacent cross-section bands.
+The absorption cross section is related to absorption coefficient by $\kappa=CN$, where $N$ is molar density of the radiatively participating gas.
+The SLW gases, then, are gray in a given band, by definition, at least to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
 In contrast, in traditional WSGG approaches, the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
@@
     \begin{equation} \label{e:albdf}
-    F(C,\phi,T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C(\eta,\phi)<C\}}E_b(\eta,T)d\eta,
+        F(C,\BS{\phi},T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C(\eta,\BS{\phi})<C\}}E_b(\eta,T)d\eta,
 \end{equation}
@@
 \begin{equation}
-a_j = F(\tilde{C}_j,\phi, T) - F(\tilde{C}_{j-1}, \phi,T).
+    a_j = F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1}, \BS{\phi},T).
 \end{equation}
@@
 %todo: deal with T versus Tb in e:albdf and previous eqn.
-Note that $F$ varies between zero and one, and is monotonic in $C$, allowing calculation of the inverse $C(F,\phi,T_b)$.
+Note that $F$ varies between zero and one, and is monotonic in $C$, allowing calculation of the inverse $C(F,\BS{\phi},T_b)$.
 
-Equation~(\ref{e:RTE_wsgg}) assumes the sets $\Delta_j$ are independent of spatial position, but care must be taken since C depends on the thermodynamic state (denoted by vector $\phi$ with nominal components $T$, $P$, and $y_i$), which does vary spatially.
-That is, $C=C(\eta,\phi)$.
-Hence, the fixed $\Delta_j$ imply a corresponding variation in $C_j$ and $\tilde{C}_j$ from one spatial location to the next.
+Equation~(\ref{e:RTE_wsgg}) assumes the sets $\Delta_j$ are independent of spatial position $\mathbf{x}$, but care must be taken since C depends on the thermodynamic state (denoted by vector $\BS{\phi}$ with nominal components $T$, $P$, and $y_i$), which does vary spatially.
+That is, $C=C(\eta,\BS{\phi}(\mathbf{x}))$.
+Hence, the fixed $\Delta_j$ imply a corresponding spatial variation in $C_j$ and $\tilde{C}_j$.
 
-The RCSLW model uses the notion of \emph{rank correlation} to account for this variation in the $C_j$, which in turn define the absorption coefficients $\kappa_j$.
-Solovjov defines two spectra arising from thermodynamic states $\phi_1$ and $\phi_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wave number sets $\Delta_1$ and $\Delta_2$ are equal, where $\Delta_1=\{\eta: C(\eta,\phi_1)<C(\hat{\eta},\phi_1)\}$, and $\Delta_2=\{\eta: C(\eta,\phi_2)<C(\hat{\eta},\phi_2)\}$.
-Note in Eq.~(\ref{e:albdf}), that $\phi$ determines $C$, which then determines the set of $\eta$ integrated over.
+The RCSLW model uses the notion of \emph{rank correlation} to account for this variation in the $C_j$.
+Solovjov defines two spectra arising from thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wave number sets $\Delta_1$ and $\Delta_2$ are equal, where $\Delta_1=\{\eta: C(\eta,\BS{\phi}_1)<C(\hat{\eta},\BS{\phi}_1)\}$, and $\Delta_2=\{\eta: C(\eta,\BS{\phi}_2)<C(\hat{\eta},\BS{\phi}_2)\}$.
+Note in Eq.~(\ref{e:albdf}), that $\BS{\phi}$ determines $C$, which then determines the set of $\eta$ integrated over.
 But for a \emph{given} set $\eta$, e.g., $\Delta_1$, $F$ can be considered as $F(C,T)$.
-Hence, if $\Delta_1=\Delta_2$, then at a fixed reference black temperature $T_{ref}$, we have $F(C_1,\phi_1,T_{ref})=F(C_2,\phi_2,T_{ref})$.
-One can then compute the inverse to find $C_1$ at $\phi_1$ and $C_2$ at $\phi_2$ (i.e., values at two spatial positions) corresponding to the same wavenumber interval.
+Hence, if $\Delta_1=\Delta_2$, then at a fixed reference black temperature $T_{ref}$, we have $F(C_1,\BS{\phi}_1,T_{ref})=F(C_2,\BS{\phi}_2,T_{ref})$.
+One can then compute the inverse to find $C_1$ at $\BS{\phi}_1$ and $C_2$ at $\BS{\phi}_2$ (i.e., values at two spatial positions) corresponding to the same wavenumber interval.
 
 In practice, for a given problem, a grid of $\tilde{F}_j$ points are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$.
-The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position can then be found by inversion: $C_j = C(F_j,\phi,T_{ref})$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$.
+The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position can then be found by inversion: $C_j = C(F_j,\BS{\phi},T_{ref})$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$.
 $\kappa_j$ and $a_j$ can then be computed as noted above.

### 2020-12-21 manuscript/manuscript.tex
some improvements, not done yet.

@@
 The gas absorption spectrum is an extremely complex function consisting of millions of spectral lines (peaks) corresponding to quantum mechanical energy levels of the gas molecules.
-Direct solution of Eq.~(\ref{e:RTE_general}), involves so-called \emph{line-by-line} calculations that are computationally prohibitive for most practical calculations, and are used primarily for model validation.
+Direct solution of Eq.~\ref{e:RTE_general}, involves so-called \emph{line-by-line} calculations that are computationally prohibitive for most practical calculations, and are used primarily for model validation.
 Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model \cite{Hottel_1967,Modest_2013}.
-For instance, integrating Eq.~(\ref{e:RTE_general}) over fixed spectral ranges $\eta_j$ and assuming gray (spectrally uniform) properties in each region $j$, (that is, in each \emph{gray gas} $j$), gives
+For instance, integrating Eq.~\ref{e:RTE_general} over fixed spectral ranges $\eta_j$ and assuming gray (spectrally uniform) properties in each region $j$, (that is, in each \emph{gray gas} $j$), gives
 %
@@
 %
-Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~(\ref{e:RTE_wsgg}) can be computed for each of the $n+1$ gray gases.
+Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be computed for each of the $n+1$ gray gases.
 Normally, the $j=0$ gas is considered as a clear gas and represents \emph{transparent windows} in the spectrum for which $\kappa_0=0$.
@@
 
-SLW models are similar to WSGG models but instead of integrating over a given range of $\eta$, with sequential $\eta$ bands defining gray gases $j$, spectral integration is done over wavenumbers in a given range of absorption cross section, with sequential bands of cross-section defining the gray gases $j$.
-So, in Eq.~(\ref{e:RTE_wsgg}), gas $j$ would refer to wavenumbers in set $\Delta_j=\{\eta:\,\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$, using Solovjov's notation, where $C$ denotes absorption cross-section, and $\tilde{C}$ are supplemental cross sections defining interfaces between adjacent cross-section bands.
-The absorption cross section is related to absorption coefficient by $\kappa=CN$, where $N$ is molar density of the radiatively participating gas.
-The SLW gases, then, are gray in a given band, by definition, at least to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
+SLW models are written in terms of absorption cross section $C_\eta(\eta)$, where $\kappa_\eta=C_\eta N$, and $N$ is the molar density of the radiatively participating gas. 
+%
+SLW models are similar to WSGG models, but instead of integrating within a sequential band of $\eta$ to define gray gas $j$, spectral integration is done over a set of (nonsquential) wavenumbers constituting a given band $j$ of $C_\eta$.
+Consider the set of wavenumbers $\tilde{H}_j=\{\eta:C_\eta<\tilde{C}_j\}$, then $\Delta_j=\tilde{H}_j-\tilde{H}_{j-1} = \{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}.
+(Here, we are using the notation in \cite{Solovjov_2017}.)
+%
+The SLW gases, then, are gray in a given band by definition, at least to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
 In contrast, in traditional WSGG approaches, the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
 
-The gas weights $a_j$, are the fraction of the blackbody emission from $\eta$ corresponding to a given cross-section band.
+A gas weight $a_j$ is the fraction of blackbody emission from $\eta\in\Delta_j$ corresponding to a given cross-section band $j$.
 This energy is computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections less than $C$:
@@
     \begin{equation} \label{e:albdf}
-        F(C,\BS{\phi},T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C(\eta,\BS{\phi})<C\}}E_b(\eta,T)d\eta,
+        F(C,\BS{\phi},T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi})<C\}}E_b(\eta,T)d\eta,
 \end{equation}
@@
 
-Equation~(\ref{e:RTE_wsgg}) assumes the sets $\Delta_j$ are independent of spatial position $\mathbf{x}$, but care must be taken since C depends on the thermodynamic state (denoted by vector $\BS{\phi}$ with nominal components $T$, $P$, and $y_i$), which does vary spatially.
-That is, $C=C(\eta,\BS{\phi}(\mathbf{x}))$.
-Hence, the fixed $\Delta_j$ imply a corresponding spatial variation in $C_j$ and $\tilde{C}_j$.
+The WSGG RTE in Eq.~\ref{e:RTE_wsgg} assumes the sets $\Delta_j$ are independent of spatial position $\mathbf{x}$, but care must be taken since $C_\eta$ depends on the thermodynamic state (denoted by vector $\BS{\phi}$ with nominal components $T$, $P$, and $y_i$), which does vary spatially.
+That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$.
+Hence, spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ imply a spatial variation in $C_j$ and $\tilde{C}_j$.
 
-The RCSLW model uses the notion of \emph{rank correlation} to account for this variation in the $C_j$.
-Solovjov defines two spectra arising from thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wave number sets $\Delta_1$ and $\Delta_2$ are equal, where $\Delta_1=\{\eta: C(\eta,\BS{\phi}_1)<C(\hat{\eta},\BS{\phi}_1)\}$, and $\Delta_2=\{\eta: C(\eta,\BS{\phi}_2)<C(\hat{\eta},\BS{\phi}_2)\}$.
-Note in Eq.~(\ref{e:albdf}), that $\BS{\phi}$ determines $C$, which then determines the set of $\eta$ integrated over.
-But for a \emph{given} set $\eta$, e.g., $\Delta_1$, $F$ can be considered as $F(C,T)$.
-Hence, if $\Delta_1=\Delta_2$, then at a fixed reference black temperature $T_{ref}$, we have $F(C_1,\BS{\phi}_1,T_{ref})=F(C_2,\BS{\phi}_2,T_{ref})$.
+The RCSLW model uses the notion of \emph{rank correlation} to compute this variation in $C_j$ and $\tilde{C}_j$.
+Solovjov et~al.~\cite{Solovjov_2017} define two spectra at thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wavenumber sets $H_1(\BS{\phi}_1)$ and $H_2(\BS{\phi}_2)$ are equal, where
+%
+\begin{linenomath}
+\begin{align}
+    H_1(\BS{\phi}_1)&=\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}, \\
+    H_2(\BS{\phi}_2)&=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}. 
+\end{align}
+\end{linenomath}
+%
+
+Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and denote $C_\eta(\hat{\eta},\BS{\phi}_1)$ as $C_1$, and similarly for $C_2$; then we have
+%
+\begin{linenomath}
+    \begin{align} \label{e:albdf2}
+        F(C_1,\BS{\phi}_1,T) &= \frac{1}{\sigma T^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
+        F(C_2,\BS{\phi}_2,T) &= \frac{1}{\sigma T^4}\int_{H_2}E_b(\eta,T_r)d\eta.
+    \end{align}
+\end{linenomath}
+%
+
+%Note in Eq.~\ref{e:albdf}, that $\BS{\phi}$ determines $C_\eta$, which then determines the set of $\eta$ integrated over.
+But for a \emph{given} set $\eta$, e.g., $H_1$, $F$ can be considered as $F(C,T)$.
+Hence, if $H_1=H_2$, then at a fixed reference black temperature $T_{ref}$, we have $F(C_1,\BS{\phi}_1,T_{ref})=F(C_2,\BS{\phi}_2,T_{ref})$.
 One can then compute the inverse to find $C_1$ at $\BS{\phi}_1$ and $C_2$ at $\BS{\phi}_2$ (i.e., values at two spatial positions) corresponding to the same wavenumber interval.
@@
 
-%The RCSLW model begins with the SLW form of the RTE, given by Eq.~(\ref{e:RTE_SLW}). The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
+%The RCSLW model begins with the SLW form of the RTE, given by Eq.~\ref{e:RTE_SLW}. The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
 %where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}.
@@
 
-\subsection{Soot treatment} \label{s:soot}
+\subsection{Soot} \label{s:soot}
 
@@
 
-In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~(\ref{e:soot2}) is added to the gas absorption coefficient.
+In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is added to the gas absorption coefficient.
 This gives $\kappa_s=1817f_vT$ \si{m^{-1}}.
@@
 In the WSGG model, Bordbar suggested incorporating soot as follows \cite{Bordbar_personal}.
-The soot absorption coefficient is similarly calculated from Eq.~(\ref{e:soot2}) but is then added to each of the gases separately.
+The soot absorption coefficient is similarly calculated from Eq.~\ref{e:soot2} but is then added to each of the gases separately.
 Because soot radiates across all wavelengths, its absorption coefficient is added to the values of all four gray gases and the clear gas.
@@
 However, the formulation of the RCSLW model allows for a spectral soot treatment in the same manner as for the gas species~\cite{Solovjov_2001}.
-Calculation of the soot ALBDF is facilitated by the simple $\eta$ dependence of $\kappa_{s,\eta}$ in Eq.~(\ref{e:soot1}).
+Calculation of the soot ALBDF is facilitated by the simple $\eta$ dependence of $\kappa_{s,\eta}$ in Eq.~\ref{e:soot1}.
 The fraction of the black energy at wavenumbers below $\eta$ is computed directly using a series expansion from Chang and Rhee \cite{Chang_1984,Solovjov_2001}.

### 2020-12-21 manuscript/manuscript.tex
more...

@@
 The RCSLW model uses the notion of \emph{rank correlation} to compute this variation in $C_j$ and $\tilde{C}_j$.
-Solovjov et~al.~\cite{Solovjov_2017} define two spectra at thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wavenumber sets $H_1(\BS{\phi}_1)$ and $H_2(\BS{\phi}_2)$ are equal, where
+Solovjov et~al.~\cite{Solovjov_2017} define two spectra at states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wavenumber sets $H_1(\BS{\phi}_1)$ and $H_2(\BS{\phi}_2)$ are equal, where
 %
@@
 
-Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and denote $C_\eta(\hat{\eta},\BS{\phi}_1)$ as $C_1$, and similarly for $C_2$; then we have
+Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$, and similarly for $\hat{C}_2$; then we have
 %
@@
     \begin{align} \label{e:albdf2}
-        F(C_1,\BS{\phi}_1,T) &= \frac{1}{\sigma T^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
-        F(C_2,\BS{\phi}_2,T) &= \frac{1}{\sigma T^4}\int_{H_2}E_b(\eta,T_r)d\eta.
+        F(\hat{C}_1,\BS{\phi}_1,T) &= \frac{1}{\sigma T^4}\int_{H_1(\BS{\phi_1})}E_b(\eta,T_r)d\eta, \\
+        F(\hat{C}_2,\BS{\phi}_2,T) &= \frac{1}{\sigma T^4}\int_{H_2(\BS{\phi_1})}E_b(\eta,T_r)d\eta.
     \end{align}

### 2020-12-21 manuscript/manuscript.tex
good Better, BEST

@@
 SLW models are similar to WSGG models, but instead of integrating within a sequential band of $\eta$ to define gray gas $j$, spectral integration is done over a set of (nonsquential) wavenumbers constituting a given band $j$ of $C_\eta$.
-Consider the set of wavenumbers $\tilde{H}_j=\{\eta:C_\eta<\tilde{C}_j\}$, then $\Delta_j=\tilde{H}_j-\tilde{H}_{j-1} = \{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}.
-(Here, we are using the notation in \cite{Solovjov_2017}.)
+Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}.
 %
@@
 \begin{linenomath}
-\begin{equation}
+    \begin{equation}\label{e:aj}
     a_j = F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1}, \BS{\phi},T).
@@
 The RCSLW model uses the notion of \emph{rank correlation} to compute this variation in $C_j$ and $\tilde{C}_j$.
-Solovjov et~al.~\cite{Solovjov_2017} define two spectra at states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated if, for an arbirary wavenumber $\hat{\eta}$, the wavenumber sets $H_1(\BS{\phi}_1)$ and $H_2(\BS{\phi}_2)$ are equal, where
-%
-\begin{linenomath}
-\begin{align}
-    H_1(\BS{\phi}_1)&=\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}, \\
-    H_2(\BS{\phi}_2)&=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}. 
-\end{align}
-\end{linenomath}
-%
+Solovjov et~al.~\cite{Solovjov_2017} define two spectra at states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated
+if the set $H_1=\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}$ is equal to the set
+$H_2=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}$.
 
@@
     \begin{align} \label{e:albdf2}
-        F(\hat{C}_1,\BS{\phi}_1,T) &= \frac{1}{\sigma T^4}\int_{H_1(\BS{\phi_1})}E_b(\eta,T_r)d\eta, \\
-        F(\hat{C}_2,\BS{\phi}_2,T) &= \frac{1}{\sigma T^4}\int_{H_2(\BS{\phi_1})}E_b(\eta,T_r)d\eta.
+        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}}E_b(\eta,T_r)d\eta, \\
+        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}}E_b(\eta,T_r)d\eta.
     \end{align}
@@
 %
+(Note the distinction between $\hat{C}_1$ and $C_j$, where $\hat{C}_1$ is a cross section at $\hat{\eta}$ and state $\BS{\phi}_1$, and $C_j$ is the cross section of some gray gas $j$).
+In these equations, since the sets integrated over are the same: $H_1=H_2$, and since argument $T=T_r$ is the same, we have 
+%
+\begin{linenomath}
+    \begin{equation}\label{e:FeqF}
+    F(\hat{C}_1,\BS{\phi}_1,T_r)=F(\hat{C}_2,\BS{\phi}_2,T_r).
+\end{equation}
+\end{linenomath}
+%
+Recall that $F$ can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are given, we can compute $F$ and then invert to obtain $\hat{C}_2$ at $\BS{\phi}_2$.
+But Eq.~\ref{e:FeqF} holds for arbitrary states $\BS{\phi}$, so we can also just specify a value of $F$, and then do the inversion to get $\hat{C}$ at given $\BS{\phi}$.
+At this point, we can drop the \emph{hat} notation and just write $F(C,\BS{\phi},T_r)$.
 
-%Note in Eq.~\ref{e:albdf}, that $\BS{\phi}$ determines $C_\eta$, which then determines the set of $\eta$ integrated over.
-But for a \emph{given} set $\eta$, e.g., $H_1$, $F$ can be considered as $F(C,T)$.
-Hence, if $H_1=H_2$, then at a fixed reference black temperature $T_{ref}$, we have $F(C_1,\BS{\phi}_1,T_{ref})=F(C_2,\BS{\phi}_2,T_{ref})$.
-One can then compute the inverse to find $C_1$ at $\BS{\phi}_1$ and $C_2$ at $\BS{\phi}_2$ (i.e., values at two spatial positions) corresponding to the same wavenumber interval.
+In the RCSLW model for a given problem, a collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$.
+The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position (and corresponding thermodynamic state $\BS{\phi}$) can then be found by inversion: $C_j = C(F_j,\BS{\phi},T_r)$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$.
+$\kappa_j$ is then computed as $\kappa_j=C_jN$, and $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature, not $T_r$.
 
-In practice, for a given problem, a grid of $\tilde{F}_j$ points are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$.
-The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position can then be found by inversion: $C_j = C(F_j,\BS{\phi},T_{ref})$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$.
-$\kappa_j$ and $a_j$ can then be computed as noted above.
-%TODO verify this in terms of the quadrature.
-
-%The RCSLW model begins with the SLW form of the RTE, given by Eq.~\ref{e:RTE_SLW}. The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
-%where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}.
-The gray gas weights $a_j$ corresponding to each absorption coefficient are given by $a_j=F(C_j)-F(C_{j-1})$, where $F(C_j)$ is the absorption line blackbody distribution function (ALBDF) for species $j$, calculated from the detailed absorption spectrum of that species.
-In general SLW methods, the absorption cross-sections are chosen with respect to a thermodynamic reference state, classifying them as reference approaches.
-The Rank-Correlated SLW (RCSLW) model avoids specifying a reference state by relating thermodynamic states to one another instead.
-If two arbitrary absorption cross-sections define identical wavenumber intervals, the two cross-sections (neither of which is designated a reference cross-section) can be said to be rank-correlated.
-The inverse ALBDF, defined such that $C[F(C,\phi_g,T_b),\phi_g,T_b]=C$ and $F[C(F,\phi_g,T_b),\phi_g,T_b]=F$ for a given gas thermodynamic state $\phi_g$ and blackbody temperature $T_b$, is proven to have this property and can also be called the rank-correlated reordered absorption cross-sections \cite{Solovjov_2017}.
-As a result, the inverse ALBDF can be used to construct cross-section intervals for the RCSLW model that do not rely on an arbitrary reference state or spectrum.
-ALBDFs for individual gray gases are multiplied together to obtain an overall ABLDF for the gas mixture \cite{Solovjov_2001}.
-RadLib's RCSLW model uses Method 1.2.2 as defined in and recommended by \cite{Solovjov_2017}.
+The ALBDF functions are provided by Pearson et~al.~\cite{Pearson_2014} for \ce{H2O}, \ce{CO2}, and \ce{CO} at pressures ranging from 0.1 to 50 atm, and temperatures from 300 to 3000 K in both tabulated and correlated form.
+The tabulated data are currently used in Radlib, coupled with multilinear interpolation.
+For gas mixtures, the multiplication method described in \cite{Solovjov_2000} is used, in which
+%
+\begin{linenomath}
+\begin{equation}
+    F(C) = F_{CO2}(C/y_{CO2})F_{H2O}(C/y_{H2O})F_{CO}(C/y_{CO}), 
+\end{equation}
+\end{linenomath}
+%
+where the $\BS{\phi}$ and $T$ arguments of $F$ are omitted for clarity.
 

### 2020-12-21 manuscript/manuscript.tex
needed to add back in hat eta

@@
 if the set $H_1=\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}$ is equal to the set
-$H_2=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}$.
+$H_2=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}$, for an arbitrary $\hat{\eta}$.
 

### 2020-12-21 manuscript/manuscript.tex
proofreading edits to rcslw section

@@
 
-In the RCSLW model for a given problem, a collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$.
+In the RCSLW model for a given problem, a collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$; these apply to all spatial positions.
 The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position (and corresponding thermodynamic state $\BS{\phi}$) can then be found by inversion: $C_j = C(F_j,\BS{\phi},T_r)$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$.
 $\kappa_j$ is then computed as $\kappa_j=C_jN$, and $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature, not $T_r$.
+The system average temperature may be used for $T_r$, as done in \cite{Solovjov_2001}, and in the examples below.
 

### 2020-12-28 manuscript/manuscript.tex
DOL implementing VBL edits up through line 172 just before 'Consider Eq. 11 at fixed arg...'

@@
 $I_{b\eta}$ is spectral blackbody intensity (or Planck function), 
-$\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a pathlength along direction $\mathbf{s}$.
+$\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
 Radiation property models such as those implemented by RadLib are used to calculate the absorption coefficients $\kappa_{\eta}$.
@@
 The gas absorption spectrum is an extremely complex function consisting of millions of spectral lines (peaks) corresponding to quantum mechanical energy levels of the gas molecules.
-Direct solution of Eq.~\ref{e:RTE_general}, involves so-called \emph{line-by-line} calculations that are computationally prohibitive for most practical calculations, and are used primarily for model validation.
+Direct solution of Eq.~\ref{e:RTE_general}, involves so-called line-by-line calculations that are computationally prohibitive for most practical configurations, and are used primarily for model validation.
 Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model \cite{Hottel_1967,Modest_2013}.
@@
 Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be computed for each of the $n+1$ gray gases.
-Normally, the $j=0$ gas is considered as a clear gas and represents \emph{transparent windows} in the spectrum for which $\kappa_0=0$.
+Normally, the $j=0$ gas is considered as a clear gas and represents transparent windows in the spectrum for which $\kappa_0=0$.
 The total radiative intensity $I$ is calculated by summing the individual gray gas intensities:
@@
 
-The correlations provided in \cite{Bordbar_2014} are valid for $0.01\le M_r\le4$.
-In \cite{Bordbar_2020} this range was extended to arbitrary $M_r$ by interpolation of $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$, that is, for \ce{CO2}: interpolation between values at $M_r=0.01$ and pure \ce{CO2}; and for \ce{H2O}: interpolation between values at $M_r=4$ and pure \ce{H2O}.
+The correlations provided by Bordbar et~al.
+(2014) \cite{Bordbar_2014} are valid for $0.01\le M_r\le4$.
+In Bordbar et~al.
+(2020) \cite{Bordbar_2020} this range was extended to arbitrary $M_r$.
+This was done by interpolation of $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$.
+That is, for \ce{CO2}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=0.01$ and pure \ce{CO2}.
+For \ce{H2O}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=4$ and pure \ce{H2O}.
 
@@
 A brief overview of the RCSLW model is given here; detailed discussion can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
-Solovjov et al.~\cite{Solovjov_2017} present a number of methods within a generalized framework, with method I.2.2 giving the best results. That is the method implemented and summarized here.
+In particular, Solovjov et~al. \cite{Solovjov_2017} present several RCSLW methods within a generalized framework; RadLib implements method I.2.2, which gives the best results and is summarized here.
 %
 
-SLW models are written in terms of absorption cross section $C_\eta(\eta)$, where $\kappa_\eta=C_\eta N$, and $N$ is the molar density of the radiatively participating gas. 
-%
-SLW models are similar to WSGG models, but instead of integrating within a sequential band of $\eta$ to define gray gas $j$, spectral integration is done over a set of (nonsquential) wavenumbers constituting a given band $j$ of $C_\eta$.
-Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}.
-%
-The SLW gases, then, are gray in a given band by definition, at least to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
+%%%%% DOL original, with VBL suggested edits
+%  SLW models are similar to WSGG models, but instead of integrating within a sequential band of $\eta$ to define gray gas $j$, spectral integration is done over a set of (nonsquential) wavenumbers constituting a given band $j$ of absorption cross section $C_\eta$.
+%  %
+%  (The absorption coefficient is related to absorption cross section by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.)
+%  %
+%  Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}, (where $\tilde{C}$ denotes a cross section boundary between two bands/gases).
+%  %
+%  The SLW gases, then, are gray in a given band by construction, to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
 In contrast, in traditional WSGG approaches, the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
 
-A gas weight $a_j$ is the fraction of blackbody emission from $\eta\in\Delta_j$ corresponding to a given cross-section band $j$.
-This energy is computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections less than $C$:
+%%%%% DOL restructuring paragraph based on VBL suggestions
+SLW models are similar to WSGG models, but SLW gases are gray in a given band by construction, whereas in traditional WSGG approaches the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
+%
+In SLW models, instead of integrating within a sequential band of $\eta$ (with highly variable $\kappa$) to define a gray gas $j$, as in other WSGG models, spectral integration is done over a set of (nonsequential) wavenumbers constituting a given band $j$ of absorption cross section $C_\eta$.
+%
+(The absorption coefficient is related simply to absorption cross section by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.)
+%
+Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}, (where $\tilde{C}$ denotes a cross section boundary between two bands/gases).
+%
+Hence, in SLW, the gases in a given band are gray to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
+
+A gray gas weight $a_j$ is the fraction of blackbody emission from $\eta\in\Delta_j$ corresponding to a given cross-section band $j$.
+This weight $a_j$ is computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections less than $C$:
 %
@@
 %todo: deal with T versus Tb in e:albdf and previous eqn.
-Note that $F$ varies between zero and one, and is monotonic in $C$, allowing calculation of the inverse $C(F,\BS{\phi},T_b)$.
+Note that $F$ varies between zero and one, and is monotonic in $C$, allowing calculation of the inverse $C(F,\BS{\phi},T)$.
 
@@
 That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$.
-Hence, spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ imply a spatial variation in $C_j$ and $\tilde{C}_j$.
+Hence, spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and $\tilde{C}_j$.
 
-The RCSLW model uses the notion of \emph{rank correlation} to compute this variation in $C_j$ and $\tilde{C}_j$.
+The RCSLW model uses the notion of rank correlation to compute this variation in $C_j$ and $\tilde{C}_j$.
 Solovjov et~al.~\cite{Solovjov_2017} define two spectra at states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated
@@
 
-Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$, and similarly for $\hat{C}_2$; then we have
+Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$, and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$; then we have
 %
@@
     \begin{align} \label{e:albdf2}
-        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}}E_b(\eta,T_r)d\eta, \\
-        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}}E_b(\eta,T_r)d\eta.
+        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}}E_b(\eta,T_r)d\eta, \\
+        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}}E_b(\eta,T_r)d\eta.
     \end{align}

### 2020-12-28 manuscript/manuscript.tex
Further edits to RCSLW section.

@@
 %
-Hence, in SLW, the gases in a given band are gray to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
+Hence, in SLW the gases in a given band are gray to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
 
@@
 The RCSLW model uses the notion of rank correlation to compute this variation in $C_j$ and $\tilde{C}_j$. 
-Solovjov et~al.~\cite{Solovjov_2017} define two spectra at states $\BS{\phi}_1$ and $\BS{\phi}_2$ to be rank correlated
-if the set $H_1=\{\eta: C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}$ is equal to the set
-$H_2=\{\eta: C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}$, for an arbitrary $\hat{\eta}$.
+We proceed loosely following Solovjov et~al. \cite{Solovjov_2014}.
+Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$. These will have corresponding spectra $C_\eta(\eta,\BS{\phi}_1)$, and $C_\eta(\eta,\BS{\phi}_2)$.
+Now, let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some wavenumber $\hat{\eta}$.
+For each of the two spectra, we can define the set of wavenumbers that give cross sections less than $\hat{C}$:
+%
+\begin{linenomath}
+\begin{align}
+    H_1&=\{\eta: C_\eta(\eta,\BS{\phi}_1)<\hat{C}_1\}, \\
+    H_2&=\{\eta: C_\eta(\eta,\BS{\phi}_2)<\hat{C}_2\}.
+    \end{align}
+\end{linenomath}
+%
+If $H_1=H_2$ for arbitrary $\hat{\eta}$, the spectra corresponding to $\BS{\phi}_1$ and $\BS{\phi}_2$ are said to be rank correlated.
+% Solovjov provides some visual representations...
 
-Consider Eq.~\ref{e:albdf} at fixed argument $T=T_r$, and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$, and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$; then we have
+This rank correlation is used as follows. Consider Eq.~\ref{e:albdf} evaluated at $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at
+$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
 %
@@
     \begin{align} \label{e:albdf2}
-        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi}_1)<C_\eta(\hat{\eta},\BS{\phi}_1)\}}E_b(\eta,T_r)d\eta, \\
-        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi}_2)<C_\eta(\hat{\eta},\BS{\phi}_2)\}}E_b(\eta,T_r)d\eta.
+        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
+        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_2}E_b(\eta,T_r)d\eta.
     \end{align}
@@
 %
-(Note the distinction between $\hat{C}_1$ and $C_j$, where $\hat{C}_1$ is a cross section at $\hat{\eta}$ and state $\BS{\phi}_1$, and $C_j$ is the cross section of some gray gas $j$).
-In these equations, since the sets integrated over are the same: $H_1=H_2$, and since argument $T=T_r$ is the same, we have 
+Since $H_1=H_2$, we have 
 %
@@
 Recall that $F$ can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are given, we can compute $F$ and then invert to obtain $\hat{C}_2$ at $\BS{\phi}_2$.
-But Eq.~\ref{e:FeqF} holds for arbitrary states $\BS{\phi}$, so we can also just specify a value of $F$, and then do the inversion to get $\hat{C}$ at given $\BS{\phi}$.
+Now, note that Eq.~\ref{e:FeqF} is assumed to hold for arbitrary states $\BS{\phi}_1$ and $\BS{\phi}_2$; hence, if some $F$ is given or specified, we can invert $F=F(\hat{C},\BS{\phi},T_r)$ to get $\hat{C}$ at corresponding state $\BS{\phi}$.
 At this point, we can drop the \emph{hat} notation and just write $F(C,\BS{\phi},T_r)$.
 
-In the RCSLW model for a given problem, a collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$; these apply to all spatial positions.
-The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position (and corresponding thermodynamic state $\BS{\phi}$) can then be found by inversion: $C_j = C(F_j,\BS{\phi},T_r)$, and similarly for $\tilde{C}_j$ in terms of $\tilde{F}_j$.
-$\kappa_j$ is then computed as $\kappa_j=C_jN$, and $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature, not $T_r$.
-The system average temperature may be used for $T_r$, as done in \cite{Solovjov_2001}, and in the examples below.
+Given the above summary development, the RCSLW model is applied as follows. 
+%
+\begin{itemize}
+    \item A reference temperature is specified. This is taken to be the average temperature on the domain of interest in \cite{Solovjov_2001}.
+    \item A collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$. These apply to all spatial positions. 
+    \item The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position and corresponding thermodynamic state $\BS{\phi}$ are found by inversion: $C_j = C(F_j,\BS{\phi},T_r)$, and $\tilde{C}_j = C(\tilde{F}_j,\BS{\phi},T_r)$
+    \item $\kappa_j$ is then computed as $\kappa_j=C_jN$. 
+    \item $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature.
+\end{itemize}
+%
 

### 2020-12-29 manuscript/manuscript.tex
soot example added

@@
 The examples correspond to those presented by Solvojov et al.
-(S) \cite{Solovjov_2017} and Bordbar et al.
-(B) \cite{Bordbar_2020}, and the number of each example corresponds to the example number in the respective reference.
+\cite{Solovjov_2017} (S), Bordbar et al.
+\cite{Bordbar_2020} (B), Solovjov et~al.
+\cite{Solovjov_2001} (Sb), and the number of each example corresponds to the example number in the respective reference.
 A ray-tracing code is used to solve the radiative transport equation between two parallel plates.
@@
 Example S1 is a hot slab next to a cold slab where the cold slab's thickness varies; Example S2 is isothermal with a thick slab of high CO$_2$ next to a thin slab of low CO$_2$ with variable thickness; Example S3 uses parabolic temperature and H$_2$O mole fraction profiles; Example S4 has a triangular temperature profile between equally-spaced isothermal regions; Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K; and Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$).
+Example Sb1 is a simple uniform temperature and composition profile with soot radiation.
 Each case is presented alongside the line-by-line (LBL) data presented in the references.
@@
 \begin{table}
-    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2020}. All cases use $P=1$ atm and black walls.}
+    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2020}; Sb1 is from \cite{Solovjov_2001}. All cases use $P=1$ atm and black walls.}
     \label{t:examples}
@@
            &                                     & $y_{CO2}=1-y_{H2O}$                                   &         &                \\
+        Sb1& $T = 1000$                          & $y_{H2O} = 0.2$, $y_{CO2}=0.1$, $y_{CO}=0.03$         & 1       & cold, cold     \\
         \hline
@@
 Example S5 shows the sensitivity of the RCSLW model to the number of gases used.
-When $n$ is increased to eight the RCSLW model improves to show nearly perfect agreement with the LBL data in Example S2.
+The difference between $n=2$ and $n=8$ is very small for all examples shwon, except for Example S2.
+When $n$ is increased from four to eight for that example the RCSLW model improves to show nearly perfect agreement with the LBL data.
 In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain.
 In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.
+
+Figure~\ref{f:exSb1} shows the results from Example Sb1, which includes soot radiation.
+Results for three values of the soot volume fraction are shown.
+Both the WSGG and RCSLW models perform very well for each case.
+%
+\begin{figure}
+    \begin{center}
+        \includegraphics[width=5.5 in]{ex_Sb1.pdf}
+    \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
+    \label{f:exSb1}
+    \end{center}
+\end{figure}
+%
 

### 2020-12-30 manuscript/manuscript.tex
figure size to fit
adding cost comparison results using Isaacs code and plotting tools

@@
         Example S1 & Example S2 \\
-        \includegraphics[width=3 in]{ex_1.pdf} &
-        \includegraphics[width=3 in]{ex_2b.pdf} \\
+        \includegraphics[width=2.75 in]{ex_1.pdf} &
+        \includegraphics[width=2.75 in]{ex_2b.pdf} \\
         Example S3 & Example S4 \\
-        \includegraphics[width=3 in]{ex_3a.pdf} &
-        \includegraphics[width=3 in]{ex_4a.pdf} \\
+        \includegraphics[width=2.75 in]{ex_3a.pdf} &
+        \includegraphics[width=2.75 in]{ex_4a.pdf} \\
         Example S5 & Example B3 \\
-        \includegraphics[width=3 in]{ex_5b.pdf} &
-        \includegraphics[width=3 in]{ex_6.pdf}
+        \includegraphics[width=2.75 in]{ex_5b.pdf} &
+        \includegraphics[width=2.75 in]{ex_6.pdf}
     \end{tabular}
@@
 
-% TODO: do the cost comparison  <13-11-20, dol> %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Computational Cost} \label{s:cost}
+
+A comparison was made of the computational cost of the current models implemented.
+Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7.
+Figure~\ref{f:cost}a shows the cost to compute the gas properties $k$ and $a$.
+This was done by timing the C++ code execution to evaluate the gas properties one million times in a loop and then averaging the results.
+The figure shows times normalized by the time for the WSGG model, which required 8.0E-7~s.
+The costs of the models, relative to WSGG, is 0.098, 1.9, 4.9, 9.4, and 18, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively.
+The cost of the RCSLW model is very nearly proportional to the number of gray gases considered.
+%
+\begin{figure}
+    \begin{center}
+    \begin{tabular}{c c}
+        (a) & (b) \\
+        \includegraphics[width=2.75 in]{fig_getka_c++.pdf} &
+        \includegraphics[width=2.75 in]{fig_exS3_c++.pdf}
+    \end{tabular}
+    \caption{Computational cost to evaluate gas properties (a) and to run Example S3. Results are normalized by the cost of the WSSG model.}
+    \label{f:cost}
+    \end{center}
+\end{figure}
+%
+
+Figure~\ref{f:cost}b shows the cost to evaluate Example S3. 
+In this case the costs of the models, relative to WSGG, is approximately 0.75, 1.1, 1.4, 1.9, and 2.9, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively.
+Here, the WSGG model took 0.0079 s.
+In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead required in performing the calculations.
+In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.
+
+Cost comparisons were also attempted with Python, but it is difficult to get meaningful results when mixing Python and C++.
+In particular, the cost of a single evaluation of the gas properties is small end valuating the gas properties in a Python loop results in the loop appearing to dominate the computational cost.
+Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Fig.~\ref{f:cost} the cost only varied by about 4\%.
+The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version.
+It is possible that improvements in the Python speed are possible by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.
 

### 2020-12-30 manuscript/manuscript.tex
minor edits

@@
 Cost comparisons were also attempted with Python, but it is difficult to get meaningful results when mixing Python and C++.
-In particular, the cost of a single evaluation of the gas properties is small end valuating the gas properties in a Python loop results in the loop appearing to dominate the computational cost.
-Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Fig.~\ref{f:cost} the cost only varied by about 4\%.
+In particular, the cost of a single evaluation of the gas properties is small and evaluating the gas properties in a Python loop results in the loop appearing to dominate the computational cost.
+Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Fig.~\ref{f:cost} the cost only varied by about 4\%, indicating that the costs are dominated by the Python and not by the model calculations themselves.
 The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version.
-It is possible that improvements in the Python speed are possible by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.
+It is possible that improvements to the Python speed could be made by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.
 

### 2020-12-30 manuscript/manuscript.tex
dol implementing vbl edits, fixing a reference

@@
 The gas absorption spectrum is an extremely complex function consisting of millions of spectral lines (peaks) corresponding to quantum mechanical energy levels of the gas molecules.
-Direct solution of Eq.~\ref{e:RTE_general}, involves so-called line-by-line calculations that are computationally prohibitive for most practical configurations, and are used primarily for model validation.
+Direct solution of Eq.~\ref{e:RTE_general}, involves so-called line-by-line calculations that are computationally prohibitive for most practical configurations and are used primarily for model validation.
 Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model \cite{Hottel_1967,Modest_2013}.
-For instance, integrating Eq.~\ref{e:RTE_general} over fixed spectral ranges $\eta_j$ and assuming gray (spectrally uniform) properties in each region $j$, (that is, in each \emph{gray gas} $j$), gives
+For instance, integrating Eq.~\ref{e:RTE_general} over fixed spectral ranges $\eta_j$ and assuming gray (spectrally uniform) properties in each region $j$, (that is, in each gray gas $j$), gives
 %
@@
 %
-In the above, $I$ is a function of direction $\mathbf{s}$. The heat flux vector $\mathbf{q}$ is found by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere:
+Radiative intensity $I$ is a function of direction $\mathbf{s}$. The heat flux vector $\mathbf{q}$ is found by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere:
 %
@@
 
-The WSGG model was outlined in Sec.~\ref{s:models}.
+The WSGG model was introduced in Sec.~\ref{s:models}.
 RadLib implements the WSGG model presented by Bordbar et al.
@@
 It uses four gray gases and one transparent gas, and considers gaseous species \ce{CO2} and \ce{H2O}.
-This version of the WSGG model has the advantage over some others in that it allows for arbitrary \ce{CO2} and \ce{H2O} compositions, increasing its accuracy and flexibility.
+This version of the WSGG model is advantageous because it allows for arbitrary \ce{CO2} and \ce{H2O} compositions, increasing its accuracy and flexibility.
 Absorption coefficients are calculated by
@@
 In Bordbar et~al.
-(2020) \cite{Bordbar_2020} this range was extended to arbitrary $M_r$.
-This was done by interpolation of $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$.
-That is, for \ce{CO2}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=0.01$ and pure \ce{CO2}.
-For \ce{H2O}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=4$ and pure \ce{H2O}.
+(2020) \cite{Bordbar_2020} this range was extended to arbitrary $M_r$ by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$.
+That is, for \ce{CO2}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=0.01$ and pure \ce{CO2}; for \ce{H2O}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=4$ and pure \ce{H2O}.
 
@@
 
-%%%%% DOL original, with VBL suggested edits
-%  SLW models are similar to WSGG models, but instead of integrating within a sequential band of $\eta$ to define gray gas $j$, spectral integration is done over a set of (nonsquential) wavenumbers constituting a given band $j$ of absorption cross section $C_\eta$.
-%  %
-%  (The absorption coefficient is related to absorption cross section by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.)
-%  %
-%  Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}, (where $\tilde{C}$ denotes a cross section boundary between two bands/gases).
-%  %
-%  The SLW gases, then, are gray in a given band by construction, to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
-In contrast, in traditional WSGG approaches, the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
-
-%%%%% DOL restructuring paragraph based on VBL suggestions
 SLW models are similar to WSGG models, but SLW gases are gray in a given band by construction, whereas in traditional WSGG approaches the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
 %
-In SLW models, instead of integrating within a sequential band of $\eta$ (with highly variable $\kappa$) to define a gray gas $j$, as in other WSGG models, spectral integration is done over a set of (nonsequential) wavenumbers constituting a given band $j$ of absorption cross section $C_\eta$.
+Instead of integrating within a sequential band of $\eta$ (with highly variable $\kappa$) to define a gray gas $j$ as in other WSGG models, SLW models perform their spectral integration over a set of nonsequential wavenumbers constituting a given band $j$ of absorption cross sections $C_\eta$.
 %
-(The absorption coefficient is related simply to absorption cross section by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.)
+The absorption coefficient is related to the absorption cross section by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.
 %
-Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}, (where $\tilde{C}$ denotes a cross section boundary between two bands/gases).
+Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}, where $\tilde{C}$ denotes a cross section boundary between two bands/gases.
 %
-Hence, in SLW the gases in a given band are gray to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
+Hence, in SLW models, the gases in a given band are gray to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
 
@@
 The RCSLW model uses the notion of rank correlation to compute this variation in $C_j$ and $\tilde{C}_j$. 
-We proceed loosely following Solovjov et~al. \cite{Solovjov_2014}.
 Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$. These will have corresponding spectra $C_\eta(\eta,\BS{\phi}_1)$, and $C_\eta(\eta,\BS{\phi}_2)$.
@@
 %
-\begin{itemize}
+\begin{enumerate}
     \item A reference temperature is specified. This is taken to be the average temperature on the domain of interest in \cite{Solovjov_2001}.
@@
     \item $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature.
-\end{itemize}
+\end{enumerate}
 %
@@
 The gas weights $a_j$ are not changed.
-This model yeilds the expected behavior for the soot-only and gas-only limits.
+This model yeilds the expected behavior in the soot-only and gas-only limits.
 
 The soot model used in the WSGG model can be applied to the RCSLW model as well.
-However, the formulation of the RCSLW model allows for a spectral soot treatment in the same manner as for the gas species~\cite{Solovjov_2001}.
+However, the formulation of the RCSLW model allows for a spectral soot treatment in the same manner as the gas species~\cite{Solovjov_2001}.
 Calculation of the soot ALBDF is facilitated by the simple $\eta$ dependence of $\kappa_{s,\eta}$ in Eq.~\ref{e:soot1}.
@@
     \end{tabular}
-    \caption{Computational cost to evaluate gas properties (a) and to run Example S3. Results are normalized by the cost of the WSSG model.}
+    \caption{Computational cost to evaluate gas properties (a) and to run Example S3 (b). Results are normalized by the cost of the WSSG model.}
     \label{f:cost}
@@
 
-\begin{table}[!h]
+\begin{table}[!ht]
 \begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
@@
 \caption{Software metadata.}
-\label{} 
+\label{t:softmd} 
 \end{table}

### 2020-12-30 data/timing/c++/bkp_ex_S3_timer.cc
adding timing files

@@ -1,0 +1,192 @@
+#include <iostream>
+#include "rad_rcslw.h"
+#include "rad_wsgg.h"
+#include "rad_planck_mean.h"
+#include "rad.h"
+
+using namespace std;
+
+void parallel_planes(rad                  *RAD,
+                     const double         L,
+                     const int            ntheta,
+                     const double         P, 
+                     const vector<double> &T,
+                     const vector<double> &xH2O,
+                     const vector<double> &xCO2,
+                     const vector<double> &xCO,
+                     const vector<double> &xCH4,
+                     const vector<double> &fvsoot,
+                     vector<double>       &q,
+                     vector<double>       &Q,
+                     vector<double>       &x,
+                     vector<double>       &xQ,
+                     const bool           LzeroIbc=false
+                     );
+
+///////////////////////////////////////////////////////////////////////////////
+
+int main() {
+
+    //--------------------- parameters
+
+    double P      = 101325.0;
+    double L      = 1.0;
+    int    nGG    = 24;
+    int    ntheta = 101;
+    int    nx     = 1001;
+    double Twall  = 800;
+
+    int    nGGa   = nGG+1;
+
+    double xco2=0.0, xco=0.0, xh2o=0.12, xch4=0.0, fvs=0.0;
+
+    //---------------------
+
+    vector<double> xCO2(nx, xco2);
+    vector<double> xCO(nx, xco);
+    vector<double> xH2O(nx, xh2o);
+    vector<double> xCH4(nx, 0.0);
+    vector<double> fvsoot(nx, fvs);
+
+    vector<double> x(nx, 0.0);
+    vector<double> xQ;
+    vector<double> T(nx, Twall);
+
+    double dx = L/(nx-1);
+    x[0] = 0.0;
+    double Tavg = T[0];
+    double xH2O_avg = 0.0;
+    for(int i=1; i<nx; ++i){
[…]

### 2020-12-30 data/timing/c++/bkp_timer.cc

@@ -1,0 +1,145 @@
+#include "rad_planck_mean.h"
+#include "rad_wsgg.h"
+#include "rad_rcslw.h"
+#include <vector>
+#include <iostream>
+#include <iomanip>
+
+using namespace std;
+
+///////////////////////////////////////////////////////////////////////////////
+
+int main() {
+
+    //----------------- define parameters
+
+    double T      = 2000.0;    // K
+    double P      = 101325.0;  // atm
+    double xH2O   = 0.8;       // xH2O=0.2 is roughly stoich. CH4/air products
+    double xCO2   = 0.2;       // xCO2=0.1 is roughly stoich. CH4/air products
+    double xCO    = 0.;
+    double xCH4   = 0.;
+    double fvsoot = 0.;
+
+    vector<double> kabs_pm, kabs_wsgg, kabs_rcslw;
+    vector<double> awts_pm, awts_wsgg, awts_rcslw;
+
+    //----------------- create radiation objects
+
+    rad *planckmean = new rad_planck_mean();
+    rad *wsgg       = new rad_wsgg();
+    rad *rcslw      = new rad_rcslw(4, P, T, xH2O, xCO2, xCO, fvsoot);
+    rad *rc1        = new rad_rcslw(1, P, T, xH2O, xCO2, xCO, fvsoot);
+    rad *rc8        = new rad_rcslw(8, P, T, xH2O, xCO2, xCO, fvsoot);
+    rad *rc24       = new rad_rcslw(24, P, T, xH2O, xCO2, xCO, fvsoot);
+
+    //----------------- compute absorption coefficients and weights
+
+    // planckmean->get_k_a(T, P, xH2O, xCO2, xCO, xCH4, fvsoot, kabs_pm,    awts_pm);
+    // wsgg->get_k_a(      T, P, xH2O, xCO2, xCO, xCH4, fvsoot, kabs_wsgg,  awts_wsgg);
+    // rcslw->get_k_a(     T, P, xH2O, xCO2, xCO, xCH4, fvsoot, kabs_rcslw, awts_rcslw);
+
+    int n_sim = 100;
+    int skipped = 0;
+    clock_t c1, c2;
+    double d1, d2;
+    double time;
[…]

### 2020-12-30 data/timing/c++/ex_B3.cc

@@ -1,0 +1,96 @@
+#include <iostream>
+#include "rad_rcslw.h"
+#include "rad.h"
+#include <cmath>
+
+using namespace std;
+
+void parallel_planes(rad                  *RAD,
+                     const double         L,
+                     const int            ntheta,
+                     const double         P, 
+                     const vector<double> &T,
+                     const vector<double> &xH2O,
+                     const vector<double> &xCO2,
+                     const vector<double> &xCO,
+                     const vector<double> &xCH4,
+                     const vector<double> &fvsoot,
+                     vector<double>       &q,
+                     vector<double>       &Q,
+                     vector<double>       &x,
+                     vector<double>       &xQ,
+                     const bool           LzeroIbc=false
+                     );
+
+///////////////////////////////////////////////////////////////////////////////
+
+int main() {
+
+    //--------------------- parameters
+
+    double P      = 101325.0;
+    double L      = 1.0;
+    int    nGG    = 24;
+    int    ntheta = 101;
+    int    nx     = 1001;
+    double Twall  = 400;
+
+    int    nGGa   = nGG+1;
+
+    double xco2=0.0, xco=0.0, xh2o=0.0, xch4=0.0, fvs=0.0;
+
+    //---------------------
+
+    vector<double> xCO2(nx, xco2);
+    vector<double> xCO(nx, xco);
+    vector<double> xH2O(nx, xh2o);
+    vector<double> xCH4(nx, 0.0);
+    vector<double> fvsoot(nx, fvs);
+
+    vector<double> x(nx, 0.0);
+    vector<double> xQ;
+    vector<double> T(nx, Twall);
+
+    double dx = L/(nx-1);
+    x[0] = 0.0;
+    double Tavg = T[0];
+    double xH2O_avg = 0.0;
+    double xCO2_avg = 0.0;
+    for(int i=1; i<nx; ++i){
+        x[i] = x[i-1] + dx;
+        T[i] = 400 + 1400*pow(sin(M_PI*x[i]/L),2);
+        xH2O[i] = 1E-4 + (1.0-1E-4)*pow(sin(M_PI*x[i]/L),2);
+        xCO2[i] = 1.0-xH2O[i];
+        Tavg += T[i];
+        xH2O_avg += xH2O[i];
+        xCO2_avg += xCO2[i];
+    }
[…]

### 2020-12-30 data/timing/c++/ex_S3_timer.cc

@@ -1,0 +1,192 @@
+#include <iostream>
+#include "rad_rcslw.h"
+#include "rad_wsgg.h"
+#include "rad_planck_mean.h"
+#include "rad.h"
+
+using namespace std;
+
+void parallel_planes(rad                  *RAD,
+                     const double         L,
+                     const int            ntheta,
+                     const double         P, 
+                     const vector<double> &T,
+                     const vector<double> &xH2O,
+                     const vector<double> &xCO2,
+                     const vector<double> &xCO,
+                     const vector<double> &xCH4,
+                     const vector<double> &fvsoot,
+                     vector<double>       &q,
+                     vector<double>       &Q,
+                     vector<double>       &x,
+                     vector<double>       &xQ,
+                     const bool           LzeroIbc=false
+                     );
+
+///////////////////////////////////////////////////////////////////////////////
+
+int main() {
+
+    //--------------------- parameters
+
+    double P      = 101325.0;
+    double L      = 1.0;
+    int    nGG    = 24;
+    int    ntheta = 101;
+    int    nx     = 1001;
+    double Twall  = 800;
+
+    int    nGGa   = nGG+1;
+
+    double xco2=0.0, xco=0.0, xh2o=0.12, xch4=0.0, fvs=0.0;
+
+    //---------------------
+
+    vector<double> xCO2(nx, xco2);
+    vector<double> xCO(nx, xco);
+    vector<double> xH2O(nx, xh2o);
+    vector<double> xCH4(nx, 0.0);
+    vector<double> fvsoot(nx, fvs);
+
+    vector<double> x(nx, 0.0);
+    vector<double> xQ;
+    vector<double> T(nx, Twall);
+
+    double dx = L/(nx-1);
+    x[0] = 0.0;
+    double Tavg = T[0];
+    double xH2O_avg = 0.0;
+    for(int i=1; i<nx; ++i){
[…]

### 2020-12-30 data/timing/c++/make_examples.sh

@@ -1,0 +1,18 @@
+#!/bin/bash
+
+set -x
+
+include="../../installed/include"
+lib="../../installed/lib"
+
+#g++ -O3 -std=c++11 -I$include -L$lib simple_interface.cc -lradlib -o simple_interface.x; 
+#g++ -O3 -std=c++11 -I$include -L$lib ex_S1.cc parallel_planes.cc -lradlib -o ex_S1.x; 
+#g++ -O3 -std=c++11 -I$include -L$lib ex_S2.cc parallel_planes.cc -lradlib -o ex_S2.x; 
+#g++ -O3 -std=c++11 -I$include -L$lib ex_S3.cc parallel_planes.cc -lradlib -o ex_S3.x; 
+#g++ -O3 -std=c++11 -I$include -L$lib ex_S4.cc parallel_planes.cc -lradlib -o ex_S4.x; 
+#g++ -O3 -std=c++11 -I$include -L$lib ex_S5.cc parallel_planes.cc -lradlib -o ex_S5.x; 
+#g++ -O3 -std=c++11 -I$include -L$lib ex_B3.cc parallel_planes.cc -lradlib -o ex_B3.x; 
+#g++ -O3 -std=c++11 -I$include -L$lib ex_Sb1.cc parallel_planes.cc -lradlib -o ex_Sb1.x; 
+g++ -O3 -std=c++11 -I$include -L$lib timer.cc parallel_planes.cc -lradlib -o timer.x; 
+g++ -O3 -std=c++11 -I$include -L$lib ex_S3_timer.cc parallel_planes.cc -lradlib -o ex_S3_timer.x; 
+

### 2020-12-30 data/timing/c++/make_timer.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+set -x
+
+include="../../installed/include"
+lib="../../installed/lib"
+
+g++ -O3 -std=c++11 -I$include -L$lib timer.cc parallel_planes.cc -lradlib -o timer.x; 
+g++ -O3 -std=c++11 -I$include -L$lib ex_S3_timer.cc parallel_planes.cc -lradlib -o ex_S3_timer.x; 
+

### 2020-12-30 data/timing/c++/parallel_planes.cc

@@ -1,0 +1,165 @@
+#include <cmath>          // M_PI, sin, cos
+#include "rad.h"
+
+#include <iostream>   //doldb
+
+using namespace std;
+
+////////////////////////////////////////////////////////////////////////////////
+
+/** Compute intensity at each grid point for a given angle.
+ *  Solution using an implicit trapazoid method.
+ *  @param x     \input vector of grid points
+ *  @param theta \input angle measured: grid between plates aligned with theta=0
+ *  @param T     \input vector of temperatures (K)
+ *  @param kabs  \input 2D vector of absorption coefficients for each gas [igrid, igas]
+ *  @param awts  \input 2D vector of weights for each gas [igrid, igas]
+ *  @param Ilo   \input vector of gas intensities on the lower plane.
+ *  @param Ihi   \input vector of gas intensities on the upper plane.
+ *  @param I     \ouput vector of vector of gas intensities in direction theta [igrid, igas]
+ */
+
+void I_IT(const vector<double> &x, 
+          const double theta, 
+          const vector<double> &T,
+          const vector<vector<double>> &kabs,
+          const vector<vector<double>> &awts,
+          const vector<double> &Ilo, 
+          const vector<double> &Ihi, 
+          vector<vector<double>> &I){
+
+    int n     = x.size();
+    int nGGa  = I[0].size();
+    double dx;
+
+    double Ib1, Ib2;
+    double mu = abs(cos(theta));
+
+    if(theta <= M_PI/2){
+        I[0] = Ilo;
+        for(int i=0; i<n-1; ++i){
+            Ib1 = rad::sigma/M_PI*pow(T[i+1],4.0);
+            Ib2 = rad::sigma/M_PI*pow(T[i],4.0);
+            dx  = x[i+1] - x[i];
+            //I[i+1][0] = I[0][0];          // do the clear gas intensity
+            //for(int j=1; j<nGGa; ++j)     // j=1 skips the clear gas, done in previous line
+            for(int j=0; j<nGGa; ++j)       // OR, just do all (needed for Planck mean)
+                I[i+1][j] = (I[i][j] + dx/mu*0.5*(kabs[i+1][j]*awts[i+1][j]*Ib1 + kabs[i][j]*(awts[i][j]*Ib2 - I[i][j]))) /
+                            (1.0+dx/mu*0.5*kabs[i+1][j]);
+        }
+    }
+    else{
+        I[n-1] = Ihi;
[…]

### 2020-12-30 data/timing/c++/timer.cc

@@ -1,0 +1,153 @@
+#include "rad_planck_mean.h"
+#include "rad_wsgg.h"
+#include "rad_rcslw.h"
+#include <vector>
+#include <iostream>
+#include <iomanip>
+
+using namespace std;
+
+///////////////////////////////////////////////////////////////////////////////
+
+int main() {
+
+    //----------------- define parameters
+
+    double T      = 2000.0;    // K
+    double P      = 101325.0;  // atm
+    double xH2O   = 0.8;       // xH2O=0.2 is roughly stoich. CH4/air products
+    double xCO2   = 0.2;       // xCO2=0.1 is roughly stoich. CH4/air products
+    double xCO    = 0.;
+    double xCH4   = 0.;
+    double fvsoot = 0.;
+
+    vector<double> kabs_pm, kabs_wsgg, kabs_rcslw;
+    vector<double> awts_pm, awts_wsgg, awts_rcslw;
+
+    //----------------- create radiation objects
+
+    rad *planckmean = new rad_planck_mean();
+    rad *wsgg       = new rad_wsgg();
+    rad *rcslw      = new rad_rcslw(4, P, T, xH2O, xCO2, xCO, fvsoot);
+    rad *rc1        = new rad_rcslw(1, P, T, xH2O, xCO2, xCO, fvsoot);
+    rad *rc8        = new rad_rcslw(8, P, T, xH2O, xCO2, xCO, fvsoot);
+    rad *rc2        = new rad_rcslw(2, P, T, xH2O, xCO2, xCO, fvsoot);
+
+    //----------------- compute absorption coefficients and weights
+
+    // planckmean->get_k_a(T, P, xH2O, xCO2, xCO, xCH4, fvsoot, kabs_pm,    awts_pm);
+    // wsgg->get_k_a(      T, P, xH2O, xCO2, xCO, xCH4, fvsoot, kabs_wsgg,  awts_wsgg);
+    // rcslw->get_k_a(     T, P, xH2O, xCO2, xCO, xCH4, fvsoot, kabs_rcslw, awts_rcslw);
+
+    int n_sim = 100;
+    int skipped = 0;
+    clock_t c1, c2;
+    double d1, d2;
+    double time;
[…]

### 2020-12-30 data/timing/python/cyparallel_planes.pyx

@@ -1,0 +1,139 @@
+
+import  numpy as np
+cimport numpy as np
+
+ctypedef np.int_t INT
+ctypedef np.float64_t FLOAT
+
+cdef FLOAT sigma = 5.670367E-8     # Stephan-Boltzmann constant
+
+cdef I_IT(np.ndarray[FLOAT, ndim=1] x,
+          FLOAT                     theta, 
+          np.ndarray[FLOAT, ndim=1] T,
+          np.ndarray[FLOAT, ndim=2] kabs,
+          np.ndarray[FLOAT, ndim=2] awts,
+          np.ndarray[FLOAT, ndim=1] Ilo,
+          np.ndarray[FLOAT, ndim=1] Ihi):
+    '''
+    Compute intensity at each grid point for a given angle.
+    Solution using an implicit trapazoid method.
+    @param x     \input vector of grid points
+    @param theta \input angle measured: grid between plates aligned with theta=0
+    @param T     \input vector of temperatures (K)
+    @param kabs  \input 2D vector of absorption coefficients for each gas [igrid, igas]
+    @param awts  \input 2D vector of weights for each gas [igrid, igas]
+    @param Ilo   \input vector of gas intensities on the lower plane.
+    @param Ihi   \input vector of gas intensities on the upper plane.
+    @param I     \ouput vector of vector of gas intensities in direction theta [igrid, igas]
+    '''
+
+    cdef INT n     = len(x)
+    cdef INT nGGa  = len(kabs[0,:])
+
+    cdef np.ndarray[FLOAT, ndim=2] I = np.empty((n, nGGa), dtype=np.float64)
+
+    cdef FLOAT Ib1, Ib2, dx
+    cdef FLOAT mu = np.abs(np.cos(theta))
+
+    cdef int i,j
+
+    if(theta <= np.pi/2):
+        I[0] = Ilo
+        for i in range(n-1):     
+            Ib1 = sigma/np.pi*T[i+1]**4
+            Ib2 = sigma/np.pi*T[i]**4
+            dx  = x[i+1] - x[i]
+            #I[i+1,0] = I[0,0]           # do the clear gas intensity
+            #for j in range(1,nGGa):
+            for j in range(0,nGGa):      # OR, just do all (needed for Planck mean)     
[…]

### 2020-12-30 data/timing/python/ex_B3.py

@@ -1,0 +1,76 @@
+def ex_B3(method, nGG=4):
+
+    import numpy as np
+    
+    from cyparallel_planes import parallel_planes
+    #from parallel_planes import parallel_planes
+    
+    from pyrad import pyrad_planck_mean as rad_planck_mean
+    from pyrad import pyrad_wsgg        as rad_wsgg
+    from pyrad import pyrad_rcslw       as rad_rcslw
+    
+    ################################################################################
+    
+    #--------------------- parameters
+
+    nGGa = nGG + 1
+    
+    P      = 101325.0
+    L      = 1.0
+    ntheta = 101
+    nx     = 1001
+    Twall  = 400.0
+    
+    xco2=0.0; xco=0.0; xh2o=0.0; xch4=0.0; fvs=0.0
+    
+    #---------------------
+    
+    xCO2   = np.full(nx, xco2, dtype=np.float64)
+    xCO    = np.full(nx, xco,  dtype=np.float64)
+    xH2O   = np.full(nx, xh2o, dtype=np.float64)
+    xCH4   = np.full(nx, xch4, dtype=np.float64)
+    fvsoot = np.full(nx, fvs,  dtype=np.float64)
+    
+    x = np.zeros(nx)
+    T = np.full(nx,Twall, dtype=np.float64)
+    
+    x = np.linspace(0,L,nx)
+    for i in range(nx):
+        T[i]    = 400.0 + 1400.0*   np.sin(np.pi*x[i]/L)**2
+        xH2O[i] = 1E-4 + (1.0-1E-4)*np.sin(np.pi*x[i]/L)**2
+        xCO2[i] = 1.0-xH2O[i]
+    xH2O_avg = np.average(xH2O)
+    xCO2_avg = 1.0-xH2O_avg
+    T_avg    = np.average(T)
+    
+    if method=='rcslw':
+        rad = rad_rcslw(nGG, P, T_avg, xH2O_avg, xCO2_avg, xco, fvs)
+    elif method=='wsgg':
+        rad = rad_wsgg()
+    elif method=='planckmean':
+        rad = rad_planck_mean()
+    else:
+        raise ValueError('unknown radiation method')
+    
+    #------------------- get q, Q
+    
+    x, xQ, q, Q = parallel_planes(rad, L, ntheta, P, T, xH2O, xCO2, xCO, xCH4, fvsoot)
+    
+    print("# x (m), Q (kW/m3)")
[…]

### 2020-12-30 data/timing/python/ex_S1.py

@@ -1,0 +1,88 @@
+def ex_S1(method, nGG=24):
+    
+    import numpy as np
+    import time
+    
+    from cyparallel_planes import parallel_planes
+    #from parallel_planes import parallel_planes
+    
+    from pyrad import pyrad_planck_mean as rad_planck_mean
+    from pyrad import pyrad_wsgg        as rad_wsgg
+    from pyrad import pyrad_rcslw       as rad_rcslw
+    
+    sigma = 5.670367E-8     # Stephan-Boltzmann constant
+    
+    ################################################################################
+    
+    #--------------------- parameters
+    
+    t0 = time.time()
+    
+    P      = 101325.0
+    Thot   = 2000
+    Tcold  = 300
+    Lhot   = 0.5
+    ntheta = 101
+    nxh    = 1001    # for Lcold=0 changes below to keep dx roughly constant
+    
+    Lcold  = np.array([0, 0.01, 0.025, 0.05, 0.1, 0.2, 0.3, 0.4, 0.5, 0.75, 1.0, 1.5, 2.0])
+    
+    nGGa   = nGG+1
+    
+    xco2=0.1; xco=0.0; xh2o=0.2; xch4=0.0; fvs=0.0
+    
+    #---------------------
+    
+    print("# Lcold (m),     q(L)/σThot^4")
+    
+    qsigT4 = np.empty(len(Lcold))
+    
+    for iLcold in range(len(Lcold)):
+    
+        L  = Lcold[iLcold] + Lhot
+    
+        Tavg = (Thot*0.5+Tcold*Lcold[iLcold])/L
+    
+        nx = int(nxh*L/Lhot)
+    
+        xCO2   = np.full(nx, xco2, dtype=np.float64)
+        xCO    = np.full(nx, xco,  dtype=np.float64)
+        xH2O   = np.full(nx, xh2o, dtype=np.float64)
+        xCH4   = np.full(nx, xch4, dtype=np.float64)
+        fvsoot = np.full(nx, fvs,  dtype=np.float64)
+    
+        x = np.zeros(nx)
+        dx = L/(nx-1)
+        T = np.full(nx, Thot, dtype=np.float64)
+        for i in range(1,nx):        # mimic c++; pythonic gives different grid/T due to roundoff
+            x[i] = x[i-1] + dx
+            T[i] = Thot if x[i] <= Lhot else Tcold
+    
+        if method=='rcslw':
[…]

### 2020-12-30 data/timing/python/ex_S2.py

@@ -1,0 +1,84 @@
+def ex_S2(method, nGG=24):
+
+    import numpy as np
+    
+    from cyparallel_planes import parallel_planes
+    #from parallel_planes import parallel_planes
+    
+    from pyrad import pyrad_planck_mean as rad_planck_mean
+    from pyrad import pyrad_wsgg        as rad_wsgg
+    from pyrad import pyrad_rcslw       as rad_rcslw
+    
+    sigma = 5.670367E-8     # Stephan-Boltzmann constant
+    
+    ################################################################################
+    
+    #--------------------- parameters
+    
+    TT     = 1000.0
+    P      = 101325.0
+    xco2_1 = 0.4
+    xco2_2 = 0.1
+    Lhot   = 0.5
+    ntheta = 101
+    nxh    = 1001    # for Lcold=0 changes below to keep dx roughly constant
+    
+    Lcold  = np.array([0, 0.01, 0.025, 0.05, 0.1, 0.2, 0.3, 0.4, 0.5, 0.75, 1.0, 1.5, 2.0])
+    
+    nGGa   = nGG+1
+    
+    xco = 0.0; xh2o=0.0; xch4=0.0; fvs = 0.0
+    
+    #---------------------
+    
+    print("# Lcold (m),     q(L)/σT^4")
+    
+    qsigT4 = np.empty(len(Lcold))
+    
+    for iLcold in range(len(Lcold)):
+    
+        L  = Lcold[iLcold] + Lhot
+    
+        xco2_avg = (xco2_1*0.5+xco2_2*Lcold[iLcold])/L
+    
+        nx = int(nxh*L/Lhot)
+    
+        xCO2   = np.full(nx, xco2_1, dtype=np.float64)
+        xCO    = np.full(nx, xco,    dtype=np.float64)
+        xH2O   = np.full(nx, xh2o,   dtype=np.float64)
+        xCH4   = np.full(nx, xch4,   dtype=np.float64)
+        fvsoot = np.full(nx, fvs,    dtype=np.float64)
+    
+        x = np.zeros(nx)
+        dx = L/(nx-1)
+        T = np.full(nx, TT, dtype=np.float64)
+        for i in range(1,nx):        # mimic c++; pythonic gives different grid/T due to roundoff
+            x[i] = x[i-1] + dx
+            xCO2[i] = xco2_1 if x[i] <= Lhot else xco2_2
+    
+        if method=='rcslw':
[…]

### 2020-12-30 data/timing/python/ex_S3.py

@@ -1,0 +1,80 @@
+def ex_S3(method, nGG=24):
+
+    import numpy as np
+    
+    from cyparallel_planes import parallel_planes
+    #from parallel_planes import parallel_planes
+    
+    from pyrad import pyrad_planck_mean as rad_planck_mean
+    from pyrad import pyrad_wsgg        as rad_wsgg
+    from pyrad import pyrad_rcslw       as rad_rcslw
+    
+    ################################################################################
+    
+    #--------------------- parameters
+    
+    P      = 101325.0
+    L      = 1.0
+    ntheta = 101
+    nx     = 1001
+    Twall  = 800.0
+    
+    nGGa   = nGG+1
+    
+    xco2=0.0; xco=0.0; xh2o=0.12; xch4=0.0; fvs=0.0
+    
+    #---------------------
+    
+    xCO2   = np.full(nx, xco2, dtype=np.float64)
+    xCO    = np.full(nx, xco,  dtype=np.float64)
+    xH2O   = np.full(nx, xh2o, dtype=np.float64)
+    xCH4   = np.full(nx, xch4, dtype=np.float64)
+    fvsoot = np.full(nx, fvs,  dtype=np.float64)
+    
+    x = np.zeros(nx)
+    T = np.full(nx,Twall, dtype=np.float64)
+    
+    dx = L/(nx-1)
+    x[0] = 0.0
+    Tavg = T[0]
+    xH2O_avg = 0.0
+    for i in range(1,nx):
+        x[i] = x[i-1] + dx
+        T[i] = 4000*x[i]*(L-x[i])/L/L + Twall
+        xH2O[i] = 0.8*x[i]*(L-x[i])/L/L + xh2o
+        Tavg += T[i]
+        xH2O_avg += xH2O[i]
+    Tavg     /= nx
+    xH2O_avg /= nx
+    
+    if method=='rcslw':
+        rad = rad_rcslw(nGG, P, Tavg, xH2O_avg, xco2, xco, fvs)
+    elif method=='wsgg':
+        rad = rad_wsgg()
+    elif method=='planckmean':
+        rad = rad_planck_mean()
+    else:
+        raise ValueError('unknown radiation method')
+    
+    #------------------- get q, Q
+    
+    x, xQ, q, Q = parallel_planes(rad, L, ntheta, P, T, xH2O, xCO2, xCO, xCH4, fvsoot)
+    
+    print("# x (m), Q (kW/m3)")
+    for i in range(len(xQ)):
[…]

### 2020-12-30 data/timing/python/ex_S3_timer.py

@@ -1,0 +1,89 @@
+def ex_S3(method, nGG=24):
+
+    import numpy as np
+    import time
+    
+    from cyparallel_planes import parallel_planes
+    #from parallel_planes import parallel_planes
+    
+    from pyrad import pyrad_planck_mean as rad_planck_mean
+    from pyrad import pyrad_wsgg        as rad_wsgg
+    from pyrad import pyrad_rcslw       as rad_rcslw
+    
+    ################################################################################
+    
+    #--------------------- parameters
+    
+    P      = 101325.0
+    L      = 1.0
+    ntheta = 101
+    nx     = 1001
+    Twall  = 800.0
+    
+    nGGa   = nGG+1
+    
+    xco2=0.0; xco=0.0; xh2o=0.12; xch4=0.0; fvs=0.0
+    
+    #---------------------
+    
+    xCO2   = np.full(nx, xco2, dtype=np.float64)
+    xCO    = np.full(nx, xco,  dtype=np.float64)
+    xH2O   = np.full(nx, xh2o, dtype=np.float64)
+    xCH4   = np.full(nx, xch4, dtype=np.float64)
+    fvsoot = np.full(nx, fvs,  dtype=np.float64)
+    
+    x = np.zeros(nx)
+    T = np.full(nx,Twall, dtype=np.float64)
+    
+    dx = L/(nx-1)
+    x[0] = 0.0
+    Tavg = T[0]
+    xH2O_avg = 0.0
+    for i in range(1,nx):
+        x[i] = x[i-1] + dx
+        T[i] = 4000*x[i]*(L-x[i])/L/L + Twall
+        xH2O[i] = 0.8*x[i]*(L-x[i])/L/L + xh2o
+        Tavg += T[i]
+        xH2O_avg += xH2O[i]
+    Tavg     /= nx
+    xH2O_avg /= nx
+
+    if method=='rcslw':
+        rad = rad_rcslw(nGG, P, Tavg, xH2O_avg, xco2, xco, fvs)
+    elif method=='wsgg':
+        rad = rad_wsgg()
+    elif method=='planckmean':
+        rad = rad_planck_mean()
+    else:
+        raise ValueError('unknown radiation method')
+    
+    #------------------- get q, Q
+    
+    t1 = time.time()
+    n_sim = 1 #20
+    for i in range(n_sim):
+        x, xQ, q, Q = parallel_planes(rad, L, ntheta, P, T, xH2O, xCO2, xCO, xCH4, fvsoot)
[…]

### 2020-12-30 data/timing/python/ex_S4.py

@@ -1,0 +1,83 @@
+def ex_S4(method, nGG=24):
+
+    import numpy as np
+    
+    from cyparallel_planes import parallel_planes
+    #from parallel_planes import parallel_planes
+    
+    from pyrad import pyrad_planck_mean as rad_planck_mean
+    from pyrad import pyrad_wsgg        as rad_wsgg
+    from pyrad import pyrad_rcslw       as rad_rcslw
+    
+    ################################################################################
+    
+    #--------------------- parameters
+    
+    P      = 101325.0
+    L      = 0.3
+    ntheta = 101
+    nx     = 1001
+    Twall  = 500.0
+    Tmax   = 2500.0
+    H      = 0.1
+    
+    nGGa   = nGG+1
+    
+    xco2=0.0; xco=0.0; xh2o=0.1; xch4=0.0; fvs=0.0
+    
+    #---------------------
+    
+    xCO2   = np.full(nx, xco2, dtype=np.float64)
+    xCO    = np.full(nx, xco,  dtype=np.float64)
+    xH2O   = np.full(nx, xh2o, dtype=np.float64)
+    xCH4   = np.full(nx, xch4, dtype=np.float64)
+    fvsoot = np.full(nx, fvs,  dtype=np.float64)
+    
+    x = np.zeros(nx)
+    T = np.full(nx,Twall, dtype=np.float64)
+    
+    dx = L/(nx-1)
+    x[0] = 0.0
+    Tavg = T[0]
+    for i in range(1,nx):
+        x[i] = x[i-1] + dx
+        if x[i] <= L/2-H/2 or x[i] >= L/2+H/2:
+            T[i] = Twall
+        elif x[i] < L/2:
+            T[i] = Twall + (Tmax-Twall)/(L/2-(L/2-H/2))*(x[i]-(L/2-H/2))
+        else:
+            T[i] = Tmax + (Twall-Tmax)/((L/2+H/2)-L/2)*(x[i]-L/2)
+        Tavg += T[i]
+    Tavg /= nx
+    
+    if method=='rcslw':
+        #rad = rad_rcslw(nGG, P, Tmax, xh2o, xco2, xco, fvs)  # CHANGE: use T=Tmax or T=Tavg for plot
+        rad = rad_rcslw(nGG, P, Tavg, xh2o, xco2, xco, fvs)  # CHANGE: use T=Tmax or T=Tavg for plot
+    elif method=='wsgg':
+        rad = rad_wsgg()
[…]

### 2020-12-30 data/timing/python/ex_S5.py

@@ -1,0 +1,77 @@
+def ex_S5(method, nGG=24, use_Tmax=False):
+
+    import numpy as np
+    
+    from cyparallel_planes import parallel_planes
+    #from parallel_planes import parallel_planes
+    
+    from pyrad import pyrad_planck_mean as rad_planck_mean
+    from pyrad import pyrad_wsgg        as rad_wsgg
+    from pyrad import pyrad_rcslw       as rad_rcslw
+    
+    ################################################################################
+
+
+    #--------------------- parameters
+    
+    P      = 101325.0
+    L      = 2.0
+    ntheta = 101
+    nx     = 1001
+    T0     = 1500.0
+    TL     = 500.0
+    
+    nGGa   = nGG+1
+    
+    TT = 1500; xco2=0.0; xco=0.0; xh2o=0.1; fvs=0.0
+    
+    #---------------------
+    
+    xCO2   = np.full(nx, xco2, dtype=np.float64)
+    xCO    = np.full(nx, xco,  dtype=np.float64)
+    xH2O   = np.full(nx, xh2o, dtype=np.float64)
+    xCH4   = np.full(nx, 0.0,  dtype=np.float64)
+    fvsoot = np.full(nx, fvs,  dtype=np.float64)
+    
+    x = np.zeros(nx)
+    T = np.full(nx,T0, dtype=np.float64)
+    
+    dx = L/(nx-1)
+    x[0] = 0.0
+    Tavg = T[0]
+    for i in range(1,nx):
+        x[i] = x[i-1] + dx
+        T[i] = 1000.0 + 500*np.cos(np.pi*x[i]/L)
+        Tavg += T[i]
+    Tavg /= nx
+    
+    if method=='rcslw':
+        rad = rad_rcslw(nGG, P, TT if use_Tmax else Tavg, xh2o, xco2, xco, fvs)     # TT gives better results than Tavg
+    elif method=='wsgg':
+        rad = rad_wsgg()
+    elif method=='planckmean':
+        rad = rad_planck_mean()
+    else:
+        raise ValueError('unknown radiation method')
+    
+    #------------------- get q, Q
+    
+    x, xQ, q, Q = parallel_planes(rad, L, ntheta, P, T, xH2O, xCO2, xCO, xCH4, fvsoot)
+    
+    print("# x (m), Q (kW/m3)")
+    for i in range(len(xQ)):
[…]

### 2020-12-30 data/timing/python/get_pythonpath_command.py

@@ -1,0 +1,14 @@
+import re
+import glob
+
+p = glob.glob('/Users/ugrad/codes/radlib/installed/lib/py*', recursive=False)[0]
+
+p = re.search(r'python[0-9].[0-9]$', p)
+p = p.group()
+
+p = '/Users/ugrad/codes/radlib/installed/lib/'+p+'/site-packages'
+
+print("\n\n*********************** Installation complete *************************")
+print("   To use the Python interface, update your PYTHONPATH environment variable:")
+print("   For example, on Linux/MAC Put the following in your .bashrc file:")
+print(f'\n     export PYTHONPATH="{p}:$PYTHONPATH"')

### 2020-12-30 data/timing/python/parallel_planes.py

@@ -1,0 +1,131 @@
+################################################################################
+
+import numpy as np
+from typing import Tuple, Any
+from nptyping import NDArray
+
+sigma = 5.670367E-8     # Stephan-Boltzmann constant
+
+def I_IT(x:     NDArray[Any],
+         theta: float, 
+         T:     NDArray[Any],
+         kabs:  NDArray[Any,Any],
+         awts:  NDArray[Any,Any],
+         Ilo:   NDArray[Any],
+         Ihi:   NDArray[Any]) -> NDArray[Any,Any]:
+    '''
+    Compute intensity at each grid point for a given angle.
+    Solution using an implicit trapazoid method.
+    @param x     \input vector of grid points
+    @param theta \input angle measured: grid between plates aligned with theta=0
+    @param T     \input vector of temperatures (K)
+    @param kabs  \input 2D vector of absorption coefficients for each gas [igrid, igas]
+    @param awts  \input 2D vector of weights for each gas [igrid, igas]
+    @param Ilo   \input vector of gas intensities on the lower plane.
+    @param Ihi   \input vector of gas intensities on the upper plane.
+    @param I     \ouput vector of vector of gas intensities in direction theta [igrid, igas]
+    '''
+
+    n     = len(x)
+    nGGa  = len(kabs[0,:])
+
+    mu = np.abs(np.cos(theta))
+
+    I = np.empty((n, nGGa))
+
+    if(theta <= np.pi/2):
+        I[0] = Ilo
+        for i in range(n-1):     
+            Ib1 = sigma/np.pi*T[i+1]**4
+            Ib2 = sigma/np.pi*T[i]**4
+            dx  = x[i+1] - x[i]
+            #I[i+1,0] = I[0,0]           # do the clear gas intensity
+            #for j in range(1,nGGa):     # j=1 skips the clear gas, done in previous line
+            for j in range(0,nGGa):      # OR, just do all (needed for Planck mean)     
+                I[i+1,j] = (I[i,j] + dx/mu*0.5*(kabs[i+1,j]*awts[i+1,j]*Ib1 + kabs[i,j]*(awts[i,j]*Ib2 - I[i,j]))) / (1.0+dx/mu*0.5*kabs[i+1,j])
+    else:
+        I[n-1] = Ihi
+        for i in range(n-1,0,-1):
+            Ib1 = sigma/np.pi*T[i-1]**4
+            Ib2 = sigma/np.pi*T[i]**4
+            dx  = x[i] - x[i-1]
[…]

### 2020-12-30 data/timing/python/setup.py

@@ -1,0 +1,9 @@
+from setuptools import setup
+from Cython.Build import cythonize
+import numpy as np
+
+setup(
+    ext_modules = cythonize("/Users/ugrad/codes/radlib/examples/python/cyparallel_planes.pyx", language_level="3", annotate=False),
+    include_dirs=[np.get_include()]
+)
+

### 2020-12-30 data/timing/python/simple_interface.py

@@ -1,0 +1,69 @@
+import numpy as np
+import sys
+
+sys.path.append('/Users/dol4/codes/radlib/installed/lib/python3.8/site-packages')
+
+from pyrad import pyrad_planck_mean as rad_planck_mean
+from pyrad import pyrad_wsgg        as rad_wsgg
+from pyrad import pyrad_rcslw       as rad_rcslw
+
+#--------------------------------------------------------------------------------
+
+#----------------- define parameters
+
+T      = 2000.0     # K
+P      = 101325.0   # atm
+xH2O   = 0.8        # xH2O=0.2 is roughly stoich. CH4/air products
+xCO2   = 0.2        # xCO2=0.1 is roughly stoich. CH4/air products
+xCO    = 0.0
+xCH4   = 0.0
+fvsoot = 0.0
+
+#----------------- create radiation objects
+
+planckmean = rad_planck_mean()
+wsgg       = rad_wsgg()
+rcslw      = rad_rcslw(4, P, T, xH2O, xCO2, xCO, fvsoot)
+
+#----------------- compute absorption coefficients and weights
+
+kabs_pm,    awts_pm     = planckmean.get_k_a(T, P, xH2O, xCO2, xCO, xCH4, fvsoot)
+kabs_wsgg,  awts_wsgg   = wsgg.get_k_a(      T, P, xH2O, xCO2, xCO, xCH4, fvsoot)
+kabs_rcslw, awts_rcslw  = rcslw.get_k_a(     T, P, xH2O, xCO2, xCO, xCH4, fvsoot)
+
+#----------------- output results
+
+print(f"---------------------------")
+print(f"T (K)  = {T:.3f}")
+print(f"P (Pa) = {P:.3f}")
+print(f"xH2O   = {xH2O:.3f}")
+print(f"xCO2   = {xCO2:.3f}")
+print(f"xCO    = {xCO:.3f}")
+print(f"xCH4   = {xCH4:.3f}")
+
+print(f"---------------------------")
+print("Planck Mean:")
+print(f"   kabs (1/m) = ", end='')
+for i in range(len(kabs_pm)):
+    print(f"{kabs_pm[i]:12.3e}", end='\n' if i==len(kabs_pm)-1 else ',')  
+print(f"   awts       = ", end='')
+for i in range(len(awts_pm)):
+    print(f"{awts_pm[i]:12.3e}", end='\n' if i==len(awts_pm)-1 else ',')  
+
[…]

### 2020-12-30 data/timing/python/timer.py

@@ -1,0 +1,75 @@
+import numpy as np
+import time
+import sys
+
+from pyrad import pyrad_planck_mean as rad_planck_mean
+from pyrad import pyrad_wsgg        as rad_wsgg
+from pyrad import pyrad_rcslw       as rad_rcslw
+
+#----------------- define parameters
+
+T      = 2000.0     # K
+P      = 101325.0   # atm
+xH2O   = 0.8        # xH2O=0.2 is roughly stoich. CH4/air products
+xCO2   = 0.2        # xCO2=0.1 is roughly stoich. CH4/air products
+xCO    = 0.0
+xCH4   = 0.0
+fvsoot = 0.0
+
+#----------------- create radiation objects
+
+planckmean = rad_planck_mean()
+wsgg       = rad_wsgg()
+rcslw_comp      = rad_rcslw(4, P, T, xH2O, xCO2, xCO, fvsoot)
+
+n_upper = 24
+rc_many = [rad_rcslw(i, P, T, xH2O, xCO2, xCO, fvsoot) for i in range(1, 1+n_upper)]
+
+
+n_sim = 10000
+pm_list = []
+for i in range(n_sim):
+    t1 = time.time()
+    kabs_pm,    awts_pm     = planckmean.get_k_a(T, P, xH2O, xCO2, xCO, xCH4, fvsoot)
+    t2 = time.time()
+    pm_list.append(t2-t1)
+# print(t_list)
+pm_tot = np.sum(pm_list)
+print("pm", pm_tot)
+print(n_sim, pm_tot/n_sim)
+
+wsgg_list = []
+for i in range(n_sim):
+    t1 = time.time()
+    kabs_wsgg,    awts_wsgg     = wsgg.get_k_a(T, P, xH2O, xCO2, xCO, xCH4, fvsoot)
+    t2 = time.time()
+    wsgg_list.append(t2-t1)
+# print(t_list)
+wsgg_tot = np.sum(wsgg_list)
+print("wsgg", wsgg_tot)
+print(n_sim, wsgg_tot/n_sim)
+
+rc_list = []
+for i in range(n_sim):
+    t1 = time.time()
+    kabs_rc,    awts_rc     = rcslw_comp.get_k_a(T, P, xH2O, xCO2, xCO, xCH4, fvsoot)
+    t2 = time.time()
+    rc_list.append(t2-t1)
+# print(t_list)
+rc_tot = np.sum(rc_list)
[…]

### 2020-12-31 manuscript/manuscript.tex
added conclusion and abstract

@@
 \begin{abstract}
-%% Text of abstract 
-Ca. 100 words
+RadLib is a modular C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations.
+RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and multiple interface options (C++ and Python) permit convenient expansion to additional models.
+Several example cases illustrate the use of the models with a simple ray-tracing solver and compare them in terms of accuracy and computational cost relative to line-by-line solutions.
+RadLib provides researchers with convenient access to radiation property models and a proven framework for further development.
 \end{abstract}
@@
 %
-
 The examples are provided with the RadLib code and implemented in both C++ and Python.
@@
 
-Set out the conclusion of this original software publication.
+RadLib is a C++ library of radiation property models developed to address the complexity and difficulty inherent in implementing radiative property models in CFD simulations.
+At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and multiple interface options permit convenient expansion to additional property models.
+To that end, the basic structure and use of the RadLib library has been laid out.
+In addition, the RadLib package includes example cases in several variations of a parallel planes geometry using a simple ray tracing solver to illustrate the use of the three radiation property models.
+In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy, but, under the appropriate conditions, the PM and WSGG models can also perform well and boast lower computational costs than the RCSLW model.
+As a whole, RadLib provides a convenient access point for researchers that require radiation property models for simulation tools and can be applied to research problems in a wide variety of fields.
 

### 2020-12-31 manuscript/manuscript.tex
minor edits to abstract, conclusions, and keywords

--- 2020-12-30 manuscript/manuscript.tex
@@
 \begin{abstract}
-%% Text of abstract 
-Ca. 100 words
+RadLib is a modular C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations.
+RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interface options permit convenient expansion to additional models.
+Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
+The computational cost of the models is also compared.
+RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-radiative heat transfer \sep reacting flows  \sep CFD
+radiative heat transfer \sep reacting flows  \sep CFD \sep WSGG \sep RCSLW
 \end{keyword}
@@
 
-Set out the conclusion of this original software publication.
+RadLib is a C++ library of radiation property models developed to address the complexity and difficulty inherent in implementing radiative property models in CFD simulations.
+At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interfaces permit convenient expansion to additional property models.
+To that end, the basic structure and use of the RadLib library has been laid out.
+In addition, the RadLib package includes example cases in several variations of a parallel planes geometry using a simple ray tracing solver to illustrate the use of the three radiation property models.
+These examples are compared to line-by-line solutions.
+In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy, but, under the appropriate conditions, the PM and WSGG models can also perform well and boast lower computational costs than the RCSLW model.
+As a whole, RadLib provides a convenient access point for researchers that require radiation property models for simulation tools and can be applied to research problems in a variety of fields.
 

### 2020-12-31 manuscript/manuscript.tex
setup for submission to computer physics communications

@@
+%% This template can be used to write a paper for
+%% Computer Physics Communications using LaTeX.
+%% For authors who want to write a computer program description,
+%% an example Program Summary is included that only has to be
+%% completed and which will give the correct layout in the
+%% preprint and the journal.
+%% The `elsarticle' style is used and more information on this style
+%% can be found at 
+%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
 %%
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
 %%
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%% SP 2008/03/01
-
-\documentclass[preprint,12pt, a4paper]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}
 
 %% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+%% \documentclass[preprint,review,12pt]{elsarticle}
 
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% if you use PostScript figures in your article
+%% use the graphics package for simple commands
+%% \usepackage{graphics}
+%% or use the graphicx package for more complicated commands
+%% \usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+%% \usepackage{epsfig}
 
@@
 %% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
 
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%
+%% \biboptions{comma,round}
+
+% \biboptions{}
+
+%% This list environment is used for the references in the
+%% Program Summary
+%%
 \usepackage{lineno}
@@
 
-\journal{SoftwareX}
+\newcounter{bla}
+\newenvironment{refnummer}{%
+\list{[\arabic{bla}]}%
+{\usecounter{bla}%
+ \setlength{\itemindent}{0pt}%
+ \setlength{\topsep}{0pt}%
+ \setlength{\itemsep}{0pt}%
+ \setlength{\labelsep}{2pt}%
+ \setlength{\listparindent}{0pt}%
+ \settowidth{\labelwidth}{[9]}%
+ \setlength{\leftmargin}{\labelwidth}%
+ \addtolength{\leftmargin}{\labelsep}%
+ \setlength{\rightmargin}{0pt}}}
+ {\endlist}
+
+\journal{Computer Physics Communications}
 
@@
 %% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
+%% use the tnotetext command for the associated footnote;
 %% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
+%% use the fntext command for the associated footnote;
 %% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
+%% use the cortext command for the associated footnote;
 %% use the ead command for the email address,
 %% and the form \ead[url] for the home page:
+%%
 %% \title{Title\tnoteref{label1}}
@@
 %% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
+%% \author[label1,label2]{<author name>}
+%% \address[label1]{<address>}
+%% \address[label2]{<address>}
 
-%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+%\author[a]{First Author\corref{author}}
+%\author[a,b]{Second Author}
+%\author[b]{Third Author}
+
+%\cortext[author] {Corresponding author.\\\textit{E-mail address:} firstAuthor@somewhere.edu}
+%\address[a]{First Address}
+%\address[b]{Second Address}
+
 \author{Victoria B. Stephens}
@@
 
+%In addition to the manuscript you must supply: the program source code; a README file giving the names and a brief description of the files/directory structure that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual.
+
+%A compressed archive program file or files, containing these items, should be uploaded at the "Attach Files" stage of the EM submission.
+
+%For files larger than 1Gb, if difficulties are encountered during upload the author should contact the Technical Editor at cpc.mendeley@gmail.com.
+
 \begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
 radiative heat transfer \sep reacting flows  \sep CFD \sep WSGG \sep RCSLW
@@
 
-\begin{table}[H]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-\hline
-\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
-\hline
-C1 & Current code version & TODO 2.1 \\
-\hline
-C2 & Permanent link to code/repository used for this code version & $github.com/BYUignite/radlib$ \\
-\hline
-C3 & Code Ocean compute capsule & (in review) \\
-\hline
-C4 & Legal Code License   & MIT license (MIT) \\
-\hline
-C5 & Code versioning system used & Git \\
-\hline
-C6 & Software code languages, tools, and services used & C++, Python 3 \\
-\hline
-C7 & Compilation requirements, operating environments \& dependencies & CMake, C++, Python 3, Cython \\
-\hline
-C8 & If available Link to developer documentation/manual & TODO \\
-\hline
-C9 & Support email for questions & davidlignell@byu.edu \\
-\hline
-\end{tabular}
-\caption{Code metadata.}
-\label{} 
-\end{table}
-
 \linenumbers
 
-% TODO tag software version
+% PROGRAM SUMMARY.
+
+{\bf PROGRAM SUMMARY/NEW VERSION PROGRAM SUMMARY}
+  %Delete as appropriate.
+
+\begin{small}
+\noindent
+{\em Program Title:} RadLib                                         \\
+{\em CPC Library link to program files:} (to be added by Technical Editor) \\
+{\em Developer's repository link:} https://github.com/BYUignite/radlib \\
+{\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
+{\em Licensing provisions(please choose one):} MIT \\
+{\em Programming language:} C++, Python                                   \\
+{\em Nature of problem(approx. 50-250 words):} \\
+Radiation property models can be difficult to understand and implement, often requiring a high degree of specialization.
+This presents a problem for practitioners who wish to use/implement radiation models for which such models consitute only a small but important part of a larger simulation.
+Turbulent combustion simulations are one such example.
+Often, rudimentary assumptions are made and this can negatively impact results.
+\\
+{\em Solution method(approx. 50-250 words):}\\
+We provide a well-written, documented, and validated radiation property library that is open source, and uses modern versioning build tools.
+C++ and Python interfaces are provided along with several examples demonstrating usage of the model.
+The library can be extended to other models and interfaces.
+\\
+{\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
+The library is intended to be used in Linux-like terminal applications.  
+   \\
+
+\end{small}
 
@@
 
-\section{Motivation and significance} \label{s:motivation}
+\section{Introduction} \label{s:motivation}
 
@@
 
-\section{Illustrative Examples} \label{s:Examples}
+\section{Validation and Examples} \label{s:Examples}
 
@@
 
-\section{Impact} \label{s:impact}
+\section{Discussion} \label{s:impact}
 
@@
 
-\section*{Current executable software version} \label{s:current_software}
-
-%Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.
-
-\begin{table}[!ht]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-\hline
-\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Metadata} \\
-\hline
-S1 & Current software version & 1.0 \\
-\hline
-S2 & Permanent link to executables of this version  & \href{https://github.com/BYUignite/radlib}{https://github.com/BYUignite/radlib} \\
-\hline
-S3 & Legal Software License & MIT license (MIT) \\
-\hline
-S4 & Computing platforms/Operating Systems & Linux, OS X, Microsoft Windows\\
-\hline
-S5 & Installation requirements \& dependencies & CMake, C++, Python 3, Cython \\
-\hline
-S6 & If available, link to user manual - if formally published include a reference to the publication in the reference
-    list & \href{https://github.com/BYUignite/radlib}{https://github.com/BYUignite/radlib} \\
-\hline
-S7 & Support email for questions & davidlignell@byu.edu \\
-\hline
-\end{tabular}
-\caption{Software metadata.}
-\label{t:softmd} 
-\end{table}
-
 \end{document}

### 2021-01-01 submissions/initial_submission/manuscript.tex
renaming files, adding submission

--- 2020-12-31 manuscript/manuscript.tex
@@
 	\begin{center}
-		\includegraphics[width=\textwidth]{../figures/radlib_structure.pdf}
+        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
 	\end{center}
@@
         Example S1 & Example S2 \\
-        \includegraphics[width=2.75 in]{ex_1.pdf} &
-        \includegraphics[width=2.75 in]{ex_2b.pdf} \\
+        \includegraphics[width=2.75 in]{fig_ex_1.pdf} &
+        \includegraphics[width=2.75 in]{fig_ex_2b.pdf} \\
         Example S3 & Example S4 \\
-        \includegraphics[width=2.75 in]{ex_3a.pdf} &
-        \includegraphics[width=2.75 in]{ex_4a.pdf} \\
+        \includegraphics[width=2.75 in]{fig_ex_3a.pdf} &
+        \includegraphics[width=2.75 in]{fig_ex_4a.pdf} \\
         Example S5 & Example B3 \\
-        \includegraphics[width=2.75 in]{ex_5b.pdf} &
-        \includegraphics[width=2.75 in]{ex_6.pdf}
+        \includegraphics[width=2.75 in]{fig_ex_5b.pdf} &
+        \includegraphics[width=2.75 in]{fig_ex_6.pdf}
     \end{tabular}
@@
     \begin{center}
-        \includegraphics[width=5.5 in]{ex_Sb1.pdf}
+        \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
     \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
@@
 
-\bibliographystyle{elsarticle-num} 
-\bibliography{references}
+%\bibliographystyle{elsarticle-num} 
+%\bibliography{references}
+
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\expandafter\ifx\csname href\endcsname\relax
+  \def\href#1#2{#2} \def\path#1{#1}\fi
+
+\bibitem{Hottel_1967}
+H.~Hottel, A.~Sarofim, Radiative Transfer, {McGraw-Hill}, New York, 1967.
+
+\bibitem{Modest_2013}
+M.~F. Modest, Radiative Heat Transfer, third edition Edition, {Academic Press},
+  New York, 2013.
+
+\bibitem{Smith_2003}
+N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
+  \href{https://tnfworkshop.org/radiation/}{{TNF} workshop radiation models}
+  (2003).
+\newline\urlprefix\url{https://tnfworkshop.org/radiation/}
+
+\bibitem{Grosshandler_1993}
+W.~L. Grosshandler, {RADCAL}: A narrow-band model for radiation calculations in
+  a combustion environment: Nist technical note 1402.
+
+\bibitem{Barlow_2001}
+R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, Scalar profiles and {NO}
+  formation in laminar opposed-flow partially premixed methane/air flames,
+  Combustion and Flame 127~(3) (2001) 2102--2118.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
+  {\path{doi:10.1016/S0010-2180(01)00313-3}}.
+
+\bibitem{Barlow_1999}
+R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
+  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{Nitric
+  oxide formation in dilute hydrogen jet flames: isolation of the effects of
+  radiation and turbulence-chemistry submodels}, Combustion and Flame 117~(1-2)
+  (1999) 4--31.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
+  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}
+
+\bibitem{Frank_2000}
+J.~H. Frank, R.~S. Barlow, C.~Lundquist, Radiation and nitric oxide formation
+  in turbulent non-premixed jet flames, Proceedings of the Combustion Institute
+  28~(1) (2000) 447--454.
+\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
+  {\path{doi:10.1016/S0082-0784(00)80242-8}}.
+
+\bibitem{Zhu_2002}
+X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
+  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{The
+  effects of self-absorption of radiation on an opposed flow partially premixed
+  flame}, Combustion and Flame 129~(3) (2002) 342--345.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
+  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}
+
+\bibitem{Coelho_2002}
+P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, Spectral radiative effects and
+  turbulence-radiation-interaction in sandia flame {D}, in: {Barlow, Robert S.,
+  Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), The
+  Proceedings of the Sixth International Workshop on Measurement and
+  Computation of Turbulent Nonpremixed Flames, 2002.
+
+\bibitem{Bordbar_2014}
+M.~H. Bordbar, G.~Wecel, T.~Hyppanen, A line by line based weighted sum of gray
+  gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
+  combustion, Combustion and Flame 161~(9) (2014) 2435--2445.
+\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
+  {\path{doi:10.1016/j.combustflame.2014.03.013}}.
+
+\bibitem{Bordbar_2020}
+H.~Bordbar, G.~C. Fraga, S.~Hostikka,
+  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{An
+  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
+  molar fraction ratios in thermal radiation}, International Communications in
+  Heat and Mass Transfer 110 (2020) 104400.
+\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
+  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}
+
+\bibitem{Rothman_2010}
+L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
+  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
+  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{HITEMP},
+  the high-temperature molecular spectroscopic database}, Journal of
+  Quantitative Spectroscopy {\&} Radiative Transfer 111~(15) (2010) 2139--2150.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
+  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}
+
+\bibitem{Solovjov_2016}
+V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The generalized {SLW}
+  model, Journal of Physics: Conference Series 676 (2016) 1--36.
+
+\bibitem{Solovjov_2017}
+V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The rank correlated
+  {SLW} model of gas radiation in non-uniform media, Journal of Quantitative
+  Spectroscopy {\&} Radiative Transfer 197 (2017) 26--44.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
+  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.
+
+\bibitem{Badger_2019}
+J.~Badger, B.~W. Webb, V.~P. Solovjov, An exploration of advanced {SLW}
+  modeling approaches in comprehensive combustion predictions, Combustion
+  Science and Technology 012022~(676) (2019) 1--17.
+\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
+  {\path{doi:10.1080/00102202.2019.1678907}}.
+
+\bibitem{Solovjov_2000}
+V.~P. Solovjov, B.~W. Webb, {SLW} modeling of radiative transfer in
+  multicomponent gas mixtures, Journal of Quantitative Spectroscopy and
+  Radiative Transfer 65 (2000) 655--672.
+
+\bibitem{Solovjov_2001}
+V.~P. Solovjov, B.~W. Webb, An efficient method for modeling radiative transfer
+  in multicomponent gas mixtures with soot, Transactions of the ASME 123 (2001)
+  450--457.
+
+\bibitem{Solovjov_2008}
+V.~P. Solovjov, B.~W. Webb, Multilayer modeling of radiative transfer by {SLW}
+  and {CW} methods in non-isothermal gaseous medium, Journal of Quantitative
+  Spectroscopy and Radiative Transfer 109~(2) (2008) 245--257.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
+  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.
+
+\bibitem{Solovjov_2011}
+V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, The {SLW}-1 model for efficient
+  prediction of radiative transfer in high temperature gases, Journal of
+  Quantitative Spectroscopy and Radiative Transfer 112~(7) (2011) 1205--1212.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
+  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.
+
+\bibitem{Solovjov_2014}
+V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, Extension of the exact {SLW} model to
+  non-isothermal gaseous media, Journal of Quantitative Spectroscopy and
+  Radiative Transfer 143 (2014) 83--91.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
+  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.
+
+\bibitem{Webb_2018}
+B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, An exploration of the influence of
+  spectral model parameters on the accuracy of the rank correlated slw model,
+  Journal of Quantitative Spectroscopy and Radiative Transfer 218 (2018)
+  161--170.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
+  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.
+
+\bibitem{Pearson_2014}
+J.~Pearson, B.~Webb, S.~V.P., J.~Ma, Efficient representation of the absorption
+  line blackbody distribution function for {H$_2$O}, {CO$_2$}, and {CO} at
+  variable temperature, mole fraction, and total pressure, Journal of
+  Quantitative Spectrosopy and Radiative Transfer 138 (2014) 82--96.
+
+\bibitem{Brewster_1992}
+M.~Q. Brewster, Thermal Radiative Transfer and Properties, Wiley, 1992.
+
+\bibitem{Lee_1981}
+S.~C. Lee, C.~L. Tien, Optical constants of soot in hydrocarbon flames,
+  Symposium (International) on Combustion 18~(1) (1981) 1159--1166.
+\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
+  {\path{doi:10.1016/S0082-0784(81)80120-8}}.
+
+\bibitem{Stull_1960}
+V.~R. Stull, G.~N. Plass, Emissivity of dispersed carbon particles, Journal of
+  the Optical Society of America 50~(2) (1960) 121.
+\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
+  {\path{doi:10.1364/JOSA.50.000121}}.
+
+\bibitem{Dalzell_1969}
+W.~H. Dalzell, A.~F. Sarofim, Optical constants of soot and their application
+  to heat-flux calculations, Journal of Heat Transfer 91~(1) (1969) 100--104.
+\newblock \href {http://dx.doi.org/10.1115/1.3580063}
+  {\path{doi:10.1115/1.3580063}}.
+
+\bibitem{Howarth_1966}
+C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), The Effect of Temperature on
+  the Extinction of Radiation By Soot Particles, Begellhouse, 1966.
+\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
+  {\path{doi:10.1615/IHTC3.1210}}.
+
+\bibitem{Chang_1990}
+H.-c. Chang, T.~T. Charalampopoulos, Determination of the wavelength dependence
+  of refractive indices of flame soot, Proceedings of the Royal Society of
+  London. Series A: Mathematical and Physical Sciences 430~(1880) (1990)
+  577--591.
+\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
+  {\path{doi:10.1098/rspa.1990.0107}}.
+
+\bibitem{Felske_1984}
+J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, Determination of the
+  refractive indices of soot particles from the reflectivities of compressed
+  soot pellets, Combustion Science and Technology 37~(5-6) (1984) 263--283.
+\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
+  {\path{doi:10.1080/00102208408923757}}.
+
+\bibitem{Williams_2007}
+T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, Measurement of
+  the dimensionless extinction coefficient of soot within laminar diffusion
+  flames, International Journal of Heat and Mass Transfer 50~(7-8) (2007)
+  1616--1630.
+\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
+  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.
+
+\bibitem{Felske_1977}
+J.~Felske, T.~C.L., The use of the {M}ilne-{E}ddington absorption coefficient
+  for radiative heat transfer in combustion systems, ASME Journal of Heat
+  Transfer 99~(3) (1977) 633--647.
+
+\bibitem{Bordbar_personal}
+H.~Bordbar, personal communication.
+
+\bibitem{Chang_1984}
+S.~Chang, K.~Rhee, Blackbody radiation functions, International communictions
+  in Heat and Mass Transfer 11 (1984) 451--455.
+
+\bibitem{Stephens_2020}
+V.~Stephens, D.~Lignell, One-dimensional turbulence ({ODT}): computationally
+  efficient modeling and simulation of turbulent flows, Software{X} 13 (2020)
+  100641.
+\newblock \href {http://dx.doi.org/10.1016/j.softx.2020.100641}
+  {\path{doi:10.1016/j.softx.2020.100641}}.
+
+\end{thebibliography}
 

### 2021-01-01 manuscript/manuscript.tex
initial submission

@@
 
-{\bf PROGRAM SUMMARY/NEW VERSION PROGRAM SUMMARY}
+{\bf PROGRAM SUMMARY}
   %Delete as appropriate.
@@
 
-\section{Conflict of Interest} \label{s:coi}
+\section{Declaration of Competing Interes} \label{s:coi}
 
-There are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
 
@@
 
-The authors extend special thanks to Hadi Bordbar for assistance with the WSGG model and to Vladimir Solovjov and Brent Webb of Brigham Young University for their insights and assistance with the RCSLW model.
+The authors extend special thanks to Hadi Bordbar for assistance with the WSGG model and to Vladimir Solovjov and Brent Webb for their insights and assistance with the RCSLW model. 
+This research did not receive any specific grant from funding agencies in the public, commercial, or
+not-for-profit sectors.
 

### 2021-03-23 submissions/CPC_response_to_reviewers.md
Added response to reviewers document

#Response to Reviewers: CPC initial submission

##Reviwer 1

##Reviewer 2

##Reviewer 3

### 2021-03-23 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
-#Response to Reviewers: CPC initial submission
+# Response to Reviewers: CPC initial submission
 
-##Reviwer 1
+## Reviewer 1
 
-##Reviewer 2
+This manuscript introduces “RadLib,” a C++ library to calculate absorption coefficients for use in radiative heat transfer calculations.
+The library has reasonable value to the research community, despite a few limitations in its scope and design.
+The library is self-contained (doesn’t have any external dependencies), which is convenient.
 
-##Reviewer 3
+I have a number of comments on the manuscript as well as the software itself which the authors should consider to improve the manuscript and software.
+Manuscript:
+1.	There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.
+2.	Section 5 makes several editorial claims that are quite subjective, and not well-supported:
+a.	First sentence: “historically difficult to implement … complexity and high computational costs”
+i.	Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
+ii.	I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
+b.	At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling.
+Again, it is the RTE solver, not the property evaluation, that is the largest time-sink in terms of computer and human resources.
+c.	These kinds of statements persist throughout the second paragraph as well.
+There are limitations in RadLib such as lack of scattering treatment for particle-laden flows, inability to include more species, lack of any line-by-line capabilities, etc.
+The library checks a few useful boxes, but the verbiage here seems to take more credit than the authors may be due.
+3.	Section 5 claims that “RadLib’s modular framework is designed to easily accommodate new models as well,” which is a bit of an overstatement.
+See comments below w.r.t.
+assumptions on species considered, hard-coded polynomial coefficients, etc.
+all of which reduce extensibility.
+4.	There are several minor issues that need to be addressed:
+a.	Abstract: “well-written” is subjective and should be removed.
+b.	Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
+c.	Page 10: “[INSERT RUNTIME COMPARISONS HERE]”
+d.	Section 7 heading: “Interes”
+Software deficiencies & suggestions:
+1.	API doxygen documentation is non-standard.
+It appears that the doxygen documentation is provided in the .cc files rather than the header files, which is where it is typically found.
+Downstream developers would typically be working from headers and the installed library, so it is convention to have doxygen documentation in the header only.
+This also reduces clutter in the implementation files.
+2.	make_examples.sh:
+a.	will only work with a g++ compiler in the user’s path.
+b.	Is referred to as build_examples.sh in the README.md file
+c.	is redundant with the cmake build system and isn’t portable. It should probably be removed.
+3.	It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.
+4.	CMake build system:
+a.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).
+b.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.
+c.	the default build type isn’t defaulting to Release for me; it remains blank.
+d.	I suggest not using verbose makefiles by default.
+e.	Using GLOB to install the headers is not the appropriate CMake approach.
+f.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
+i.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
+g.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...
+5.	It appears that line-by-line data from HITEMP/HITRAN files cannot be loaded into RadLib. That’s an unfortunate limitation, but not a deal-breaker. 
+6.	It looks like the software hard-codes Plank mean absorption coefficients as (fourth-order?) polynomial fits?
+Same for WSGG.
+There is no discussion of why this was chosen, how the coefficients were determined, or a characterization of its accuracy.
+Do you observe any problematic behavior with the fourth order polynomials over temperatures from 300 to 3000 K?
+Are these interpolants or regression of data?
+7.	The two previous items combined lead to a significant limitation of RadLib: one cannot easily add new species or modify existing data that is used to generate the absorption coefficients since there has been internal preprocessing of (an unknown subset of) the HITEMP/HITRAN databases to produce curve fits.
+And given that this process is opaque, it isn’t reproducible.
+8.	RadLib only considers CO2 and H2O for WSGG, which is fairly limited.
+Even for Plank mean, only H2O, CO2, CO and CH4 are considered.
+NO and OH would be nice to include.
+It appears that including additional species would be a non-trivial undertaking.
+9.	Documentation:
+a.	Generating the documentation directly via doxygen v.
+1.8.20 gives numerous warnings about obsolete tags and then fails because it is looking for a relative path “../../docs/doxygen” that doesn’t exist.
+This should be fixed.
+b.	Generating the doxygen documentation via the build system target (“make doxygen”) does seem to work fine.
+
+## Reviewer 2
+
+A radiation spectral property library is developed in this study using C++.
+A Planck-mean absorption coefficient based model, a WSGG model and a RCSLM model from the literature are implemented  in the package.
+Verification results are presented and discussed.
+Although the authors addressed an important issue of radiation modeling, the contribution is marginal in the reviewer's opinion.
+No new models/methods are proposed in this study.
+As the authors correctly pointed out, the solver for radiative transfer equation is equally important, which is not included in the library.
+The coupling of a spectral model to a specific RTE solver, can have different levels of challenges depending on the combination.
+The design of the library doesn't really address any of the RTE-related issues, nor provide any new solutions to simplify the coupling of spectral models to RTEs.
+If the authors can demonstrate that the library can be coupled with popular CFD software and popular RTE
+solvers such as P1 and DOM, it would further improve the quality of this study. A few other concerns are listed as follows:
+
+1) RADCAL data were used to generate the PlanckMean absorption coefficient.
+Based on the reviewer's experience, the PlanckMean absorption coefficients can have meaningful differences when generated from RADCAL and from HiTEMP2010.
+It is recommended a more recent database being used for the library.
+2) Page 10, missing information on [INSERT RUNTIME COMPARISONS HERE].
+3) In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?
+4) Equation 6 appears to be inaccurate.
+5) Typo: page 4, line 49, "relating them" -> "relating the"
+
+## Reviewer 3
+
+The Computer Program in Physics (CPiP) submission titled, "RadLib: a radiative heat transfer model library for CFD" by Stephens et al reports a library of radiative property models that is modular and can be interfaced with other radiation model components.
+The manuscript is well-written and well-organized.
+The works cited are reasonable.
+RadLib contains a gray Planck-mean (PM) model, a weighted sum of gray gases (WSGG) model, and the rank-correlated SLW model.
+This is definitely an important tool for the combustion community, where the radiation modeling is often oversimplified mainly because of the lack of readily available appropriate radiation model libraries!
+I am not aware of any open-source libraries that combine the three property models presented here.
+The models included in RadLib are already well-established and well-validated in the radiation community.
+The library is written in C++ and is supposed to work in any Linux-like system.
+The code is well commented, although the associated documentation needs to be improved (see major comment #1).
+
+Considering all these, I think that this CPiP submission is definitely within the scope of the journal and of interest to the research community.
+However, the following concerns must be addressed before the submission is considered for publication.
+
+1) I could not successfully build and run the library in two different Linux systems. In both cases, first, the cmake returned an error:
+"CMake Error at c++/CMakeLists.txt:34 (install): install TARGETS given no ARCHIVE DESTINATION for static library target "radlib"."
+I could resolve this by adding ARCHIVE DESTINATION line on the c++/CMakeLists.txt file.
+But, then on during "make" my installation was interrupted several times because of missing packages in my Python installation.
+I would strongly recommend that the authors modify the installation instructions to include: a) list of dependencies (i.e., what compilers, what versions of python, what python packages, etc.), b) how to install the dependencies before building RadLib, c) a way to build RadLib with either only C++ or only Python.
+These installation notes do not necessarily need to be in the main manuscript, but they must be in the installation README of the code package.
+
+2) The library includes PM, one WSGG, and a RCSLW model.
+The authors should clearly indicate the rationale of these choices (i.e., why only these three models) early on in the manuscript.
+Since this is intended for researchers who, presumably, are not experts in radiation modeling, the inclusion of these three models can be misleading.
+One might think that these three models are the most appropriate models for their simulations.
+
+3) RadLib is intended to be expanded with new radiation property models in the future and interfaced with a user-supplied solver module for RTE.
+A brief discussion on how to interface such an external solver module should be presented.
+There is an example of a ray-tracing solver presented in the code files, but a brief discussion on coupling one's own RTE solver is important in the manuscript.
+Additionally, a brief discussion on how a user can add a new radiative property model should also be included.
+
+4) The Planck-mean absorption coefficient included in RadLib is based on TNF workshop data (from 2003).
+According to the references cited, these are fairly old correlations.
+If the authors use these data, I am concerned that the model parameters and correlations used in RadLib for the PM model may be obsolete and inaccurate.
+Can the authors please comment on this?
+
+5) On page 13, the authors present a paragraph describing Figs.
+2 and 3 - the comparison of various radiation property models present in RadLib in one-dimensional configurations.
+The comparisons are presented simply as observations without any explanation or reasoning why the models behave the way as seen in Fig.
+2 and 3.
+If I understand correctly, the focus of the work presented here is not the comparison of the accuracy of the three models but to showcase the library.
+Therefore, these comparisons - specifically without any explanation of the results - may not be essential to the current manuscript, and can be shortened.
+These results do serve as descriptions of example cases provided in RadLib.
+On the same page, the authors say that "While ommitted [should be omitted] here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in [11, 14] such that these examples also serve as a validation of the implementation of the
+models." The authors should avoid qualitative description such as "essentially identical" in the context of validation and present a quantitative (e.g., % error) metric wherever possible.
+A strong validation is important for programs like this.
+
+6) The computational cost tables for two cases show a significantly different trend, which the authors attribute to "additional overhead required in performing the calculations." Can the authors be more specific as to what these overheads may be?
+They say that they have neglected the initialization and input/output costs.
+Also, do these CPU times presented include the cost for the ray-tracing solver as well?
+Are the grids kept the same for all configurations?
+
+7) In line 53 on page 4, the authors claim to have CH4 property in RadLib but none of the validation cases contain CH4.
+Furthermore, for RCSLW, the refer to Pearson's work as a source for data of CO2, H2O, and CO without indicating the source data for CH4.
+
+MINOR:
+
+1) It should be clarified that RadLib only provides radiation properties for non-scattering media.
+
+2) In the program summary the description of the nature of the program is somewhat confusing from a grammatical construction standpoint.
+Particularly, the following part, "This presents a problem for practitioners who wish to use/implement radiation models for which [refers to what?] such models consitute [constitute?] only a small but important part of a larger simulation.
+Turbulent combustion simulations are one such example [example of what?].
+Often, rudimentary assumptions [in what?] are made and this can negatively impact results."
+
+3) In Page 2, "In some cases, radiative gains or losses are small compared to other energy sources or heat transfer modes and radiation can be safely neglected, ...
+difficult to simulate accurately without a robust radiation model." Please provide some references to support these arguments.
+
+4) Please explain all the symbols used in equations. For example, eta in Eqn. 1 (and subsequent equations), Eb  in Eqn. 11.
+
+5) Page, 4: "Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model [1, 2]." This sentence is somewhat misleading.
+It may be more appropriate to think of WSGG models as special cases of SLW or FSK models.
+
+6) In lines 48-52 on Page 4, the authors say that the absorption coefficients are calculated using some correlations after some curve-fitting to spectroscopic databases.
+I am not sure what the authors refer to as correlations.
+There may be some correlations involved in WSGG models, but it is not clear to me where are correlations involved in RCSLW.
+
+7) On page 7, the authors mention that the PM model can be "reasonably accurate" in some cases and go on to say that, "The Planck Mean model is most appropriate under optically thin conditions  with  relatively  low  radiative  transfer  relative  to  other  heat  sources such  as  reactive  heat  release  rates." The Planck Mean model will be appropriate in optically thin cases as there is very little reabsorption.
+This may or may not be connected with "relatively  low  radiative  transfer  relative  to  other  heat  sources." In fact, if the radiative heat transfer is much lower than chemical heat release, neglecting radiation altogether may also be reasonable!
+Although, the definition of "relatively low" is subjective.
+
+8) On the same page, lines 40-41, "This version of  the  WSGG  model  is  advantageous  because  it  allows  for  arbitrary  CO2 and  H2O  compositions,  increasing  its  accuracy  and  flexibility." Can the authors provide some references that show the increased accuracy and/or flexibility of this WSGG over any other WSGG?
+9) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?
+
+10) Please remove the words "[INSERT RUNTIME COMPARISONS HERE]" on Page 10.
+
+11) In lines 29-30 on page 13, please insert the units for Q in -80 and 200.
+
+12) In the Discussion (page 16), the authors write, "Neglecting radiation or using simple models like the optically thin assumption is adequate for some cases with simple geometry or limited chemical reactions…" This can be misleading.
+I am not sure if either the simple geometry or the limited chemical reactions give any indication of the importance of radiation.
+Rather, something like a radiant fraction or optical thickness may be a more appropriate metric to justify neglecting radiation or using an optically thin model.

### 2021-03-23 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 I have a number of comments on the manuscript as well as the software itself which the authors should consider to improve the manuscript and software.
-Manuscript:
+
+### Manuscript:
 1.	There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.
 2.	Section 5 makes several editorial claims that are quite subjective, and not well-supported:
-a.	First sentence: “historically difficult to implement … complexity and high computational costs”
-i.	Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
-ii.	I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
-b.	At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling.
+	1. First sentence: “historically difficult to implement … complexity and high computational costs”
+		- Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
+        - I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
+    1.	At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling.
 Again, it is the RTE solver, not the property evaluation, that is the largest time-sink in terms of computer and human resources.
-c.	These kinds of statements persist throughout the second paragraph as well.
+    1.	These kinds of statements persist throughout the second paragraph as well.
 There are limitations in RadLib such as lack of scattering treatment for particle-laden flows, inability to include more species, lack of any line-by-line capabilities, etc.
@@
 4.	There are several minor issues that need to be addressed:
-a.	Abstract: “well-written” is subjective and should be removed.
-b.	Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
-c.	Page 10: “[INSERT RUNTIME COMPARISONS HERE]”
-d.	Section 7 heading: “Interes”
-Software deficiencies & suggestions:
+    1. Abstract: “well-written” is subjective and should be removed.
+    1. Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
+    1.	Page 10: “[INSERT RUNTIME COMPARISONS HERE]”
+    1.	Section 7 heading: “Interes”
+
+### Software deficiencies & suggestions:
 1.	API doxygen documentation is non-standard.
@@
 2.	make_examples.sh:
-a.	will only work with a g++ compiler in the user’s path.
-b.	Is referred to as build_examples.sh in the README.md file
-c.	is redundant with the cmake build system and isn’t portable. It should probably be removed.
+    1.	will only work with a g++ compiler in the user’s path.
+    1.	Is referred to as build_examples.sh in the README.md file
+    1.	is redundant with the cmake build system and isn’t portable. It should probably be removed.
 3.	It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.
 4.	CMake build system:
-a.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).
-b.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.
-c.	the default build type isn’t defaulting to Release for me; it remains blank.
-d.	I suggest not using verbose makefiles by default.
-e.	Using GLOB to install the headers is not the appropriate CMake approach.
-f.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
-i.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
-g.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...
+    1.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).
+    1.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.
+    1.	the default build type isn’t defaulting to Release for me; it remains blank.
+    1.	I suggest not using verbose makefiles by default.
+    1.	Using GLOB to install the headers is not the appropriate CMake approach.
+    1.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
+    1.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
+    1.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...
 5.	It appears that line-by-line data from HITEMP/HITRAN files cannot be loaded into RadLib. That’s an unfortunate limitation, but not a deal-breaker. 
@@
 9.	Documentation:
-a.	Generating the documentation directly via doxygen v.
+    1.	Generating the documentation directly via doxygen v.
 1.8.20 gives numerous warnings about obsolete tags and then fails because it is looking for a relative path “../../docs/doxygen” that doesn’t exist.
 This should be fixed.
-b.	Generating the doxygen documentation via the build system target (“make doxygen”) does seem to work fine.
+    1.	Generating the doxygen documentation via the build system target (“make doxygen”) does seem to work fine.
 

### 2021-03-23 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 
-1) RADCAL data were used to generate the PlanckMean absorption coefficient.
+1.
+RADCAL data were used to generate the PlanckMean absorption coefficient.
 Based on the reviewer's experience, the PlanckMean absorption coefficients can have meaningful differences when generated from RADCAL and from HiTEMP2010.
 It is recommended a more recent database being used for the library.
-2) Page 10, missing information on [INSERT RUNTIME COMPARISONS HERE].
-3) In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?
-4) Equation 6 appears to be inaccurate.
-5) Typo: page 4, line 49, "relating them" -> "relating the"
+2. Page 10, missing information on [INSERT RUNTIME COMPARISONS HERE].
+3. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?
+4. Equation 6 appears to be inaccurate.
+5. Typo: page 4, line 49, "relating them" -> "relating the"
+
+	<span style="color:blue">The phrase has been amended to ". . .using correlations relating them to local properties such as. . .".</span>
 

### 2021-03-23 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
     1.	Page 10: “[INSERT RUNTIME COMPARISONS HERE]”
-    1.	Section 7 heading: “Interes”
+    	**This was a placeholder that should not have been included in the document. It has been removed.**
+    3.	Section 7 heading: “Interes”
 
@@
 2. Page 10, missing information on [INSERT RUNTIME COMPARISONS HERE].
-3. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?
-4. Equation 6 appears to be inaccurate.
-5. Typo: page 4, line 49, "relating them" -> "relating the"
 
-	<span style="color:blue">The phrase has been amended to ". . .using correlations relating them to local properties such as. . .".</span>
+	**This was a placeholder statement that should not have been included in the document. It has been removed.**
+
+4. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?
+5. Equation 6 appears to be inaccurate.
+6. Typo: page 4, line 49, "relating them" -> "relating the"
+
+	**The phrase has been amended to ". . .using correlations relating them to local properties such as. . .".**
 
@@
 
+	**The authors agree that this statement could be potentially misleading. The second half of the sentence (beginning with ". . .and are usually. . .") has been removed.*
+
 6) In lines 48-52 on Page 4, the authors say that the absorption coefficients are calculated using some correlations after some curve-fitting to spectroscopic databases.
@@
 8) On the same page, lines 40-41, "This version of  the  WSGG  model  is  advantageous  because  it  allows  for  arbitrary  CO2 and  H2O  compositions,  increasing  its  accuracy  and  flexibility." Can the authors provide some references that show the increased accuracy and/or flexibility of this WSGG over any other WSGG?
-9) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?
+
+	**Two references for the chosen WSGG model are given earlier in the paragraph.
+The second (Bordbar et al.
+2020) includes detailed comparisons between this model, its immediate predecessor (see Bordbar et al.
+2014), five other WSGG models, and line-by-line calculations for four different test cases that show high accuracy over a wide range of molar ratio values.
+While other models may have performed better in individual tests, this model demonstrated consistent accuracy over a range of scenarios.
+For clarity, this reference has been added to the end of the aforementioned sentence so as to better indicate where to obtain relevant information.**
+
+10) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?
 
@@
 
+	**This was a placeholder that should not have been included in the document. It has been removed.**
+
 11) In lines 29-30 on page 13, please insert the units for Q in -80 and 200.
+
+	**Appropriate units have been added to the specified values.**
 

### 2021-03-23 manuscript/manuscript.tex
Update manuscript.tex

@@
 Direct solution of Eq.~\ref{e:RTE_general}, involves so-called line-by-line calculations that are computationally prohibitive for most practical configurations and are used primarily for model validation.
-Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model \cite{Hottel_1967,Modest_2013}.
+Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013}.
 For instance, integrating Eq.~\ref{e:RTE_general} over fixed spectral ranges $\eta_j$ and assuming gray (spectrally uniform) properties in each region $j$, (that is, in each gray gas $j$), gives
@@
 RadLib currently implements three models of varying complexity and accuracy to calculate the radiation absorption coefficients $\kappa_j$ and their weight factors $a_j$ for each gas $j$.
-The absorption coefficients are typically calculated using correlations relating them local properties such as temperature, pressure, and composition.
+The absorption coefficients are typically calculated using correlations relating them to local properties such as temperature, pressure, and composition.
 Correlations come from curve fits to high-resolution radiation property databases.
@@
 It uses four gray gases and one transparent gas, and considers gaseous species \ce{CO2} and \ce{H2O}.
-This version of the WSGG model is advantageous because it allows for arbitrary \ce{CO2} and \ce{H2O} compositions, increasing its accuracy and flexibility.
+This version of the WSGG model is advantageous because it allows for arbitrary \ce{CO2} and \ce{H2O} compositions, increasing its accuracy and flexibility \citep{Bordbar_2020}.
 Absorption coefficients are calculated by
@@
 The C++ interface produces the fastest-running code, followed by the Cython-wrapped Python interface and then the regular Python interface.
-[INSERT RUNTIME COMPARISONS HERE]
 
@@
 Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models.
-For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 at $x=0$ to a peak of 200 at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m.
+For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m.
 In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model.

### 2021-03-24 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md
Updates to response to reviewers document and associated changes to the paper text.

@@
 ### Manuscript:
-1.	There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.
+1.There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.
+
 2. Section 5 makes several editorial claims that are quite subjective, and not well-supported:
@@
         - I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
-    1.	At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling.
+
+    1.
+At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling.
 Again, it is the RTE solver, not the property evaluation, that is the largest time-sink in terms of computer and human resources.
-    1.	These kinds of statements persist throughout the second paragraph as well.
+
+    1.
+These kinds of statements persist throughout the second paragraph as well.
 There are limitations in RadLib such as lack of scattering treatment for particle-laden flows, inability to include more species, lack of any line-by-line capabilities, etc.
 The library checks a few useful boxes, but the verbiage here seems to take more credit than the authors may be due.
-3.	Section 5 claims that “RadLib’s modular framework is designed to easily accommodate new models as well,” which is a bit of an overstatement.
+
+3.
+Section 5 claims that “RadLib’s modular framework is designed to easily accommodate new models as well,” which is a bit of an overstatement.
 See comments below w.r.t.
@@
 all of which reduce extensibility.
-4.	There are several minor issues that need to be addressed:
+
+**In order to avoid subjective language, this sentence has been revised as follows: "RadLib's modular framework can also accomodate new models, .
+.
+.".
+Specific extensibility issues are addressed below with their respective reviewer comments.**
+
+4.There are several minor issues that need to be addressed:
+
     1. Abstract: “well-written” is subjective and should be removed.
+
+	** The offending sentence (actually located in the "Solution method" section of the Program Summary) has been revised to eliminate subjective language.**
+
     1. Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
+
+	** Technically, no, this is not a run-on sentence, but its structure is awkward and inhibits readability.
+It has been revised to the following: "For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost."**
+
     1. Page 10: “[INSERT RUNTIME COMPARISONS HERE]”
+
     	**This was a placeholder that should not have been included in the document. It has been removed.**
+
     3. Section 7 heading: “Interes”
 
+	**Fixed section heading. Now correctly reads "Declaration of Competing Interests".**
+
 ### Software deficiencies & suggestions:
-1.	API doxygen documentation is non-standard.
+
+1.
+API doxygen documentation is non-standard.
 It appears that the doxygen documentation is provided in the .cc files rather than the header files, which is where it is typically found.
@@
 This also reduces clutter in the implementation files.
+
+** The authors were previously unaware of any such standards or conventions, and follow up research indicates that this is a stylistic preference rather than a flaw in the software.
+The locations of doxygen documentation blocks were chosen for overall readability as they tended to clutter the header files and were less obtrusive when located in the implementation files.
+However, the reviewer does make a valid point regarding usage by downstream developers, and while we would expect the typical RadLib user to be comfortable working with both header files and source code, it is worthwhile to consider all possible usages.
+Because this is an issue of style rather than function, no immediate changes have been made to the code or its documentation, but the authors appreciate this information about standard practice and will consider its implications moving forward.**
+
 2. make_examples.sh:
@@
     1.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...
+
 5. It appears that line-by-line data from HITEMP/HITRAN files cannot be loaded into RadLib. That’s an unfortunate limitation, but not a deal-breaker.
-6.	It looks like the software hard-codes Plank mean absorption coefficients as (fourth-order?) polynomial fits?
+
+** At present, RadLib's models cannot accommodate such data input, but this is a limitation of the models themselves, not the software.
+The appropriate line-by-line data is included within the RadLib package, which the authors consider a convenience rather than a hindrance.
+The ability to load database files directly into RadLib could be useful to researchers looking to extend RadLib's model library, however.
+The authors appreciate the suggestion and will consider it for future development.**
+
+6.
+It looks like the software hard-codes Plank mean absorption coefficients as (fourth-order?) polynomial fits?
 Same for WSGG.
@@
 Are these interpolants or regression of data?
-7.	The two previous items combined lead to a significant limitation of RadLib: one cannot easily add new species or modify existing data that is used to generate the absorption coefficients since there has been internal preprocessing of (an unknown subset of) the HITEMP/HITRAN databases to produce curve fits.
+
+** This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation property data, not to evaluate or compare the included models.
+All of the reviewer's questions are addressed in detail in the referenced literature (Planck Mean coefficients in [3,5] and WSGG in [10,11]).
+The authors believe that this is an issue of scope rather than missing information, but they are willing to extend the discussion at the editor's discretion.
+**
+
+7.
+The two previous items combined lead to a significant limitation of RadLib: one cannot easily add new species or modify existing data that is used to generate the absorption coefficients since there has been internal preprocessing of (an unknown subset of) the HITEMP/HITRAN databases to produce curve fits.
 And given that this process is opaque, it isn’t reproducible.
-8.	RadLib only considers CO2 and H2O for WSGG, which is fairly limited.
+
+8.
+RadLib only considers CO2 and H2O for WSGG, which is fairly limited.
 Even for Plank mean, only H2O, CO2, CO and CH4 are considered.
@@
 It appears that including additional species would be a non-trivial undertaking.
+
+** All WSGG correlations consider only CO2-H2O mixtures with the exception of specialized subset of WSGG models that consider CO2-H2O-soot mixtures.
+This WSGG model was chosen for RadLib due to its popularity, relative simplicity, and good performance.
+Note that WSGG models usually address radiation in combustion environments.
+RadLib implements the WSGG model presented by Bordbar et al.
+in references [10] and [11], which was developed specifically for use in oxy-fired combustion simulations.
+CO2 and H2O are the major products of all combustion processes, and CO is a major product of rich combustion.
+NO and OH are minor species that, while important to other aspects of combustion processes, do not typically participate significantly in radiative heat transfer processes.
+For more information, please refer to Section 20.6 of reference [2] and/or Section 3.4.1 of *Radiative Heat Transfer in Turbulent Combustion Systems* by Modest and Haworth.
+
+It should also be noted that the Planck Mean absorption coefficients model as implemented in RadLib refers specifically to the radiation model in [3,5], which is one of the most common radiation models applied to turbulent combustion simulations.
+This is why Section 2.1 explicitly references the TNF radiation model and its calculated Planck Mean absorption coefficients.
+As implemented, the model is not intended to be general or extensible to other gas species and was never presented as such.
+Adding additional species would indeed be a non-trivial undertaking, but that is neither the goal nor purpose of RadLib as a software package, which presents and validates models rather than evaluating them.
+**
+
 9. Documentation:
@@
 The design of the library doesn't really address any of the RTE-related issues, nor provide any new solutions to simplify the coupling of spectral models to RTEs.
-If the authors can demonstrate that the library can be coupled with popular CFD software and popular RTE
-solvers such as P1 and DOM, it would further improve the quality of this study. A few other concerns are listed as follows:
+If the authors can demonstrate that the library can be coupled with popular CFD software and popular RTE solvers such as P1 and DOM, it would further improve the quality of this study.
+A few other concerns are listed as follows:
 
@@
 It is recommended a more recent database being used for the library.
+
 2. Page 10, missing information on [INSERT RUNTIME COMPARISONS HERE].
@@
 
-4. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?
-5. Equation 6 appears to be inaccurate.
-6. Typo: page 4, line 49, "relating them" -> "relating the"
+3. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?
+
+4. Equation 6 appears to be inaccurate.
+
+	** Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations near it.
+**
+
+5. Typo: page 4, line 49, "relating them" -> "relating the"
 
@@
 
-	**The authors agree that this statement could be potentially misleading. The second half of the sentence (beginning with ". . .and are usually. . .") has been removed.*
+	**The authors agree that this statement could be potentially misleading. The second half of the sentence (beginning with ". . .and are usually. . .") has been removed.**
 

### 2021-03-24 manuscript/manuscript.tex
Updates to response to reviewers document and associated changes to the paper text.

@@
 {\em Solution method(approx. 50-250 words):}\\
-We provide a well-written, documented, and validated radiation property library that is open source, and uses modern versioning build tools.
-C++ and Python interfaces are provided along with several examples demonstrating usage of the model.
+We provide an open source radiation property library that uses modern versioning build tools, including C++ and Python interfaces and examples demonstrating usage of the models.
 The library can be extended to other models and interfaces.
@@
 Modeling radiative heat transfer for CFD is complex and challenging.
-Combustion simulations, for example, which require many physics models, are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to simulation cost.
+For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
 This can lead to simulations that use oversimplified radiation models, but in cases where radiation is significant relative to the other physical phenomena, oversimplified models can negatively impact the accuracy of simulation results.
@@
 RadLib makes researchers' work easier by consolidating various approaches into a modular library of interchangeable, prevalidated radiation models.
-Additionally, RadLib's modular framework is designed to easily accommodate new models as well, allowing researchers to compare new or existing models with very little overhead.
+Additionally, RadLib's modular framework can also accommodate new models, allowing researchers to compare new or existing models with very little overhead.
 Sometimes, it is not clear which radiation model may be the best fit for a particular simulation.
@@
 
-\section{Declaration of Competing Interes} \label{s:coi}
+\section{Declaration of Competing Interests} \label{s:coi}
 
@@
 
-%\bibliographystyle{elsarticle-num} 
+\bibliographystyle{elsarticle-num} 
 %\bibliography{references}

### 2021-03-24 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 
-	** The offending sentence (actually located in the "Solution method" section of the Program Summary) has been revised to eliminate subjective language.**
+	**The offending sentence (actually located in the "Solution method" section of the Program Summary) has been revised to eliminate subjective language.**
 
-    1. Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
+	2.Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
 
-	** Technically, no, this is not a run-on sentence, but its structure is awkward and inhibits readability.
+	**Technically, no, this is not a run-on sentence, but its structure is awkward and inhibits readability.
 It has been revised to the following: "For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost."**
 
-    1. Page 10: “[INSERT RUNTIME COMPARISONS HERE]”
+    3. Page 10: “[INSERT RUNTIME COMPARISONS HERE]”
 
@@
 
-    3. Section 7 heading: “Interes”
+	4. Section 7 heading: “Interes”
 
@@
 
-** The authors were previously unaware of any such standards or conventions, and follow up research indicates that this is a stylistic preference rather than a flaw in the software.
+	**The authors were previously unaware of any such standards or conventions, and follow up research indicates that this is a stylistic preference rather than a flaw in the software.
 The locations of doxygen documentation blocks were chosen for overall readability as they tended to clutter the header files and were less obtrusive when located in the implementation files.
@@
 
-** At present, RadLib's models cannot accommodate such data input, but this is a limitation of the models themselves, not the software.
+	**At present, RadLib's models cannot accommodate such data input, but this is a limitation of the models themselves, not the software.
 The appropriate line-by-line data is included within the RadLib package, which the authors consider a convenience rather than a hindrance.
@@
 
-** This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation property data, not to evaluate or compare the included models.
+	**This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation property data, not to evaluate or compare the included models.
 All of the reviewer's questions are addressed in detail in the referenced literature (Planck Mean coefficients in [3,5] and WSGG in [10,11]).
-The authors believe that this is an issue of scope rather than missing information, but they are willing to extend the discussion at the editor's discretion.
-**
+The authors believe that this is an issue of scope rather than missing information, but they are willing to extend the discussion at the editor's discretion.**
 
@@
 
-** All WSGG correlations consider only CO2-H2O mixtures with the exception of specialized subset of WSGG models that consider CO2-H2O-soot mixtures.
+	**All WSGG correlations consider only CO2-H2O mixtures with the exception of specialized subset of WSGG models that consider CO2-H2O-soot mixtures.
 This WSGG model was chosen for RadLib due to its popularity, relative simplicity, and good performance.
@@
 NO and OH are minor species that, while important to other aspects of combustion processes, do not typically participate significantly in radiative heat transfer processes.
-For more information, please refer to Section 20.6 of reference [2] and/or Section 3.4.1 of *Radiative Heat Transfer in Turbulent Combustion Systems* by Modest and Haworth.
+For more information, please refer to Section 20.6 of reference [2] and/or Section 3.4.1 of *Radiative Heat Transfer in Turbulent Combustion Systems* by Modest and Haworth.**
 
-It should also be noted that the Planck Mean absorption coefficients model as implemented in RadLib refers specifically to the radiation model in [3,5], which is one of the most common radiation models applied to turbulent combustion simulations.
+	**It should also be noted that the Planck Mean absorption coefficients model as implemented in RadLib refers specifically to the radiation model in [3,5], which is one of the most common radiation models applied to turbulent combustion simulations.
 This is why Section 2.1 explicitly references the TNF radiation model and its calculated Planck Mean absorption coefficients.
 As implemented, the model is not intended to be general or extensible to other gas species and was never presented as such.
-Adding additional species would indeed be a non-trivial undertaking, but that is neither the goal nor purpose of RadLib as a software package, which presents and validates models rather than evaluating them.
-**
+Adding additional species would indeed be a non-trivial undertaking, but that is neither the goal nor purpose of RadLib as a software package, which presents and validates models rather than evaluating them.**
 
@@
 
-	** Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations near it.
+	**Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations near it.
 **

### 2021-03-26 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 
-    1.
+    2.
 At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling.
@@
 
-    1.
+    3.
 These kinds of statements persist throughout the second paragraph as well.
@@
 
-4.There are several minor issues that need to be addressed:
-
+4. There are several minor issues that need to be addressed: 
 	1. Abstract: “well-written” is subjective and should be removed.
@@
 
-	2.Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
+	2. Introduction: second sentence: “Combustion simulations…” is a run-on sentence.
 
@@
 All of the reviewer's questions are addressed in detail in the referenced literature (Planck Mean coefficients in [3,5] and WSGG in [10,11]).
-The authors believe that this is an issue of scope rather than missing information, but they are willing to extend the discussion at the editor's discretion.**
+The authors believe that this is an issue of scope rather than missing information but are willing to extend the discussion at the editor's discretion.**
 
@@
 And given that this process is opaque, it isn’t reproducible.
+
+	**The authors acknowledge that modifying existing models in RadLib is non-trivial, but would like to note that the paper does not claim that the implemented models are easily modified, only that the RadLib framework can be used to implement and validate additional models.
+Additionally, the authors disagree with the reviewer's statement regarding opacity and reproducability.
+The referenced literature (see above) clearly outlines the data sources and preprocessing methods applied; this information was omitted from the current paper for the reasons stated above.
+Given the provided sources, the process is neither opaque nor non-reproducible.**
 
@@
 
+	**The Planck Mean absorption coefficients model as implemented in RadLib refers specifically to the radiation model in [3,5], which is one of the most common radiation models applied to turbulent combustion simulations.
+It was chosen because of its popularity and widespread use in combustion simulations (despite its limitations).
+That said, there is value in using the most current tools.
+Given the reviewer's experience with variance in the Planck Mean absorption coefficients as calculated from various databases, the authors will strongly consider adding an updated Planck Mean model using the most current available data.**
+
 2. Page 10, missing information on [INSERT RUNTIME COMPARISONS HERE].
@@
 
-	**Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations near it.
-**
+	**Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations in the paper.**
 
@@
 
+**TO DO: add something to introduction to address this**
+
 3) RadLib is intended to be expanded with new radiation property models in the future and interfaced with a user-supplied solver module for RTE.
@@
 Can the authors please comment on this?
+
+	**The authors purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations.
+The paper includes a brief discussion on the limited applicability of this model, especially for combustion simulations, and demonstrates its deficiencies in the example cases.
+It is true that this model is neither current nor particularly accurate, and the authors are strongly considering adding an updated Planck Mean model using the most current available data.**
+
+	**TO DO: add discussion to address the age of the model and why we chose to include it anyway**
 
@@
 
+**TO DO: add this**
+
 2) In the program summary the description of the nature of the program is somewhat confusing from a grammatical construction standpoint.
@@
 
+**TO DO: revise program summary**
+
 3) In Page 2, "In some cases, radiative gains or losses are small compared to other energy sources or heat transfer modes and radiation can be safely neglected, ...
@@
 
+**TO DO: add requested references**
+
 4) Please explain all the symbols used in equations. For example, eta in Eqn. 1 (and subsequent equations), Eb  in Eqn. 11.
+
+**TO DO: explain and/or list equation symbols not already addressed**
 
@@
 There may be some correlations involved in WSGG models, but it is not clear to me where are correlations involved in RCSLW.
+
+	**The RCSLW model's key tool is the absorption line blackbody distribution function (ALBDF), which is calculated using sppectral data available from databases like HITEMP.
+This is discussed briefly at the end of Section 2.3 on pages 8-9.
+For more information on how spectral data is used to calculate the ALBDFs, please see reference [22].**
 

### 2021-03-30 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 	1. First sentence: “historically difficult to implement … complexity and high computational costs”
-		- Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
-        - I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
+		-Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
+        	-I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
 
@@
 The library checks a few useful boxes, but the verbiage here seems to take more credit than the authors may be due.
+
+    **The authors have a number of concerns about the reviewer's claims here that they would like to address.
+First, note that the subject of the first sentence of Section 5 is "radiative heat transfer models", which does not refer specifically to either radiation property models or RTE evaluation methods, but the treatment of computational radiative heat transfer as a whole.
+This generalization holds for the entire first paragraph of Section 5.
+Additionally, at no point in the paper do the authors claim that property evaluation is more complex or computationally expensive than the RTE solution, only that it "can be a difficult and time-consuming portion of radiation calculations" (pg.
+2).
+Likewise, the paper contains no claims about the complexity of radiation property models in relation to other aspects of combustion simulations.
+(On this topic, however, the authors would like to point out that these other aspects of combustion simulations are typically well-characterized in both commercial and open-source CFD codes and do not require very much user interaction, whereas radiation modeling is often absent or highly simplified.) The second paragraph of Section 5 is a brief discussion on how RadLib can benefit researchers that draws from the authors' experiences.
+It does not claim that RadLib will solve any of the challenges of radiation modeling, only that it can "ease .
+.
+.
+obstacles", which the authors believe it can do.**
+
+    **All of that said, however, the fact that the reviewer made these assumptions and pointed out these implications indicates that the paper's language is, in fact, too subjective.
+Even though none of these statements were explicitly made, they must be implied for the reviewer to come to these conclusions.
+As such, revisions have been made throughout the paper to reduce subjective language, support generalized statements with additional explanation and/or references, and include due discussion of RadLib's limitations.**
 

### 2021-04-07 manuscript/manuscript.tex
Adding to section 3 to include more information on user interaction with the RadLib library according to reviewer comments.

@@
 RadLib installation is automated with CMake.
-First, navigate to the \texttt{radlib/build} directory.
-If the user requires an installation location other than the default \texttt{radlib/installed} directory, edit the \texttt{user\textunderscore config} file before running CMake.
+First, navigate to the \texttt{build} directory.
+If the user requires an installation location other than the default \texttt{installed} directory, edit the \texttt{user\textunderscore config} file before running CMake.
 To compile the package, run the command \texttt{cmake -C user\textunderscore config ../source}.
 Upon successful completion, run \texttt{make} and then \texttt{make install} to complete the process.
-The generated C++ library file is located at \texttt{radlib/installled/lib/libradlib.a}.
+To use RadLib in C++ projects, include the generated C++ library file, located at \texttt{installled/lib/libradlib.a}, and/or header files, located in \texttt{installed/include}, according to the project's build scheme.
+To use RadLib in Python, update the system \texttt{PYTHONPATH} environment variable and import the module, named \texttt{pyrad}, into the project.
 
+The interfaces, solver, and examples included with the library serve to demonstrate its use and validate the implementation and results.
 Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces.
-The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry, making it a versatile tool for any simulation that requires radiative heat transfer, regardless of configuration.
-The interfaces, solver, and examples included with the library serve to illustrate its use and validate the implementation and results.
+The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry.
+After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights.
+For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively.
 %

### 2021-04-07 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 
+**The authors would like to thank the reviewer for their time and knowledge.
+While we disagree with some of the reviewer's comments and suggestions, they are, overall, constructive and helpful to the paper's development.**
+
 ### Manuscript:
-1.There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.
+
+1. There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.
+
+	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.**
 
@@
 3. It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.
-4. CMake build system:
+
+**TO DO: consult Josh about appropriate tests for RadLib**
+
+5. CMake build system:
     1.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).
@@
 This WSGG model was chosen for RadLib due to its popularity, relative simplicity, and good performance.
-Note that WSGG models usually address radiation in combustion environments.
 RadLib implements the WSGG model presented by Bordbar et al.
@@
 A few other concerns are listed as follows:
+
+**The authors would like to thank the reviewer for their comments and suggestions.
+We have already begun working on coupling RadLib to CFD software (that includes a DOM model for the RTE solution, among other features) in order to demonstrate RadLib's capabilities.**
+
+**TO DO: couple RadLib to ODT for demonstration purposes**
 
@@
 
+**The authors would like to thank the reviewer for their insightful comments and suggestions.
+As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**
+
 1) I could not successfully build and run the library in two different Linux systems. In both cases, first, the cmake returned an error:
@@
 Additionally, a brief discussion on how a user can add a new radiative property model should also be included.
+
+	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.**
+
+	**TO DO: add discussion and/or documentation on how to add new property models**
 
@@
 
+	**These statements regarding PM absorption coefficients are generally true.
+In combustion simulations, low radiative heat transfer relative to other heat sources, including chemical heat release and convective heat transfer, usually does, in fact, indicate very low radiative reabsorption rates.
+Sectiom 2.1 has been revised to clarify this connection.
+The quoted sentence now reads as follows: "The Planck Mean model is most appropriate under optically thin conditions in which low radiative transfer relative to other heat sources, including but not limited to chemical heat release and buoyancy-driven convection in combustion systems, indicates that very little radiative reabsorption is occuring."**
+
+	**The reviewer may be interested to know that there are, in fact, numerous computational studies of combustion systems in which radiative heat transfer is entirely neglected on the basis that it is overwhelmed by or insignificant compared to reactive and/or convective heat release.
+This is typically only true of highly controlled systems and/or combustion fuels consisting of small gaseous hydrocarbons like H2 and CH4 and few impurities.
+Because their parameters and boundary conditions are well-characterized, such systems are common in "canonical flame" libraries that comprise many of the validation targets used in combustion CFD.
+Most practical and everyday combustion systems, however, are neither highly controlled nor dependent on simple fuels---wildfires, coal and biomass fueled processes, and oxy-fired combustion, among other things, come to mind---and such justifications for neglecting or simplifying radiation treatments become increasingly tenuous.
+The phrase "relatively low" is indeed subjective, and it is liberally applied in the field of computational combustion.
+We, the authors, created and now present RadLib as a tool that can, ideally, enable researchers to apply more appropriate radiation modeling to simulation studies that might otherwise rely on such subjective assumptions.
+The paper touches on these ideas in the introduction and discussion sections, but does not go into detail for the sake of brevity.**
+
 8) On the same page, lines 40-41, "This version of  the  WSGG  model  is  advantageous  because  it  allows  for  arbitrary  CO2 and  H2O  compositions,  increasing  its  accuracy  and  flexibility." Can the authors provide some references that show the increased accuracy and/or flexibility of this WSGG over any other WSGG?
@@
 10) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?
+
+	**This is correct. The molar ratio was defined using these variables by Bordbar et al. [10,11] for the WSGG model and have been retained for consistency.**
 

### 2021-04-07 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 Rather, something like a radiant fraction or optical thickness may be a more appropriate metric to justify neglecting radiation or using an optically thin model.
+
+	**This issue was partially addressed in the discussion above (see point 7).
+In combustion simulations, things like simple geometry and small domain sizes limit the extent of any chemical heat release or convective heat transfer, which usually indicates that radiative heat transfer plays a more prominent role than it would otherwise.
+In order to clarify this association, the sentence in question has been revised to read as follows: "Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results."**

### 2021-04-07 manuscript/manuscript.tex
Revisions to address reviewer comments on clarity

@@
 Planck Mean absorption coefficients are commonly used to model radiation, especially in combustion systems, because the model is relatively easy to implement, computationally inexpensive, and reasonably accurate in some cases.
-The Planck Mean model is most appropriate under optically thin conditions with relatively low radiative transfer relative to other heat sources such as reactive heat release rates.
+The Planck Mean model is most appropriate under optically thin conditions in which low radiative transfer relative to other heat sources, including but not limited to chemical heat release and buoyancy-driven convection in combustion systems, indicates that very little radiative reabsorption is occuring.
 In cases where the optically thin assumption applies, such as simple hydrogen jet flames, this model and the associated Planck Mean absorption coefficients can produce accurate results \citep{Barlow_1999}.
-In cases where the optically thin assumption is not reasonable, including many other combustion scenarios, the Planck Mean model does not produce accurate results.
+In cases where the optically thin assumption is not reasonable, which includes most practical combustion scenarios of interest to engineers, the Planck Mean model does not produce accurate results.
 For example, it significantly overpredicts radiative losses from the TNF library's CH$_4$ flames \cite{Frank_2000,Zhu_2002,Coelho_2002}.
@@
 Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs.
-Neglecting radiation or using simple models like the optically thin assumption is adequate for some cases with simple geometry or limited chemical reactions, but most simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results.
+Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results.
 In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error.

### 2021-04-08 manuscript/manuscript.tex
Major revisions to introduction. Moved large portions of the model description introductory paragraph to the introduction. Added brief discussion of property model types and spectral vs. global property models. Added references and made clarifications to address reviewer comments.

@@
 
-Modeling radiative heat transfer for CFD is complex and challenging.
+Combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
+Specifically, combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
+Historically, radiative heat transfer modeling in combustion problems is either neglected or oversimplified, resulting in significant over- or underprediction of flame temperatures by up to 200$^{\circ}$C, respectively \citep{Modest_2016}.
+Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
+These problems motivated development of the RadLib library, which provides a consistent framework for radiation property modeling and implements three powerful models in C++ and Python, giving researchers more convenient access to advanced radiation property models and a consistent framework for further model development.
+%
+%Modeling radiative heat transfer for CFD is complex and challenging.
 For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
@@
 For example, simple jet flames demonstrate both possibilities: early in a flame's development, turbulent mixing typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and are difficult to simulate accurately without a robust radiation model.
-These problems motivated development of the RadLib library, which provides a framework and uniform interface for radiation property models and implements three powerful models in C++ and Python, giving researchers more convenient access to advanced radiation property models and a consistent framework for further model development.
 
@@
 Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
-Solving the RTE for a given system also requires information about the radiative properties of the materials and media involved, typically radiation absorption coefficients.
-These absorption coefficients are dependent on a number of local system properties such as temperature, pressure, and gas composition.
-As a result, computational radiation solvers require two parts: first, a solution approach for the radiative transfer equations (RTE); and second, a radiation property model.
+Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiation property model.
 RadLib addresses the second part by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
 
-%Like combustion, the core mechanisms of radiation are physically and mathematically complex.
-Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength.
-Only the simplest systems have analytic solutions, and most practical systems require a numerical solution.
-Ray tracing solutions are very accurate but extremely computationally expensive, and often require high-performance computing resources to execute.
-Modeling assumptions are common and can reduce simulation cost at the expense of accuracy, depending on their validity for the system in question.
-
-With RadLib, we provide a convenient, easy-to-use access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
-RadLib is a modular C++ library with an optional Python interface used to compute the radiation properties of participating media, which can be a difficult and time-consuming portion of radiation calculations.
-RadLib's current focus is calculating radiation absorption coefficients and weighting factors for use in global radiation models, but the expansion to other radiative properties is possible.
-Three models are fully implemented and validated and use a common interface, allowing researchers convenient access to radiation modeling tools suitable for various applications.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Model descriptions} \label{s:models}
-
-The RTE for intensity $I$ in (unit) direction $\mathbf{s}$ for an absorbing, emitting, and non-scattering medium is described by
+For an absorbing, emitting, and non-scattering medium, the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
 % 
@@
 %
-where $I_{\eta}$ is the radiative spectral intensity, 
-$I_{b\eta}$ is spectral blackbody intensity (or Planck function), 
-$\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
-Radiation property models such as those implemented by RadLib are used to calculate the absorption coefficients $\kappa_{\eta}$.
-%
-The gas absorption spectrum is an extremely complex function consisting of millions of spectral lines (peaks) corresponding to quantum mechanical energy levels of the gas molecules.
-Direct solution of Eq.~\ref{e:RTE_general}, involves so-called line-by-line calculations that are computationally prohibitive for most practical configurations and are used primarily for model validation.
-Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013}.
-For instance, integrating Eq.~\ref{e:RTE_general} over fixed spectral ranges $\eta_j$ and assuming gray (spectrally uniform) properties in each region $j$, (that is, in each gray gas $j$), gives
+where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
+Solving the RTE requires information about the radiative properties of the materials and media in the system.
+Radiative property data typically takes the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model.
+Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, reflecting varying degrees of dependence on local system properties like temperature, pressure, and gas composition.
+Radiation property models, including those implemented in RadLib, typically use high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} to calculate spectral absorption coefficients, reducing or simplifying the huge amount of spectral data using correlations and modeling assumptions \cite{Zhang_2002b}.
+
+Direct solution of the spectral RTE involves so-called line-by-line calculations in which the RTE is solved for each individual spectral line, potentially millions of evaluations; this is computationally prohibitive for most practical configurations and used primarily for model validation.
+Traditional band models rely on estimated or averaged "line-of-sight" property values that, as a result, cannot be incorporated into the RTE.
+Modern band models require high-resolution databases and reorder rather than averaging absorption coefficients, but tend to lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.
+
+Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}.
+Assuming spectrally uniform (gray) properties over a region $j$ (that is, for a gray gas $j$), we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ defined by $j$ to obtain
 %
@@
 %
-where $a_j$ is a weight factor defined as
+where $I_b$ is the spectrally integrated blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
 %
@@
 %
-Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be computed for each of the $n+1$ gray gases.
-Normally, the $j=0$ gas is considered as a clear gas and represents transparent windows in the spectrum for which $\kappa_0=0$.
-The total radiative intensity $I$ is calculated by summing the individual gray gas intensities:
+Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be computed for each of the $n+1$ gray gases, where $j=0$ is defined as a clear gas that represents transparent windows in the spectrum for which $\kappa_0=0$.
+This "gray gas" approach allows us to calculate the total radiative intensity $I$ by summing the individual gray gas intensities rather than integrating over the entire wavenumber spectrum:
 %
@@
 %
-Radiative intensity $I$ is a function of direction $\mathbf{s}$. The heat flux vector $\mathbf{q}$ is found by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere:
-%
-\begin{linenomath}
-\begin{equation}
-    \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
-\end{equation}
-\end{linenomath}
-%
-The volumetric radiative heat source is then 
-%
-\begin{linenomath}
-\begin{equation}
-    Q = -\nabla\cdot\mathbf{q}.
-\end{equation}
-\end{linenomath}
-%
+%The heat flux $\mathbf{q}$ and volumetric radiative heat source $Q$ can then be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence or the resulting vector field, respectively:
+%%
+%\begin{linenomath}
+%\begin{equation}
+%    \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
+%\end{equation}
+%\end{linenomath}
+%%
+%\begin{linenomath}
+%\begin{equation}
+%    Q = -\nabla\cdot\mathbf{q}.
+%\end{equation}
+%\end{linenomath}
+%%
+Global models are especially attractive to computational combustion researchers because they significantly reduce the required number of RTE evaluations.
 
-RadLib currently implements three models of varying complexity and accuracy to calculate the radiation absorption coefficients $\kappa_j$ and their weight factors $a_j$ for each gas $j$.
+With RadLib, we aim to provide researchers with a convenient, easy-to-use access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
+RadLib is a modular C++ library with an optional Python interface.
+Currently, RadLib only calculates radiation absorption coefficients and weighting factors for use in global radiation models, but expansion to other radiative properties and model types is possible.
+Three models---the Planck Mean absorption coefficient (PM) model, the weighted sum of gray gases (WSGG) model, and the rank correlated spectral line weighted-sum-of-gray-gases (RCSLW) model---are fully implemented and validated.
+All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Model descriptions} \label{s:models}
+
+At present, RadLib includes three radiation property models of varying complexity and accuracy.
+
+ to calculate the radiation absorption coefficients $\kappa_j$ and their weight factors $a_j$ for each gas $j$.
 The absorption coefficients are typically calculated using correlations relating them to local properties such as temperature, pressure, and composition.
@@
 At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot.
+Note that the property models implemented in RadLib apply only to non-scattering media.
 
@@
 
-%[OTHER THINGS THAT APPLY TO ALL MODELS GO HERE]
+Absorption coefficients and other radiative property data may take on different forms depending on the RTE solution approach, but can generally be classified as either spectral (wavenumber-dependent) or global (integrated over wavenumber).
+Spectral absorption coefficients can be applied to the spectral RTE (\ref{e:RTE_general}), while global absorption coefficients are used in the spectrally-integrated RTE (\ref{e:RTE_wsgg}).
 
@@
 \bibitem{Modest_2013}
-M.~F. Modest, Radiative Heat Transfer, third edition Edition, {Academic Press},
+M.~F. Modest, Radiative Heat Transfer, third edition, {Academic Press},
   New York, 2013.
+
+\bibitem{Modest_2016}
+M.~F. Modest, D.~C. Haworth, Radiative Heat Transfer in Turbulent Combustion Systems, {Springer}, New York, 2016.
 
@@
 
+\bibitem{Zhang_2002b}
+H.~Zhang, M.~F.~Modest, Evaluation of the Planck-mean absorption coefficients from HITRAN and HITEMP databases, Journal of Quantitative Spectroscopy \& Radiative Transfer 73~(6) (2002) 649--653.
+
 \end{thebibliography}

### 2021-04-08 submissions/CPC_response_to_reviewers.md

@@
 The appropriate line-by-line data is included within the RadLib package, which the authors consider a convenience rather than a hindrance.
-The ability to load database files directly into RadLib could be useful to researchers looking to extend RadLib's model library, however.
+The ability to load database files directly into RadLib could be useful to researchers looking to extend RadLib's model library to include modern spectral models, however.
 The authors appreciate the suggestion and will consider it for future development.**
@@
 
+	**Um, no?**
+
+	**TO DO: remove or explain weird example cases**
+
 4. Equation 6 appears to be inaccurate.
@@
 
+**TO DO: decide on whether or not to keep example plots in the paper**
+
 6) The computational cost tables for two cases show a significantly different trend, which the authors attribute to "additional overhead required in performing the calculations." Can the authors be more specific as to what these overheads may be?
@@
 
+**TO DO**
+
 7) In line 53 on page 4, the authors claim to have CH4 property in RadLib but none of the validation cases contain CH4.
 Furthermore, for RCSLW, the refer to Pearson's work as a source for data of CO2, H2O, and CO without indicating the source data for CH4.
+
+	**The Plank Mean absorption coefficients model sourced from the TNF workshop and associated literature [3,5] includes CH4, so it can be done, but none of the examples include it.**
+
+**TO DO: ask DOL how to handle this**
 
@@
 
-**TO DO: add this**
+	**This clarification has been made explicitly in Section 2.**
+
+	**TO DO: make sure this is mentioned in other relevant places**
 
@@
 
-**TO DO: add requested references**
+	**References have been added throughout to bolster weakly supported arguments. Note that the quoted statement and related discussion has been moved to Section 5 due to unrelated revisions.**
 

### 2021-04-12 manuscript/manuscript.tex
Revised and rewrote PM model section

@@
 Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, reflecting varying degrees of dependence on local system properties like temperature, pressure, and gas composition.
-Radiation property models, including those implemented in RadLib, typically use high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} to calculate spectral absorption coefficients, reducing or simplifying the huge amount of spectral data using correlations and modeling assumptions \cite{Zhang_2002b}.
+Radiation property models, including those implemented in RadLib, typically use high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} to calculate spectral absorption coefficients, reducing or simplifying the huge amount of spectral data using correlations and modeling assumptions.
 
@@
 Currently, RadLib only calculates radiation absorption coefficients and weighting factors for use in global radiation models, but expansion to other radiative properties and model types is possible.
-Three models---the Planck Mean absorption coefficient (PM) model, the weighted sum of gray gases (WSGG) model, and the rank correlated spectral line weighted-sum-of-gray-gases (RCSLW) model---are fully implemented and validated.
+Three models are fully implemented and validated.
 All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.
@@
 
-At present, RadLib includes three radiation property models of varying complexity and accuracy.
+At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients (assuming optically thin media), a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
+Each of these models was specifically chosen for its notable qualities, attributes such popularity, ease of implementation, or accuracy; their individual strengths, weaknesses, and limitations are discussed in the sections that follow.
 
- to calculate the radiation absorption coefficients $\kappa_j$ and their weight factors $a_j$ for each gas $j$.
-The absorption coefficients are typically calculated using correlations relating them to local properties such as temperature, pressure, and composition.
-Correlations come from curve fits to high-resolution radiation property databases.
+Absorption coefficients and other radiative property data may take on different forms depending on the RTE solution approach, but can generally be classified as either spectral (wavenumber-dependent) or global (integrated over wavenumber).
+Spectral absorption coefficients can be applied to the spectral RTE (Eq.~\ref{e:RTE_general}), while global absorption coefficients are used in the spectrally-integrated RTE (Eq.~\ref{e:RTE_wsgg}).
+The type of absorption coefficient generated by each model and potential RTE integration strategies will also be discussed in the following sections.
+While solving the RTE is not the focus of this software, RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
+Refer to Section \ref{s:Examples} for details.
+
+Radiation absorption coefficients are typically calculated by correlations developed using high-resolution databases like RADCAL, HITEMP, and HITRAN \citep{Grosshandler_1993,Rothman_2010} that relate spectral lines to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
 At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot.
 Note that the property models implemented in RadLib apply only to non-scattering media.
-
-While solving the RTE is not the focus of this software, RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
-
-Absorption coefficients and other radiative property data may take on different forms depending on the RTE solution approach, but can generally be classified as either spectral (wavenumber-dependent) or global (integrated over wavenumber).
-Spectral absorption coefficients can be applied to the spectral RTE (\ref{e:RTE_general}), while global absorption coefficients are used in the spectrally-integrated RTE (\ref{e:RTE_wsgg}).
 
@@
 
-RadLib's simplest model uses Planck Mean absorption coefficients calculated from the correlations given on the TNF Workshop site \citep{Smith_2003}.
-The temperature-dependent correlations are based on the RADCAL model \citep{Grosshandler_1993}.
-The TNF radiation model is also documented in \citep{Barlow_2001}.
+RadLib's simplest radiation property model generates Planck Mean absorption coefficients under the assumption of optically thin media, from here on referred to as the Planck Mean (PM) model.
+The optically thin approximation assumes that there is little to no reabsorption of radiative energy in the system, or, in other words, that the system only emits radiation and does not absorb it.
+In combustion systems, optical thinness is often justified in terms of other flame properties such as low radiative heat transfer relative to chemical heat release or convective heat transfer (also used to justify neglecting radiation altogether in some cases).
+Assuming optical thinness, however, has the distinct advantage of simplifying the radiative source term (here denoted $S_{rad}$) of the energy conservation equation to
+\begin{equation}
+	S_{rad}=-4\kappa \sigma T^4,
+\end{equation}
+where $\kappa$ is the radiation absorption coefficient, $\sigma$ is the Stefan-Boltzmann constant, and $T$ is temperature.
+Using an optically thin approximation means that no RTE solution is required when calculating radiative source terms.
 
-Planck Mean absorption coefficients are commonly used to model radiation, especially in combustion systems, because the model is relatively easy to implement, computationally inexpensive, and reasonably accurate in some cases.
-The Planck Mean model is most appropriate under optically thin conditions in which low radiative transfer relative to other heat sources, including but not limited to chemical heat release and buoyancy-driven convection in combustion systems, indicates that very little radiative reabsorption is occuring.
-In cases where the optically thin assumption applies, such as simple hydrogen jet flames, this model and the associated Planck Mean absorption coefficients can produce accurate results \citep{Barlow_1999}.
-In cases where the optically thin assumption is not reasonable, which includes most practical combustion scenarios of interest to engineers, the Planck Mean model does not produce accurate results.
-For example, it significantly overpredicts radiative losses from the TNF library's CH$_4$ flames \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-The examples included with the code and illustrated in Section \ref{s:Examples} demonstrate the deficiencies of the Planck Mean model in comparison to the others included with RadLib.
+In combustion systems, this simplification is convenient because it makes radiation modeling easy to implement and computationally inexpensive.
+The vast majority of computational combustion research that considers radiation employs an optically thin approximation despite its limited applicability to combustion processes.
+Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flame or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}.
+
+The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
+These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its notable limitations.
+Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}.
+TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}.
+In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.
+
+Because of these limitations, the authors do not consider the PM model adequate for most combustion simulation cases and strongly recommend that RadLib users carefully consider its implications before using the PM model.
+It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its popularity and widespread use.
+The examples included with the RadLib code and shown in Section \ref{s:Examples} demonstrate the deficiencies of the Planck Mean model in comparison to other models included with RadLib.
 

### 2021-04-13 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 	**The authors purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations.
-The paper includes a brief discussion on the limited applicability of this model, especially for combustion simulations, and demonstrates its deficiencies in the example cases.
-It is true that this model is neither current nor particularly accurate, and the authors are strongly considering adding an updated Planck Mean model using the most current available data.**
-
-	**TO DO: add discussion to address the age of the model and why we chose to include it anyway**
+Section 2.1 has been revised to include a more explicit dicsussion of why the TNF radiation model was chosen and concerns related to its relative age and limited applicability.
+Section 4 includes example cases that clearly demonstrate the deficiencies of the PM model compared to the other models included with RadLib, and some additional discussion is available there.**
 
@@
 
-**TO DO**
+	**Section 4.1 already includes details of the computational cost calculations presented in Figure 4.
+The left hand plot (a) refers to one million evaluations of the absorption coefficients directly, while the right hand plot (b) refers to the cost to evaluate Example S3, which, like all of the example cases described in the first paragraph of Section 4, includes the ray-tracing solver.
+The quoted sentence has been revised to specify that the ray-tracing solver is primarily responsible for the additional overhead.
+Grids are identical for each configuration.
+Note that the RadLib library does not generate or manipulate grids as it is not involved in the RTE solution.
+The ray-tracing solver used in the example cases is provided for convenience and demonstration purposes.**
 
@@
 
-	**The Plank Mean absorption coefficients model sourced from the TNF workshop and associated literature [3,5] includes CH4, so it can be done, but none of the examples include it.**
-
-**TO DO: ask DOL how to handle this**
+	**CH4 is present only in the PM model sourced from the TNF Workshop [3,5], which includes CH4 absorption coefficients because most of the TNF Workshop target flames are fueled by Ch4.
+In general, CH4 is not a significant radiatively participating species in combustion systems, but it is included for completeness.**
 
@@
 
-	**This clarification has been made explicitly in Section 2.**
-
-	**TO DO: make sure this is mentioned in other relevant places**
+	**This clarification has been made explicitly in Section 2 and now appears throughout the text where appropriate.**
 
@@
 
-**TO DO: explain and/or list equation symbols not already addressed**
+	**Text surrounding equations has been revised throughout to ensure explicit definitions of variables.**
 

### 2021-04-14 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md
All non-technical comments have been addressed

@@
 
-	**Um, no?**
-
-	**TO DO: remove or explain weird example cases**
+	**The PM and WSGG models are primarily empirical and contain very little representative physics, which could explain their unexpected behavior in Examples 2 and 4 but also makes it very difficult to find or treat sources of error.
+Any model, but especially empirical models, can behave unexpectedly when applied to conditions or parameters outside of those for which it was developed.
+The example cases are meant to be illusrative of the software's capabilities, not an evaluation of the models themselves, which is outside the scope of this paper.
+The reviewer's request for an explanation, however, is valid.
+A brief discussion has been added to Section 5 to address these specific discrepancies.
+Additional information about the specific limitations, strengths, and weaknesses associated with each model can be found in Section 2.**
 
@@
 
-**TO DO: add something to introduction to address this**
+	**Section 2 has been heavily revised to address this issue.
+Each model's description now also includes a discussion of its strengths, weaknesses, and limitations when applied to combustion CFD in addition to the authors' rationale in choosing them for RadLib.**
 
@@
 
-	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.**
-
-	**TO DO: add discussion and/or documentation on how to add new property models**
+	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.
+Adding additional radiative property models to the RadLib library, however, is nontrivial, and we chose to move its discussion to the package documentation so as not to clutter the manuscript.
+This can be changed, if necessary, at the editor's discretion.**
 
@@
 
-**TO DO: decide on whether or not to keep example plots in the paper**
+	**While it is true that the purpose of this paper is to present the RadLib library rather than evaluate or compare the models, the authors believe that example case results in Figures 2 and 3 are important to the illustration of RadLib's capabilities.
+The reviewer's point about presentation without explanation, however, is valid; to that end, the discussion in Section 5 has been expanded somewhat to acknowledge, if not fully explain or provide cause for, various features and descrepancies in the example case results.
+Due to the empirical nature of the PM and WSGG models, it is very difficult to identify, explain, or rectify unexpected behavior.
+It should be noted, however, that any model, and especially empirical models, can behave unpredictably when applied to parameter ranges or conditions outside of those for which is was developed.**
+
+	**In regards to validation, the authors are unclear as to what the reviewer expects to see.
+RadLib's model implementations give results that are, in fact, essentially identical to those presented in the literature to within any visual margin.
+We do not have access to the data used to generate the plots in the literature, without which any quantitative measure of error is meaningless.
+We do, however, compare model results to the line-by-line data, which amounts to a direct solution of the RTE and is also identical to the line-by-line data in the literature (as expected).
+The authors believe that this serves as adequate validation of RadLib's model implementations given the lack of originial data for comparison.**
 
@@
 
-**TO DO: revise program summary**
+	**The program summary has been rewritten for clarity.**
 
@@
 
-	**The reviewer may be interested to know that there are, in fact, numerous computational studies of combustion systems in which radiative heat transfer is entirely neglected on the basis that it is overwhelmed by or insignificant compared to reactive and/or convective heat release.
-This is typically only true of highly controlled systems and/or combustion fuels consisting of small gaseous hydrocarbons like H2 and CH4 and few impurities.
-Because their parameters and boundary conditions are well-characterized, such systems are common in "canonical flame" libraries that comprise many of the validation targets used in combustion CFD.
-Most practical and everyday combustion systems, however, are neither highly controlled nor dependent on simple fuels---wildfires, coal and biomass fueled processes, and oxy-fired combustion, among other things, come to mind---and such justifications for neglecting or simplifying radiation treatments become increasingly tenuous.
-The phrase "relatively low" is indeed subjective, and it is liberally applied in the field of computational combustion.
-We, the authors, created and now present RadLib as a tool that can, ideally, enable researchers to apply more appropriate radiation modeling to simulation studies that might otherwise rely on such subjective assumptions.
-The paper touches on these ideas in the introduction and discussion sections, but does not go into detail for the sake of brevity.**
-
 8) On the same page, lines 40-41, "This version of  the  WSGG  model  is  advantageous  because  it  allows  for  arbitrary  CO2 and  H2O  compositions,  increasing  its  accuracy  and  flexibility." Can the authors provide some references that show the increased accuracy and/or flexibility of this WSGG over any other WSGG?

### 2021-04-14 manuscript/manuscript.tex
Reviewer revisions. All non-technical comments have been addressed. See response to reviewers document.

@@
 {\em Nature of problem(approx. 50-250 words):} \\
-Radiation property models can be difficult to understand and implement, often requiring a high degree of specialization.
-This presents a problem for practitioners who wish to use/implement radiation models for which such models consitute only a small but important part of a larger simulation.
-Turbulent combustion simulations are one such example.
-Often, rudimentary assumptions are made and this can negatively impact results.
+Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations.
+Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations.
 \\
 {\em Solution method(approx. 50-250 words):}\\
-We provide an open source radiation property library that uses modern versioning build tools, including C++ and Python interfaces and examples demonstrating usage of the models.
-The library can be extended to other models and interfaces.
-\\
+We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD.
+The package includes multiple interface options (C++ and Python), several illustrative examples with a provided ray-tracing solver, and a framework for expansion to include additional radiation property models and interfaces.\\
 {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
@@
 For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively.
+For information about adding additional radiative property models to the RadLib library, please refer to the package documentation.
 %
@@
 
-These cases are intended to illustrate the use of the RadLib library and are not exhaustive.
-Details about these examples and their motivations can be found in their respective references.
+These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. 
+%TO DO address this:
 While ommitted here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020} such that these examples also serve as a validation of the implementation of the models.
@@
 
+\section{Discussion} \label{s:impact}
+
+%Note that we are presenting and not evaluating the models and make no claims as to causes of the results presented in the previous section.
+Several of the example cases deviate from the expected behavior (i.e.
+S2, S4).
+Also note that the PM and WSGG models are mostly empirical and contain very little representative physics, which can cause them to behave unpredictably in parameter ranges outside of those for which the models were specifically developed.
+If we look at Bordbar's paper, WSGG looks really good, but Example S4 gives us behavior we don't expect---WSGG performs very poorly.
+We don't know why, and we don't intend to explain it, but this is a good illustration of the fact that sometimes models need to be tested independently before application to a specific project.
+Sometimes a model that seems perfect may not be for your case, and RadLib is a good tool for investigating things like that.
+
+Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs.
+Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results.
+In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error.
+Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.
+
+RadLib makes researchers' work easier by consolidating various approaches into a modular library of interchangeable, prevalidated radiation models.
+Additionally, RadLib's modular framework can also accommodate new models, allowing researchers to compare new or existing models with very little overhead.
+Sometimes, it is not clear which radiation model may be the best fit for a particular simulation.
+When simulations are especially complex or computationally expensive, researchers may have to extrapolate from theory and literature to choose an appropriate radiation model rather than testing for their specific case.
+RadLib is designed to ease both of these obstacles by facilitating comparison between radiation models through a common interface and providing a practical means of testing various models without the restriction of prespecified geometry or case parameters.
+With RadLib, researchers can put more of their time and effort into useful results rather than code or model development.
+
+Currently, RadLib is only used within the authors' research group, where it is applied to combustion CFD simulations using the One-Dimensional Turbulence (ODT) model \cite{Stephens_2020}, but its design and structure as a C++ library allows it to be incorporated easily into existing codes.
+It can be applied to  research questions in various other fields involving radiative heat transfer as well, including energy engineering or atmospheric and climate sciences.
+Radiation is a universal phenomenon, and RadLib can assist researchers in many areas with systems and processes that involve heat transfer.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Computational Cost} \label{s:cost}
@@
 Here, the WSGG model took 0.0079 s.
-In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead required in performing the calculations.
+In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.
 In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.
@@
 It is possible that improvements to the Python speed could be made by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion} \label{s:impact}
-
-Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs.
-Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results.
-In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error.
-Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.
-
-RadLib makes researchers' work easier by consolidating various approaches into a modular library of interchangeable, prevalidated radiation models.
-Additionally, RadLib's modular framework can also accommodate new models, allowing researchers to compare new or existing models with very little overhead.
-Sometimes, it is not clear which radiation model may be the best fit for a particular simulation.
-When simulations are especially complex or computationally expensive, researchers may have to extrapolate from theory and literature to choose an appropriate radiation model rather than testing for their specific case.
-RadLib is designed to ease both of these obstacles by facilitating comparison between radiation models through a common interface and providing a practical means of testing various models without the restriction of prespecified geometry or case parameters.
-With RadLib, researchers can put more of their time and effort into useful results rather than code or model development.
-
-Currently, RadLib is only used within the authors' research group, where it is applied to combustion CFD simulations using the One-Dimensional Turbulence (ODT) model \cite{Stephens_2020}, but its design and structure as a C++ library allows it to be incorporated easily into existing codes.
-It can be applied to  research questions in various other fields involving radiative heat transfer as well, including energy engineering or atmospheric and climate sciences.
-Radiation is a universal phenomenon, and RadLib can assist researchers in many areas with systems and processes that involve heat transfer.
-
-%Author guidelines for this section
-%\begin{itemize}
-% \item \textbf{This is the main section of the article and the reviewers weight the description here appropriately}
-% \item Indicate in what way new research questions can be pursued as a result of the software (if any).
-% \item Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
-% \item Indicate in what way the software has changed the daily practice of its users (if so).
-% \item Indicate how widespread the use of the software is within and outside the intended user group.
-% \item Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
-%\end{itemize}
 
@@
 \bibliographystyle{elsarticle-num} 
-%\bibliography{references}
+\bibliography{references}
 
-\begin{thebibliography}{10}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname href\endcsname\relax
-  \def\href#1#2{#2} \def\path#1{#1}\fi
+%\begin{thebibliography}{10}
+%\expandafter\ifx\csname url\endcsname\relax
+%  \def\url#1{\texttt{#1}}\fi
+%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+%\expandafter\ifx\csname href\endcsname\relax
+%  \def\href#1#2{#2} \def\path#1{#1}\fi
+%
+%\bibitem{Hottel_1967}
+%H.~Hottel, A.~Sarofim, Radiative Transfer, {McGraw-Hill}, New York, 1967.
+%
+%\bibitem{Modest_2013}
+%M.~F. Modest, Radiative Heat Transfer, third edition, {Academic Press},
+%  New York, 2013.
+%  
+%\bibitem{Modest_2016}
+%M.~F. Modest, D.~C. Haworth, Radiative Heat Transfer in Turbulent Combustion Systems, {Springer}, New York, 2016.
+%
+%\bibitem{Smith_2003}
+%N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
+%  \href{https://tnfworkshop.org/radiation/}{{TNF} workshop radiation models}
+%  (2003).
+%\newline\urlprefix\url{https://tnfworkshop.org/radiation/}
+%
+%\bibitem{Grosshandler_1993}
+%W.~L. Grosshandler, {RADCAL}: A narrow-band model for radiation calculations in
+%  a combustion environment: Nist technical note 1402.
+%
+%\bibitem{Barlow_2001}
+%R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, Scalar profiles and {NO}
+%  formation in laminar opposed-flow partially premixed methane/air flames,
+%  Combustion and Flame 127~(3) (2001) 2102--2118.
+%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
+%  {\path{doi:10.1016/S0010-2180(01)00313-3}}.
+%
+%\bibitem{Barlow_1999}
+%R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
+%  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{Nitric
+%  oxide formation in dilute hydrogen jet flames: isolation of the effects of
+%  radiation and turbulence-chemistry submodels}, Combustion and Flame 117~(1-2)
+%  (1999) 4--31.
+%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
+%  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
+%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}
+%
+%\bibitem{Frank_2000}
+%J.~H. Frank, R.~S. Barlow, C.~Lundquist, Radiation and nitric oxide formation
+%  in turbulent non-premixed jet flames, Proceedings of the Combustion Institute
+%  28~(1) (2000) 447--454.
+%\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
+%  {\path{doi:10.1016/S0082-0784(00)80242-8}}.
+%
+%\bibitem{Zhu_2002}
+%X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
+%  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{The
+%  effects of self-absorption of radiation on an opposed flow partially premixed
+%  flame}, Combustion and Flame 129~(3) (2002) 342--345.
+%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
+%  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
+%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}
+%
+%\bibitem{Coelho_2002}
+%P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, Spectral radiative effects and
+%  turbulence-radiation-interaction in sandia flame {D}, in: {Barlow, Robert S.,
+%  Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), The
+%  Proceedings of the Sixth International Workshop on Measurement and
+%  Computation of Turbulent Nonpremixed Flames, 2002.
+%
+%\bibitem{Bordbar_2014}
+%M.~H. Bordbar, G.~Wecel, T.~Hyppanen, A line by line based weighted sum of gray
+%  gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
+%  combustion, Combustion and Flame 161~(9) (2014) 2435--2445.
+%\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
+%  {\path{doi:10.1016/j.combustflame.2014.03.013}}.
+%
+%\bibitem{Bordbar_2020}
+%H.~Bordbar, G.~C. Fraga, S.~Hostikka,
+%  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{An
+%  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
+%  molar fraction ratios in thermal radiation}, International Communications in
+%  Heat and Mass Transfer 110 (2020) 104400.
+%\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
+%  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
+%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}
+%
+%\bibitem{Rothman_2010}
+%L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
+%  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
+%  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{HITEMP},
+%  the high-temperature molecular spectroscopic database}, Journal of
+%  Quantitative Spectroscopy {\&} Radiative Transfer 111~(15) (2010) 2139--2150.
+%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
+%  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
+%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}
+%
+%\bibitem{Solovjov_2016}
+%V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The generalized {SLW}
+%  model, Journal of Physics: Conference Series 676 (2016) 1--36.
+%
+%\bibitem{Solovjov_2017}
+%V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The rank correlated
+%  {SLW} model of gas radiation in non-uniform media, Journal of Quantitative
+%  Spectroscopy {\&} Radiative Transfer 197 (2017) 26--44.
+%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
+%  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.
+%
+%\bibitem{Badger_2019}
+%J.~Badger, B.~W. Webb, V.~P. Solovjov, An exploration of advanced {SLW}
+%  modeling approaches in comprehensive combustion predictions, Combustion
+%  Science and Technology 012022~(676) (2019) 1--17.
+%\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
+%  {\path{doi:10.1080/00102202.2019.1678907}}.
+%
+%\bibitem{Solovjov_2000}
+%V.~P. Solovjov, B.~W. Webb, {SLW} modeling of radiative transfer in
+%  multicomponent gas mixtures, Journal of Quantitative Spectroscopy and
+%  Radiative Transfer 65 (2000) 655--672.
+%
+%\bibitem{Solovjov_2001}
+%V.~P. Solovjov, B.~W. Webb, An efficient method for modeling radiative transfer
+%  in multicomponent gas mixtures with soot, Transactions of the ASME 123 (2001)
+%  450--457.
+%
+%\bibitem{Solovjov_2008}
+%V.~P. Solovjov, B.~W. Webb, Multilayer modeling of radiative transfer by {SLW}
+%  and {CW} methods in non-isothermal gaseous medium, Journal of Quantitative
+%  Spectroscopy and Radiative Transfer 109~(2) (2008) 245--257.
+%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
+%  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.
+%
+%\bibitem{Solovjov_2011}
+%V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, The {SLW}-1 model for efficient
+%  prediction of radiative transfer in high temperature gases, Journal of
+%  Quantitative Spectroscopy and Radiative Transfer 112~(7) (2011) 1205--1212.
+%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
+%  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.
+%
+%\bibitem{Solovjov_2014}
+%V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, Extension of the exact {SLW} model to
+%  non-isothermal gaseous media, Journal of Quantitative Spectroscopy and
+%  Radiative Transfer 143 (2014) 83--91.
+%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
+%  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.
+%
+%\bibitem{Webb_2018}
+%B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, An exploration of the influence of
+%  spectral model parameters on the accuracy of the rank correlated slw model,
+%  Journal of Quantitative Spectroscopy and Radiative Transfer 218 (2018)
+%  161--170.
+%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
+%  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.
+%
+%\bibitem{Pearson_2014}
+%J.~Pearson, B.~Webb, S.~V.P., J.~Ma, Efficient representation of the absorption
+%  line blackbody distribution function for {H$_2$O}, {CO$_2$}, and {CO} at
+%  variable temperature, mole fraction, and total pressure, Journal of
+%  Quantitative Spectrosopy and Radiative Transfer 138 (2014) 82--96.
+%
+%\bibitem{Brewster_1992}
+%M.~Q. Brewster, Thermal Radiative Transfer and Properties, Wiley, 1992.
+%
+%\bibitem{Lee_1981}
+%S.~C. Lee, C.~L. Tien, Optical constants of soot in hydrocarbon flames,
+%  Symposium (International) on Combustion 18~(1) (1981) 1159--1166.
+%\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
+%  {\path{doi:10.1016/S0082-0784(81)80120-8}}.
+%
+%\bibitem{Stull_1960}
+%V.~R. Stull, G.~N. Plass, Emissivity of dispersed carbon particles, Journal of
+%  the Optical Society of America 50~(2) (1960) 121.
+%\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
+%  {\path{doi:10.1364/JOSA.50.000121}}.
+%
+%\bibitem{Dalzell_1969}
+%W.~H. Dalzell, A.~F. Sarofim, Optical constants of soot and their application
+%  to heat-flux calculations, Journal of Heat Transfer 91~(1) (1969) 100--104.
+%\newblock \href {http://dx.doi.org/10.1115/1.3580063}
+%  {\path{doi:10.1115/1.3580063}}.
+%
+%\bibitem{Howarth_1966}
+%C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), The Effect of Temperature on
+%  the Extinction of Radiation By Soot Particles, Begellhouse, 1966.
+%\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
+%  {\path{doi:10.1615/IHTC3.1210}}.
+%
+%\bibitem{Chang_1990}
+%H.-c. Chang, T.~T. Charalampopoulos, Determination of the wavelength dependence
+%  of refractive indices of flame soot, Proceedings of the Royal Society of
+%  London. Series A: Mathematical and Physical Sciences 430~(1880) (1990)
+%  577--591.
+%\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
+%  {\path{doi:10.1098/rspa.1990.0107}}.
+%
+%\bibitem{Felske_1984}
+%J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, Determination of the
+%  refractive indices of soot particles from the reflectivities of compressed
+%  soot pellets, Combustion Science and Technology 37~(5-6) (1984) 263--283.
+%\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
+%  {\path{doi:10.1080/00102208408923757}}.
+%
+%\bibitem{Williams_2007}
+%T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, Measurement of
+%  the dimensionless extinction coefficient of soot within laminar diffusion
+%  flames, International Journal of Heat and Mass Transfer 50~(7-8) (2007)
+%  1616--1630.
+%\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
+%  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.
+%
+%\bibitem{Felske_1977}
+%J.~Felske, T.~C.L., The use of the {M}ilne-{E}ddington absorption coefficient
+%  for radiative heat transfer in combustion systems, ASME Journal of Heat
+%  Transfer 99~(3) (1977) 633--647.
+%
+%\bibitem{Bordbar_personal}
+%H.~Bordbar, personal communication.
+%
+%\bibitem{Chang_1984}
+%S.~Chang, K.~Rhee, Blackbody radiation functions, International communictions
+%  in Heat and Mass Transfer 11 (1984) 451--455.
+%
+%\bibitem{Stephens_2020}
+%V.~Stephens, D.~Lignell, One-dimensional turbulence ({ODT}): computationally
+%  efficient modeling and simulation of turbulent flows, Software{X} 13 (2020)
+%  100641.
+%\newblock \href {http://dx.doi.org/10.1016/j.softx.2020.100641}
+%  {\path{doi:10.1016/j.softx.2020.100641}}.
+%  
+%\bibitem{Zhang_2002b}
+%H.~Zhang, M.~F.~Modest, Evaluation of the Planck-mean absorption coefficients from HITRAN and HITEMP databases, Journal of Quantitative Spectroscopy \& Radiative Transfer 73~(6) (2002) 649--653.
 
-\bibitem{Hottel_1967}
-H.~Hottel, A.~Sarofim, Radiative Transfer, {McGraw-Hill}, New York, 1967.
-
-\bibitem{Modest_2013}
-M.~F. Modest, Radiative Heat Transfer, third edition, {Academic Press},
-  New York, 2013.
-
-\bibitem{Modest_2016}
-M.~F. Modest, D.~C. Haworth, Radiative Heat Transfer in Turbulent Combustion Systems, {Springer}, New York, 2016.
-
-\bibitem{Smith_2003}
-N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
-  \href{https://tnfworkshop.org/radiation/}{{TNF} workshop radiation models}
-  (2003).
-\newline\urlprefix\url{https://tnfworkshop.org/radiation/}
-
-\bibitem{Grosshandler_1993}
-W.~L. Grosshandler, {RADCAL}: A narrow-band model for radiation calculations in
-  a combustion environment: Nist technical note 1402.
-
-\bibitem{Barlow_2001}
-R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, Scalar profiles and {NO}
-  formation in laminar opposed-flow partially premixed methane/air flames,
-  Combustion and Flame 127~(3) (2001) 2102--2118.
-\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
-  {\path{doi:10.1016/S0010-2180(01)00313-3}}.
-
-\bibitem{Barlow_1999}
-R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
-  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{Nitric
-  oxide formation in dilute hydrogen jet flames: isolation of the effects of
-  radiation and turbulence-chemistry submodels}, Combustion and Flame 117~(1-2)
-  (1999) 4--31.
-\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
-  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
-\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}
-
-\bibitem{Frank_2000}
-J.~H. Frank, R.~S. Barlow, C.~Lundquist, Radiation and nitric oxide formation
-  in turbulent non-premixed jet flames, Proceedings of the Combustion Institute
-  28~(1) (2000) 447--454.
-\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
-  {\path{doi:10.1016/S0082-0784(00)80242-8}}.
-
-\bibitem{Zhu_2002}
-X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
-  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{The
-  effects of self-absorption of radiation on an opposed flow partially premixed
-  flame}, Combustion and Flame 129~(3) (2002) 342--345.
-\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
-  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
-\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}
-
-\bibitem{Coelho_2002}
-P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, Spectral radiative effects and
-  turbulence-radiation-interaction in sandia flame {D}, in: {Barlow, Robert S.,
-  Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), The
-  Proceedings of the Sixth International Workshop on Measurement and
-  Computation of Turbulent Nonpremixed Flames, 2002.
-
-\bibitem{Bordbar_2014}
-M.~H. Bordbar, G.~Wecel, T.~Hyppanen, A line by line based weighted sum of gray
-  gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
-  combustion, Combustion and Flame 161~(9) (2014) 2435--2445.
-\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
-  {\path{doi:10.1016/j.combustflame.2014.03.013}}.
-
-\bibitem{Bordbar_2020}
-H.~Bordbar, G.~C. Fraga, S.~Hostikka,
-  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{An
-  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
-  molar fraction ratios in thermal radiation}, International Communications in
-  Heat and Mass Transfer 110 (2020) 104400.
-\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
-  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
-\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}
-
-\bibitem{Rothman_2010}
-L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
-  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
-  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{HITEMP},
-  the high-temperature molecular spectroscopic database}, Journal of
-  Quantitative Spectroscopy {\&} Radiative Transfer 111~(15) (2010) 2139--2150.
-\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
-  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
-\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}
-
-\bibitem{Solovjov_2016}
-V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The generalized {SLW}
-  model, Journal of Physics: Conference Series 676 (2016) 1--36.
-
-\bibitem{Solovjov_2017}
-V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The rank correlated
-  {SLW} model of gas radiation in non-uniform media, Journal of Quantitative
-  Spectroscopy {\&} Radiative Transfer 197 (2017) 26--44.
-\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
-  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.
-
-\bibitem{Badger_2019}
-J.~Badger, B.~W. Webb, V.~P. Solovjov, An exploration of advanced {SLW}
-  modeling approaches in comprehensive combustion predictions, Combustion
-  Science and Technology 012022~(676) (2019) 1--17.
-\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
-  {\path{doi:10.1080/00102202.2019.1678907}}.
-
-\bibitem{Solovjov_2000}
-V.~P. Solovjov, B.~W. Webb, {SLW} modeling of radiative transfer in
-  multicomponent gas mixtures, Journal of Quantitative Spectroscopy and
-  Radiative Transfer 65 (2000) 655--672.
-
-\bibitem{Solovjov_2001}
-V.~P. Solovjov, B.~W. Webb, An efficient method for modeling radiative transfer
-  in multicomponent gas mixtures with soot, Transactions of the ASME 123 (2001)
-  450--457.
-
-\bibitem{Solovjov_2008}
-V.~P. Solovjov, B.~W. Webb, Multilayer modeling of radiative transfer by {SLW}
-  and {CW} methods in non-isothermal gaseous medium, Journal of Quantitative
-  Spectroscopy and Radiative Transfer 109~(2) (2008) 245--257.
-\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
-  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.
-
-\bibitem{Solovjov_2011}
-V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, The {SLW}-1 model for efficient
-  prediction of radiative transfer in high temperature gases, Journal of
-  Quantitative Spectroscopy and Radiative Transfer 112~(7) (2011) 1205--1212.
-\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
-  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.
-
-\bibitem{Solovjov_2014}
-V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, Extension of the exact {SLW} model to
-  non-isothermal gaseous media, Journal of Quantitative Spectroscopy and
-  Radiative Transfer 143 (2014) 83--91.
-\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
-  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.
-
-\bibitem{Webb_2018}
-B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, An exploration of the influence of
-  spectral model parameters on the accuracy of the rank correlated slw model,
-  Journal of Quantitative Spectroscopy and Radiative Transfer 218 (2018)
-  161--170.
-\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
-  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.
-
-\bibitem{Pearson_2014}
-J.~Pearson, B.~Webb, S.~V.P., J.~Ma, Efficient representation of the absorption
-  line blackbody distribution function for {H$_2$O}, {CO$_2$}, and {CO} at
-  variable temperature, mole fraction, and total pressure, Journal of
-  Quantitative Spectrosopy and Radiative Transfer 138 (2014) 82--96.
-
-\bibitem{Brewster_1992}
-M.~Q. Brewster, Thermal Radiative Transfer and Properties, Wiley, 1992.
-
-\bibitem{Lee_1981}
-S.~C. Lee, C.~L. Tien, Optical constants of soot in hydrocarbon flames,
-  Symposium (International) on Combustion 18~(1) (1981) 1159--1166.
-\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
-  {\path{doi:10.1016/S0082-0784(81)80120-8}}.
-
-\bibitem{Stull_1960}
-V.~R. Stull, G.~N. Plass, Emissivity of dispersed carbon particles, Journal of
-  the Optical Society of America 50~(2) (1960) 121.
-\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
-  {\path{doi:10.1364/JOSA.50.000121}}.
-
-\bibitem{Dalzell_1969}
-W.~H. Dalzell, A.~F. Sarofim, Optical constants of soot and their application
-  to heat-flux calculations, Journal of Heat Transfer 91~(1) (1969) 100--104.
-\newblock \href {http://dx.doi.org/10.1115/1.3580063}
-  {\path{doi:10.1115/1.3580063}}.
-
-\bibitem{Howarth_1966}
-C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), The Effect of Temperature on
-  the Extinction of Radiation By Soot Particles, Begellhouse, 1966.
-\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
-  {\path{doi:10.1615/IHTC3.1210}}.
-
-\bibitem{Chang_1990}
-H.-c. Chang, T.~T. Charalampopoulos, Determination of the wavelength dependence
-  of refractive indices of flame soot, Proceedings of the Royal Society of
-  London. Series A: Mathematical and Physical Sciences 430~(1880) (1990)
-  577--591.
-\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
-  {\path{doi:10.1098/rspa.1990.0107}}.
-
-\bibitem{Felske_1984}
-J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, Determination of the
-  refractive indices of soot particles from the reflectivities of compressed
-  soot pellets, Combustion Science and Technology 37~(5-6) (1984) 263--283.
-\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
-  {\path{doi:10.1080/00102208408923757}}.
-
-\bibitem{Williams_2007}
-T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, Measurement of
-  the dimensionless extinction coefficient of soot within laminar diffusion
-  flames, International Journal of Heat and Mass Transfer 50~(7-8) (2007)
-  1616--1630.
-\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
-  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.
-
-\bibitem{Felske_1977}
-J.~Felske, T.~C.L., The use of the {M}ilne-{E}ddington absorption coefficient
-  for radiative heat transfer in combustion systems, ASME Journal of Heat
-  Transfer 99~(3) (1977) 633--647.
-
-\bibitem{Bordbar_personal}
-H.~Bordbar, personal communication.
-
-\bibitem{Chang_1984}
-S.~Chang, K.~Rhee, Blackbody radiation functions, International communictions
-  in Heat and Mass Transfer 11 (1984) 451--455.
-
-\bibitem{Stephens_2020}
-V.~Stephens, D.~Lignell, One-dimensional turbulence ({ODT}): computationally
-  efficient modeling and simulation of turbulent flows, Software{X} 13 (2020)
-  100641.
-\newblock \href {http://dx.doi.org/10.1016/j.softx.2020.100641}
-  {\path{doi:10.1016/j.softx.2020.100641}}.
-
-\bibitem{Zhang_2002b}
-H.~Zhang, M.~F.~Modest, Evaluation of the Planck-mean absorption coefficients from HITRAN and HITEMP databases, Journal of Quantitative Spectroscopy \& Radiative Transfer 73~(6) (2002) 649--653.
-
-\end{thebibliography}
+%\end{thebibliography}
 

### 2021-04-19 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
     1.	is redundant with the cmake build system and isn’t portable. It should probably be removed.
+
+	**The make_examples.sh file has been removed.**
+
 3. It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.
@@
     1.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.
-    1.	the default build type isn’t defaulting to Release for me; it remains blank.
-    1.	I suggest not using verbose makefiles by default.
-    1.	Using GLOB to install the headers is not the appropriate CMake approach.
-    1.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
-    1.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
-    1.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...
+
+		**Build has been updated to reflect this.**
+
+    3.	the default build type isn’t defaulting to Release for me; it remains blank.
+    4.	I suggest not using verbose makefiles by default.
+
+   		**Build has be updated so that verbose makefiles is no longer the default.**
+
+    3.	Using GLOB to install the headers is not the appropriate CMake approach.		
+    3.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
+    4.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
+
+		**Executables are built within the example folders in addition to the build directories, so run_examples.sh runs without any issues and serves as a simple illustration of the example cases.**
+
+    3.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...
+
+		**Build target name has been changed from "doxygen" to "docs" for safety.**
 
@@
     1.	Generating the doxygen documentation via the build system target (“make doxygen”) does seem to work fine.
+
+	**Build process has been updated so that documentation can be generated by the system target or manually.**
 

### 2021-04-20 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
     1.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).
-    1.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.
+
+		**Installation now includes a radlib.cmake file, located in the installed/cmake/radlib directory, for downstream usage.**
+
+    3.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.
 
@@
     3.	the default build type isn’t defaulting to Release for me; it remains blank.
-    4.	I suggest not using verbose makefiles by default.
 
-   		**Build has be updated so that verbose makefiles is no longer the default.**
+		**The authors have not experienced problems with this, but have verified that it works correctly.
+Note that the build type can be overridden by IDE build settings, among other things, and that this may be a system issue specific to the reviewer.**
+
+    5.	I suggest not using verbose makefiles by default.
+
+  		**Build has be updated so that verbose makefiles are no longer the default.**
 
     3.	Using GLOB to install the headers is not the appropriate CMake approach.
-    3.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
-    4.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
+
+		**Build updated accordingly; GLOB no longer used to install header files.**
+
+    5.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
+
+		**The authors have experienced no issues running the example executables from either the build/examples directory or directly from the examples directory.**
+
+    7.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
 
@@
 
-**TO DO: couple RadLib to ODT for demonstration purposes**
-
 1.
@@
 These installation notes do not necessarily need to be in the main manuscript, but they must be in the installation README of the code package.
+
+	**The CMake build system has been updated such that ARCHIVE DESTINATION is explicitly specified, so that error should no longer occur.
+A build option has been added that makes the Python interface installation optional.
+Note that the C++ source code is required to install the Python interface, so there is no option to build only the Python interface.
+All of this information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages.**
 

### 2021-04-20 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 
-	**The make_examples.sh file has been removed.**
+	**The ```make_examples.sh``` file has been removed.**
 
@@
 
-		**Installation now includes a radlib.cmake file, located in the installed/cmake/radlib directory, for downstream usage.**
+		**Installation now includes a ```radlib.cmake``` file, located in the ```installed/cmake/radlib``` directory, for downstream usage.**
 
@@
 
-		**The authors have experienced no issues running the example executables from either the build/examples directory or directly from the examples directory.**
+		**The authors have experienced no issues running the example executables from either the ```build/examples``` directory or directly from the ```examples``` directory.**
 
@@
 
-		**Executables are built within the example folders in addition to the build directories, so run_examples.sh runs without any issues and serves as a simple illustration of the example cases.**
+		**Executables are built within the example folders in addition to the build directories, so ```run_examples.sh``` runs without any issues and serves as a simple illustration of the example cases.**
 
@@
 
-	**The CMake build system has been updated such that ARCHIVE DESTINATION is explicitly specified, so that error should no longer occur.
+	**The CMake build system has been updated such that ```ARCHIVE DESTINATION``` is explicitly specified, so that error should no longer occur.
 A build option has been added that makes the Python interface installation optional.

### 2021-04-29 manuscript/manuscript.tex
Revisions to RCSLW description section. Various other revisions.

@@
 
-\title{RadLib: a radiative heat transfer model library for CFD}
+\title{RadLib: a radiative property model library for combustion CFD}
 
@@
 
-\section{Introduction} \label{s:motivation}
+\section{Introduction} \label{s:intro}
 
@@
 Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
-These problems motivated development of the RadLib library, which provides a consistent framework for radiation property modeling and implements three powerful models in C++ and Python, giving researchers more convenient access to advanced radiation property models and a consistent framework for further model development.
+These problems motivated development of the RadLib library, which implements three radiation property models in C++ and Python and provides a framework for additional models and further development, giving researchers more convenient access to advanced radiation property modeling tools.
 %
@@
 Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, reflecting varying degrees of dependence on local system properties like temperature, pressure, and gas composition.
-Radiation property models, including those implemented in RadLib, typically use high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} to calculate spectral absorption coefficients, reducing or simplifying the huge amount of spectral data using correlations and modeling assumptions.
+Radiation property models, including those implemented in RadLib, typically use high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} to calculate spectral absorption coefficients, reducing or simplifying the huge amount of spectral data using correlations and modeling assumptions \citep{Zhang_2002b}.
 
@@
 %
-where $I_b$ is the spectrally integrated blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
+where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
 %
@@
 %
-Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be computed for each of the $n+1$ gray gases, where $j=0$ is defined as a clear gas that represents transparent windows in the spectrum for which $\kappa_0=0$.
+Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases with the addition of one "clear gas" $j=0$ that represents transparent windows in the spectrum for which $\kappa_0=0$.
 This "gray gas" approach allows us to calculate the total radiative intensity $I$ by summing the individual gray gas intensities rather than integrating over the entire wavenumber spectrum:
@@
 %%
-Global models are especially attractive to computational combustion researchers because they significantly reduce the required number of RTE evaluations.
+Global models are especially attractive to computational combustion researchers because they significantly reduce the required number of RTE evaluations during calculations of radiative source terms for the energy conservation equations.
 
-With RadLib, we aim to provide researchers with a convenient, easy-to-use access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
+With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
 RadLib is a modular C++ library with an optional Python interface.
@@
 
-At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients (assuming optically thin media), a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
-Each of these models was specifically chosen for its notable qualities, attributes such popularity, ease of implementation, or accuracy; their individual strengths, weaknesses, and limitations are discussed in the sections that follow.
+At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients using the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
+Each of these models was specifically chosen for its notable attributes such as popularity, ease of implementation, or accuracy; their individual strengths, weaknesses, and limitations are discussed in the sections that follow.
 
@@
 While solving the RTE is not the focus of this software, RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
-Refer to Section \ref{s:Examples} for details.
+Refer to the example cases in Section \ref{s:Examples} for details.
 
-Radiation absorption coefficients are typically calculated by correlations developed using high-resolution databases like RADCAL, HITEMP, and HITRAN \citep{Grosshandler_1993,Rothman_2010} that relate spectral lines to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
+Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITEMP, and HITRAN \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
 At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The optically thin approximation assumes that there is little to no reabsorption of radiative energy in the system, or, in other words, that the system only emits radiation and does not absorb it.
-In combustion systems, optical thinness is often justified in terms of other flame properties such as low radiative heat transfer relative to chemical heat release or convective heat transfer (also used to justify neglecting radiation altogether in some cases).
-Assuming optical thinness, however, has the distinct advantage of simplifying the radiative source term (here denoted $S_{rad}$) of the energy conservation equation to
+In combustion systems, optical thinness is associated with various other flame properties such as low radiative heat transfer relative to chemical heat release or convective heat transfer, negligible amounts of soot or other large molecules, and relatively small flame lengths.
+These flame attributes are not universally indicative of optical thinness, but are often used to justify neglecting or simplifying radiative heat transfer modeling.
+Assuming optical thinness, however, has the distinct advantage of simplifying the radiative source term (denoted $S_{rad}$) of the energy conservation equation to
 \begin{equation}
@@
 
-Because of these limitations, the authors do not consider the PM model adequate for most combustion simulation cases and strongly recommend that RadLib users carefully consider its implications before using the PM model.
+Because of these limitations, the authors strongly recommend that RadLib users carefully consider the implications of the PM model before using it in combustion simulations.
 It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its popularity and widespread use.
-The examples included with the RadLib code and shown in Section \ref{s:Examples} demonstrate the deficiencies of the Planck Mean model in comparison to other models included with RadLib.
+The examples included with the RadLib code and shown in Section \ref{s:Examples} demonstrate the deficiencies of the PM model in comparison to other radiation property models included with RadLib.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The WSGG model was introduced in Sec.~\ref{s:models}.
+Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
 RadLib implements the WSGG model presented by Bordbar et al.
 \citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}.
-It uses four gray gases and one transparent gas, and considers gaseous species \ce{CO2} and \ce{H2O}.
-This version of the WSGG model is advantageous because it allows for arbitrary \ce{CO2} and \ce{H2O} compositions, increasing its accuracy and flexibility \citep{Bordbar_2020}.
+It models mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas.
 Absorption coefficients are calculated by
@@
 
-The correlations provided by Bordbar et~al.
-(2014) \cite{Bordbar_2014} are valid for $0.01\le M_r\le4$.
-In Bordbar et~al.
-(2020) \cite{Bordbar_2020} this range was extended to arbitrary $M_r$ by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$.
-That is, for \ce{CO2}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=0.01$ and pure \ce{CO2}; for \ce{H2O}, $\kappa_j$ and $a_j$ are interpolated between values at $M_r=4$ and pure \ce{H2O}.
+This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility.
+Most WSGG models are limited to a specific range of \ce{H2O}--\ce{CO2} molar ratios, including the predecessor of the current model, which used correlations valid for $0.01\le M_r\le4$ \citep{Bordbar_2014}.
+Bordbar et al.~\citep{Bordbar_2020} extended this range to arbitrary values of $M_r$ by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of the correlated range.
+As a result, the updated WSGG model, implemented in RadLib, can consistently and accurately handle any value of the \ce{H2O}--\ce{CO2} molar ratio.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The Spectral Line Weighted-Sum-of-Gray Gases (SLW) model represents a family of global approaches to radiative heat transfer in high-temperature gases that also includes Absorption Distribution Function (ADF) and Full Spectrum $k$-distribution (FSK) models, all of which are based on the same fundamental principle in modeling the gas absorption spectrum \cite{Solovjov_2016}.
+The spectral line-weighted-sum-of-gray-gases (SLW) model represents a family of global approaches to radiative heat transfer in high-temperature gases that also includes absorption distribution functions (ADF) and full spectrum $k$-distribution (FSK) models, all of which are based on the same fundamental principle in modeling the gas absorption spectrum \cite{Solovjov_2016}.
 In order to extend their spectral models from uniform conditions (isothermal, homogeneous gases) to nonuniform conditions (non-isothermal, non-homogeneous gases), these models take a reference approach in which local gas states are corrected relative to a reference state.
 Reference approaches, however, generally lack consistent reference states and can yield significant errors in cases with large spatial temperature gradients \cite{Solovjov_2017}.
-The Rank Correlated SLW (RCSLW) model is a unique extension of the generalized SLW model that does not require a specified gas reference state and preserves the emission term of the spectrally integrated RTE.
-% TODO: what does this last phrase mean: preserves the emission...?
+The Rank Correlated SLW (RCSLW) model is a unique extension of the generalized SLW model that does not require a specified gas reference state.
+
+The RCSLW model was chosen for RadLib for its accuracy and performance compared to other SLW and WSGG modeling approaches.
+A recent comparison of SLW modeling approaches revealed that ``the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases" \citep{Badger_2019}.
+The literature indicates that the RCSLW model has not yet been successfully applied to turbulent combustion simulations \cite{Modest_2016,Coelho_2017}.
+Other SLW models have been applied to gas--soot mixtures \cite{Solovjov_2001,Solovjov_2001b} and high-temperature non-isothermal gases \cite{Solovjov_2011,Solovjov_2020} with results that suggest their applicability to combustion systems.
+
+RadLib implements the RCSLW method presented by Solovjov et al.
+\cite{Solovjov_2017} as method I.2.2, which gives the best and most consistent results of the SLW methods discussed in the aforementioned study.
+A summary of the general SLW method and the RCSLW method are presented here, but additional information about these and various other SLW methods can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
+
+SLW and WSGG models are similar in that they approximate a real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed.
+In traditional WSGG models, the component gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}.
+In SLW approaches, however, the gases are gray in a given spectral band by construction.
+Rather than defining a gray gas $j$ by integrating over a band of sequential wavenumbers $\eta$ (which may have a highly variable absorption coefficient), SLW models define a gray gas $j$ by integrating over a set of nonsequential wavenumbers that correspond to a given value of the absorption cross section $C_{\eta}$.
+The absorption cross section is related to the absorption coefficient by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.
 %
-Recent comparison of advanced SLW modeling approaches revealed that ``the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases" \citep{Badger_2019}.
-A brief overview of the RCSLW model is given here; detailed discussion can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
-In particular, Solovjov et~al. \cite{Solovjov_2017} present several RCSLW methods within a generalized framework; RadLib implements method I.2.2, which gives the best results and is summarized here.
-%
-
-SLW models are similar to WSGG models, but SLW gases are gray in a given band by construction, whereas in traditional WSGG approaches the gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \cite{Badger_2019}.
-%
-Instead of integrating within a sequential band of $\eta$ (with highly variable $\kappa$) to define a gray gas $j$ as in other WSGG models, SLW models perform their spectral integration over a set of nonsequential wavenumbers constituting a given band $j$ of absorption cross sections $C_\eta$.
-%
-The absorption coefficient is related to the absorption cross section by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.
-%
-Using Solovjov's notation~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is the set of wavenumbers constituting gas $j$ in Eq.~\ref{e:RTE_wsgg}, where $\tilde{C}$ denotes a cross section boundary between two bands/gases.
-%
+Using Solovjov's notation in~\cite{Solovjov_2017}, $\Delta_j=\{\eta:\tilde{C}_{j-1}<C_\eta<\tilde{C}_j\}$ is defined as the set of wavenumbers that constitute the gray gas $j$, where $\tilde{C}$ denotes a cross section boundary between two gray gases.
 Hence, in SLW models, the gases in a given band are gray to within the width $\tilde{C}_j-\tilde{C}_{j-1}$.
 
-A gray gas weight $a_j$ is the fraction of blackbody emission from $\eta\in\Delta_j$ corresponding to a given cross-section band $j$.
-This weight $a_j$ is computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections less than $C$:
+The gray gas weight $a_j$ is the fraction of blackbody emission from the set of wavenumbers $\Delta_j$ that correspond to a given cross-section band $j$.
+Weights are computed using the absorption line blackbody distribution function (ALBDF) \cite{Pearson_2014}, which gives the fraction of total blackbody emission from $\eta$ corresponding to absorption cross sections smaller than an arbitrary absorption cross-section $C$:
 %
@@
 %
-so that
+where $\phi$ represents the thermodynamic state, $\sigma$ is the Stefan-Boltzmann constant, $T$ is temperature, and $E_b(\eta,T)$ is the blackbody emission at a given wavenumber $\eta$ and temperature $T$.
+As a result, a specific gray gas weight $a_j$ can be calculated as the difference between the ALBDF values at its cross-section boundaries:
 %
@@
 %todo: deal with T versus Tb in e:albdf and previous eqn.
-Note that $F$ varies between zero and one, and is monotonic in $C$, allowing calculation of the inverse $C(F,\BS{\phi},T)$.
+Note that $F$ varies between zero and one and is monotonic in $C$, which permits calculation of an inverse ALBDF $C(F,\BS{\phi},T)$.
 
-The WSGG RTE in Eq.~\ref{e:RTE_wsgg} assumes the sets $\Delta_j$ are independent of spatial position $\mathbf{x}$, but care must be taken since $C_\eta$ depends on the thermodynamic state (denoted by vector $\BS{\phi}$ with nominal components $T$, $P$, and $y_i$), which does vary spatially.
-That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$.
-Hence, spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and $\tilde{C}_j$.
+For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}.
+RadLib's RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
+%
+\begin{linenomath}
+	\begin{equation} \label{e:multiC}
+		C_{\eta} = Y_{\ce{CO2}}C_{\ce{CO2},\eta} + Y_{\ce{H2O}}C_{\ce{H2O},\eta} + Y_{\ce{CO}}C_{\ce{CO},\eta}
+	\end{equation}
+\end{linenomath}
+%
+Assuming that the absorption cross sections of each species are statistically independent, we can calculate the mixture ALBDF for a given gray gas using the multiplication method \cite{Solovjov_2000}:
+%
+\begin{linenomath}
+\begin{equation} \label{e:multiF}
+    F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{Y_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{Y_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{Y_{\ce{CO}}} \right).
+\end{equation}
+\end{linenomath}
+%
+Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
 
-The RCSLW model uses the notion of rank correlation to compute this variation in $C_j$ and $\tilde{C}_j$. 
-Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$. These will have corresponding spectra $C_\eta(\eta,\BS{\phi}_1)$, and $C_\eta(\eta,\BS{\phi}_2)$.
-Now, let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some wavenumber $\hat{\eta}$.
-For each of the two spectra, we can define the set of wavenumbers that give cross sections less than $\hat{C}$:
+The spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}) assumes the sets $\Delta_j$ are independent of spatial position $\mathbf{x}$, but $C_\eta$ depends on the thermodynamic state (denoted by vector $\BS{\phi}$), which does vary spatially.
+%That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$. 
+Hence, a spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and $\tilde{C}_j$. 
+The RCSLW model uses the notion of rank correlation to handle  this spatial variation in the ALBDF. 
+Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ with corresponding absorption cross section spectra $C_\eta(\eta,\BS{\phi}_1)$, and $C_\eta(\eta,\BS{\phi}_2)$ and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some wavenumber $\hat{\eta}$.
+For each spectrum, we define the set of wavenumbers that give cross sections less than $\hat{C}$ as
 %
@@
 %
-If $H_1=H_2$ for arbitrary $\hat{\eta}$, the spectra corresponding to $\BS{\phi}_1$ and $\BS{\phi}_2$ are said to be rank correlated.
+If $H_1=H_2$ for an arbitrary $\hat{\eta}$, then the spectra $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are said to be rank correlated.
 % Solovjov provides some visual representations...
 
-This rank correlation is used as follows. Consider Eq.~\ref{e:albdf} evaluated at $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at
-$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
+The RCSLW model uses rank correlation as follows.
+Consider Eq.~\ref{e:albdf} evaluated at an arbitray reference temperature $T_r$ for thermodynamic states $\phi_1$ and $\phi_2$ as detailed above:
+% $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
 %
@@
 %
-Since $H_1=H_2$, we have 
+Since $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are rank correlated (by definition), $H_1=H_2$ and we have 
 %
@@
 %
-Recall that $F$ can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are given, we can compute $F$ and then invert to obtain $\hat{C}_2$ at $\BS{\phi}_2$.
-Now, note that Eq.~\ref{e:FeqF} is assumed to hold for arbitrary states $\BS{\phi}_1$ and $\BS{\phi}_2$; hence, if some $F$ is given or specified, we can invert $F=F(\hat{C},\BS{\phi},T_r)$ to get $\hat{C}$ at corresponding state $\BS{\phi}$.
-At this point, we can drop the \emph{hat} notation and just write $F(C,\BS{\phi},T_r)$.
+Recall that the ALBDF can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are known, we can compute $F=F(\hat{C}_1,\BS{\phi_1},T_r)$ and then invert $F$ to obtain $\hat{C}_2$ at $\BS{\phi}_2$.
+Note that Eq.~\ref{e:FeqF} holds for arbitrary states $\BS{\phi}_1$ and $\BS{\phi}_2$, so any known $F=F(C,\BS{\phi},T)$ can be inverted to get $C$ at the corresponding state $\BS{\phi}$.
 
-Given the above summary development, the RCSLW model is applied as follows. 
+Given the concepts summarized above, the RCSLW model is applied to a problem of interest to calculate radiation absorption coefficients and weights as follows:
 %
 \begin{enumerate}
-    \item A reference temperature is specified. This is taken to be the average temperature on the domain of interest in \cite{Solovjov_2001}.
-    \item A collection of $\tilde{F}_j$ values are specified, with $F_j$ points between $\tilde{F}_j$ and $\tilde{F}_{j-1}$. These apply to all spatial positions. 
-    \item The corresponding $\tilde{C}_j$ and $C_j$ values at any spatial position and corresponding thermodynamic state $\BS{\phi}$ are found by inversion: $C_j = C(F_j,\BS{\phi},T_r)$, and $\tilde{C}_j = C(\tilde{F}_j,\BS{\phi},T_r)$
-    \item $\kappa_j$ is then computed as $\kappa_j=C_jN$. 
-    \item $a_j$ is computed from Eq.~\ref{e:aj}, where $T$ is taken as the local temperature.
+    \item Specify a reference temperature $T_r$ as the average temperature on the domain of interest \cite{Solovjov_2001}.
+Note that this is not the same as specifying a reference state $\BS{\phi}=\BS{\phi}_r(T_r,Y_r,P_r)$ as in done for SLW reference approaches.
+The RCSLW model has the significant advantage that it does not require a thermodynamic reference state.
+    \item Specify a collection of $F_j$ points and $\tilde{F}_j$ boundary values such that $F_j$ lies between $\tilde{F}_j$ and $\tilde{F}_{j-1}$. These apply to all spatial positions. 
+    \item Invert the ALBDF to calculate $C_j$ and $\tilde{C}_j$ at the corresponding thermodynamic state $\BS{\phi}$ and any spatial position where $C_j = C(F_j,\BS{\phi},T_r)$ and $\tilde{C}_j = C(\tilde{F}_j,\BS{\phi},T_r)$
+    \item Compute the gray gas absorption coefficients $\kappa_j=C_jN$. 
+    \item Compute the gray gas weights $a_j=F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1},\BS{\phi}, T)$ (Eq.~\ref{e:aj}) with the $C_j$ and $\tilde{C}_j$ values calculated in Step 3, the local thermodynamic state $\BS{\phi}$, and the local temperature $T$.
 \end{enumerate}
-%
 
-The ALBDF functions are provided by Pearson et~al.~\cite{Pearson_2014} for \ce{H2O}, \ce{CO2}, and \ce{CO} at pressures ranging from 0.1 to 50 atm, and temperatures from 300 to 3000 K in both tabulated and correlated form.
-The tabulated data are currently used in Radlib, coupled with multilinear interpolation.
-For gas mixtures, the multiplication method described in \cite{Solovjov_2000} is used, in which
-%
-\begin{linenomath}
-\begin{equation}
-    F(C) = F_{CO2}(C/y_{CO2})F_{H2O}(C/y_{H2O})F_{CO}(C/y_{CO}), 
-\end{equation}
-\end{linenomath}
-%
-where the $\BS{\phi}$ and $T$ arguments of $F$ are omitted for clarity.
+The ALBDF data for \ce{H2O}, \ce{CO2}, and \ce{CO}---valid for pressures between 0.1 atm and 50 atm and temperatures between 300 K and 3000 K---are provided by Pearson et al.
+\cite{Pearson_2014} and can be accessed in both correlated and tabulated form at \cite{Solovjov_2014b}.
+RadLib uses the tabulated data coupled with multilinear interpolation; both the tabulated data and the multilinear interpolator are included with the RadLib package as part of the RCSLW method.
 

### 2021-05-04 manuscript/manuscript.tex
Finished overall and reviewer-based revisions to paper text. Updated soem of the figures for consistent presentation.

@@
 The vast majority of computational combustion research that considers radiation employs an optically thin approximation despite its limited applicability to combustion processes.
-Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flame or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}.
+Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flames or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}.
 
@@
 
-RadLib can also account for the radiative properties of soot in combustion environments.
+RadLib can also account for the radiative properties of soot in gaseous combustion environments.
 Soot particles are assumed to be unagglomerated spheres that absorb and emit radiation at all wavelengths such that their optical properties can be determined using the Rayleigh small particle limit.
-Radiation scattering may be neglected because unagglomerated soot particles in the Rayleigh regime are still small relative to the wavelength of infrared radiation in flames \cite{Brewster_1992,Solovjov_2001}.
+This assumption implies that radiation scattering may be neglected because unagglomerated soot particles in the Rayleigh regime are still small relative to the wavelength of infrared radiation in flames \cite{Brewster_1992,Solovjov_2001}.
 The spectral soot absorption coefficient is given by
@@
 Various values for the refraction index have been proposed and applied \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}.
-% INSERT FIGURE SHOWING DIFFERENT MODELS
-RadLib uses the values $n=1.75$ and $k=1.03$ given in \cite{Williams_2007}, which result in a value of $C_0=7.03$, which is nearly the same as the value $C_0=7.0$ used in \cite{Solovjov_2001}. 
+RadLib uses the most current values in the literature: $n=1.75$ and $k=1.03$ \cite{Williams_2007}, resulting in a value of $C_0=7.03$, which is nearly the same as the value of $C_0=7.0$ used by Solovjov and Webb \cite{Solovjov_2001} to study radiative transfer in sooty gas mixtures.
 The Planck mean and Rosseland mean soot absorption coefficients are given in \cite{Modest_2013} as $\kappa_s=3.83f_vC_0T/C_2$ and $\kappa_s=3.60f_vC_0T/C_2$, respectively.
-Due to the small difference between the coefficients in these two expressions, a mean value is suggested \cite{Felske_1977,Modest_2013}:
+Due to the small difference between the coefficients in these two expressions, the mean value suggested by \cite{Modest_2013,Felske_1977} is used in RadLib's soot calculations:
 %
@@
 
-In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is added to the gas absorption coefficient.
-This gives $\kappa_s=1817f_vT$ \si{m^{-1}}.
-
-In the WSGG model, Bordbar suggested incorporating soot as follows \cite{Bordbar_personal}.
-The soot absorption coefficient is similarly calculated from Eq.~\ref{e:soot2} but is then added to each of the gases separately.
-Because soot radiates across all wavelengths, its absorption coefficient is added to the values of all four gray gases and the clear gas.
+In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient.
+Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ \si{m^{-1}}.
+
+In the WSGG model, the soot absorption coefficient is also computed using Eq.~\ref{e:soot2} but then added to each of the gray gases separately \cite{Bordbar_personal}.
+Because soot radiates across all wavelengths, its absorption coefficient is added to the value of the clear gas in addition to the values of all four gray gases.
 The gas weights $a_j$ are not changed.
-This model yeilds the expected behavior in the soot-only and gas-only limits.
-
-The soot model used in the WSGG model can be applied to the RCSLW model as well.
-However, the formulation of the RCSLW model allows for a spectral soot treatment in the same manner as the gas species~\cite{Solovjov_2001}.
+This model yields the expected behavior in the soot-only and gas-only limits.
+
+The WSGG soot treatment can be applied to the RCSLW model as well.
+Alternatively, the RCSLW model's formulation permits a spectral soot treatment in the same manner as the gas species~\cite{Solovjov_2001}.
 Calculation of the soot ALBDF is facilitated by the simple $\eta$ dependence of $\kappa_{s,\eta}$ in Eq.~\ref{e:soot1}.
-The fraction of the black energy at wavenumbers below $\eta$ is computed directly using a series expansion from Chang and Rhee \cite{Chang_1984,Solovjov_2001}.
-The soot ALBDF is then included in the product of species ALBDFs to obtain the mixture ALBDF.
+The fraction of total blackbody emission at wavenumbers below $\eta$ is computed directly using a series expansion presented by Chang and Rhee \cite{Chang_1984}.
+The soot ALBDF is then included in the product of species ALBDFs to obtain the mixture ALBDF, as in Eq.~\ref{e:multiF}.
 
@@
 RadLib is an object-oriented C++ class library that includes both C++ and Python interfaces.
-The RadLib package contains five subdirectories (upon initial download): \texttt{source} contains the RadLib source code; \texttt{build} contains installation files; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to generate code documentation with Doxygen (optional).
+Upon initial download, the RadLib package contains five subdirectories: \texttt{src} contains the RadLib source code; \texttt{build} contains installation files; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to optionally generate code documentation with Doxygen.
+An additional directory, \texttt{installed}, is created and populated with RadLib's executables and header files during installation if no other installation location is specified.
 
@@
 
-RadLib installation is automated with CMake.
-First, navigate to the \texttt{build} directory.
-If the user requires an installation location other than the default \texttt{installed} directory, edit the \texttt{user\textunderscore config} file before running CMake.
-To compile the package, run the command \texttt{cmake -C user\textunderscore config ../source}.
-Upon successful completion, run \texttt{make} and then \texttt{make install} to complete the process.
+RadLib installation is automated with CMake from within the \texttt{build} directory.
+If the user requires an installation location other than the default \texttt{installed} directory, edit the "Project Options" section of \texttt{build/CMakeLists.txt} file before running CMake.
+First, configure CMake by running the command \texttt{cmake .} from within the \texttt{build} directory.
+Upon successful completion, run \texttt{make} to compile the library and then \texttt{make install} to install it.
 To use RadLib in C++ projects, include the generated C++ library file, located at \texttt{installled/lib/libradlib.a}, and/or header files, located in \texttt{installed/include}, according to the project's build scheme.
+Installation also generates a relocatable RadLib package, located at \texttt{build/cmake/radlib/radlib.cmake}, for downstream usage.
 To use RadLib in Python, update the system \texttt{PYTHONPATH} environment variable and import the module, named \texttt{pyrad}, into the project.
@@
 Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces.
-The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry.
+The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular case geometry.
 After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights.
@@
 
-\section{Validation and Examples} \label{s:Examples}
-
-Several examples are presented to illustrate the behavior of the models.
-The examples show heat flux $q$ or volumetric heat source $Q$ in one one-dimensional configurations with varying gas compositions and temperatures.
-We compare the PM, WSGG, and RCSLW models for each example.
-The examples correspond to those presented by Solvojov et al.
+\section{Examples} \label{s:Examples}
+
+The RadLib package includes several example cases that illustrate the behavior of the models and interfaces.
+The examples compare the PM, WSGG, and RCSLW models via output heat flux $q$ or volumetric heat source $Q$ in one-dimensional configurations with varying gas compositions and temperatures.
+The RTE is solved between two parallel plates with a ray-tracing code, included in the RadLib package.
+Each case's results is presented alongside the line-by-line (LBL) data from its respective reference.
+
+Table~\ref{t:examples} summarizes the example cases.
+Each case is labeled according to its source---Solvojov et al.
 \cite{Solovjov_2017} (S), Bordbar et al.
-\cite{Bordbar_2020} (B), Solovjov et~al.
-\cite{Solovjov_2001} (Sb), and the number of each example corresponds to the example number in the respective reference.
-A ray-tracing code is used to solve the radiative transport equation between two parallel plates.
-Table~\ref{t:examples} summarizes the cases.
-Example S1 is a hot slab next to a cold slab where the cold slab's thickness varies; Example S2 is isothermal with a thick slab of high CO$_2$ next to a thin slab of low CO$_2$ with variable thickness; Example S3 uses parabolic temperature and H$_2$O mole fraction profiles; Example S4 has a triangular temperature profile between equally-spaced isothermal regions; Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K; and Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$).
-Example Sb1 is a simple uniform temperature and composition profile with soot radiation.
-Each case is presented alongside the line-by-line (LBL) data presented in the references.
+\cite{Bordbar_2020} (B), or Solovjov et~al.
+\cite{Solovjov_2001} (Sb)---and the number of each example corresponds to the example number in its respective reference.
+Each example case consists of one or more gas layers ("slabs") bounded by black walls.
+Example S1 consists of two adjacent gas layers with identical species compositions: one hot layer of constant thickness and one cold layer of varying thickness. 
+In Example S2, the two gas layers are isothermal but differ in the value of the \ce{CO2} mole fraction, where the layer thickness of the "thin" slab (with the smaller \ce{CO2} mole fraction) varies.
+Example S3 applies parabolic temperature and \ce{H2O} mole fraction profiles across a single gas layer. 
+Example S4 divides the gas into three equally-spaced layers and applies a triangular temperature profile to the middle layer and a constant temperature to the two outer layers.
+Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K applied to a single gas layer of constant species composition.
+Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$). 
+Example Sb1 consists of a single gas with a uniform temperature and composition profile and soot radiation. 
 %
 \begin{table}
-    \caption{Summary of example cases presented. S1-S5 are from \cite{Solovjov_2017}; B3 is from \cite{Bordbar_2020}; Sb1 is from \cite{Solovjov_2001}. All cases use $P=1$ atm and black walls.}
+    \caption{Summary of example cases. All cases use $P=1$ atm and black walls.}
     \label{t:examples}
@@
     \resizebox{\textwidth}{!}{
-    \begin{tabular}{c l l c c c}
+    \begin{tabular}{c l l c c c c}
         \hline
-        Example & T(K)                           & $y_{H2O}$  $y_{CO2}$ (mole frac.)                     & L (m)   & $T_{walls}$ (K)\\
+        Example & T(K)                          & $y_{H2O}$  $y_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.\\
         \hline
-        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$     & $y_{CO2}=0.1$, $y_{H2O}=0.2$                          & 0.5-2.5 & cold, cold     \\
-        S2 & T=1000                              & $y_{CO2}(x<0.5)=0.4$, $y_{CO2}(x>0.5)=0.1$            & 0.5-2.5 & cold, cold     \\
+        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$    & $y_{CO2}=0.1$, $y_{H2O}=0.2$                    & 0.5-2.5 & cold, cold	& \cite{Solovjov_2017}     \\
+        S2 & T=1000                             & $y_{CO2}(x<0.5)=0.4$, $y_{CO2}(x>0.5)=0.1$      & 0.5-2.5 & cold, cold & \cite{Solovjov_2017}    \\
            &                                    & $y_{H2O}=0.0$                                   &         &                \\
-        S3 & $T(x) = 4000x(L-x)/L^2 + 800$       & $y_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$                   & 1       & 800, 800       \\
+        S3 & $T(x) = 4000x(L-x)/L^2 + 800$      & $y_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$             & 1       & 800, 800 & \cite{Solovjov_2017}      \\
            &                                    & $y_{CO2}=0$                                     &         &                \\
-        S4 & middle third triangular to 2500     & $y_{H2O}=0.1$, $y_{CO2}=0$                            & 0.3     & 500, 500       \\
-        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$    & $y_{H2O}=0.1$, $y_{CO2}=0$                            & 2       & 1500, 500      \\
-        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$  & $y_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$         & 1       & 400, 400       \\
+        S4 & middle third triangular to 2500    & $y_{H2O}=0.1$, $y_{CO2}=0$                      & 0.3     & 500, 500 & \cite{Solovjov_2017}      \\
+        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$ 	 & $y_{H2O}=0.1$, $y_{CO2}=0$                      & 2       & 1500, 500 & \cite{Solovjov_2017}     \\
+        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $y_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$	& 1       & 400, 400 & \cite{Bordbar_2020}      \\
            &                                    & $y_{CO2}=1-y_{H2O}$                             	&         &                \\
-        Sb1& $T = 1000$                          & $y_{H2O} = 0.2$, $y_{CO2}=0.1$, $y_{CO}=0.03$         & 1       & cold, cold     \\
+        Sb1& $T = 1000$                         & $y_{H2O} = 0.2$, $y_{CO2}=0.1$, $y_{CO}=0.03$   	& 1       & cold, cold & \cite{Solovjov_2001}    \\
         \hline
@@
 %
+
 The examples are provided with the RadLib code and implemented in both C++ and Python.
@@
 
-These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these examples and their motivations can be found in their respective references. 
-%TO DO address this:
-While ommitted here for brevity, the implemented WSGG and RCSLW models give essentially identical results to those presented in \cite{Solovjov_2017,Bordbar_2020} such that these examples also serve as a validation of the implementation of the models.
-
-Figure~\ref{f:examples} shows comparative results for the different radiation models for these cases. 
+These cases are intended to illustrate the use of the RadLib library and are not exhaustive.
+Details about these examples and their motivations can be found in their respective references.
+Comparison of these results to the LBL data and to the results presented in the source references also serves as a validation of RadLib's implementation of the WSGG and RCSLW models.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Results and Discussion} \label{s:discussion}
+
+Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}.
+In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied.
+The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature instead.
 %
@@
         Example S1 & Example S2 \\
-        \includegraphics[width=2.75 in]{fig_ex_1.pdf} &
-        \includegraphics[width=2.75 in]{fig_ex_2b.pdf} \\
+        \includegraphics[width=2.75 in]{fig_ex_S1.pdf} &
+        \includegraphics[width=2.75 in]{fig_ex_S2b.pdf} \\
         Example S3 & Example S4 \\
-        \includegraphics[width=2.75 in]{fig_ex_3a.pdf} &
-        \includegraphics[width=2.75 in]{fig_ex_4a.pdf} \\
+        \includegraphics[width=2.75 in]{fig_ex_S3a.pdf} &
+        \includegraphics[width=2.75 in]{fig_ex_S4a.pdf} \\
         Example S5 & Example B3 \\
-        \includegraphics[width=2.75 in]{fig_ex_5b.pdf} &
-        \includegraphics[width=2.75 in]{fig_ex_6.pdf}
+        \includegraphics[width=2.75 in]{fig_ex_S5c.pdf} &
+        \includegraphics[width=2.75 in]{fig_ex_B3.pdf}
     \end{tabular}
-    \caption{Results for examples summarized in Table~\ref{t:examples}.}
+    \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}.}
     \label{f:examples}
@@
 \end{figure}
-%
-In general, the PM model performs poorly compared to the WSSGG and RCSLW models.
-A notable exception is Example S4.
-In Example S2, the PM $q(L)/\sigma T^4$ is off scale at an essentially constant at a value of unity.
-The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, giving optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively, which are relatively small compared to the isothermal domain size greater than 0.5 m.
-Example S5 omits the PM model to more clearly show the behavior of the WSGG and RCSLW models.
-For that example, the PM values follow the shape of the other curves but $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m, and dropping to 100 kW/m$^3$ at $x=2$ m.
-In all examples, four gray ($n=4$) and one clear gas are computed for the RCSLW models to give a consistent comparison to the WSGG model.
-Example S5 shows the sensitivity of the RCSLW model to the number of gases used.
-The difference between $n=2$ and $n=8$ is very small for all examples shwon, except for Example S2.
-When $n$ is increased from four to eight for that example the RCSLW model improves to show nearly perfect agreement with the LBL data.
-In all Examples, the RCSLW model is initialized using the mean temperature and composition on the domain.
-In Example S5, the RCSLW model converges to the LBL solution when the model is initialized using the maximum temperature instead of the average temperature.
-
-Figure~\ref{f:exSb1} shows the results from Example Sb1, which includes soot radiation.
-Results for three values of the soot volume fraction are shown.
-Both the WSGG and RCSLW models perform very well for each case.
 %
@@
 
+In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data.
+The data for Examples S1, S3, and B3 show that the PM model tends to exaggerate the trends displayed by the other models; this is also true of Example S4, though the effect is somewhat overshadowed by the WSGG model results.
+The PM data mimics the shape of the other curves in Example S5 as well, but with such greatly exaggerated peaks and valleys that its data was omitted from the plot to more clearly display the behavior of the WSGG and RCSLW models; for the PM model in Example S5, $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m and drops to 100 kW/m$^3$ at $x=2$ m.
+In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity.
+The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively.
+These values are small compared to the domain sizes considered in Example S2, which coincides with the PM model's use of the optically thin approximation, but the high error in its predictions of radiative heat flux relative to the LBL data indicates that neither the optically thin approximation nor absorption coefficients calculated with this model are accurate for this case.
+Example S3 is the clearest illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model severely overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.
+
+The WSGG model gives somewhat accurate but inconsistent results for the example cases considered here.
+In Examples S1, S3, S5, B3, and Sb1, it behaves as expected, producing results that are closer to the LBL data than those produced by the PM model but fall short of the RCSLW model's level of accuracy.
+In general, the WSGG model appears to perform best at intermediate temperatures and deviates from the desired behavior at boundary conditions, but this is not universal.
+For example, the WSGG model shows uncharacteristically high accuracy in Example S2; its results with four gray gases are comparable in accuracy to the RCSLW model's performance using eight or more gray gases.
+In contrast, the WSGG model performs exceptionally poorly in Example S4, in which it deviates from the LBL data by nearly an order of magnitude at its largest.
+The WSGG model, alongside with the PM model, is primarily empirical and contains little to no representative physics, which could explain the unexpected behavior in Examples S2 and S4.
+Given that all of the example cases use parameters within those specified for the WSGG model in the literature \cite{Bordbar_2014,Bordbar_2020}, neither anomalous result has an obvious source.
+While we cannot offer an explanation for the WSGG model's inconsistent performance, it serves to underscore the importance of individual model validation on a case-by-case basis, a task potentially made easier with tools like RadLib.
+
+The RCSLW model displays the most accurate results of the three implemented property models when compared to LBL data, capturing the relevant trends without exaggerating them.
+It is, however, the most difficult of the three models to implement and requires either correlated or tabulated spectral data to draw from.
+The RCSLW model can also be sensitive to the number of gray gases used, illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
+The difference in accuracy between $n=2$ and $n=8$ gray gases is very small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
+Example S2 shows the most prominent variations in predicted radiative heat flux based on changes in the number of gray gases, improving drastically in agreement to the LBL data with the addition of just four gray gases.
+RCSLW model convergence can also vary with the value of the chosen reference temperature; in Example S5, for instance, the RCSLW model converges to the LBL data if it is initialized with the maximum rather than the average temperature on the domain.
+When treated properly, however, the RCSLW model provides the most accurate results of all of the radiation property models considered here.
+
+Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume fraction in addition to the radiating gas.
+Both the WSGG and RCSLW models perform accurately in all three cases, but the PM model displays significant deviations from the LBL data.
+In sooting flames, soot acts as a significant source and sink of radiation, and its radiative properties differ significantly from those of the participating gaseous species.
+Soot reactions and transport are both sensitive to and strongly influence local variations in flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
+The agreement produced by RadLib's approach to soot radiation in Example Sb1 is an encouraging step toward accurate, detailed treatment of soot's radiative properties in complex combustion simulations.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Discussion} \label{s:impact}
-
-%Note that we are presenting and not evaluating the models and make no claims as to causes of the results presented in the previous section.
-Several of the example cases deviate from the expected behavior (i.e.
-S2, S4).
-Also note that the PM and WSGG models are mostly empirical and contain very little representative physics, which can cause them to behave unpredictably in parameter ranges outside of those for which the models were specifically developed.
-If we look at Bordbar's paper, WSGG looks really good, but Example S4 gives us behavior we don't expect---WSGG performs very poorly.
-We don't know why, and we don't intend to explain it, but this is a good illustration of the fact that sometimes models need to be tested independently before application to a specific project.
-Sometimes a model that seems perfect may not be for your case, and RadLib is a good tool for investigating things like that.
-
-Radiative heat transfer models are historically difficult to implement in CFD codes due to their complexity and high computational costs.
-Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results.
-In such cases, radiation models that are incorrectly implemented or inappropriate for the simulation parameters can become additional sources of error that may be extremely difficult to separate from existing sources or error.
-Currently, researchers that require detailed radiation modeling must code and validate it themselves at the expense of valuable research time and funding.
-
-RadLib makes researchers' work easier by consolidating various approaches into a modular library of interchangeable, prevalidated radiation models.
-Additionally, RadLib's modular framework can also accommodate new models, allowing researchers to compare new or existing models with very little overhead.
-Sometimes, it is not clear which radiation model may be the best fit for a particular simulation.
-When simulations are especially complex or computationally expensive, researchers may have to extrapolate from theory and literature to choose an appropriate radiation model rather than testing for their specific case.
-RadLib is designed to ease both of these obstacles by facilitating comparison between radiation models through a common interface and providing a practical means of testing various models without the restriction of prespecified geometry or case parameters.
-With RadLib, researchers can put more of their time and effort into useful results rather than code or model development.
-
-Currently, RadLib is only used within the authors' research group, where it is applied to combustion CFD simulations using the One-Dimensional Turbulence (ODT) model \cite{Stephens_2020}, but its design and structure as a C++ library allows it to be incorporated easily into existing codes.
-It can be applied to  research questions in various other fields involving radiative heat transfer as well, including energy engineering or atmospheric and climate sciences.
-Radiation is a universal phenomenon, and RadLib can assist researchers in many areas with systems and processes that involve heat transfer.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \subsection{Computational Cost} \label{s:cost}
 
-A comparison was made of the computational cost of the current models implemented.
-Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7.
-Figure~\ref{f:cost}a shows the cost to compute the gas properties $k$ and $a$.
-This was done by timing the C++ code execution to evaluate the gas properties one million times in a loop and then averaging the results.
-The figure shows times normalized by the time for the WSGG model, which required 8.0E-7~s.
-The costs of the models, relative to WSGG, is 0.098, 1.9, 4.9, 9.4, and 18, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively.
+In addition to comparing model attributes and performance, we evaluated and compared the computational cost of the implemented radiation property models. 
+Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7; the results, normalized by the cost of the WSGG model, are summarized in Figure~\ref{f:cost}.
+
+Figure~\ref{f:cost}a displays the relative cost to compute the gas properties $k$ and $a$, represented by the time required to execute the C++ function \texttt{get\textunderscore k\textunderscore a()}, averaged over one million evaluations.
+The results for each model are normalized by the WSGG model, which required an average of 8.0E-7~s.
+Relative to the WSGG model, the cost to evaluate the gas properties with the PM model was 0.098.
+The RCSLW model was evaluated with $n=1$, 2, 4, and 8 gray gases, which resulted in relative costs of 1.9, 4.9, 9.4, and 18, respectively.
 The cost of the RCSLW model is very nearly proportional to the number of gray gases considered.
@@
     \end{tabular}
-    \caption{Computational cost to evaluate gas properties (a) and to run Example S3 (b). Results are normalized by the cost of the WSSG model.}
+    \caption{Relative computational cost to (a) evaluate gas properties only and (b) run Example S3, including the ray-tracing solver.
+Results are normalized by the cost of the WSSG model for each case.}
     \label{f:cost}
@@
 
-Figure~\ref{f:cost}b shows the cost to evaluate Example S3. 
-In this case the costs of the models, relative to WSGG, is approximately 0.75, 1.1, 1.4, 1.9, and 2.9, for PM, and RCSLW with $n=1$, 2, 4, 8 gray gases, respectively.
-Here, the WSGG model took 0.0079 s.
-In running Example S3, the costs of the various models are much more similar than in evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.
+Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver.
 In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.
-
-Cost comparisons were also attempted with Python, but it is difficult to get meaningful results when mixing Python and C++.
-In particular, the cost of a single evaluation of the gas properties is small and evaluating the gas properties in a Python loop results in the loop appearing to dominate the computational cost.
-Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Fig.~\ref{f:cost} the cost only varied by about 4\%, indicating that the costs are dominated by the Python and not by the model calculations themselves.
+Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.
+In running Example S3, the model costs vary much less than when evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.
+
+Cost comparisons were also attempted with Python, but  meaningful results are difficult to obtain when mixing Python and C++.
+In particular, the cost of a single evaluation of the gas properties is small and evaluating the gas properties in a Python loop results in the loop itself appearing to dominate the computational cost.
+Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Figure~\ref{f:cost} the cost only varied by about 4\%, indicating that the computational cost is dominated by Python itself rather than by the model evaluations or solver.
 The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version.
-It is possible that improvements to the Python speed could be made by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.
+It is possible that optimizing the Cython interface could improve the speed and relative cost of using Python with RadLib, but RadLib's Python interface and examples are mainly intended to demonstrate the library's use rather than serve as a point of incorporation into detailed CFD calculations, which rarely employ Python.
 
@@
 
-RadLib is a C++ library of radiation property models developed to address the complexity and difficulty inherent in implementing radiative property models in CFD simulations.
-At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interfaces permit convenient expansion to additional property models.
-To that end, the basic structure and use of the RadLib library has been laid out.
-In addition, the RadLib package includes example cases in several variations of a parallel planes geometry using a simple ray tracing solver to illustrate the use of the three radiation property models.
-These examples are compared to line-by-line solutions.
-In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy, but, under the appropriate conditions, the PM and WSGG models can also perform well and boast lower computational costs than the RCSLW model.
-As a whole, RadLib provides a convenient access point for researchers that require radiation property models for simulation tools and can be applied to research problems in a variety of fields.
+Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to their high level of conceptual and mathematical complexity and potentially large computational cost.
+The vast majority of combustion CFD studies either neglect radiative heat transfer modeling or employ oversimplified models that do not accurately represent combustion systems.
+Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield accurate results.
+
+We presented RadLib, a C++ library of radiation property models developed to ease some of the obstacles and reduce the complexity inherent to the process of implementing radiative property models in CFD simulations.
+At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interfaces permit expansion to additional property models.
+Each of the implemented models has been validated and the library's structure and functionality has been outlined.
+
+In addition to the library itself, the RadLib package includes several illustrative example cases in a one-dimensional parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model implementation.
+Results are compared to line-by-line (LBL) solutions.
+In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy at the expense of computational cost.
+Under appropriate conditions, the WSGG model can also produce accurate results at significantly lower computational cost, but may perform inconsistently under certain conditions.
+In general, the PM model is adequate in situations to which the optically thin approximation can be reasonably applied, but does not produce accurate results in any of the example cases presented here.
+
+RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for combustion CFD, but could potentially be applied to research problems involving radiative heat transfer in a variety of other fields as well.
+RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single extensible library with a consistent framework, reducing some of the overhead associated with choosing,  implementing, and testing radiation property models.
+Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions.
+By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations.
+With RadLib, we believe that researchers will be able to put more of their time and effort into meaningful results rather than code or model development for radiative heat transfer in combustion CFD.
 

### 2021-05-04 submissions/CPC_response_to_reviewers.md
Update CPC_response_to_reviewers.md

@@
 Even though none of these statements were explicitly made, they must be implied for the reviewer to come to these conclusions.
-As such, revisions have been made throughout the paper to reduce subjective language, support generalized statements with additional explanation and/or references, and include due discussion of RadLib's limitations.**
+As such, revisions have been made throughout the paper to reduce subjective language, support generalized statements with additional explanation and/or references, and include due discussion of RadLib's limitations.
+Section 5 in particular has undergone heavy revision.**
 
@@
 
-**TO DO: consult Josh about appropriate tests for RadLib**
+	**The authors acknowledge the lack of tests associated with the library and note that basic test coverage is currently being developed.**
 
@@
 
-		**Installation now includes a ```radlib.cmake``` file, located in the ```installed/cmake/radlib``` directory, for downstream usage.**
+		**Installation now includes a ```radlib.cmake``` file, located by default in the ```installed/cmake/radlib``` directory, for downstream usage.**
 
@@
 
-		**The authors have experienced no issues running the example executables from either the ```build/examples``` directory or directly from the ```examples``` directory.**
+		**The authors have experienced no issues running the example executables from either the ```build/examples``` directory or directly from the ```examples``` directory.
+More information is required to address this issue.**
 
@@
 
-		**Executables are built within the example folders in addition to the build directories, so ```run_examples.sh``` runs without any issues and serves as a simple illustration of the example cases.**
+		**Executables are built within the example folders in addition to the build directories, so ```run_examples.sh``` runs without any issues.**
 
@@
 
-	**This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation property data, not to evaluate or compare the included models.
+	**This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation properties, not to evaluate the included models.
 All of the reviewer's questions are addressed in detail in the referenced literature (Planck Mean coefficients in [3,5] and WSGG in [10,11]).
@@
 
+	**Major revisions have been made to the paper text to clarify points like these for readers who do not specialize in combustion processes or modeling and provide additional information about why these models were chosen for implementation in RadLib.**
+
 9. Documentation:
@@
 **The authors would like to thank the reviewer for their comments and suggestions.
-We have already begun working on coupling RadLib to CFD software (that includes a DOM model for the RTE solution, among other features) in order to demonstrate RadLib's capabilities.**
+We have already begun working on coupling RadLib to CFD software (that includes a DOM solver for the RTE solution, among other features) in order to demonstrate RadLib's capabilities.**
 
@@
 The reviewer's request for an explanation, however, is valid.
-A brief discussion has been added to Section 5 to address these specific discrepancies.
+The discussion in Section 5 has been expanded and revised to address these specific discrepancies.
 Additional information about the specific limitations, strengths, and weaknesses associated with each model can be found in Section 2.**
@@
 	**While it is true that the purpose of this paper is to present the RadLib library rather than evaluate or compare the models, the authors believe that example case results in Figures 2 and 3 are important to the illustration of RadLib's capabilities.
-The reviewer's point about presentation without explanation, however, is valid; to that end, the discussion in Section 5 has been expanded somewhat to acknowledge, if not fully explain or provide cause for, various features and descrepancies in the example case results.
-Due to the empirical nature of the PM and WSGG models, it is very difficult to identify, explain, or rectify unexpected behavior.
-It should be noted, however, that any model, and especially empirical models, can behave unpredictably when applied to parameter ranges or conditions outside of those for which is was developed.**
+The reviewer's point about presentation without explanation, however, is valid; to that end, the discussion in Section 5 has been expanded to acknowledge, if not fully explain or provide cause for, various features and descrepancies in the example case results.
+Due to the empirical nature of the PM and WSGG models, it is very difficult to identify, explain, or rectify unexpected behavior.**
 
@@
 The ray-tracing solver used in the example cases is provided for convenience and demonstration purposes.**
+
+	**Note that Section 4.1 has since been moved to Section 5. It and the appropriate figure captions have also been revised for clearer communication of the points above.**
 
@@
 
-	**References have been added throughout to bolster weakly supported arguments. Note that the quoted statement and related discussion has been moved to Section 5 due to unrelated revisions.**
+	**References have been added throughout the text to bolster weakly supported arguments.
+Due to unrelated revisions, the quoted statement and related discussion is now located in Section 2.1 since it is most closely related to the Planck Mean model and its limitations.**
 
@@
 
-	**These statements regarding PM absorption coefficients are generally true.
+	**The reviewer's statements regarding PM absorption coefficients are generally true.
 In combustion simulations, low radiative heat transfer relative to other heat sources, including chemical heat release and convective heat transfer, usually does, in fact, indicate very low radiative reabsorption rates.
-Sectiom 2.1 has been revised to clarify this connection.
+Sectiom 2.1 and related discussion elsewhere has been revised to clarify this connection.
 The quoted sentence now reads as follows: "The Planck Mean model is most appropriate under optically thin conditions in which low radiative transfer relative to other heat sources, including but not limited to chemical heat release and buoyancy-driven convection in combustion systems, indicates that very little radiative reabsorption is occuring."**

### 2021-07-19 submissions/CPC_response_to_reviewers.md
Editing the software section: fortran, get_k_a_onebranch

@@
 
-**The authors would like to thank the reviewer for their time and knowledge.
-While we disagree with some of the reviewer's comments and suggestions, they are, overall, constructive and helpful to the paper's development.**
+**The authors would like to thank the reviewer for their time and careful review.**
 

### 2021-07-19 manuscript/manuscript.tex
Editing the software section: fortran, get_k_a_onebranch

@@
 
-RadLib is an object-oriented C++ class library that includes both C++ and Python interfaces.
-Upon initial download, the RadLib package contains five subdirectories: \texttt{src} contains the RadLib source code; \texttt{build} contains installation files; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to optionally generate code documentation with Doxygen.
+RadLib is an object-oriented C++ library that includes C++, Python, and Fortran interfaces.
+Upon initial download, the RadLib package contains four subdirectories: \texttt{src} contains the RadLib source code; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to optionally generate code documentation with Doxygen.
 An additional directory, \texttt{installed}, is created and populated with RadLib's executables and header files during installation if no other installation location is specified.
-
-The \texttt{source} and \texttt{examples} directories are further divided into \texttt{C++} and \texttt{Python} subdirectories to differentiate between interfaces.
-There are three interface options for using this code: C++, Python, and Cython-wrapped Python.
-C++ interfaces are located within the \texttt{examples/c++} folder, while Python interfaces are located within the \texttt{examples/python} folder.
-When running examples with Python, the Cython-wrapped version is the default; to run the regular Python version without the Cython wrapper, edit the comments near the top of the example files (i.e \texttt{ex\textunderscore S1.py}).
+The \texttt{src} and \texttt{examples} directories are further divided into \texttt{c++}, \texttt{python}, and \texttt{fortran} subdirectories to differentiate between interfaces. 
+%There are three interface options for using this code: C++, Python, and Cython-wrapped Python. 
+%C++ interfaces are located within the \texttt{examples/c++} folder, while Python interfaces are located within the \texttt{examples/python} folder. 
+%When running examples with Python, the Cython-wrapped version is the default; to run the regular Python version without the Cython wrapper, edit the comments near the top of the example files (i.e \texttt{ex\textunderscore S1.py}).
 The C++ interface produces the fastest-running code, followed by the Cython-wrapped Python interface and then the regular Python interface.
 
-RadLib installation is automated with CMake from within the \texttt{build} directory.
-If the user requires an installation location other than the default \texttt{installed} directory, edit the "Project Options" section of \texttt{build/CMakeLists.txt} file before running CMake.
-First, configure CMake by running the command \texttt{cmake .} from within the \texttt{build} directory.
-Upon successful completion, run \texttt{make} to compile the library and then \texttt{make install} to install it.
-To use RadLib in C++ projects, include the generated C++ library file, located at \texttt{installled/lib/libradlib.a}, and/or header files, located in \texttt{installed/include}, according to the project's build scheme.
-Installation also generates a relocatable RadLib package, located at \texttt{build/cmake/radlib/radlib.cmake}, for downstream usage.
-To use RadLib in Python, update the system \texttt{PYTHONPATH} environment variable and import the module, named \texttt{pyrad}, into the project.
-
-The interfaces, solver, and examples included with the library serve to demonstrate its use and validate the implementation and results.
-Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces.
-The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular case geometry.
-After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights.
-For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively.
-For information about adding additional radiative property models to the RadLib library, please refer to the package documentation.
+RadLib installation is automated with CMake as follows.
+Inside the downloaded \texttt{radlib} folder, the user creates and enters a \texttt{build} directory, then enters the commands \texttt{cmake ..}, followed by \texttt{make}, followed by \texttt{make install}.
+Project options are specified by editing the top-level \texttt{CMakeLists.txt} file where the options are clearly marked.
+These can also be specified at the command line.
+Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and fortran; and an option to build the documentation.
+
+The code installation folder includes directories \texttt{include} containing header files and a fortran module file, \texttt{lib} containing library files for each interface, and \texttt{rcslw_data} containing binary data files used by the RCSLW model.
+These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name.
+The \texttt{include} directory contains the following interface header and module files:
+%
+\begin{itemize}
+    \item \texttt{rad_planck_mean.h},
+    \item \texttt{rad_wsgg.h},
+    \item \texttt{rad_rcslw.h},
+    \item \texttt{rad_module.mod}.
+\end{itemize}
+%
+The C++ and Fortran libraries in the \texttt{lib} folder are
+\begin{itemize}
+    \item \texttt{libradlib.a},
+    \item \texttt{libradlib_fortran.a},
+\end{itemize}
+%
+This folder also contains the python module.
+The code installation additionally generates a relocatable CMake package for downstream usage, located at \texttt{build/cmake/radlib/radlib.cmake}.
+If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable.
+A command to do this is provided at the end of the installation (for example, \texttt{export PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:$PYTHONPATH"}).
+
+To use RadLib in C++, a user code includes the header file for the desired radiation model, e.g., \texttt{#include "rad_rcslw.h"}.
+For Fortran, a \texttt{use rad_module} statement provides access to the required interface functions.
+The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad_rcslw}.
+Such usage is demonstrated in the code examples, discussed below.
+Compilation of C++ and Fortran programs requires specification of the header/module and library directory locations and linking against the installed libraries (\texttt{libradlib.a} for C++ and both \texttt{libradlib.a} and \texttt{libradlib_fortran.a} for Fortran).
+
+Figure \ref{fig:flowchart} illustrates the basic structure of using of RadLib in a generic one-dimensional RTE solution.
+The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver.
+A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()}, or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
+These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}.
+The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}.
+A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters.
+The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first).
+The PM model only considers one gas and the vectors are of unity size.
+The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument.
+This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}.
+The absorption coefficients and weights are returned through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface.
+Additional details are included in the program documentation and code listing.
 %

### 2021-07-19 manuscript/manuscript.tex
edits to section 3 software, and latex compilation

@@
 The \texttt{src} and \texttt{examples} directories are further divided into \texttt{c++}, \texttt{python}, and \texttt{fortran} subdirectories to differentiate between interfaces.
-%There are three interface options for using this code: C++, Python, and Cython-wrapped Python. 
-%C++ interfaces are located within the \texttt{examples/c++} folder, while Python interfaces are located within the \texttt{examples/python} folder. 
-%When running examples with Python, the Cython-wrapped version is the default; to run the regular Python version without the Cython wrapper, edit the comments near the top of the example files (i.e \texttt{ex\textunderscore S1.py}).
-The C++ interface produces the fastest-running code, followed by the Cython-wrapped Python interface and then the regular Python interface.
 
@@
 These can also be specified at the command line.
-Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and fortran; and an option to build the documentation.
-
-The code installation folder includes directories \texttt{include} containing header files and a fortran module file, \texttt{lib} containing library files for each interface, and \texttt{rcslw_data} containing binary data files used by the RCSLW model.
+Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and an option to build the documentation.
+
+The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, 
+\texttt{lib} containing library files for each interface, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model.
 These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name.
-The \texttt{include} directory contains the following interface header and module files:
+The \texttt{include} directory contains the following interface header and module (Fortran) files:
 %
 \begin{itemize}
-    \item \texttt{rad_planck_mean.h},
-    \item \texttt{rad_wsgg.h},
-    \item \texttt{rad_rcslw.h},
-    \item \texttt{rad_module.mod}.
+    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
+    \item \texttt{rad\textunderscore wsgg.h},
+    \item \texttt{rad\textunderscore rcslw.h},
+    \item \texttt{rad\textunderscore module.mod}.
 \end{itemize}
@@
     \item \texttt{libradlib.a},
-    \item \texttt{libradlib_fortran.a},
+    \item \texttt{libradlib\textunderscore fortran.a},
 \end{itemize}
 %
-This folder also contains the python module.
+This folder also contains the Python module.
 The code installation additionally generates a relocatable CMake package for downstream usage, located at \texttt{build/cmake/radlib/radlib.cmake}.
 If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable.
-A command to do this is provided at the end of the installation (for example, \texttt{export PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:$PYTHONPATH"}).
-
-To use RadLib in C++, a user code includes the header file for the desired radiation model, e.g., \texttt{#include "rad_rcslw.h"}.
-For Fortran, a \texttt{use rad_module} statement provides access to the required interface functions.
-The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad_rcslw}.
-Such usage is demonstrated in the code examples, discussed below.
-Compilation of C++ and Fortran programs requires specification of the header/module and library directory locations and linking against the installed libraries (\texttt{libradlib.a} for C++ and both \texttt{libradlib.a} and \texttt{libradlib_fortran.a} for Fortran).
+A command to do this is provided at the end of the installation, for example, \\ {\scriptsize \texttt{export PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.
+
+To use RadLib in C++, a user code includes the header file for the desired radiation model, e.g., \texttt{\#include "rad\textunderscore rcslw.h"}.
+For Fortran, a \texttt{use rad\textunderscore module} statement provides access to the required interface functions.
+The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}.
+Such usage is demonstrated in the code listing for the examples discussed below.
+Compilation of C++ and Fortran programs requires specification of the header/module and library directory locations and linking against the installed libraries (\texttt{libradlib.a} for C++ and both \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a} for Fortran).
 
@@
 This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}.
-The absorption coefficients and weights are returned through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface.
+The absorption coefficients and weights are set through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface.
 Additional details are included in the program documentation and code listing.

### 2021-07-19 submissions/CPC_response_to_reviewers.md
DOL: reviewer 1 responses finished, with corresponding checks of the paper and code. The paper will need to be gone through and edited still.

@@
 
-**The authors would like to thank the reviewer for their time and careful review.**
+**The authors thank the reviewer for their time and careful review.**
 
@@
 
-	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.**
+	**Section 3 has been significantly revised and extended to include more information on how users can include and interact with the RadLib library.
+This includes a description of the build procedure and a list of installed files.
+Compilation of user code with RadLib is outline.
+A description of the interface functions is also provided.
+The key interface function was ```get_k_a(...)```.
+An additional function is now included and described, ```get_k_a_oneband(...)```.
+The function arguments are now described.
+Since the initial submission, a Fortran 90 interface has been added and this is included in the section.**
 
@@
 	1. First sentence: “historically difficult to implement … complexity and high computational costs”
-		-Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
-        	-I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
+		- Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
+        	- I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).
 
@@
 
-    **The authors have a number of concerns about the reviewer's claims here that they would like to address.
-First, note that the subject of the first sentence of Section 5 is "radiative heat transfer models", which does not refer specifically to either radiation property models or RTE evaluation methods, but the treatment of computational radiative heat transfer as a whole.
-This generalization holds for the entire first paragraph of Section 5.
-Additionally, at no point in the paper do the authors claim that property evaluation is more complex or computationally expensive than the RTE solution, only that it "can be a difficult and time-consuming portion of radiation calculations" (pg.
-2).
-Likewise, the paper contains no claims about the complexity of radiation property models in relation to other aspects of combustion simulations.
-(On this topic, however, the authors would like to point out that these other aspects of combustion simulations are typically well-characterized in both commercial and open-source CFD codes and do not require very much user interaction, whereas radiation modeling is often absent or highly simplified.) The second paragraph of Section 5 is a brief discussion on how RadLib can benefit researchers that draws from the authors' experiences.
-It does not claim that RadLib will solve any of the challenges of radiation modeling, only that it can "ease .
-.
-.
-obstacles", which the authors believe it can do.**
+    **In the first sentence and paragraph of Section 5, "radiative heat transfer models" does not refer specifically to either radiation property models or RTE evaluation methods, but the treatment of computational radiative heat transfer as a whole.
+This generalization was intended for the entire first paragraph of Section 5.**
 
-    **All of that said, however, the fact that the reviewer made these assumptions and pointed out these implications indicates that the paper's language is, in fact, too subjective.
-Even though none of these statements were explicitly made, they must be implied for the reviewer to come to these conclusions.
-As such, revisions have been made throughout the paper to reduce subjective language, support generalized statements with additional explanation and/or references, and include due discussion of RadLib's limitations.
-Section 5 in particular has undergone heavy revision.**
+    **Regarding solution of the RTE versus the radiative property model, the reviewer is correct that in most engineering calculations, specification and implementation of the RTE can be more complex and costly than that of the property model.
+For both parts, however, this depends strongly on the particular model used, (and the geometry considered).
+The optically-thin model RTE model is trivial, and the RCSLW property model is not.
+We revised the manuscript to include a discussion of this in the second paragraph of the introduction, with a specific note that "In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation..." That said, we believe that access to good radiative property models as presented in this paper is a valuable contribution.**
+
+    **We want to be careful with what is claimed in the paper, and some major revision has occurred in response to this reviewer's comments and others.
+Section 4 contained examples provided along with results, but now contains a description of the examples provided with the code.
+Section 5 contained some discussion items as noted by the reviewer, but now includes simulation results for the examples along with a CFD demonstration.
+The discussion items noted by the reviewer have been modified and folded into the Conclusions section.
+    **
 
@@
 
-	**In order to avoid subjective language, this sentence has been revised as follows: "RadLib's modular framework can also accomodate new models, .
-.
-.".
-Specific extensibility issues are addressed below with their respective reviewer comments.**
+    **We have reworded this to "...but its design and C++, Python, and Fortran interfaces permit expansion to additional property models." We remove the word "modular" throughout the paper.
+We do believe that the library can be easily extended.
+The reviewer is correct that we do not provide explicit functionality, for, e.g., generic extension to other species.
+In some cases, like the PM model, such extension would be trivial within the existing code structure.
+In the RCSLW model, extension to other species would require provision of the species ALBDF, and then extension would be a straightforward extension of the code, but the code is not set up for arbitrary species in arbitrary order.
+The library is primarily targeted at combustion applications where CO2 and H2O are the primary radiative species.
+Future efforts may motivate further extension.
 
@@
 
-		**The offending sentence (actually located in the "Solution method" section of the Program Summary) has been revised to eliminate subjective language.**
+		**Done.**
 
@@
 
-		**Technically, no, this is not a run-on sentence, but its structure is awkward and inhibits readability.
-It has been revised to the following: "For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost."**
+    **We have reworded the sentence to "For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost."**
 
@@
 
-		**This was a placeholder that should not have been included in the document. It has been removed.**
+		**This has been corrected.**
 
@@
 
-	**The authors were previously unaware of any such standards or conventions, and follow up research indicates that this is a stylistic preference rather than a flaw in the software.
-The locations of doxygen documentation blocks were chosen for overall readability as they tended to clutter the header files and were less obtrusive when located in the implementation files.
-However, the reviewer does make a valid point regarding usage by downstream developers, and while we would expect the typical RadLib user to be comfortable working with both header files and source code, it is worthwhile to consider all possible usages.
-Because this is an issue of style rather than function, no immediate changes have been made to the code or its documentation, but the authors appreciate this information about standard practice and will consider its implications moving forward.**
+**We believe this to be a stylistic preference.
+The reviewer's argument makes more sense for libraries that are distributed without the source.
+In our case, we provide the source and the header files.
+We follow the approach of putting class comments, data member documentation, and class usage in the header, and documentation of how the methods/functions work in the source files where they are defined.
+This has the benefit of not cluttering the header files.
+There certainly is precedence for this in online discussions.
+Here's a quote from the [doxygen website](https://www.doxygen.nl/manual/docblocks.html): "Unlike most other documentation systems, doxygen also allows you to put the documentation of members (including global functions) in front of the definition.
+This way the documentation can be placed in the source file instead of the header file.
+This keeps the header file compact, and allows the implementer of the members more direct access to the documentation." Furthermore, Doxygen is primarily used to build external documentation (html), so, from that perspective, it does not seem as important where the Doxygen comments are in the source code.**
 
@@
 
-	**The ```make_examples.sh``` file has been removed.**
+	**The ```make_examples.sh``` file has been removed and examples are built with CMake. This script was originally included for reference.**
 
@@
 
+    **The API is pretty simple and consists of two functions.
+Extensive examples are provided, which are compared to LBL data, and which, as published here, are identical to the results of the published radiation models.**
+
+<!--
 	**The authors acknowledge the lack of tests associated with the library and note that basic test coverage is currently being developed.**
+-->
 
@@
 
-		**Installation now includes a ```radlib.cmake``` file, located by default in the ```installed/cmake/radlib``` directory, for downstream usage.**
+		**This is a good point. The installation now includes ```radlib.cmake``` files, located by default in the ```installed/cmake/``` directory, for downstream usage.**
 
@@
 
-		**Build has been updated to reflect this.**
+		**The CMake build has been updated to reflect this.**
 
@@
 
-		**The authors have not experienced problems with this, but have verified that it works correctly.
+        **This appears to be working in the revised version of the code.
+Testing shows the value of CMAKE_BUILD_TYPE as set to Release if not otherwise set.
+This is specified at the very top of the base CMakeLists.txt file.
 Note that the build type can be overridden by IDE build settings, among other things, and that this may be a system issue specific to the reviewer.**
@@
 
-  		**Build has be updated so that verbose makefiles are no longer the default.**
+  		**The build has be updated so that verbose makefiles are no longer the default.**
 
@@
 
-		**Build updated accordingly; GLOB no longer used to install header files.**
+		**The build updated accordingly; GLOB is no longer used to install header files.**
 
@@
 
-		**The authors have experienced no issues running the example executables from either the ```build/examples``` directory or directly from the ```examples``` directory.
-More information is required to address this issue.**
+        **The original code has been updated and tested and this does not appear to be an issue.**
 
@@
 
-		**Executables are built within the example folders in addition to the build directories, so ```run_examples.sh``` runs without any issues.**
+		**Executables for the examples are installed within the example folders (in addition to the build directories), so ```run_examples.sh``` runs without any issues.**
 
@@
 
-		**Build target name has been changed from "doxygen" to "docs" for safety.**
+		**Build target name has been changed from "doxygen" to "docs" for safety. Note that building the documentation is off by default.**
 
@@
 
-	**At present, RadLib's models cannot accommodate such data input, but this is a limitation of the models themselves, not the software.
-The appropriate line-by-line data is included within the RadLib package, which the authors consider a convenience rather than a hindrance.
-The ability to load database files directly into RadLib could be useful to researchers looking to extend RadLib's model library to include modern spectral models, however.
-The authors appreciate the suggestion and will consider it for future development.**
+    **This is true. The code is not presently set up to load HITEMP/HITRAN data. This is a good suggestion and we plan to extend the model to allow LBL simulations in the future.**
 
@@
 
-	**This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation properties, not to evaluate the included models.
-All of the reviewer's questions are addressed in detail in the referenced literature (Planck Mean coefficients in [3,5] and WSGG in [10,11]).
-The authors believe that this is an issue of scope rather than missing information but are willing to extend the discussion at the editor's discretion.**
+    **The software implements the PM and WSGG models as provided in the cited references, which use polynomial fits.
+Model details are noted in the cited references.
+Use of a polynomial fit is standard for WSGG models, and a polynomial fit to temperature for species for the PM model seems reasonable.
+The PM model used is the one advocated by the TNF workshop cited in the paper, which is standard in the combustion community.
+The temperature range is 300-2500 K for the PM model.
+This is now stated in the paper, and the code enforces this range.
+The range for the WSGG model is 300-2400 K.
+The range for the RCSLW model is 300-3000 K.
+Temperatures outside these bounds use these bounds for the WSGG and RCSLW models.
+This is now stated in the paper.**
 
@@
 
-	**The authors acknowledge that modifying existing models in RadLib is non-trivial, but would like to note that the paper does not claim that the implemented models are easily modified, only that the RadLib framework can be used to implement and validate additional models.
-Additionally, the authors disagree with the reviewer's statement regarding opacity and reproducability.
-The referenced literature (see above) clearly outlines the data sources and preprocessing methods applied; this information was omitted from the current paper for the reasons stated above.
-Given the provided sources, the process is neither opaque nor non-reproducible.**
+    **The implemented models are not opaque, they come from the literature.
+The novelty of the presented library is not the development of the absorption models, but the implementation, validation, and documentation of a library for application.
+Using radlib to generate correlations for species using HITEMP/HITRAN is outside of the intended scope.
+We acknowledge that extra work is required to extend the models to additional species, or to extend the temperature ranges.
+However, the species included cover a very wide range of practical applications, certainly in the combustion field, and models for other species (e.g., for WSGG, and RCSLW) are often not available.
+Indeed, Bordbar's WSGG model is one of the few (if not the only one) that is provided for arbitrary compositions of CO2 and H2O, with others assuming fixed or limited ratios.
+That said, radlib is documenented and while the code does not provide extension machinery directly, extending to additional species by following the existing code structure would not be difficult if such data/correlations were available.**
 
@@
 
-	**All WSGG correlations consider only CO2-H2O mixtures with the exception of specialized subset of WSGG models that consider CO2-H2O-soot mixtures.
-This WSGG model was chosen for RadLib due to its popularity, relative simplicity, and good performance.
-RadLib implements the WSGG model presented by Bordbar et al.
-in references [10] and [11], which was developed specifically for use in oxy-fired combustion simulations.
-CO2 and H2O are the major products of all combustion processes, and CO is a major product of rich combustion.
-NO and OH are minor species that, while important to other aspects of combustion processes, do not typically participate significantly in radiative heat transfer processes.
-For more information, please refer to Section 20.6 of reference [2] and/or Section 3.4.1 of *Radiative Heat Transfer in Turbulent Combustion Systems* by Modest and Haworth.**
+    **See our reply to the previous comment regarding additional species.
+For heat transfer applications in combustion, NO and OH are minor species and will not contribute in any meaningful way.
+CO2, H2O, and soot will drive the radiation in practical configurations.
+It would be nice to include CO in the WSGG model, and we would like to do this following Bordbar's approach.
+But even CO is a minor species compared to CO2, both in terms of its concentration in practical systems (usually), and it's asorption coefficient on an equal concentration basis.
+CH4 was only included in the PM model from the TNF workshop since many of the fuels used there include CH4.
+But CH4 will largely be present at relatively low temperatures, not the highly radiating flame zones.**
 
-	**It should also be noted that the Planck Mean absorption coefficients model as implemented in RadLib refers specifically to the radiation model in [3,5], which is one of the most common radiation models applied to turbulent combustion simulations.
-This is why Section 2.1 explicitly references the TNF radiation model and its calculated Planck Mean absorption coefficients.
-As implemented, the model is not intended to be general or extensible to other gas species and was never presented as such.
-Adding additional species would indeed be a non-trivial undertaking, but that is neither the goal nor purpose of RadLib as a software package, which presents and validates models rather than evaluating them.**
-
-	**Major revisions have been made to the paper text to clarify points like these for readers who do not specialize in combustion processes or modeling and provide additional information about why these models were chosen for implementation in RadLib.**
+	**We note that major revisions have been made to the paper text to clarify points like these for readers who do not specialize in combustion processes or modeling and provide additional information about why these models were chosen for implementation in RadLib.**
 
@@
 
-	**Build process has been updated so that documentation can be generated by the system target or manually.**
+	**The build process has been updated so that documentation can be generated by the system target or manually by running the command ```doxygen``` in the docs folder.**
+
+----------------------------------------------------
 

### 2021-07-19 manuscript/manuscript.tex
DOL: reviewer 1 responses finished, with corresponding checks of the paper and code. The paper will need to be gone through and edited still.

@@
 \usepackage{bm}
+\usepackage{seqsplit}
 
@@
 \begin{abstract}
-RadLib is a modular C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations.
-RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interface options permit convenient expansion to additional models.
+RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations.
+RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its design and C++ and Python interface options permit convenient expansion to additional models.
 Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
@@
 Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiation property model.
-RadLib addresses the second part by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
+Complexity, implementation, and computational costs of these two parts can vary widely, depending on the models chosen.
+The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and Reverse Monte Carlo Ray Tracing (RMCRC) model, among others, are significantly more involved.
+Similarly for radiation property models, which range from simple correlations for mean absorption coefficients, to gray gas models such as the weighted sum of gray gas model (WSGG), to the more advanced Spectral Line WSGG (SLW) family of model, to full line-by-line (LBL) approaches.
+In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models, such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
+RadLib addresses this second, radiative property model part of radiative simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
 
@@
 With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
-RadLib is a modular C++ library with an optional Python interface.
+RadLib is a C++ library with an optional Python interface.
 Currently, RadLib only calculates radiation absorption coefficients and weighting factors for use in global radiation models, but expansion to other radiative properties and model types is possible.
@@
 The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
-These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its notable limitations.
+These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its limitations.
 Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}.
+The absorption coefficient correlations use fourth or fifth order polynomial fits in the range 300-2500 K.
 TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}.
@@
 %
-where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K. The value of $b_{i,j}$ is calculated by 
+where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K.
+The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound.
+The value of $b_{i,j}$ is calculated by
 %
@@
 \cite{Pearson_2014} and can be accessed in both correlated and tabulated form at \cite{Solovjov_2014b}.
+Temperatures outside the stated range use the value at the respective bound.
 RadLib uses the tabulated data coupled with multilinear interpolation; both the tabulated data and the multilinear interpolator are included with the RadLib package as part of the RCSLW method.
@@
 This folder also contains the Python module.
-The code installation additionally generates a relocatable CMake package for downstream usage, located at \texttt{build/cmake/radlib/radlib.cmake}.
+The code installation additionally generates relocatable CMake files for downstream usage, located at \texttt{\seqsplit{installed/cmake/radlib/radlib.cmake}} and \texttt{\seqsplit{installed/cmake/radlib\textunderscore fortran/radlib\textunderscore fortran.cmake}}, where \texttt{installed/} may be replaced with a user-specified installation path.
 If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable.
-A command to do this is provided at the end of the installation, for example, \\ {\scriptsize \texttt{export PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.
+A command to do this is provided at the end of the installation, for example, \texttt{\seqsplit{export\ PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.
 
@@
 Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to their high level of conceptual and mathematical complexity and potentially large computational cost.
-The vast majority of combustion CFD studies either neglect radiative heat transfer modeling or employ oversimplified models that do not accurately represent combustion systems.
+Many combustion CFD studies either neglect radiative heat transfer modeling or employ oversimplified models that do not accurately represent combustion systems.
 Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield accurate results.
 
-We presented RadLib, a C++ library of radiation property models developed to ease some of the obstacles and reduce the complexity inherent to the process of implementing radiative property models in CFD simulations.
-At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its modular design and C++ and Python interfaces permit expansion to additional property models.
+RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations.
+At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its design and C++, Python, and Fortran interfaces permit expansion to additional property models.
 Each of the implemented models has been validated and the library's structure and functionality has been outlined.
@@
 
-RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for combustion CFD, but could potentially be applied to research problems involving radiative heat transfer in a variety of other fields as well.
+RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for combustion CFD, but could potentially be applied to research problems involving radiative heat transfer in other fields as well.
 RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single extensible library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models.

### 2021-07-19 submissions/CPC_response_to_reviewers.md
DOL: edits to responses to Reviewer 2. TODO: add the FDS section.

@@
 **The authors would like to thank the reviewer for their comments and suggestions.
-We have already begun working on coupling RadLib to CFD software (that includes a DOM solver for the RTE solution, among other features) in order to demonstrate RadLib's capabilities.**
+It is true that the library presented does not develop new models, but implementing and providing those models is nontrivial, and we believe makes a good contribution that is within the scope of this software journal.**
+
+**We agree the reviewer's suggestion regarding coupling with popular CFD software and a corresponding RTE solver, and that this would strengthen the paper.
+We have made significant revisions to the paper and code in this regard.
+First, we developed a new Fortran interface that calls the underlying C++ code.
+Second, we coupled the code to the Fire Dynamics Simulator (FDS) code, developed by NIST.
+FDS is a Fortran code that required the new Fortran interface.
+FDS has several radiation models available including WSGG DOM implementation.
+Radlib was interfaced to this model by using the radlib fortran module in the source code.
+We then replaced the existing calls to the functions for computing the absorption coefficient and weighting factors with calls to radlib.
+FDS does an outer loop over the gases/bands with inner loops over the local grid points.
+RadLib was not set up for this, since it computes the properties for all bands at a given point.
+Hence, direct use of RadLib would have been inefficient.
+As a result, we implemented a new interface function get_k_a_oneband, that facilitated implementation in FDS.
+In the revised paper, we present results comparing the WSGG and RCSLW models in FDS applied to the FM Burner validation case that is detailed in the FDS Validation Documentation.
+We hope that this effort will satisfy the reviewer and improve the paper as desired.**
 
@@
 That said, there is value in using the most current tools.
-Given the reviewer's experience with variance in the Planck Mean absorption coefficients as calculated from various databases, the authors will strongly consider adding an updated Planck Mean model using the most current available data.**
+Given the reviewer's experience with variance in the Planck Mean absorption coefficients as calculated from various databases, the authors will strongly consider adding an updated Planck Mean model using the most current available data.
+That said, the PM model implemented is generally applied in optically-thin situations with relatively low radiative transfer in which case the errors are not as significant.**
 
@@
 
-	**The PM and WSGG models are primarily empirical and contain very little representative physics, which could explain their unexpected behavior in Examples 2 and 4 but also makes it very difficult to find or treat sources of error.
+	**The PM and WSGG models are primarily empirical and contain very little representative physics, which could explain their unexpected behavior in Examples 2 and 4, but also makes it very difficult to find or treat sources of error.
 Any model, but especially empirical models, can behave unexpectedly when applied to conditions or parameters outside of those for which it was developed.
+We were suprised by the poor performance of the WSGG model in the case the author notes.
+This is one area where it is nice to have a model (as presented) that is easily implemented with access to validation cases that can be extended.
 The example cases are meant to be illusrative of the software's capabilities, not an evaluation of the models themselves, which is outside the scope of this paper.
@@
 
-	**Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations in the paper.**
+	**Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations in the paper.
+The equation is q = int(I(s)sdΩ).
+The notation here is that I is a function of direction, but is itself a scalar so that I(s)s is equivalent to a vector I in direction s.**
 
@@
 
-	**The phrase has been amended to ". . .using correlations relating them to local properties such as. . .".**
+	**This phrase has been removed in the revison.**
+
+-------------------------------------
 

### 2021-07-20 manuscript/manuscript.tex
DOL: adding FDS results for the FM burner

@@
 
+\subsection{CFD Results} \label{s:cfd}
+
+The RadLib model was coupled to the Fire Dynamics Simulator (FDS) code developed at NIST \cite{FDS}.
+FDS is written in Fortran, and the Fortran interface of Radlib was used for simulations.
+FDS includes several radiative models, but the spectral WSGG model coupled to a finite volume discrete ordinates model is used here.
+This was done by editing the \texttt{radi.f90} file.
+A \texttt{use rad\textunderscore module} statement is included and the functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} were replaced with calls to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}.
+The \texttt{oneband} version was used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.
+
+FDS includes a number of validation cases.
+Here, we compare to the FM Burner case.
+The configuration is a vertically fired gas burner with various fuels and with a coflow oxidizer stream of varying nitrogen dilution.
+The burner has outer and inner diameters of 15.2 and 13.7 cm and is near the floor in the center of a 1.22 by 1.22 by 1.83 m tall compartment.
+The heat release rate was 10 kW and included a 1 kW pilot in a surrounding ring.
+The coflow oxidizer was fed through the floor.
+Simulations performed here used the ethylene fuel with 20.9\% \ce{N2} oxidizer (i.e., air).
+Further FDS model and case simulation details are provided in the FDS validation and user guides \cite{FDS}.
+
+Figure~\ref{f:fds} shows results of the simulation with comparison to experimental data. Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib. 
+The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL. Further details are provided in the FDS user guide \cite{FDS}. 
+Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions.
+The models produce centerline temperature differences of about 80 K (7\%) between the RCSLW and the WSGG at z=2.5D, and 90 K (12\%) at z=3.5D.
+The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative.
+Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 1.3 kW/m (11\%).
+%
+\begin{figure}
+    \begin{center}
+    \begin{tabular}{c c}
+        (a) & (b) \\
+        \includegraphics[width=2.5 in]{fig_fds_T_mean.pdf} &
+        \includegraphics[width=2.5 in]{fig_fds_rad_mean.pdf}
+    \end{tabular}
+    \caption{Radial profiles of mean temperature at two heights (a), and height versus radiative emission (b) for FDS simulations of the FM Burner validation case comparing three models to experimental data.}
+    \label{f:fds}
+    \end{center}
+\end{figure}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Computational Cost} \label{s:cost}
@@
         (a) & (b) \\
-        \includegraphics[width=2.75 in]{fig_getka_c++.pdf} &
-        \includegraphics[width=2.75 in]{fig_exS3_c++.pdf}
+        \includegraphics[width=2.5 in]{fig_getka_c++.pdf} &
+        \includegraphics[width=2.5 in]{fig_exS3_c++.pdf}
     \end{tabular}

### 2021-07-20 submissions/CPC_response_to_reviewers.md
DOL: edits to the results section; updating figures with revised wsgg coefficients; modified response to reviewers

@@
 
-	**The PM and WSGG models are primarily empirical and contain very little representative physics, which could explain their unexpected behavior in Examples 2 and 4, but also makes it very difficult to find or treat sources of error.
-Any model, but especially empirical models, can behave unexpectedly when applied to conditions or parameters outside of those for which it was developed.
-We were suprised by the poor performance of the WSGG model in the case the author notes.
-This is one area where it is nice to have a model (as presented) that is easily implemented with access to validation cases that can be extended.
-The example cases are meant to be illusrative of the software's capabilities, not an evaluation of the models themselves, which is outside the scope of this paper.
-The reviewer's request for an explanation, however, is valid.
-The discussion in Section 5 has been expanded and revised to address these specific discrepancies.
-Additional information about the specific limitations, strengths, and weaknesses associated with each model can be found in Section 2.**
+    ** The WSGG model coefficients presented were those from Bordbar's paper.
+These have since been updated and included in the revised code and we have likewise updated the simulation results in the paper.
+For the new results, the WSGG model no longer performs poorly for example S4.
+For example S2, the RCSLW model converges to the LBL results as the number of gases increases, but the WSGG model outperforms the RCSLW model for 4 gray gases.
+It is not clear why the WSGG model outperforms the RCSLW model for this case.
+We have added some relevant discussion to the paper.
+We do note that the WSGG model is empirical and contains very little representative physics, which makes it difficult to explain the behavior of the model.**
 

### 2021-07-20 manuscript/manuscript.tex
DOL: edits to the results section; updating figures with revised wsgg coefficients; modified response to reviewers

@@
 %
-where $C_{j,k,i}$ is another correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020}.
+where $C_{j,k,i}$ is another correlated model coefficient.
+The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al.
+\citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.
 
@@
 Example S1 consists of two adjacent gas layers with identical species compositions: one hot layer of constant thickness and one cold layer of varying thickness. 
-In Example S2, the two gas layers are isothermal but differ in the value of the \ce{CO2} mole fraction, where the layer thickness of the "thin" slab (with the smaller \ce{CO2} mole fraction) varies.
+In Example S2, the two gas layers are isothermal but differ in the value of the \ce{CO2} mole fraction, where the layer thickness of the ``thin'' slab (with the smaller \ce{CO2} mole fraction) varies.
 Example S3 applies parabolic temperature and \ce{H2O} mole fraction profiles across a single gas layer. 
@@
 Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}.
+These plots are included to demonstrate the examples that are provided with the code, and to compare the models to give an indication of their relative accuracy.
 In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied.
-The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature instead.
+The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature.
 %
@@
 In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data.
-The data for Examples S1, S3, and B3 show that the PM model tends to exaggerate the trends displayed by the other models; this is also true of Example S4, though the effect is somewhat overshadowed by the WSGG model results.
-The PM data mimics the shape of the other curves in Example S5 as well, but with such greatly exaggerated peaks and valleys that its data was omitted from the plot to more clearly display the behavior of the WSGG and RCSLW models; for the PM model in Example S5, $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m and drops to 100 kW/m$^3$ at $x=2$ m.
+The results show that the PM model tends to exaggerate the trends displayed by the other models.
+The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity.
+For the PM model in Example S5, $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m and drops to 100 kW/m$^3$ at $x=2$ m.
 In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity.
 The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively.
-These values are small compared to the domain sizes considered in Example S2, which coincides with the PM model's use of the optically thin approximation, but the high error in its predictions of radiative heat flux relative to the LBL data indicates that neither the optically thin approximation nor absorption coefficients calculated with this model are accurate for this case.
-Example S3 is the clearest illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model severely overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.
-
-The WSGG model gives somewhat accurate but inconsistent results for the example cases considered here.
+These values are small compared to the domain sizes greater than 0.5 m that are considered in Example S2.
+%, which coincides with the PM model's use of the optically thin approximation, but the high error in its predictions of radiative heat flux relative to the LBL data indicates that neither the optically thin approximation nor absorption coefficients calculated with this model are accurate for this case.
+Example S3 is the clearest illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.
+
+The WSGG model closely follows the trends of the LBL data for all examples, and in most examples gives reasonable quantitative agreement.
+This is especially true for Example S2, S4, and B3.
+For example S5, the WSGG model shows peak errors of around 50\%, and somewhat higher in Example S1.
+The heat flux near the boundaries in Example B3 is low by around 30\%.
+The RCSLW model gives results in very close agreement to the LBL data for all examples.
+A notable exception is example S2, where the heat flux at the right boundary is not well-predicted for four gray gases.
+The heat flux does converge to the LBL results when the number of gray gases increases.
+This behavior was not discussed in \cite{Solovjov_2017} where 24 gray gases were used.
+The WSGG model is very close to the LBL data for this case.
+The good agreement is likely a result of the simplicity of this case that is isothermal with pure \ce{CO2} at uniform concentration in either of the two adjacent gas slabs.
+The RCSLW model is sensitive to the number of gray gases used, as illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
+The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
+The RCSLW model also depends on the value of the chosen reference temperature that is used to set the ALBDF grid.
+In Example S5, the RCSLW model does not converge to the LBL data at $x>0.5$ m when the domain average temperature was used.
+
+%The WSGG model gives somewhat accurate but inconsistent results for the example cases considered here.
 In Examples S1, S3, S5, B3, and Sb1, it behaves as expected, producing results that are closer to the LBL data than those produced by the PM model but fall short of the RCSLW model's level of accuracy.
@@
 In contrast, the WSGG model performs exceptionally poorly in Example S4, in which it deviates from the LBL data by nearly an order of magnitude at its largest.
-The WSGG model, alongside with the PM model, is primarily empirical and contains little to no representative physics, which could explain the unexpected behavior in Examples S2 and S4.
+%The WSGG model, alongside with the PM model, is primarily empirical and contains little to no representative physics, which could explain the unexpected behavior in Examples S2 and S4.
 Given that all of the example cases use parameters within those specified for the WSGG model in the literature \cite{Bordbar_2014,Bordbar_2020}, neither anomalous result has an obvious source.
@@
 
-The RCSLW model displays the most accurate results of the three implemented property models when compared to LBL data, capturing the relevant trends without exaggerating them.
+%The RCSLW model displays the most accurate results of the three implemented property models when compared to LBL data, capturing the relevant trends without exaggerating them.
 It is, however, the most difficult of the three models to implement and requires either correlated or tabulated spectral data to draw from.
-The RCSLW model can also be sensitive to the number of gray gases used, illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
-The difference in accuracy between $n=2$ and $n=8$ gray gases is very small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
+%The RCSLW model can be sensitive to the number of gray gases used, illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
+The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
 Example S2 shows the most prominent variations in predicted radiative heat flux based on changes in the number of gray gases, improving drastically in agreement to the LBL data with the addition of just four gray gases.
@@
 Soot reactions and transport are both sensitive to and strongly influence local variations in flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
-The agreement produced by RadLib's approach to soot radiation in Example Sb1 is an encouraging step toward accurate, detailed treatment of soot's radiative properties in complex combustion simulations.
+%The agreement produced by RadLib's approach to soot radiation in Example Sb1 is an encouraging step toward accurate, detailed treatment of soot's radiative properties in complex combustion simulations.
 
@@
 
-Figure~\ref{f:fds} shows results of the simulation with comparison to experimental data. Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib. 
+Figure~\ref{f:fds} shows results of the simulation with comparison to experimental data.
+Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib (both using four gray gases and one clear gas).
 The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL. Further details are provided in the FDS user guide \cite{FDS}. 

### 2021-07-22 submissions/CPC_response_to_reviewers.md
DOL edits: done with responses to reviewers, which include some revisions to the paper. TODO: go through the paper start to finish and make edits. Some notes need to be implemented or verified in the paper to make sure the paper is consistent with the responses to reviewers.

@@
 
-**The authors would like to thank the reviewer for their insightful comments and suggestions.
+**The authors thank the reviewer for their insightful comments and suggestions.
 As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**
@@
 Note that the C++ source code is required to install the Python interface, so there is no option to build only the Python interface.
-All of this information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages.**
+All of this information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages.
+Furthermore, we have now done full tests of the installation and running of all examples on a desktop Mac, a desktop Linux machine, and a large Linux-based cluster.**
 
@@
 	**Section 3 has been revised and extended to include more information on how users can include and interact with the RadLib library, including explicit references to example files that further illustrate usage of the library.
-Adding additional radiative property models to the RadLib library, however, is nontrivial, and we chose to move its discussion to the package documentation so as not to clutter the manuscript.
-This can be changed, if necessary, at the editor's discretion.**
+We have also added a subsection to the results discussion that describes the integration of RadLib with the Fire Dynamics Simulator (FDS) code developed by NIST.
+Adding additional radiative property models to RadLib would require creating another class object for the implementation.
+The intention would be for the new model to inherit from the ```rad``` base class and reimplement the interface functions ```get_k_a``` and ```get_k_a_oneband```.
+Depending on the model, additional functionality may be needed.
+The Fortran and Python interfaces are wrapper functions that can be extended by paralleling the existing code, which is much simpler than writing these interfaces from scratch.
+A discussion on these points has been added to Section 3.**
 
@@
 
-	**The authors purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations.
+	**We purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations.
 Section 2.1 has been revised to include a more explicit dicsussion of why the TNF radiation model was chosen and concerns related to its relative age and limited applicability.
-Section 4 includes example cases that clearly demonstrate the deficiencies of the PM model compared to the other models included with RadLib, and some additional discussion is available there.**
+Section 4 includes example cases that clearly demonstrate the deficiencies of the PM model compared to the other models included with RadLib, and some additional discussion is available there.
+We intend to extend the model to include updated PM data.**
 
@@
 
-	**While it is true that the purpose of this paper is to present the RadLib library rather than evaluate or compare the models, the authors believe that example case results in Figures 2 and 3 are important to the illustration of RadLib's capabilities.
-The reviewer's point about presentation without explanation, however, is valid; to that end, the discussion in Section 5 has been expanded to acknowledge, if not fully explain or provide cause for, various features and descrepancies in the example case results.
-Due to the empirical nature of the PM and WSGG models, it is very difficult to identify, explain, or rectify unexpected behavior.**
+	**While it is true that the purpose of this paper is to present the RadLib library rather than evaluate or compare the models, the authors believe that example case results in Figures 2 and 3 are important.
+These illustrated examples RadLib's capabilities, demonstrate the example cases provided with the code, and provide comparison between the models and with reference to the LBL data.
+Comparison between the models has relevance to the reviewer's second comment above regarding the rationale of the models chosen, and our discussion of them in reply in the text.
+The reviewer's point about presentation without explanation is valid.
+The discussion in Section 5 has been expanded.
+Some of the results and discussion have changed since are now using updated parameters for the WSGG model that improves the agreement of that model, especially for Example S4.
+This makes the models for the different cases presented more consistent, lessening some of the burden for explaining anomolous behavior, though, due to the empirical nature of the PM and WSGG models, full explainations can still be difficult.**
 
-	**In regards to validation, the authors are unclear as to what the reviewer expects to see.
-RadLib's model implementations give results that are, in fact, essentially identical to those presented in the literature to within any visual margin.
-We do not have access to the data used to generate the plots in the literature, without which any quantitative measure of error is meaningless.
-We do, however, compare model results to the line-by-line data, which amounts to a direct solution of the RTE and is also identical to the line-by-line data in the literature (as expected).
-The authors believe that this serves as adequate validation of RadLib's model implementations given the lack of originial data for comparison.**
+    **Regarding validation, we agree with the reviewer in being careful about the language used.
+We are fully confident in the implementations of the models presented.
+Model parameters were checked and rechecked, and results from RadLib were carefully compared to the corresponding model results presenting in the original papers.
+In the case of the RCSLW model, which is the most complex to implement, we had the benefit of discussions with the inventors of the model (noted in the Acknowlegements), and even compared our code output to their Fortran implementation.
+We have modified the text to avoid qualitative description.**
 
@@
 
-	**Section 4.1 already includes details of the computational cost calculations presented in Figure 4.
-The left hand plot (a) refers to one million evaluations of the absorption coefficients directly, while the right hand plot (b) refers to the cost to evaluate Example S3, which, like all of the example cases described in the first paragraph of Section 4, includes the ray-tracing solver.
-The quoted sentence has been revised to specify that the ray-tracing solver is primarily responsible for the additional overhead.
-Grids are identical for each configuration.
-Note that the RadLib library does not generate or manipulate grids as it is not involved in the RTE solution.
-The ray-tracing solver used in the example cases is provided for convenience and demonstration purposes.**
-
-	**Note that Section 4.1 has since been moved to Section 5. It and the appropriate figure captions have also been revised for clearer communication of the points above.**
+    **We have modified the discussion slightly by moving the note about the cost not including model initialization and input/output earlier to make it clear that that applied to all results.
+Two cost comparisons are given: (1) cost of the property evaluation itself; and (2) cost of the full RTE solve (including the ray-tracing solution and property evaluation).
+Item (2) is relevant since property evaluations are not normally done in isolation, but part of a larger RTE solve, so that differences in the property model costs have less impact on the overall cost.
+This is now noted in the paper.
+The revision should be clear about the costs including the ray-tracing solver and the constant grids.
+Regarding the "overhead," the revision reorders the discussion and that word is not used.
+This discussion parallels what is noted here, that differences in the overall costs are smaller when accounting for the cost of the RTE solver as well as the property evaluation.
+(Note that Section 4.1 has since been moved to Section 5.
+It and the appropriate figure captions have also been revised for clearer communication of the points above.)**
 
@@
 
-	**CH4 is present only in the PM model sourced from the TNF Workshop [3,5], which includes CH4 absorption coefficients because most of the TNF Workshop target flames are fueled by Ch4.
-In general, CH4 is not a significant radiatively participating species in combustion systems, but it is included for completeness.**
+	**CH4 is present only in the PM model sourced from the TNF Workshop [3,5], which includes CH4 absorption coefficients because most of the TNF Workshop target flames are fueled by CH4.
+In general, CH4 is not a significant radiatively participating species in combustion systems, but it is included in the PM model for completeness with the PM source.
+The revision notes differences in the models and species, and default values are included for species in the interfaces (also now noted) so that users don't have to specify mole fractions for species that are not used in a given model.**
 
@@
 
-	**This clarification has been made explicitly in Section 2 and now appears throughout the text where appropriate.**
+	**This clarification has been made explicitly in Section 2 and now appears elsewhere the text where appropriate.**
 
@@
 
-	**References have been added throughout the text to bolster weakly supported arguments.
-Due to unrelated revisions, the quoted statement and related discussion is now located in Section 2.1 since it is most closely related to the Planck Mean model and its limitations.**
+	**This statement has been removed in the revision.
+In the spirit of this comment, we have added references to the text where needed to bolster weakly supported arguments.
+In particular, due to unrelated revisions, such discussion appears in Section 2.1 since it is most closely related to the Planck Mean model and its limitations.**
 
@@
 
-	**The RCSLW model's key tool is the absorption line blackbody distribution function (ALBDF), which is calculated using sppectral data available from databases like HITEMP.
-This is discussed briefly at the end of Section 2.3 on pages 8-9.
-For more information on how spectral data is used to calculate the ALBDFs, please see reference [22].**
+	**The absorption coefficients for the gray gases are developed from high resolution databased, and correlated, for each gray gas considered, as functions of the local gas state (temperature, pressure, and composition).
+The PM model uses a temperature correlation for each species absorbtion coefficient, with the overall absorption coefficient computed by combining the species.
+The WSGG model uses correlations developed for the gray gases based on emmivity calculations from the high resolution databases, and treats the composition through the molar H2O/CO2 ratio.
+The RCSLW model's key tool is the absorption line blackbody distribution function (ALBDF), which is calculated using spectral data available from databases like HITEMP.
+See Solvjov 2017 (cited in the paper) for details.
+The revision includes such discussions for the individual models.
+The modification of the original statement is in the last paragraph in Section 2 before section 2.1.**
 
@@
 
-	**The reviewer's statements regarding PM absorption coefficients are generally true.
-In combustion simulations, low radiative heat transfer relative to other heat sources, including chemical heat release and convective heat transfer, usually does, in fact, indicate very low radiative reabsorption rates.
-Sectiom 2.1 and related discussion elsewhere has been revised to clarify this connection.
-The quoted sentence now reads as follows: "The Planck Mean model is most appropriate under optically thin conditions in which low radiative transfer relative to other heat sources, including but not limited to chemical heat release and buoyancy-driven convection in combustion systems, indicates that very little radiative reabsorption is occuring."**
+    **This discussion is modified in the revision.
+The PM model is not directly connected to optical thickness of flames.
+In combustion applications, the PM model is often used in situations that are optically thin.
+In such cases, the radiative losses are relatively low (often around 5% for laboratory jet flames), and use of the PM model provides sufficient accuracy given that errors are active at the 5% level of the overall radiative losses, so not severe.
+When coupled with the optically thin assumption for RTE treatment, the radiative solve is relatively simple and inexpensive.**
 
@@
 
-10) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?
+9) With respect to Eqn 8, Mr is defined as molar ratio y_H2O/y_CO2. Are the authors using y as a symbol for mole fraction rather than mass fraction as is conventionally done?
 
-	**This is correct. The molar ratio was defined using these variables by Bordbar et al. [10,11] for the WSGG model and have been retained for consistency.**
+    **We have changed the notation in the paper to use x instead of y.
+This is consistent with our use in the code, and we also prefer x for mole fraction and y for mass fraction.
+Solovjov (RCSLW) and Bordbar (WSGG) both use Y for mole fraction though.**
 
@@
 
-	**This was a placeholder that should not have been included in the document. It has been removed.**
+	**Done.**
 
@@
 
-	**Appropriate units have been added to the specified values.**
+	**Done.**
 
@@
 
-	**This issue was partially addressed in the discussion above (see point 7).
-In combustion simulations, things like simple geometry and small domain sizes limit the extent of any chemical heat release or convective heat transfer, which usually indicates that radiative heat transfer plays a more prominent role than it would otherwise.
-In order to clarify this association, the sentence in question has been revised to read as follows: "Neglecting radiation or using simple models like the Planck Mean model is adequate for some cases with simple geometry or limited chemical heat release, which are usually associated with optical thinness and low rates of radiative reabsorption, but most combustion simulations of interest to engineers and researchers require more advanced radiation modeling to yield accurate results."**
+    **This is a good point.
+The revision should correct this.
+We partially answer this in reply to your comment above regarding page 7 that the "PM model can be 'reasonably accurate'".
+In particular, we are revising the discussion around the PM model to note that it is not an overly accurate model in comparison to the others, but it is widely used, and its use is warranted in situations with relatively low radiative losses that may occur, for example, in cases where radiative losses are low compared to heat release rates, or where flow timescales are low compared to radiative transfer timescales.**

### 2021-07-22 manuscript/manuscript.tex
DOL edits: done with responses to reviewers, which include some revisions to the paper. TODO: go through the paper start to finish and make edits. Some notes need to be implemented or verified in the paper to make sure the paper is consistent with the responses to reviewers.

@@
 {\em Licensing provisions(please choose one):} MIT \\
-{\em Programming language:} C++, Python                                   \\
+{\em Programming language:} C++, Fortran, Python \\
 {\em Nature of problem(approx. 50-250 words):} \\
@@
 We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD.
-The package includes multiple interface options (C++ and Python), several illustrative examples with a provided ray-tracing solver, and a framework for expansion to include additional radiation property models and interfaces.\\
+The package includes C++, Fortran, and Python interfaces, several illustrative examples with a provided ray-tracing solver, and possibility for expansion to include additional radiation property models and interfaces.\\
 {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
@@
 
-Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITEMP, and HITRAN \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
-At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$) and soot.
+Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITRAN, and HITEMP \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
+At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot.
 Note that the property models implemented in RadLib apply only to non-scattering media.
@@
 %
-where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $y_{\mathrm{H_2O}}/y_{\mathrm{CO_2}}$.
+where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$.
 The weight factors are calculated by
@@
 	\begin{equation} \label{e:multiC}
-		C_{\eta} = Y_{\ce{CO2}}C_{\ce{CO2},\eta} + Y_{\ce{H2O}}C_{\ce{H2O},\eta} + Y_{\ce{CO}}C_{\ce{CO},\eta}
-	\end{equation}
-\end{linenomath}
-%
+		C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
+	\end{equation}
+\end{linenomath}
+%
+where $x$ denotes mole fraction.
 Assuming that the absorption cross sections of each species are statistically independent, we can calculate the mixture ALBDF for a given gray gas using the multiplication method \cite{Solovjov_2000}:
@@
 \begin{equation} \label{e:multiF}
-    F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{Y_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{Y_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{Y_{\ce{CO}}} \right).
+    F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right).
 \end{equation}
@@
     \item Specify a reference temperature $T_r$ as the average temperature on the domain of interest \cite{Solovjov_2001}.
-Note that this is not the same as specifying a reference state $\BS{\phi}=\BS{\phi}_r(T_r,Y_r,P_r)$ as in done for SLW reference approaches.
+Note that this is not the same as specifying a reference state $\BS{\phi}=\BS{\phi}_r(T_r,x_r,P_r)$ as in done for SLW reference approaches.
 The RCSLW model has the significant advantage that it does not require a thermodynamic reference state.
@@
     \item \texttt{libradlib.a},
-    \item \texttt{libradlib\textunderscore fortran.a},
+    \item \texttt{libradlib\textunderscore fortran.a}.
 \end{itemize}
@@
 The PM model only considers one gas and the vectors are of unity size.
-The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument.
+The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index argument (starting at zero for all interfaces) is provided as an additional argument.
 This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}.
@@
 %
+
+The RadLib source code is build around a base class called \texttt{rad} from which the individual property models, e.g., \texttt{rad\textunderscore rcslw}, inherit.
+To extend RadLib to include new radiative property models, a user would create a new derived class for the model that inherits from the \texttt{rad} base class.
+The interface functions \texttt{get\textunderscore k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} would be reimplemented in the new model.
+Additional functions and capabilities could be added as desired.
+The Fortran and Python interface codes consist of wrapper functions to the underlying C++.
+These can be easily extended by paralleling the existing interface functions.
 
@@
 Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K applied to a single gas layer of constant species composition.
-Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $y_{CO2}=1-y_{H2O}$). 
+Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $x_{CO2}=1-x_{H2O}$). 
 Example Sb1 consists of a single gas with a uniform temperature and composition profile and soot radiation. 
@@
         \hline
-        Example & T(K)                          & $y_{H2O}$  $y_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.\\
+        Example & T(K)                          & $x_{H2O}$  $x_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.\\
         \hline
-        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$    & $y_{CO2}=0.1$, $y_{H2O}=0.2$                    & 0.5-2.5 & cold, cold	& \cite{Solovjov_2017}     \\
-        S2 & T=1000                             & $y_{CO2}(x<0.5)=0.4$, $y_{CO2}(x>0.5)=0.1$      & 0.5-2.5 & cold, cold & \cite{Solovjov_2017}    \\
-           &                                    & $y_{H2O}=0.0$                                   &         &                \\
-        S3 & $T(x) = 4000x(L-x)/L^2 + 800$      & $y_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$             & 1       & 800, 800 & \cite{Solovjov_2017}      \\
-           &                                    & $y_{CO2}=0$                                     &         &                \\
-        S4 & middle third triangular to 2500    & $y_{H2O}=0.1$, $y_{CO2}=0$                      & 0.3     & 500, 500 & \cite{Solovjov_2017}      \\
-        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$ 	 & $y_{H2O}=0.1$, $y_{CO2}=0$                      & 2       & 1500, 500 & \cite{Solovjov_2017}     \\
-        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $y_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$	& 1       & 400, 400 & \cite{Bordbar_2020}      \\
-           &                                    & $y_{CO2}=1-y_{H2O}$                             	&         &                \\
-        Sb1& $T = 1000$                         & $y_{H2O} = 0.2$, $y_{CO2}=0.1$, $y_{CO}=0.03$   	& 1       & cold, cold & \cite{Solovjov_2001}    \\
+        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$    & $x_{CO2}=0.1$, $x_{H2O}=0.2$                    & 0.5-2.5 & cold, cold	& \cite{Solovjov_2017}     \\
+        S2 & T=1000                             & $x_{CO2}(x<0.5)=0.4$, $x_{CO2}(x>0.5)=0.1$      & 0.5-2.5 & cold, cold & \cite{Solovjov_2017}    \\
+           &                                    & $x_{H2O}=0.0$                                   &         &                \\
+        S3 & $T(x) = 4000x(L-x)/L^2 + 800$      & $x_{H2O}(x) = 0.8x(L-x)/L^2 + 0.12$             & 1       & 800, 800 & \cite{Solovjov_2017}      \\
+           &                                    & $x_{CO2}=0$                                     &         &                \\
+        S4 & middle third triangular to 2500    & $x_{H2O}=0.1$, $x_{CO2}=0$                      & 0.3     & 500, 500 & \cite{Solovjov_2017}      \\
+        S5 & $T(x) = 1000 + 500\cos(\pi x/L)$ 	 & $x_{H2O}=0.1$, $x_{CO2}=0$                      & 2       & 1500, 500 & \cite{Solovjov_2017}     \\
+        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $x_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$	& 1       & 400, 400 & \cite{Bordbar_2020}      \\
+           &                                    & $x_{CO2}=1-x_{H2O}$                             	&         &                \\
+        Sb1& $T = 1000$                         & $x_{H2O} = 0.2$, $x_{CO2}=0.1$, $x_{CO}=0.03$   	& 1       & cold, cold & \cite{Solovjov_2001}    \\
         \hline
@@
 Details about these examples and their motivations can be found in their respective references.
-Comparison of these results to the LBL data and to the results presented in the source references also serves as a validation of RadLib's implementation of the WSGG and RCSLW models.
+Comparison of these results to the LBL data, shown here, serve as model validation.
+For WSGG and RCSLW, direct comparison (not shown) of RadLib was made to examples presented in the model references with identical results (up to the resolution of the available data), which serves as verification of the implementation.
 
@@
 Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7; the results, normalized by the cost of the WSGG model, are summarized in Figure~\ref{f:cost}. 
+In the results presented, only the cost of evaluating the solution was included; model initialization and input/output costs were neglected.
+In the results including the ray-tracing solver, the same number of rays and grid points is used in all calculations.
 
@@
 Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver.
-In the results presented, only the cost of evaluating the solution was included; initialization and input/output costs were neglected.
+This is relavant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evalations themselves.
+This is consistent with the results of the figure and as follows.
 Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.
-In running Example S3, the model costs vary much less than when evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.
+%In running Example S3, the overall solution cost using different property models is shown to vary much less than when evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.
 
@@
 In particular, the cost of a single evaluation of the gas properties is small and evaluating the gas properties in a Python loop results in the loop itself appearing to dominate the computational cost.
-Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Figure~\ref{f:cost} the cost only varied by about 4\%, indicating that the computational cost is dominated by Python itself rather than by the model evaluations or solver.
+Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Figure~\ref{f:cost} the cost only varied by about 4\%, indicating that the computational cost is dominated by Python wrapper itself rather than by the underlying C++ model evaluations or solver.
 The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version.
-It is possible that optimizing the Cython interface could improve the speed and relative cost of using Python with RadLib, but RadLib's Python interface and examples are mainly intended to demonstrate the library's use rather than serve as a point of incorporation into detailed CFD calculations, which rarely employ Python.
+It is possible that optimizing the Cython interface could improve the speed and relative cost of using Python with RadLib, but RadLib's Python interface and examples are mainly intended to demonstrate the library's use and provide a convenient interface, rather than serve as a point of incorporation into detailed CFD calculations.%, which rarely employ Python.
 

### 2021-07-24 submissions/CPC_response_to_reviewers.md
DOL proofread and edit the paper. Rewrote the PM section. Checked for consistency with PM issues with reviewer 3

@@
 
-	**Section 2 has been heavily revised to address this issue.
-Each model's description now also includes a discussion of its strengths, weaknesses, and limitations when applied to combustion CFD in addition to the authors' rationale in choosing them for RadLib.**
+	**Section 2 has been heavily revised and should better address this issue.
+In particular, at the beginning of section 2, we note the why these models were chosen.
+The three models are practically relevant, and represent a variation in complexity and accuracy.**
 
@@
 	**We purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations.
-Section 2.1 has been revised to include a more explicit dicsussion of why the TNF radiation model was chosen and concerns related to its relative age and limited applicability.
-Section 4 includes example cases that clearly demonstrate the deficiencies of the PM model compared to the other models included with RadLib, and some additional discussion is available there.
+Section 2.1 has been revised to include a more explicit dicsussion of why the TNF radiation model was chosen.
+Sections 4 and 5 include example cases and results that demonstrate the deficiencies of the PM model compared to the other models included, and some additional discussion is given there.
 We intend to extend the model to include updated PM data.**
@@
 2014), five other WSGG models, and line-by-line calculations for four different test cases that show high accuracy over a wide range of molar ratio values.
+We have noted this in the revision.
 While other models may have performed better in individual tests, this model demonstrated consistent accuracy over a range of scenarios.

### 2021-07-24 manuscript/manuscript.tex
DOL proofread and edit the paper. Rewrote the PM section. Checked for consistency with PM issues with reviewer 3

@@
 \usepackage{seqsplit}
+\usepackage{enumitem}
 
@@
 \newcommand{\BS}{\boldsymbol}
+\setlist[itemize]{noitemsep}%, topsep=0pt}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
     RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations.
-RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its design and C++ and Python interface options permit convenient expansion to additional models.
-Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
-The computational cost of the models is also compared.
+RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
+RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
+A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS).
+The computational cost of the models is compared.
 RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
@@
 
-% PROGRAM SUMMARY.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%k%
 
 {\bf PROGRAM SUMMARY}
-  %Delete as appropriate.
 
@@
 
-Combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
-Specifically, combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
-Historically, radiative heat transfer modeling in combustion problems is either neglected or oversimplified, resulting in significant over- or underprediction of flame temperatures by up to 200$^{\circ}$C, respectively \citep{Modest_2016}.
-Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
-These problems motivated development of the RadLib library, which implements three radiation property models in C++ and Python and provides a framework for additional models and further development, giving researchers more convenient access to advanced radiation property modeling tools.
-%
-%Modeling radiative heat transfer for CFD is complex and challenging.
-For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
-This can lead to simulations that use oversimplified radiation models, but in cases where radiation is significant relative to the other physical phenomena, oversimplified models can negatively impact the accuracy of simulation results.
-In some cases, radiative gains or losses are small compared to other energy sources or heat transfer modes and radiation can be safely neglected, but many practical engineering systems do not allow this.
-For example, simple jet flames demonstrate both possibilities: early in a flame's development, turbulent mixing typically dominates heat transfer and dictates flame behavior; late-stage flame phenomena like soot behavior and flame sheet breakthrough, however, increasingly depend on the magnitude of radiative heat losses and are difficult to simulate accurately without a robust radiation model.
+Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem.
+Combustion is one of the key radiative tranfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
+Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
+Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures \citep{Modest_2016}.
+Additionally, some late-stage flame phenomena, particularly soot behavior and flamesheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
+These problems motivated development of the RadLib library, which implements three radiation property models, with C++, Python, and Fortran interfaces, and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.
 
@@
 Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
-Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiation property model.
+Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model.
 Complexity, implementation, and computational costs of these two parts can vary widely, depending on the models chosen.
 The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and Reverse Monte Carlo Ray Tracing (RMCRC) model, among others, are significantly more involved.
-Similarly for radiation property models, which range from simple correlations for mean absorption coefficients, to gray gas models such as the weighted sum of gray gas model (WSGG), to the more advanced Spectral Line WSGG (SLW) family of model, to full line-by-line (LBL) approaches.
+Similarly for radiation property models, which range from simple correlations for mean absorption coefficients, to gray gas models such as the weighted sum of gray gas model (WSGG), to the more advanced Spectral Line WSGG (SLW) family of model, to full line-by-line (LBL) treatment.
 In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models, such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
-RadLib addresses this second, radiative property model part of radiative simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
-
-For an absorbing, emitting, and non-scattering medium, the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
+RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
+
+For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
 % 
@@
 Radiative property data typically takes the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model.
-Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, reflecting varying degrees of dependence on local system properties like temperature, pressure, and gas composition.
-Radiation property models, including those implemented in RadLib, typically use high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} to calculate spectral absorption coefficients, reducing or simplifying the huge amount of spectral data using correlations and modeling assumptions \citep{Zhang_2002b}.
-
-Direct solution of the spectral RTE involves so-called line-by-line calculations in which the RTE is solved for each individual spectral line, potentially millions of evaluations; this is computationally prohibitive for most practical configurations and used primarily for model validation.
-Traditional band models rely on estimated or averaged "line-of-sight" property values that, as a result, cannot be incorporated into the RTE.
-Modern band models require high-resolution databases and reorder rather than averaging absorption coefficients, but tend to lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.
+Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, and depends on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
+Radiation property models, including those implemented in RadLib, are typically developed using high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} in order to calculate spectral absorption coefficients, thus reducing or simplifying the huge amount of spectral data by using correlations and modeling assumptions \citep{Zhang_2002b}.
+
+The direct solution of the spectral RTE using so-called line-by-line calculations in which the RTE is solved for each individual spectral line is computationally prohibitive for most practical configurations and is used primarily for model validation.
+Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
+%VBS: citation here?
+Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these cant lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.
 
 Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}.
-Assuming spectrally uniform (gray) properties over a region $j$ (that is, for a gray gas $j$), we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ defined by $j$ to obtain
+Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
 %
@@
 %
-Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases with the addition of one "clear gas" $j=0$ that represents transparent windows in the spectrum for which $\kappa_0=0$.
-This "gray gas" approach allows us to calculate the total radiative intensity $I$ by summing the individual gray gas intensities rather than integrating over the entire wavenumber spectrum:
+Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases.
+Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$.
+This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
 %
@@
 %
-%The heat flux $\mathbf{q}$ and volumetric radiative heat source $Q$ can then be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence or the resulting vector field, respectively:
-%%
-%\begin{linenomath}
-%\begin{equation}
-%    \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
-%\end{equation}
-%\end{linenomath}
-%%
-%\begin{linenomath}
-%\begin{equation}
-%    Q = -\nabla\cdot\mathbf{q}.
-%\end{equation}
-%\end{linenomath}
-%%
-Global models are especially attractive to computational combustion researchers because they significantly reduce the required number of RTE evaluations during calculations of radiative source terms for the energy conservation equations.
+
+The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
+%
+\begin{linenomath}
+\begin{equation}
+    \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
+\end{equation}
+\end{linenomath}
+%
+\begin{linenomath}
+\begin{equation}
+    Q = -\nabla\cdot\mathbf{q}.
+\end{equation}
+\end{linenomath}
+%
+Global models are especially attractive in computational heat transfer applications because they can provide good accuracy while limiting computational costs.
 
 With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
-RadLib is a C++ library with an optional Python interface.
-Currently, RadLib only calculates radiation absorption coefficients and weighting factors for use in global radiation models, but expansion to other radiative properties and model types is possible.
+RadLib is a C++ library with optional Python and Fortran interfaces.
+RadLib calculates radiation absorption coefficients and weighting factors for use in global radiation models.
+Expansion to other radiative properties and model types is possible.
 Three models are fully implemented and validated.
-All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.
+%All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.
 
@@
 At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients using the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
-Each of these models was specifically chosen for its notable attributes such as popularity, ease of implementation, or accuracy; their individual strengths, weaknesses, and limitations are discussed in the sections that follow.
-
-Absorption coefficients and other radiative property data may take on different forms depending on the RTE solution approach, but can generally be classified as either spectral (wavenumber-dependent) or global (integrated over wavenumber).
+These models were chosen for their relavance to practical radiative heat transfer simulations.
+They represent increasing levels of complexity, computational cost, and accuracy.
+Each model is discussed in more detail in the following sections.
+
+%Absorption coefficients and other radiative property data may take on different forms depending on the RTE solution approach, but can generally be classified as either spectral (wavenumber-dependent) or global (integrated over wavenumber).
 Spectral absorption coefficients can be applied to the spectral RTE (Eq.~\ref{e:RTE_general}), while global absorption coefficients are used in the spectrally-integrated RTE (Eq.~\ref{e:RTE_wsgg}).
@@
 At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot.
-Note that the property models implemented in RadLib apply only to non-scattering media.
+The property models implemented in RadLib apply only to non-scattering media.
 
@@
 
-RadLib's simplest radiation property model generates Planck Mean absorption coefficients under the assumption of optically thin media, from here on referred to as the Planck Mean (PM) model.
-The optically thin approximation assumes that there is little to no reabsorption of radiative energy in the system, or, in other words, that the system only emits radiation and does not absorb it.
+The Planck Mean (PM) model is the simplest of the three models implemented.
+This model assumes a single gray gas and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
+
+The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}.
+This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
+The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models.
+The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
+
+For each species, the PM model provides the absorption coefficient as fourth or fifth order polynomial fits in one or two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
+See \cite{TNF} for details and references.
+The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
+The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream.
+(\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
+
+The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}. 
+It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
+The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration.
+Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.
+
+The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation.
+Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss.
+It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%.
+At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.
+% todo: show the RTE equation/source term
+
+%Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}.
+The absorption coefficient correlations use fourth or fifth order polynomial fits in the range 300-2500 K.
+TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}.
+In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.
+
+%RadLib's simplest radiation property model generates Planck Mean absorption coefficients under the assumption of optically thin media, from here on referred to as the Planck Mean (PM) model.
+%The optically thin approximation assumes that there is little to no reabsorption of radiative energy in the system, or, in other words, that the system only emits radiation and does not absorb it.
 In combustion systems, optical thinness is associated with various other flame properties such as low radiative heat transfer relative to chemical heat release or convective heat transfer, negligible amounts of soot or other large molecules, and relatively small flame lengths.
@@
 Assuming optical thinness, however, has the distinct advantage of simplifying the radiative source term (denoted $S_{rad}$) of the energy conservation equation to
-\begin{equation}
-	S_{rad}=-4\kappa \sigma T^4,
-\end{equation}
-where $\kappa$ is the radiation absorption coefficient, $\sigma$ is the Stefan-Boltzmann constant, and $T$ is temperature.
+%\begin{equation}
+%	S_{rad}=-4\kappa \sigma T^4,
+%\end{equation}
+%where $\kappa$ is the radiation absorption coefficient, $\sigma$ is the Stefan-Boltzmann constant, and $T$ is temperature.
 Using an optically thin approximation means that no RTE solution is required when calculating radiative source terms.
-
-In combustion systems, this simplification is convenient because it makes radiation modeling easy to implement and computationally inexpensive.
+%
+%In combustion systems, this simplification is convenient because it makes radiation modeling easy to implement and computationally inexpensive.
 The vast majority of computational combustion research that considers radiation employs an optically thin approximation despite its limited applicability to combustion processes.
 Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flames or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}.
-
-The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
+%
+%The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
 These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its limitations.
@@
 In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-
-Because of these limitations, the authors strongly recommend that RadLib users carefully consider the implications of the PM model before using it in combustion simulations.
-It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its popularity and widespread use.
-The examples included with the RadLib code and shown in Section \ref{s:Examples} demonstrate the deficiencies of the PM model in comparison to other radiation property models included with RadLib.
+%
+%Because of these limitations, the authors strongly recommend that RadLib users carefully consider the implications of the PM model before using it in combustion simulations. 
+%It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its popularity and widespread use. 
+%The examples included with the RadLib code and shown in Section \ref{s:Examples} demonstrate the deficiencies of the PM model in comparison to other radiation property models included with RadLib.
 
@@
 RadLib implements the WSGG model presented by Bordbar et al.
-\citep{Bordbar_2014,Bordbar_2020}, which uses correlations based on the HITEMP 2010 database \cite{Rothman_2010}.
-It models mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas.
+\citep{Bordbar_2014,Bordbar_2020}.
+This model computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010 database \cite{Rothman_2010}.
+The $k_j$ and $a_j$ are then correlated to these results using polynomial fits summarized below.
+The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas.
 Absorption coefficients are calculated by
@@
 %
-where $a_j$ is the weighting factor for gas $j$ and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}=1200$K.
+where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K.
 The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound.
@@
 %
-where $C_{j,k,i}$ is another correlated model coefficient.
+where $C_{j,k,i}$ is a correlated model coefficient.
 The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al.
@@
 This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility.
-Most WSGG models are limited to a specific range of \ce{H2O}--\ce{CO2} molar ratios, including the predecessor of the current model, which used correlations valid for $0.01\le M_r\le4$ \citep{Bordbar_2014}.
-Bordbar et al.~\citep{Bordbar_2020} extended this range to arbitrary values of $M_r$ by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of the correlated range.
-As a result, the updated WSGG model, implemented in RadLib, can consistently and accurately handle any value of the \ce{H2O}--\ce{CO2} molar ratio.
+Most WSGG models are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values.
+This is true of Bordbar et al.'s 2014 model \cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$.
+That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG model versions.
+Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of the correlated range, and that is the model implemented here.
 
@@
 
-The spectral line-weighted-sum-of-gray-gases (SLW) model represents a family of global approaches to radiative heat transfer in high-temperature gases that also includes absorption distribution functions (ADF) and full spectrum $k$-distribution (FSK) models, all of which are based on the same fundamental principle in modeling the gas absorption spectrum \cite{Solovjov_2016}.
-In order to extend their spectral models from uniform conditions (isothermal, homogeneous gases) to nonuniform conditions (non-isothermal, non-homogeneous gases), these models take a reference approach in which local gas states are corrected relative to a reference state.
-Reference approaches, however, generally lack consistent reference states and can yield significant errors in cases with large spatial temperature gradients \cite{Solovjov_2017}.
+The spectral line-weighted-sum-of-gray-gases (SLW) model represents a family of global approaches to radiative heat transfer in high-temperature gases that also includes the absorption distribution function (ADF) and full spectrum $k$-distribution (FSK) models, all of which are based on the same fundamental principle in modeling the gas absorption spectrum \cite{Solovjov_2016}.
+In order to extend their spectral models from isothermal, homogeneous composition gases to non-isothermal, non-homogeneous composition gases, these models use a reference approach in which radiative properties at local gas states are computed with respect to properties a at reference state.
+Such approaches, however, generally lack consistent reference states and can yield significant errors in cases with large spatial temperature gradients \cite{Solovjov_2017}.
 The Rank Correlated SLW (RCSLW) model is a unique extension of the generalized SLW model that does not require a specified gas reference state.
@@
 A recent comparison of SLW modeling approaches revealed that ``the Rank Correlated SLW model is the most robust of all models, and demonstrates that it can achieve accurate solutions with as few as 3–5 gray gases" \citep{Badger_2019}.
-The literature indicates that the RCSLW model has not yet been successfully applied to turbulent combustion simulations \cite{Modest_2016,Coelho_2017}.
-Other SLW models have been applied to gas--soot mixtures \cite{Solovjov_2001,Solovjov_2001b} and high-temperature non-isothermal gases \cite{Solovjov_2011,Solovjov_2020} with results that suggest their applicability to combustion systems.
+The literature indicates that the RCSLW model has not yet been applied to turbulent combustion simulations \cite{Modest_2016,Coelho_2017}.
+We provide an example below using the Fire Dynamics Simulator (FDS) \cite{FDS}.
+Other SLW models have been applied to gas--soot mixtures \cite{Solovjov_2001,Solovjov_2001b} and high-temperature non-isothermal gases \cite{Solovjov_2011,Solovjov_2020} with results that suggest their good applicability to combustion systems.
 
@@
 \cite{Solovjov_2017} as method I.2.2, which gives the best and most consistent results of the SLW methods discussed in the aforementioned study.
-A summary of the general SLW method and the RCSLW method are presented here, but additional information about these and various other SLW methods can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
-
-SLW and WSGG models are similar in that they approximate a real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed.
+A summary of the general SLW method and the RCSLW method are presented here, but more detailed information about these and other SLW methods can be found in the literature \cite{Solovjov_2000, Solovjov_2001, Solovjov_2008, Solovjov_2011, Solovjov_2014, Solovjov_2016, Solovjov_2017, Webb_2018}.
+
+SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed.
 In traditional WSGG models, the component gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}.
 In SLW approaches, however, the gases are gray in a given spectral band by construction.
-Rather than defining a gray gas $j$ by integrating over a band of sequential wavenumbers $\eta$ (which may have a highly variable absorption coefficient), SLW models define a gray gas $j$ by integrating over a set of nonsequential wavenumbers that correspond to a given value of the absorption cross section $C_{\eta}$.
+Rather than defining a gray gas $j$ by integrating over a band of sequential wavenumbers $\eta$ (which may have highly variable absorption coefficients), SLW models define a gray gas $j$ by integrating over a set of nonsequential wavenumbers that correspond to a given band of the absorption cross section $C_{\eta}$ with values constant to within the width of the band.
+
 The absorption cross section is related to the absorption coefficient by $\kappa_\eta=C_\eta N$, where $N$ is the molar density of the radiatively participating gas.
@@
 For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}.
-RadLib's RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
+The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
 %
@@
 where $x$ denotes mole fraction.
-Assuming that the absorption cross sections of each species are statistically independent, we can calculate the mixture ALBDF for a given gray gas using the multiplication method \cite{Solovjov_2000}:
+Assuming that the absorption cross sections of each species are statistically independent, the mixture ALBDF for a given gray gas can be computed using the multiplication method \cite{Solovjov_2000}:
 %
@@
 %
-Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
+Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
 
@@
 Note that this is not the same as specifying a reference state $\BS{\phi}=\BS{\phi}_r(T_r,x_r,P_r)$ as in done for SLW reference approaches.
-The RCSLW model has the significant advantage that it does not require a thermodynamic reference state.
+%The RCSLW model has the significant advantage that it does not require a thermodynamic reference state.
     \item Specify a collection of $F_j$ points and $\tilde{F}_j$ boundary values such that $F_j$ lies between $\tilde{F}_j$ and $\tilde{F}_{j-1}$. These apply to all spatial positions. 
@@
 
-RadLib can also account for the radiative properties of soot in gaseous combustion environments.
+Soot is accounted for in all three implemented models.
 Soot particles are assumed to be unagglomerated spheres that absorb and emit radiation at all wavelengths such that their optical properties can be determined using the Rayleigh small particle limit.
@@
 Various values for the refraction index have been proposed and applied \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}.
-RadLib uses the most current values in the literature: $n=1.75$ and $k=1.03$ \cite{Williams_2007}, resulting in a value of $C_0=7.03$, which is nearly the same as the value of $C_0=7.0$ used by Solovjov and Webb \cite{Solovjov_2001} to study radiative transfer in sooty gas mixtures.
+RadLib uses the values $n=1.75$ and $k=1.03$ \cite{Williams_2007}, resulting in a value of $C_0=7.03$, which is nearly the same as the value of $C_0=7.0$ used by Solovjov and Webb \cite{Solovjov_2001} to study radiative transfer in sooty gas mixtures.
 The Planck mean and Rosseland mean soot absorption coefficients are given in \cite{Modest_2013} as $\kappa_s=3.83f_vC_0T/C_2$ and $\kappa_s=3.60f_vC_0T/C_2$, respectively.
@@
 In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient.
-Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ \si{m^{-1}}.
+Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ with units of \si{m^{-1}}.
 
 In the WSGG model, the soot absorption coefficient is also computed using Eq.~\ref{e:soot2} but then added to each of the gray gases separately \cite{Bordbar_personal}.
-Because soot radiates across all wavelengths, its absorption coefficient is added to the value of the clear gas in addition to the values of all four gray gases.
+Because soot radiates across all wavelengths, its absorption coefficient is added to the value of the clear gas in addition to the values of the four gray gases.
 The gas weights $a_j$ are not changed.
@@
 
-RadLib is an object-oriented C++ library that includes C++, Python, and Fortran interfaces.
-Upon initial download, the RadLib package contains four subdirectories: \texttt{src} contains the RadLib source code; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to optionally generate code documentation with Doxygen.
+RadLib is an object-oriented C++ library that includes C++, Python, and Fortran interfaces. Upon initial download, the RadLib package contains four subdirectories: 
+%
+\begin{itemize}
+    \item \texttt{src} contains the RadLib source code; 
+    \item \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; 
+    \item \texttt{data} contains ALBDF data tables required for the RCSLW model; and 
+    \item \texttt{docs} contains files used to optionally generate code documentation with Doxygen. 
+\end{itemize}
+%
 An additional directory, \texttt{installed}, is created and populated with RadLib's executables and header files during installation if no other installation location is specified.
@@
 Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and an option to build the documentation.
-
-The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, 
-\texttt{lib} containing library files for each interface, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model.
+Included \texttt{Readme.md} files provide additional information.
+
+The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, \texttt{lib} containing library files for each interface, \texttt{cmake} with relocatable CMake files for downstream usage, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model.
 These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name.
@@
 This folder also contains the Python module.
-The code installation additionally generates relocatable CMake files for downstream usage, located at \texttt{\seqsplit{installed/cmake/radlib/radlib.cmake}} and \texttt{\seqsplit{installed/cmake/radlib\textunderscore fortran/radlib\textunderscore fortran.cmake}}, where \texttt{installed/} may be replaced with a user-specified installation path.
 If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable.
@@
 
-Figure \ref{fig:flowchart} illustrates the basic structure of using of RadLib in a generic one-dimensional RTE solution.
+Figure \ref{fig:flowchart} illustrates the basic structure of using RadLib in a generic one-dimensional RTE solution.
 The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver.
@@
 The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}.
-A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters.
+A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters so that these do not need to be specified for models that do not make use of them.
 The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first).
 The PM model only considers one gas and the vectors are of unity size.
-The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index argument (starting at zero for all interfaces) is provided as an additional argument.
+The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument.
 This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}.
@@
 The RTE is solved between two parallel plates with a ray-tracing code, included in the RadLib package.
-Each case's results is presented alongside the line-by-line (LBL) data from its respective reference.
+Results for each case are presented alongside the line-by-line (LBL) data from the respective references.
 
@@
 \cite{Solovjov_2001} (Sb)---and the number of each example corresponds to the example number in its respective reference.
-Each example case consists of one or more gas layers ("slabs") bounded by black walls.
+Each example case consists of one or more gas layers (``slabs'') bounded by black walls.
 Example S1 consists of two adjacent gas layers with identical species compositions: one hot layer of constant thickness and one cold layer of varying thickness. 
@@
 Example S4 divides the gas into three equally-spaced layers and applies a triangular temperature profile to the middle layer and a constant temperature to the two outer layers.
-Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K applied to a single gas layer of constant species composition.
+Example S5 uses a half-sinusoid temperature profile that decreases from 1500 to 500 K applied to a single gas layer of constant composition.
 Example B3 has symmetric temperature and H$_2$O mole fraction profiles with central peaks of 1800 K and 1, respectively (with $x_{CO2}=1-x_{H2O}$). 
@@
 The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity.
-For the PM model in Example S5, $Q$ varies from around -80 kW/m$^3$ at $x=0$ to a peak of 200 kW/m$^3$ at x=$1.5$ m and drops to 100 kW/m$^3$ at $x=2$ m.
+For the PM model in Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100 kW/m$^3$ at $x=2$~m.
 In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity.
-The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively.
-These values are small compared to the domain sizes greater than 0.5 m that are considered in Example S2.
+The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36~m in the thick and thin layers, respectively.
+These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
 %, which coincides with the PM model's use of the optically thin approximation, but the high error in its predictions of radiative heat flux relative to the LBL data indicates that neither the optically thin approximation nor absorption coefficients calculated with this model are accurate for this case.
-Example S3 is the clearest illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.
+Example S3 illustrates that the PM model tends to overpredict radiative heat loss at hight temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.
+%illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.
 
@@
 The RCSLW model is sensitive to the number of gray gases used, as illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
-The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
+The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases (not shown) and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
 The RCSLW model also depends on the value of the chosen reference temperature that is used to set the ALBDF grid.
-In Example S5, the RCSLW model does not converge to the LBL data at $x>0.5$ m when the domain average temperature was used.
+In Example S5, the RCSLW model does not converge to the LBL data at $x>0.5$ m when the domain average temperature is used.
 
@@
 In sooting flames, soot acts as a significant source and sink of radiation, and its radiative properties differ significantly from those of the participating gaseous species.
-Soot reactions and transport are both sensitive to and strongly influence local variations in flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
+Soot reactions and transport are both sensitive to, and strongly influence local variations in, flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
 %The agreement produced by RadLib's approach to soot radiation in Example Sb1 is an encouraging step toward accurate, detailed treatment of soot's radiative properties in complex combustion simulations.
@@
 The configuration is a vertically fired gas burner with various fuels and with a coflow oxidizer stream of varying nitrogen dilution.
-The burner has outer and inner diameters of 15.2 and 13.7 cm and is near the floor in the center of a 1.22 by 1.22 by 1.83 m tall compartment.
+The burner has outer and inner diameters of 15.2 and 13.7 cm, respectively, and is near the floor in the center of a 1.22 by 1.22 by 1.83 m tall compartment.
 The heat release rate was 10 kW and included a 1 kW pilot in a surrounding ring.
@@
 Simulations performed here used the ethylene fuel with 20.9\% \ce{N2} oxidizer (i.e., air).
-Further FDS model and case simulation details are provided in the FDS validation and user guides \cite{FDS}.
+Further FDS model and case simulation details are provided in the FDS validation and user guides~\cite{FDS}.
 
@@
 In addition to comparing model attributes and performance, we evaluated and compared the computational cost of the implemented radiation property models. 
-Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7; the results, normalized by the cost of the WSGG model, are summarized in Figure~\ref{f:cost}. 
+Calculations were performed on a 4 GHz Quad Core Intel Core i7 iMac, version 10.15.7. The results, normalized by the cost of the WSGG model, are summarized in Figure~\ref{f:cost}. 
 In the results presented, only the cost of evaluating the solution was included; model initialization and input/output costs were neglected.
@@
 
-Figure~\ref{f:cost}a displays the relative cost to compute the gas properties $k$ and $a$, represented by the time required to execute the C++ function \texttt{get\textunderscore k\textunderscore a()}, averaged over one million evaluations.
+Figure~\ref{f:cost}a displays the relative cost to compute the gas properties $\kappa$ and $a$, represented by the time required to execute the C++ function \texttt{get\textunderscore k\textunderscore a()}, averaged over one million evaluations.
 The results for each model are normalized by the WSGG model, which required an average of 8.0E-7~s.
 Relative to the WSGG model, the cost to evaluate the gas properties with the PM model was 0.098.
-The RCSLW model was evaluated with $n=1$, 2, 4, and 8 gray gases, which resulted in relative costs of 1.9, 4.9, 9.4, and 18, respectively.
-The cost of the RCSLW model is very nearly proportional to the number of gray gases considered.
+The RCSLW model was evaluated with $n=1$, 2, 4, and 8 gray gases, which resulted in relative costs of 1.9, 4.9, 9.4, and 18, respectively, which is very nearly proportional to the number of gray gases considered.
 %
@@
 Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver.
-This is relavant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evalations themselves.
+This is relavant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evalations alone.
 This is consistent with the results of the figure and as follows.
@@
 In particular, the cost of a single evaluation of the gas properties is small and evaluating the gas properties in a Python loop results in the loop itself appearing to dominate the computational cost.
-Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Figure~\ref{f:cost} the cost only varied by about 4\%, indicating that the computational cost is dominated by Python wrapper itself rather than by the underlying C++ model evaluations or solver.
+Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Figure~\ref{f:cost} the cost only varied by about 4\%, indicating that the computational cost is dominated by Python wrapper rather than by the underlying C++ model evaluations or solver.
 The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version.
-It is possible that optimizing the Cython interface could improve the speed and relative cost of using Python with RadLib, but RadLib's Python interface and examples are mainly intended to demonstrate the library's use and provide a convenient interface, rather than serve as a point of incorporation into detailed CFD calculations.%, which rarely employ Python.
+It is possible that optimizing the Cython interface could improve the speed and relative cost of using Python with RadLib, but RadLib's Python interface and examples are primarily intended to demonstrate the library's use and provide a convenient interface rather than serve as a point of use for detailed CFD calculations.
 
@@
 Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to their high level of conceptual and mathematical complexity and potentially large computational cost.
-Many combustion CFD studies either neglect radiative heat transfer modeling or employ oversimplified models that do not accurately represent combustion systems.
-Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield accurate results.
+Many combustion CFD studies either neglect radiative heat transfer or employ oversimplified models that do not accurately represent combustion systems.
+Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation to yield accurate results.
 
 RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations.
-At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model---but its design and C++, Python, and Fortran interfaces permit expansion to additional property models.
+At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
 Each of the implemented models has been validated and the library's structure and functionality has been outlined.
-
-In addition to the library itself, the RadLib package includes several illustrative example cases in a one-dimensional parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model implementation.
+The library can be expanded to include additional property models.
+
+In addition to the library itself, RadLib includes several illustrative example cases in a one-dimensional parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model implementation.
 Results are compared to line-by-line (LBL) solutions.
 In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy at the expense of computational cost.
-Under appropriate conditions, the WSGG model can also produce accurate results at significantly lower computational cost, but may perform inconsistently under certain conditions.
+%Under appropriate conditions, the WSGG model can also produce accurate results at significantly lower computational cost, but may perform inconsistently under certain conditions.
 In general, the PM model is adequate in situations to which the optically thin approximation can be reasonably applied, but does not produce accurate results in any of the example cases presented here.
 
-RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for combustion CFD, but could potentially be applied to research problems involving radiative heat transfer in other fields as well.
-RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single extensible library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models.
+RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for relatively high temperature CFD applications, such as combustion, but could potentially be applied to research problems involving radiative heat transfer in other fields as well.
+RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models.
 Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions.
 By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations.
-With RadLib, we believe that researchers will be able to put more of their time and effort into meaningful results rather than code or model development for radiative heat transfer in combustion CFD.
+%With RadLib, we believe that researchers will be able to put more of their time and effort into meaningful results rather than code or model development for radiative heat transfer in combustion CFD.
 
@@
 
-%\begin{thebibliography}{10}
-%\expandafter\ifx\csname url\endcsname\relax
-%  \def\url#1{\texttt{#1}}\fi
-%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-%\expandafter\ifx\csname href\endcsname\relax
-%  \def\href#1#2{#2} \def\path#1{#1}\fi
-%
-%\bibitem{Hottel_1967}
-%H.~Hottel, A.~Sarofim, Radiative Transfer, {McGraw-Hill}, New York, 1967.
-%
-%\bibitem{Modest_2013}
-%M.~F. Modest, Radiative Heat Transfer, third edition, {Academic Press},
-%  New York, 2013.
-%  
-%\bibitem{Modest_2016}
-%M.~F. Modest, D.~C. Haworth, Radiative Heat Transfer in Turbulent Combustion Systems, {Springer}, New York, 2016.
-%
-%\bibitem{Smith_2003}
-%N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
-%  \href{https://tnfworkshop.org/radiation/}{{TNF} workshop radiation models}
-%  (2003).
-%\newline\urlprefix\url{https://tnfworkshop.org/radiation/}
-%
-%\bibitem{Grosshandler_1993}
-%W.~L. Grosshandler, {RADCAL}: A narrow-band model for radiation calculations in
-%  a combustion environment: Nist technical note 1402.
-%
-%\bibitem{Barlow_2001}
-%R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, Scalar profiles and {NO}
-%  formation in laminar opposed-flow partially premixed methane/air flames,
-%  Combustion and Flame 127~(3) (2001) 2102--2118.
-%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
-%  {\path{doi:10.1016/S0010-2180(01)00313-3}}.
-%
-%\bibitem{Barlow_1999}
-%R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
-%  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{Nitric
-%  oxide formation in dilute hydrogen jet flames: isolation of the effects of
-%  radiation and turbulence-chemistry submodels}, Combustion and Flame 117~(1-2)
-%  (1999) 4--31.
-%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
-%  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
-%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}
-%
-%\bibitem{Frank_2000}
-%J.~H. Frank, R.~S. Barlow, C.~Lundquist, Radiation and nitric oxide formation
-%  in turbulent non-premixed jet flames, Proceedings of the Combustion Institute
-%  28~(1) (2000) 447--454.
-%\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
-%  {\path{doi:10.1016/S0082-0784(00)80242-8}}.
-%
-%\bibitem{Zhu_2002}
-%X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
-%  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{The
-%  effects of self-absorption of radiation on an opposed flow partially premixed
-%  flame}, Combustion and Flame 129~(3) (2002) 342--345.
-%\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
-%  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
-%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}
-%
-%\bibitem{Coelho_2002}
-%P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, Spectral radiative effects and
-%  turbulence-radiation-interaction in sandia flame {D}, in: {Barlow, Robert S.,
-%  Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), The
-%  Proceedings of the Sixth International Workshop on Measurement and
-%  Computation of Turbulent Nonpremixed Flames, 2002.
-%
-%\bibitem{Bordbar_2014}
-%M.~H. Bordbar, G.~Wecel, T.~Hyppanen, A line by line based weighted sum of gray
-%  gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
-%  combustion, Combustion and Flame 161~(9) (2014) 2435--2445.
-%\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
-%  {\path{doi:10.1016/j.combustflame.2014.03.013}}.
-%
-%\bibitem{Bordbar_2020}
-%H.~Bordbar, G.~C. Fraga, S.~Hostikka,
-%  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{An
-%  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
-%  molar fraction ratios in thermal radiation}, International Communications in
-%  Heat and Mass Transfer 110 (2020) 104400.
-%\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
-%  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
-%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}
-%
-%\bibitem{Rothman_2010}
-%L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
-%  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
-%  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{HITEMP},
-%  the high-temperature molecular spectroscopic database}, Journal of
-%  Quantitative Spectroscopy {\&} Radiative Transfer 111~(15) (2010) 2139--2150.
-%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
-%  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
-%\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}
-%
-%\bibitem{Solovjov_2016}
-%V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The generalized {SLW}
-%  model, Journal of Physics: Conference Series 676 (2016) 1--36.
-%
-%\bibitem{Solovjov_2017}
-%V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, The rank correlated
-%  {SLW} model of gas radiation in non-uniform media, Journal of Quantitative
-%  Spectroscopy {\&} Radiative Transfer 197 (2017) 26--44.
-%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
-%  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.
-%
-%\bibitem{Badger_2019}
-%J.~Badger, B.~W. Webb, V.~P. Solovjov, An exploration of advanced {SLW}
-%  modeling approaches in comprehensive combustion predictions, Combustion
-%  Science and Technology 012022~(676) (2019) 1--17.
-%\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
-%  {\path{doi:10.1080/00102202.2019.1678907}}.
-%
-%\bibitem{Solovjov_2000}
-%V.~P. Solovjov, B.~W. Webb, {SLW} modeling of radiative transfer in
-%  multicomponent gas mixtures, Journal of Quantitative Spectroscopy and
-%  Radiative Transfer 65 (2000) 655--672.
-%
-%\bibitem{Solovjov_2001}
-%V.~P. Solovjov, B.~W. Webb, An efficient method for modeling radiative transfer
-%  in multicomponent gas mixtures with soot, Transactions of the ASME 123 (2001)
-%  450--457.
-%
-%\bibitem{Solovjov_2008}
-%V.~P. Solovjov, B.~W. Webb, Multilayer modeling of radiative transfer by {SLW}
-%  and {CW} methods in non-isothermal gaseous medium, Journal of Quantitative
-%  Spectroscopy and Radiative Transfer 109~(2) (2008) 245--257.
-%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
-%  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.
-%
-%\bibitem{Solovjov_2011}
-%V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, The {SLW}-1 model for efficient
-%  prediction of radiative transfer in high temperature gases, Journal of
-%  Quantitative Spectroscopy and Radiative Transfer 112~(7) (2011) 1205--1212.
-%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
-%  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.
-%
-%\bibitem{Solovjov_2014}
-%V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, Extension of the exact {SLW} model to
-%  non-isothermal gaseous media, Journal of Quantitative Spectroscopy and
-%  Radiative Transfer 143 (2014) 83--91.
-%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
-%  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.
-%
-%\bibitem{Webb_2018}
-%B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, An exploration of the influence of
-%  spectral model parameters on the accuracy of the rank correlated slw model,
-%  Journal of Quantitative Spectroscopy and Radiative Transfer 218 (2018)
-%  161--170.
-%\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
-%  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.
-%
-%\bibitem{Pearson_2014}
-%J.~Pearson, B.~Webb, S.~V.P., J.~Ma, Efficient representation of the absorption
-%  line blackbody distribution function for {H$_2$O}, {CO$_2$}, and {CO} at
-%  variable temperature, mole fraction, and total pressure, Journal of
-%  Quantitative Spectrosopy and Radiative Transfer 138 (2014) 82--96.
-%
-%\bibitem{Brewster_1992}
-%M.~Q. Brewster, Thermal Radiative Transfer and Properties, Wiley, 1992.
-%
-%\bibitem{Lee_1981}
-%S.~C. Lee, C.~L. Tien, Optical constants of soot in hydrocarbon flames,
-%  Symposium (International) on Combustion 18~(1) (1981) 1159--1166.
-%\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
-%  {\path{doi:10.1016/S0082-0784(81)80120-8}}.
-%
-%\bibitem{Stull_1960}
-%V.~R. Stull, G.~N. Plass, Emissivity of dispersed carbon particles, Journal of
-%  the Optical Society of America 50~(2) (1960) 121.
-%\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
-%  {\path{doi:10.1364/JOSA.50.000121}}.
-%
-%\bibitem{Dalzell_1969}
-%W.~H. Dalzell, A.~F. Sarofim, Optical constants of soot and their application
-%  to heat-flux calculations, Journal of Heat Transfer 91~(1) (1969) 100--104.
-%\newblock \href {http://dx.doi.org/10.1115/1.3580063}
-%  {\path{doi:10.1115/1.3580063}}.
-%
-%\bibitem{Howarth_1966}
-%C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), The Effect of Temperature on
-%  the Extinction of Radiation By Soot Particles, Begellhouse, 1966.
-%\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
-%  {\path{doi:10.1615/IHTC3.1210}}.
-%
-%\bibitem{Chang_1990}
-%H.-c. Chang, T.~T. Charalampopoulos, Determination of the wavelength dependence
-%  of refractive indices of flame soot, Proceedings of the Royal Society of
-%  London. Series A: Mathematical and Physical Sciences 430~(1880) (1990)
-%  577--591.
-%\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
-%  {\path{doi:10.1098/rspa.1990.0107}}.
-%
-%\bibitem{Felske_1984}
-%J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, Determination of the
-%  refractive indices of soot particles from the reflectivities of compressed
-%  soot pellets, Combustion Science and Technology 37~(5-6) (1984) 263--283.
-%\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
-%  {\path{doi:10.1080/00102208408923757}}.
-%
-%\bibitem{Williams_2007}
-%T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, Measurement of
-%  the dimensionless extinction coefficient of soot within laminar diffusion
-%  flames, International Journal of Heat and Mass Transfer 50~(7-8) (2007)
-%  1616--1630.
-%\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
-%  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.
-%
-%\bibitem{Felske_1977}
-%J.~Felske, T.~C.L., The use of the {M}ilne-{E}ddington absorption coefficient
-%  for radiative heat transfer in combustion systems, ASME Journal of Heat
-%  Transfer 99~(3) (1977) 633--647.
-%
-%\bibitem{Bordbar_personal}
-%H.~Bordbar, personal communication.
-%
-%\bibitem{Chang_1984}
-%S.~Chang, K.~Rhee, Blackbody radiation functions, International communictions
-%  in Heat and Mass Transfer 11 (1984) 451--455.
-%
-%\bibitem{Stephens_2020}
-%V.~Stephens, D.~Lignell, One-dimensional turbulence ({ODT}): computationally
-%  efficient modeling and simulation of turbulent flows, Software{X} 13 (2020)
-%  100641.
-%\newblock \href {http://dx.doi.org/10.1016/j.softx.2020.100641}
-%  {\path{doi:10.1016/j.softx.2020.100641}}.
-%  
-%\bibitem{Zhang_2002b}
-%H.~Zhang, M.~F.~Modest, Evaluation of the Planck-mean absorption coefficients from HITRAN and HITEMP databases, Journal of Quantitative Spectroscopy \& Radiative Transfer 73~(6) (2002) 649--653.
-
-%\end{thebibliography}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-07-25 submissions/CPC_response_to_reviewers.md
update response to reviewer after testing on mac, linux, code ocean

@@
 Note that the C++ source code is required to install the Python interface, so there is no option to build only the Python interface.
-All of this information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages.
-Furthermore, we have now done full tests of the installation and running of all examples on a desktop Mac, a desktop Linux machine, and a large Linux-based cluster.**
+This information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages.
+We have also done full tests of the installation and running of all examples on a desktop Mac, and a desktop Linux machine.
+The c++ and fortran interfaces were tested on a large Linux-based cluster.
+The code also runs on a code ocean module.**
 

### 2021-07-25 submissions/CPC_response_to_reviewers.md
Doxygen comment added after removing obsolete flags as requested.

@@
 This includes a description of the build procedure and a list of installed files.
-Compilation of user code with RadLib is outline.
+Compilation of user code with RadLib is outlined.
 A description of the interface functions is also provided.
@@
 Section 5 contained some discussion items as noted by the reviewer, but now includes simulation results for the examples along with a CFD demonstration.
-The discussion items noted by the reviewer have been modified and folded into the Conclusions section.
-    **
+The discussion items noted by the reviewer have been modified and folded into the Conclusions section.**
 
@@
 
-    **We have reworded this to "...but its design and C++, Python, and Fortran interfaces permit expansion to additional property models." We remove the word "modular" throughout the paper.
-We do believe that the library can be easily extended.
+    **We remove the word "modular" throughout the paper.
+We do believe that the library can be extended, and have noted this, with softer language, in the revision.
 The reviewer is correct that we do not provide explicit functionality, for, e.g., generic extension to other species.
 In some cases, like the PM model, such extension would be trivial within the existing code structure.
-In the RCSLW model, extension to other species would require provision of the species ALBDF, and then extension would be a straightforward extension of the code, but the code is not set up for arbitrary species in arbitrary order.
+In the RCSLW model, extension to other species would require provision of the species ALBDF (not trivial), and then extension would be a straightforward, but the code is not set up for arbitrary species in arbitrary order.
 The library is primarily targeted at combustion applications where CO2 and H2O are the primary radiative species.
-Future efforts may motivate further extension.
+Future efforts may motivate further extension.**
 
@@
 
-    **We have reworded the sentence to "For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost."**
+    **We have revised the wording in the introduction.**
 
@@
 
-		**Fixed section heading. Now correctly reads "Declaration of Competing Interests".**
+		**This has been corrected.**
 
@@
 **We believe this to be a stylistic preference.
+Here's a quote from the [doxygen website](https://www.doxygen.nl/manual/docblocks.html): "Unlike most other documentation systems, doxygen also allows you to put the documentation of members (including global functions) in front of the definition.
+This way the documentation can be placed in the source file instead of the header file.
+This keeps the header file compact, and allows the implementer of the members more direct access to the documentation." Furthermore, Doxygen is primarily used to build external documentation (html), so, from that perspective, it does not seem as important where the Doxygen comments are in the source code.
 The reviewer's argument makes more sense for libraries that are distributed without the source.
@@
 This has the benefit of not cluttering the header files.
-There certainly is precedence for this in online discussions.
-Here's a quote from the [doxygen website](https://www.doxygen.nl/manual/docblocks.html): "Unlike most other documentation systems, doxygen also allows you to put the documentation of members (including global functions) in front of the definition.
-This way the documentation can be placed in the source file instead of the header file.
-This keeps the header file compact, and allows the implementer of the members more direct access to the documentation." Furthermore, Doxygen is primarily used to build external documentation (html), so, from that perspective, it does not seem as important where the Doxygen comments are in the source code.**
+There certainly is some precedence for this in online discussions.**
 
@@
     **The API is pretty simple and consists of two functions.
-Extensive examples are provided, which are compared to LBL data, and which, as published here, are identical to the results of the published radiation models.**
-
-<!--
-	**The authors acknowledge the lack of tests associated with the library and note that basic test coverage is currently being developed.**
--->
+Extensive examples are provided, which are compared to LBL data, and which, as published here, are identical to the results of the published radiation models.
+That said, a branch of the code is being developed that includes tests.**
 
@@
 
-        **The original code has been updated and tested and this does not appear to be an issue.**
+        **The original code has been updated and tested and this is now corrected.**
 
@@
 
-    **This is true. The code is not presently set up to load HITEMP/HITRAN data. This is a good suggestion and we plan to extend the model to allow LBL simulations in the future.**
+    **This is true. The code is not presently set up to load HITEMP/HITRAN data. This is a good suggestion and we would like to extend the model to allow LBL simulations in the future.**
 
@@
 
-    **The implemented models are not opaque, they come from the literature.
+    **The implemented models described in the cited literature.
 The novelty of the presented library is not the development of the absorption models, but the implementation, validation, and documentation of a library for application.
-Using radlib to generate correlations for species using HITEMP/HITRAN is outside of the intended scope.
+Using RadLib to generate correlations for species using HITEMP/HITRAN is outside of the intended scope.
 We acknowledge that extra work is required to extend the models to additional species, or to extend the temperature ranges.
@@
 
-	**We note that major revisions have been made to the paper text to clarify points like these for readers who do not specialize in combustion processes or modeling and provide additional information about why these models were chosen for implementation in RadLib.**
+	**We note that major revisions have been made to the paper text to clarify points like these for readers who do not specialize in, e.g., combustion processes or modeling and provide additional information about why these models were chosen for implementation in RadLib.**
 
@@
 
-	**The build process has been updated so that documentation can be generated by the system target or manually by running the command ```doxygen``` in the docs folder.**
+	**The build process has been updated so that documentation can be generated by the system target or manually by running the command ```doxygen``` in the docs folder.
+We have removed obsolete flags, and also updated the source documentation to be consistent with function signatures.**
 
@@
 
-**The authors would like to thank the reviewer for their comments and suggestions.
+**The authors thank the reviewer for their comments and suggestions.
 It is true that the library presented does not develop new models, but implementing and providing those models is nontrivial, and we believe makes a good contribution that is within the scope of this software journal.**
@@
 
-	**This was a placeholder statement that should not have been included in the document. It has been removed.**
+	**This has been corrected.**
 
@@
 In combustion applications, the PM model is often used in situations that are optically thin.
-In such cases, the radiative losses are relatively low (often around 5% for laboratory jet flames), and use of the PM model provides sufficient accuracy given that errors are active at the 5% level of the overall radiative losses, so not severe.
+In such cases, the radiative losses are relatively low (often around 5% for laboratory jet flames), and use of the PM model may provide sufficient accuracy given that errors are active at the 5% level of the overall radiative losses, so not severe.
 When coupled with the optically thin assumption for RTE treatment, the radiative solve is relatively simple and inexpensive.**

### 2021-07-25 manuscript/manuscript.tex
DOL: removing commented lines from the manuscript
spelling

@@
 
-\title{RadLib: a radiative property model library for combustion CFD}
+\title{RadLib: a radiative property model library for CFD}
 
@@
 Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem.
-Combustion is one of the key radiative tranfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
+Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
 Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
@@
 Three models are fully implemented and validated.
-%All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.
 
@@
 At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients using the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
-These models were chosen for their relavance to practical radiative heat transfer simulations.
+These models were chosen for their relevance to practical radiative heat transfer simulations.
 They represent increasing levels of complexity, computational cost, and accuracy.
 Each model is discussed in more detail in the following sections.
-
-%Absorption coefficients and other radiative property data may take on different forms depending on the RTE solution approach, but can generally be classified as either spectral (wavenumber-dependent) or global (integrated over wavenumber).
-Spectral absorption coefficients can be applied to the spectral RTE (Eq.~\ref{e:RTE_general}), while global absorption coefficients are used in the spectrally-integrated RTE (Eq.~\ref{e:RTE_wsgg}).
-The type of absorption coefficient generated by each model and potential RTE integration strategies will also be discussed in the following sections.
-While solving the RTE is not the focus of this software, RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes.
-Refer to the example cases in Section \ref{s:Examples} for details.
 
@@
 At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.
-% todo: show the RTE equation/source term
-
-%Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}.
-The absorption coefficient correlations use fourth or fifth order polynomial fits in the range 300-2500 K.
-TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}.
-In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-
-%RadLib's simplest radiation property model generates Planck Mean absorption coefficients under the assumption of optically thin media, from here on referred to as the Planck Mean (PM) model.
-%The optically thin approximation assumes that there is little to no reabsorption of radiative energy in the system, or, in other words, that the system only emits radiation and does not absorb it.
-In combustion systems, optical thinness is associated with various other flame properties such as low radiative heat transfer relative to chemical heat release or convective heat transfer, negligible amounts of soot or other large molecules, and relatively small flame lengths.
-These flame attributes are not universally indicative of optical thinness, but are often used to justify neglecting or simplifying radiative heat transfer modeling.
-Assuming optical thinness, however, has the distinct advantage of simplifying the radiative source term (denoted $S_{rad}$) of the energy conservation equation to
-%\begin{equation}
-%	S_{rad}=-4\kappa \sigma T^4,
-%\end{equation}
-%where $\kappa$ is the radiation absorption coefficient, $\sigma$ is the Stefan-Boltzmann constant, and $T$ is temperature.
-Using an optically thin approximation means that no RTE solution is required when calculating radiative source terms.
-%
-%In combustion systems, this simplification is convenient because it makes radiation modeling easy to implement and computationally inexpensive.
-The vast majority of computational combustion research that considers radiation employs an optically thin approximation despite its limited applicability to combustion processes.
-Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flames or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}.
-%
-%The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
-These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its limitations.
-Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}.
-The absorption coefficient correlations use fourth or fifth order polynomial fits in the range 300-2500 K.
-TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}.
-In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-%
-%Because of these limitations, the authors strongly recommend that RadLib users carefully consider the implications of the PM model before using it in combustion simulations. 
-%It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its popularity and widespread use. 
-%The examples included with the RadLib code and shown in Section \ref{s:Examples} demonstrate the deficiencies of the PM model in comparison to other radiation property models included with RadLib.
 
@@
 The RCSLW model uses rank correlation as follows.
-Consider Eq.~\ref{e:albdf} evaluated at an arbitray reference temperature $T_r$ for thermodynamic states $\phi_1$ and $\phi_2$ as detailed above:
+Consider Eq.~\ref{e:albdf} evaluated at an arbitrary reference temperature $T_r$ for thermodynamic states $\phi_1$ and $\phi_2$ as detailed above:
 % $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
@@
 These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
-%, which coincides with the PM model's use of the optically thin approximation, but the high error in its predictions of radiative heat flux relative to the LBL data indicates that neither the optically thin approximation nor absorption coefficients calculated with this model are accurate for this case.
 Example S3 illustrates that the PM model tends to overpredict radiative heat loss at hight temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-%illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.
 
@@
 
-%The WSGG model gives somewhat accurate but inconsistent results for the example cases considered here.
-In Examples S1, S3, S5, B3, and Sb1, it behaves as expected, producing results that are closer to the LBL data than those produced by the PM model but fall short of the RCSLW model's level of accuracy.
-In general, the WSGG model appears to perform best at intermediate temperatures and deviates from the desired behavior at boundary conditions, but this is not universal.
-For example, the WSGG model shows uncharacteristically high accuracy in Example S2; its results with four gray gases are comparable in accuracy to the RCSLW model's performance using eight or more gray gases.
-In contrast, the WSGG model performs exceptionally poorly in Example S4, in which it deviates from the LBL data by nearly an order of magnitude at its largest.
-%The WSGG model, alongside with the PM model, is primarily empirical and contains little to no representative physics, which could explain the unexpected behavior in Examples S2 and S4.
-Given that all of the example cases use parameters within those specified for the WSGG model in the literature \cite{Bordbar_2014,Bordbar_2020}, neither anomalous result has an obvious source.
-While we cannot offer an explanation for the WSGG model's inconsistent performance, it serves to underscore the importance of individual model validation on a case-by-case basis, a task potentially made easier with tools like RadLib.
-
-%The RCSLW model displays the most accurate results of the three implemented property models when compared to LBL data, capturing the relevant trends without exaggerating them.
-It is, however, the most difficult of the three models to implement and requires either correlated or tabulated spectral data to draw from.
-%The RCSLW model can be sensitive to the number of gray gases used, illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
-The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
-Example S2 shows the most prominent variations in predicted radiative heat flux based on changes in the number of gray gases, improving drastically in agreement to the LBL data with the addition of just four gray gases.
-RCSLW model convergence can also vary with the value of the chosen reference temperature; in Example S5, for instance, the RCSLW model converges to the LBL data if it is initialized with the maximum rather than the average temperature on the domain.
-When treated properly, however, the RCSLW model provides the most accurate results of all of the radiation property models considered here.
-
 Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume fraction in addition to the radiating gas.
@@
 Soot reactions and transport are both sensitive to, and strongly influence local variations in, flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
-%The agreement produced by RadLib's approach to soot radiation in Example Sb1 is an encouraging step toward accurate, detailed treatment of soot's radiative properties in complex combustion simulations.
 
@@
 Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver.
-This is relavant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evalations alone.
+This is relevant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evaluations alone.
 This is consistent with the results of the figure and as follows.
 Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.
-%In running Example S3, the overall solution cost using different property models is shown to vary much less than when evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.
 
@@
 In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy at the expense of computational cost.
-%Under appropriate conditions, the WSGG model can also produce accurate results at significantly lower computational cost, but may perform inconsistently under certain conditions.
-In general, the PM model is adequate in situations to which the optically thin approximation can be reasonably applied, but does not produce accurate results in any of the example cases presented here.
 
@@
 By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations.
-%With RadLib, we believe that researchers will be able to put more of their time and effort into meaningful results rather than code or model development for radiative heat transfer in combustion CFD.
 

### 2021-07-25 submissions/revision_1/manuscript.tex
revision 1 submitted

--- 2021-07-25 manuscript/manuscript.tex
@@
 \usepackage{bm}
-\usepackage{seqsplit}
-\usepackage{enumitem}
+%doldb \usepackage{seqsplit}
+%doldb \usepackage{enumitem}
 
@@
 \newcommand{\BS}{\boldsymbol}
-\setlist[itemize]{noitemsep}%, topsep=0pt}
+%doldb\setlist[itemize]{noitemsep}%, topsep=0pt}
 
@@
 The C++ and Fortran libraries in the \texttt{lib} folder are
+%
 \begin{itemize}
@@
 If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable.
-A command to do this is provided at the end of the installation, for example, \texttt{\seqsplit{export\ PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.
+A command to do this is provided at the end of the installation.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\bibliographystyle{elsarticle-num} 
-\bibliography{references}
+%\bibliographystyle{elsarticle-num} 
+%\bibliography{references}
+
+\begin{thebibliography}{10}
+\expandafter\ifx\csname url\endcsname\relax
+  \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\expandafter\ifx\csname href\endcsname\relax
+  \def\href#1#2{#2} \def\path#1{#1}\fi
+
+\bibitem{Modest_2016}
+M.~F. Modest, D.~C. Haworth, {Radiative Heat Transfer In Turbulent Combustion
+  Systems: Theory and Applications}, {SpringerBriefs in Applied Sciences and
+  Technology}, Springer, 2016.
+
+\bibitem{Modest_2013}
+M.~F. Modest, {Radiative Heat Transfer}, third edition Edition, {Academic
+  Press}, New York, 2013.
+
+\bibitem{Rothman_2010}
+L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
+  V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
+  \href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{{HITEMP},
+  the high-temperature molecular spectroscopic database}}, {Journal of
+  Quantitative Spectroscopy {\&} Radiative Transfer} 111~(15) (2010)
+  2139--2150.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
+  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}
+
+\bibitem{Zhang_2002b}
+H.~Zhang, M.~F. Modest, {Evaluation of the Planck-mean absorption coefficients
+  from HITRAN and HITEMP databases}, {Journal of Quantitative Spectroscopy {\&}
+  Radiative Transfer} 73~(6) (2002) 649--653.
+\newblock \href {http://dx.doi.org/10.1016/S0022-4073(01)00178-9}
+  {\path{doi:10.1016/S0022-4073(01)00178-9}}.
+
+\bibitem{Hottel_1967}
+H.~C. Hottel, A.~F. Sarofim, {Radiative Transfer}, McGraw-Hill, 1967.
+
+\bibitem{Grosshandler_1993}
+W.~L. Grosshandler, {{RADCAL}: A Narrow-Band Model for Radiation Calculations
+  in a Combustion Environment: NIST technical note 1402}.
+
+\bibitem{TNF}
+{TNF Workshop Radiation Models}, \url{https://tnfworkshop.org/radiation/}
+  (2021).
+
+\bibitem{Smith_2003}
+N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
+  \href{https://tnfworkshop.org/radiation/}{{{TNF} Workshop Radiation Models}}
+  (2003).
+\newline\urlprefix\url{https://tnfworkshop.org/radiation/}
+
+\bibitem{Barlow_2001}
+R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, {Scalar profiles and
+  {NO} formation in laminar opposed-flow partially premixed methane/air
+  flames}, {Combustion and Flame} 127~(3) (2001) 2102--2118.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
+  {\path{doi:10.1016/S0010-2180(01)00313-3}}.
+
+\bibitem{Frank_2000}
+J.~H. Frank, R.~S. Barlow, C.~Lundquist, {Radiation and nitric oxide formation
+  in turbulent non-premixed jet flames}, {Proceedings of the Combustion
+  Institute} 28~(1) (2000) 447--454.
+\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
+  {\path{doi:10.1016/S0082-0784(00)80242-8}}.
+
+\bibitem{Zhu_2002}
+X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
+  \href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{{The
+  effects of self-absorption of radiation on an opposed flow partially premixed
+  flame}}, {Combustion and Flame} 129~(3) (2002) 342--345.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
+  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}
+
+\bibitem{Coelho_2002}
+P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, {Spectral Radiative Effects and
+  Turbulence-Radiation-Interaction in Sandia Flame {D}}, in: {Barlow, Robert
+  S., Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), {The
+  Proceedings of the Sixth International Workshop on Measurement and
+  Computation of Turbulent Nonpremixed Flames}, 2002.
+
+\bibitem{Barlow_1999}
+R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
+  \href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{{Nitric
+  oxide formation in dilute hydrogen jet flames: isolation of the effects of
+  radiation and turbulence-chemistry submodels}}, {Combustion and Flame}
+  117~(1-2) (1999) 4--31.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
+  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}
+
+\bibitem{Bordbar_2014}
+M.~H. Bordbar, G.~Wecel, T.~Hyppanen, {A line by line based weighted sum of
+  gray gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
+  combustion}, {Combustion and Flame} 161~(9) (2014) 2435--2445.
+\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
+  {\path{doi:10.1016/j.combustflame.2014.03.013}}.
+
+\bibitem{Bordbar_2020}
+H.~Bordbar, G.~C. Fraga, S.~Hostikka,
+  \href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{{An
+  extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
+  molar fraction ratios in thermal radiation}}, {International Communications
+  in Heat and Mass Transfer} 110 (2020) 104400.
+\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
+  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}
+
+\bibitem{Solovjov_2016}
+V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, {The Generalized {SLW}
+  Model}, {Journal of Physics: Conference Series} 676 (2016) 1--36.
+
+\bibitem{Solovjov_2017}
+V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, {The rank correlated
+  {SLW} model of gas radiation in non-uniform media}, {Journal of Quantitative
+  Spectroscopy {\&} Radiative Transfer} 197 (2017) 26--44.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
+  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.
+
+\bibitem{Badger_2019}
+J.~Badger, B.~W. Webb, V.~P. Solovjov, {An exploration of advanced {SLW}
+  modeling approaches in comprehensive combustion predictions}, {Combustion
+  Science and Technology} 012022~(676) (2019) 1--17.
+\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
+  {\path{doi:10.1080/00102202.2019.1678907}}.
+
+\bibitem{Coelho_2017}
+P.~J. Coelho,
+  \href{https://link-springer-com.erl.lib.byu.edu/referenceworkentry/10.1007/978-3-319-32003-8_61-1}{{Radiative
+  Transfer in Combustion Systems}}, in: F.~A. Kulacki (Ed.), {Handbook of
+  Thermal Science and Engineering}, {Springer International Publishing}, Cham,
+  2017, pp. 1--27.
+\newblock \href {http://dx.doi.org/10.1007/978-3-319-32003-8{\textunderscore
+  }61-1} {\path{doi:10.1007/978-3-319-32003-8{\textunderscore }61-1}}.
+\newline\urlprefix\url{https://link-springer-com.erl.lib.byu.edu/referenceworkentry/10.1007/978-3-319-32003-8_61-1}
+
+\bibitem{FDS}
+K.~McGrattan, R.~McDermott, C.~Weinschenk, G.~Forney, Fire dynamics simulator,
+  technical reference guide, sixth edition (2013-11-04 2013).
+\newblock \href {http://dx.doi.org/https://doi.org/10.6028/NIST.sp.1018}
+  {\path{doi:https://doi.org/10.6028/NIST.sp.1018}}.
+
+\bibitem{Solovjov_2001}
+V.~P. Solovjov, B.~W. Webb, {An Efficient Method for Modeling Radiative
+  Transfer in Multicomponent Gas Mixtures With Soot}, {Transactions of the
+  ASME} 123 (2001) 450--457.
+
+\bibitem{Solovjov_2001b}
+V.~P. Solovjov, B.~W. Webb, {An Efficient Method for Modeling Radiative
+  Transfer in Multicomponent Gas Mixtures With Soot}, {Journal of Heat
+  Transfer} 123~(3) (2001) 450--457.
+\newblock \href {http://dx.doi.org/10.1115/1.1350824}
+  {\path{doi:10.1115/1.1350824}}.
+
+\bibitem{Solovjov_2011}
+V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, {The {SLW}-1 model for efficient
+  prediction of radiative transfer in high temperature gases}, {Journal of
+  Quantitative Spectroscopy and Radiative Transfer} 112~(7) (2011) 1205--1212.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
+  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.
+
+\bibitem{Solovjov_2020}
+V.~P. Solovjov, B.~W. Webb, F.~Andr{\'e}, D.~Lemonnier, {Locally correlated
+  {SLW} model for prediction of gas radiation in non-uniform media and its
+  relationship to other global methods}, {Journal of Quantitative Spectroscopy
+  {\&} Radiative Transfer} 245 (2020) 106857.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2020.106857}
+  {\path{doi:10.1016/j.jqsrt.2020.106857}}.
+
+\bibitem{Solovjov_2000}
+V.~P. Solovjov, B.~W. Webb, {{SLW} modeling of radiative transfer in
+  multicomponent gas mixtures}, {Journal of Quantitative Spectroscopy and
+  Radiative Transfer} 65 (2000) 655--672.
+
+\bibitem{Solovjov_2008}
+V.~P. Solovjov, B.~W. Webb, {Multilayer modeling of radiative transfer by {SLW}
+  and {CW} methods in non-isothermal gaseous medium}, {Journal of Quantitative
+  Spectroscopy and Radiative Transfer} 109~(2) (2008) 245--257.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
+  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.
+
+\bibitem{Solovjov_2014}
+V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, {Extension of the exact {SLW} model
+  to non-isothermal gaseous media}, {Journal of Quantitative Spectroscopy and
+  Radiative Transfer} 143 (2014) 83--91.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
+  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.
+
+\bibitem{Webb_2018}
+B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, {An exploration of the influence of
+  spectral model parameters on the accuracy of the rank correlated SLW model},
+  {Journal of Quantitative Spectroscopy and Radiative Transfer} 218 (2018)
+  161--170.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
+  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.
+
+\bibitem{Pearson_2014}
+J.~T. Pearson, B.~W. Webb, V.~P. Solovjov, J.~Ma, {Efficient representation of
+  the absorption line blackbody distribution function for H2O, CO2, and CO at
+  variable temperature, mole fraction, and total pressure}, {Journal of
+  Quantitative Spectroscopy {\&} Radiative Transfer} 138 (2014) 82--96.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2014.01.019}
+  {\path{doi:10.1016/j.jqsrt.2014.01.019}}.
+
+\bibitem{Solovjov_2014b}
+V.~P. Solovjov, J.~T. Pearson, \href{https://albdf.byu.edu/}{{ALBDF: Absorption
+  Line Blackbody Distribution Function}} (2014).
+\newline\urlprefix\url{https://albdf.byu.edu/}
+
+\bibitem{Brewster_1992}
+M.~Q. Brewster, {Thermal Radiative Transfer and Properties}, 1992.
+
+\bibitem{Lee_1981}
+S.~C. Lee, C.~L. Tien, {Optical constants of soot in hydrocarbon flames},
+  {Symposium (International) on Combustion} 18~(1) (1981) 1159--1166.
+\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
+  {\path{doi:10.1016/S0082-0784(81)80120-8}}.
+
+\bibitem{Stull_1960}
+V.~R. Stull, G.~N. Plass, {Emissivity of Dispersed Carbon Particles}, {Journal
+  of the Optical Society of America} 50~(2) (1960) 121.
+\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
+  {\path{doi:10.1364/JOSA.50.000121}}.
+
+\bibitem{Dalzell_1969}
+W.~H. Dalzell, A.~F. Sarofim, {Optical Constants of Soot and Their Application
+  to Heat-Flux Calculations}, {Journal of Heat Transfer} 91~(1) (1969)
+  100--104.
+\newblock \href {http://dx.doi.org/10.1115/1.3580063}
+  {\path{doi:10.1115/1.3580063}}.
+
+\bibitem{Howarth_1966}
+C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), {The Effect of Temperature on
+  the Extinction of Radiation By Soot Particles}, Begellhouse, 1966.
+\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
+  {\path{doi:10.1615/IHTC3.1210}}.
+
+\bibitem{Chang_1990}
+H.-c. Chang, T.~T. Charalampopoulos, {Determination of the wavelength
+  dependence of refractive indices of flame soot}, {Proceedings of the Royal
+  Society of London. Series A: Mathematical and Physical Sciences} 430~(1880)
+  (1990) 577--591.
+\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
+  {\path{doi:10.1098/rspa.1990.0107}}.
+
+\bibitem{Felske_1984}
+J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, {Determination of the
+  Refractive Indices of Soot Particles from the Reflectivities of Compressed
+  Soot Pellets}, {Combustion Science and Technology} 37~(5-6) (1984) 263--283.
+\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
+  {\path{doi:10.1080/00102208408923757}}.
+
+\bibitem{Williams_2007}
+T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, {Measurement of
+  the dimensionless extinction coefficient of soot within laminar diffusion
+  flames}, {International Journal of Heat and Mass Transfer} 50~(7-8) (2007)
+  1616--1630.
+\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
+  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.
+
+\bibitem{Felske_1977}
+J.~D. Felske, C.~L. Tien, {The Use of the Milne-Eddington Absorption
+  Coefficient for Radiative Heat Transfer in Combustion Systems}, {Journal of
+  Heat Transfer} 99~(3) (1977) 458--465.
+\newblock \href {http://dx.doi.org/10.1115/1.3450718}
+  {\path{doi:10.1115/1.3450718}}.
+
+\bibitem{Bordbar_personal}
+H.~Bordbar, {personal communication RE: WSGG model implementation}.
+
+\bibitem{Chang_1984}
+S.~L. Chang, K.~T. Rhee, {Blackbody radiation functions}, {International
+  Communications in Heat and Mass Transfer} 11~(5) (1984) 451--455.
+\newblock \href {http://dx.doi.org/10.1016/0735-1933(84)90051-4}
+  {\path{doi:10.1016/0735-1933(84)90051-4}}.
+
+\end{thebibliography}
 

### 2021-09-08 manuscript/manuscript.tex
revision 1 submitted
Second round of revisions in response to reviewer comments.

@@
 \usepackage{bm}
-\usepackage{seqsplit}
-\usepackage{enumitem}
+%\usepackage{seqsplit}
+%\usepackage{enumitem}
 
@@
 \newcommand{\BS}{\boldsymbol}
-\setlist[itemize]{noitemsep}%, topsep=0pt}
+%\setlist[itemize]{noitemsep}%, topsep=0pt}
 
@@
     \begin{linenomath}
-\begin{equation} \label{e:RTE_general}
+        \begin{equation}
+            \label{e:RTE_general}
             \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
@@
 %
-where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
+    where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity
+    (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
+    along direction $\mathbf{s}$.
     Solving the RTE requires information about the radiative properties of the materials and media in the system.
-Radiative property data typically takes the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model.
-Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, and depends on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
-Radiation property models, including those implemented in RadLib, are typically developed using high-resolution spectral databases like HITRAN and HITEMP \cite{Rothman_2010} in order to calculate spectral absorption coefficients, thus reducing or simplifying the huge amount of spectral data by using correlations and modeling assumptions \citep{Zhang_2002b}.
-
-The direct solution of the spectral RTE using so-called line-by-line calculations in which the RTE is solved for each individual spectral line is computationally prohibitive for most practical configurations and is used primarily for model validation.
-Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
-%VBS: citation here?
-Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these cant lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.
+    Radiative property data typically takes the form of radiation absorption
+    coefficients $\kappa$, which are provided by a radiation property model.
+    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, and depends
+    on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
+    Radiation property models typically consist of correlations between radiative properties and high-resolution
+    spectral databases, reducing the huge amount of spectral data and
+    simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.
+
+    The direct solution of the spectral RTE using so-called line-by-line calculations in which the RTE is solved for each
+    individual spectral line is computationally prohibitive for most practical configurations and is used primarily for model
+    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
+    incorporated into the RTE.
+
+    Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
+    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
+    RTE evaluations \citep{Modest_2016}.
 
@@
     \begin{linenomath}
-\begin{equation} \label{e:RTE_wsgg}
+        \begin{equation}
+            \label{e:RTE_wsgg}
             \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
@@
 %
-Global models are especially attractive in computational heat transfer applications because they can provide good accuracy while limiting computational costs.
-
-With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications.
-RadLib is a C++ library with optional Python and Fortran interfaces.
-RadLib calculates radiation absorption coefficients and weighting factors for use in global radiation models.
-Expansion to other radiative properties and model types is possible.
-Three models are fully implemented and validated.
+    Global models are especially attractive in computational heat transfer applications because they can provide good accuracy
+    while limiting computational costs.
+
+    With RadLib, we aim to provide researchers with a convenient access point for radiative property models that
+    can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a C++ library with optional
+    Python and Fortran interfaces. RadLib calculates radiation absorption coefficients and weighting factors for use in global
+    radiation models. Expansion to other radiative properties and model types is possible. Three models are fully implemented
+    and validated.
 
@@
 
-At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients using the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
+    At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption
+    coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG)
+    model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
 These models were chosen for their relevance to practical radiative heat transfer simulations.
@@
 
+    Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
+    which they apply.
+
+    \begin{table}
+        \caption{Summary of radiative property models in RadLib.}
+        \label{t:models}
+        \centering
+        \resizebox{\textwidth}{!}{
+            \begin{tabular}{l l l l}
+                \hline
+                Model & T range (K) & P range (atm) & Refs.   \\
+                \hline
+                PM      & 300\textendash 2500 & 1                   & \cite{TNF} \\
+                WSGG    & 300\textendash 2400 & 1                   & \cite{Bordbar_2020,Bordbar_2014} \\
+                RCSLW   & 300\textendash 3000 & 0.1\textendash 50   &  \cite{Solovjov_2017} \\
+                \hline
+            \end{tabular}
+        }
+    \end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The Planck Mean (PM) model is the simplest of the three models implemented.
-This model assumes a single gray gas and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
+    The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas
+    (with no transparent gas)
+    and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
 
@@
 
-For each species, the PM model provides the absorption coefficient as fourth or fifth order polynomial fits in one or two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
-See \cite{TNF} for details and references.
-The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
-The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream.
-(\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
+    For each species, the PM model provides the absorption coefficient as fourth or fifth order polynomial fits in one
+    or two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
+    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
+    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
+    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
+    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
+    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
 
@@
     \begin{linenomath}
-    \begin{equation} \label{e:albdf}
+        \begin{equation}
+            \label{e:albdf}
             F(C,\BS{\phi},T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi})<C\}}E_b(\eta,T)d\eta,
@@
     \begin{linenomath}
-    \begin{equation}\label{e:aj}
+        \begin{equation}
+            \label{e:aj}
             a_j = F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1}, \BS{\phi},T).
@@
     \begin{linenomath}
-	\begin{equation} \label{e:multiC}
+        \begin{equation}
+            \label{e:multiC}
             C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
@@
     \begin{linenomath}
-\begin{equation} \label{e:multiF}
+        \begin{equation}
+            \label{e:multiF}
             F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right).
@@
     \begin{linenomath}
-    \begin{align} \label{e:albdf2}
+        \begin{align}
+            \label{e:albdf2}
             F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
@@
     \begin{linenomath}
-    \begin{equation}\label{e:FeqF}
+        \begin{equation}
+            \label{e:FeqF}
             F(\hat{C}_1,\BS{\phi}_1,T_r)=F(\hat{C}_2,\BS{\phi}_2,T_r).
@@
                 \hline
-        Example & T(K)                          & $x_{H2O}$  $x_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.\\
+                Example & T(K)                             & $x_{H2O}$  $x_{CO2}$ (mole frac.)               & L (m)   & $T_{walls}$ (K) & Ref.                 \\
                 \hline
-        S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$    & $x_{CO2}=0.1$, $x_{H2O}=0.2$                    & 0.5-2.5 & cold, cold	& \cite{Solovjov_2017}     \\
+                S1 & $T(x<0.5)=2000$; $T(x>0.5)=300$ & $x_{CO2}=0.1$, $x_{H2O}=0.2$ & 0.5-2.5 & cold, cold
+                & \cite{Solovjov_2017}
+                \\
                 S2      & T=1000                           & $x_{CO2}(x<0.5)=0.4$, $x_{CO2}(x>0.5)=0.1$    & 0.5-2.5 & cold, cold      & \cite{Solovjov_2017} \\
@@
                 S5      & $T(x) = 1000 + 500\cos(\pi x/L)$ & $x_{H2O}=0.1$, $x_{CO2}=0$                    & 2       & 1500, 500       & \cite{Solovjov_2017} \\
-        B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $x_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$	& 1       & 400, 400 & \cite{Bordbar_2020}      \\
+                B3 & $T(x) = 400 + 1400\sin(\pi x/L)^2$ & $x_{H2O}(x) = 0.0001 + 0.9999\sin(\pi x/L)^2$
+                & 1
+                & 400, 400
+                & \cite{Bordbar_2020}
+                \\
                 & & $x_{CO2}=1-x_{H2O}$ & & \\
-        Sb1& $T = 1000$                         & $x_{H2O} = 0.2$, $x_{CO2}=0.1$, $x_{CO}=0.03$   	& 1       & cold, cold & \cite{Solovjov_2001}    \\
+                Sb1     & $T = 1000$                       & $x_{H2O} = 0.2$, $x_{CO2}=0.1$, $x_{CO}=0.03$ & 1       & cold, cold      & \cite{Solovjov_2001} \\
                 \hline
@@
             \end{tabular}
-    \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}.}
+            \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}. In Examples S2 and S5, $n$
+                refers to the number of gray gases considered.}
             \label{f:examples}
@@
     In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity.
-The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36~m in the thick and thin layers, respectively.
+The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36 in the thick and thin layers, respectively.
 These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
@@
 
-The RadLib model was coupled to the Fire Dynamics Simulator (FDS) code developed at NIST \cite{FDS}.
-FDS is written in Fortran, and the Fortran interface of Radlib was used for simulations.
-FDS includes several radiative models, but the spectral WSGG model coupled to a finite volume discrete ordinates model is used here.
-This was done by editing the \texttt{radi.f90} file.
-A \texttt{use rad\textunderscore module} statement is included and the functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} were replaced with calls to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}.
-The \texttt{oneband} version was used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.
+    The RadLib model was coupled to the Fire Dynamics Simulator (FDS) code developed at NIST \cite{FDS}. FDS is
+    written in Fortran, and the Fortran interface of Radlib was used for simulations. FDS includes several radiative
+    models, but the spectral WSGG model coupled to a finite volume discrete ordinates model is used here. This was
+    done by editing the \texttt{radi.f90} file in FDS. A \texttt{use rad\textunderscore module} statement is included
+    and the FDS functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} are replaced with calls
+    to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}. The \texttt{oneband} version was
+    used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.
 
@@
 Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib (both using four gray gases and one clear gas).
-The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL. Further details are provided in the FDS user guide \cite{FDS}. 
+    The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL.
+Further details are provided in the FDS user guide \cite{FDS}.
     Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions.
@@
             \begin{tabular}{c c}
-        (a) & (b) \\
+            (a)
+                & (b) \\
                 \includegraphics[width=2.5 in]{fig_fds_T_mean.pdf} &
@@
             \begin{tabular}{c c}
-        (a) & (b) \\
+            (a)
+                & (b) \\
                 \includegraphics[width=2.5 in]{fig_getka_c++.pdf} &
@@
     RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations.
-At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients using the optically thin approximation, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
+At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
 Each of the implemented models has been validated and the library's structure and functionality has been outlined.
@@
 
-\bibliographystyle{elsarticle-num} 
-\bibliography{references}
+%\bibliographystyle{elsarticle-num}
+%\bibliography{references}
+
+    \begin{thebibliography}{10}
+        \expandafter\ifx\csname url\endcsname\relax
+        \def\url#1{\texttt{#1}}\fi
+\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+\expandafter\ifx\csname href\endcsname\relax
+\def\href#1#2{#2} \def\path#1{#1}\fi
+
+\bibitem{Modest_2016}
+M.~F. Modest, D.~C. Haworth, {Radiative Heat Transfer In Turbulent Combustion
+Systems: Theory and Applications}, {SpringerBriefs in Applied Sciences and
+Technology}, Springer, 2016.
+
+\bibitem{Modest_2013}
+M.~F. Modest, {Radiative Heat Transfer}, third edition Edition, {Academic
+Press}, New York, 2013.
+
+\bibitem{Rothman_2010}
+L.~S. Rothman, I.~E. Gordon, R.~J. Barber, H.~Dothe, R.~R. Gamache, A.~Goldman,
+V.~I. Perevalov, S.~A. Tashkun, J.~Tennyson,
+\href{http://www.sciencedirect.com/science/article/pii/S002240731000169X}{{{HITEMP},
+the high-temperature molecular spectroscopic database}}, {Journal of
+Quantitative Spectroscopy {\&} Radiative Transfer} 111~(15) (2010)
+2139--2150.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.05.001}
+  {\path{doi:10.1016/j.jqsrt.2010.05.001}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S002240731000169X}
+
+\bibitem{Zhang_2002b}
+H.~Zhang, M.~F. Modest, {Evaluation of the Planck-mean absorption coefficients
+from HITRAN and HITEMP databases}, {Journal of Quantitative Spectroscopy {\&}
+Radiative Transfer} 73~(6) (2002) 649--653.
+\newblock \href {http://dx.doi.org/10.1016/S0022-4073(01)00178-9}
+  {\path{doi:10.1016/S0022-4073(01)00178-9}}.
+
+\bibitem{Hottel_1967}
+H.~C. Hottel, A.~F. Sarofim, {Radiative Transfer}, McGraw-Hill, 1967.
+
+\bibitem{Grosshandler_1993}
+W.~L. Grosshandler, {{RADCAL}: A Narrow-Band Model for Radiation Calculations
+in a Combustion Environment: NIST technical note 1402}.
+
+\bibitem{TNF}
+{TNF Workshop Radiation Models}, \url{https://tnfworkshop.org/radiation/}
+(2021).
+
+\bibitem{Smith_2003}
+N.~Smith, J.~Gore, J.~Kim, Q.~Tang,
+\href{https://tnfworkshop.org/radiation/}{{{TNF} Workshop Radiation Models}}
+(2003).
+\newline\urlprefix\url{https://tnfworkshop.org/radiation/}
+
+\bibitem{Barlow_2001}
+R.~S. Barlow, A.~N. Karpetis, J.~H. Frank, J.-Y. Chen, {Scalar profiles and
+{NO} formation in laminar opposed-flow partially premixed methane/air
+flames}, {Combustion and Flame} 127~(3) (2001) 2102--2118.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(01)00313-3}
+  {\path{doi:10.1016/S0010-2180(01)00313-3}}.
+
+\bibitem{Frank_2000}
+J.~H. Frank, R.~S. Barlow, C.~Lundquist, {Radiation and nitric oxide formation
+in turbulent non-premixed jet flames}, {Proceedings of the Combustion
+Institute} 28~(1) (2000) 447--454.
+\newblock \href {http://dx.doi.org/10.1016/S0082-0784(00)80242-8}
+  {\path{doi:10.1016/S0082-0784(00)80242-8}}.
+
+\bibitem{Zhu_2002}
+X.~Zhu, J.~Gore, A.~N. Karpetis, R.~S. Barlow,
+\href{http://www.sciencedirect.com/science/article/pii/S0010218002003413}{{The
+effects of self-absorption of radiation on an opposed flow partially premixed
+flame}}, {Combustion and Flame} 129~(3) (2002) 342--345.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(02)00341-3}
+  {\path{doi:10.1016/S0010-2180(02)00341-3}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218002003413}
+
+\bibitem{Coelho_2002}
+P.~J. Coelho, O.~J. Teerling, D.~Roekaerts, {Spectral Radiative Effects and
+Turbulence-Radiation-Interaction in Sandia Flame {D}}, in: {Barlow, Robert
+S., Pope, Stephan B., Masri, Assaad R., Oefelein, Joseph C.} (Ed.), {The
+Proceedings of the Sixth International Workshop on Measurement and
+Computation of Turbulent Nonpremixed Flames}, 2002.
+
+\bibitem{Barlow_1999}
+R.~Barlow, N.~Smith, J.~Chen, R.~Bilger,
+\href{http://www.sciencedirect.com/science/article/pii/S0010218098000716}{{Nitric
+oxide formation in dilute hydrogen jet flames: isolation of the effects of
+radiation and turbulence-chemistry submodels}}, {Combustion and Flame}
+117~(1-2) (1999) 4--31.
+\newblock \href {http://dx.doi.org/10.1016/S0010-2180(98)00071-6}
+  {\path{doi:10.1016/S0010-2180(98)00071-6}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0010218098000716}
+
+\bibitem{Bordbar_2014}
+M.~H. Bordbar, G.~Wecel, T.~Hyppanen, {A line by line based weighted sum of
+gray gases model for inhomogeneous {CO$_2$–H$_2$O} mixture in oxy-fired
+combustion}, {Combustion and Flame} 161~(9) (2014) 2435--2445.
+\newblock \href {http://dx.doi.org/10.1016/j.combustflame.2014.03.013}
+  {\path{doi:10.1016/j.combustflame.2014.03.013}}.
+
+\bibitem{Bordbar_2020}
+H.~Bordbar, G.~C. Fraga, S.~Hostikka,
+\href{http://www.sciencedirect.com/science/article/pii/S0735193319302660}{{An
+extended weighted-sum-of-gray-gases model to account for all {CO$_2$-H$_2$O}
+molar fraction ratios in thermal radiation}}, {International Communications
+in Heat and Mass Transfer} 110 (2020) 104400.
+\newblock \href {http://dx.doi.org/10.1016/j.icheatmasstransfer.2019.104400}
+  {\path{doi:10.1016/j.icheatmasstransfer.2019.104400}}.
+\newline\urlprefix\url{http://www.sciencedirect.com/science/article/pii/S0735193319302660}
+
+\bibitem{Solovjov_2016}
+V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, {The Generalized {SLW}
+Model}, {Journal of Physics: Conference Series} 676 (2016) 1--36.
+
+\bibitem{Solovjov_2017}
+V.~P. Solovjov, F.~Andr{\'e}, D.~Lemonnier, B.~W. Webb, {The rank correlated
+{SLW} model of gas radiation in non-uniform media}, {Journal of Quantitative
+Spectroscopy {\&} Radiative Transfer} 197 (2017) 26--44.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2017.01.034}
+  {\path{doi:10.1016/j.jqsrt.2017.01.034}}.
+
+\bibitem{Badger_2019}
+J.~Badger, B.~W. Webb, V.~P. Solovjov, {An exploration of advanced {SLW}
+modeling approaches in comprehensive combustion predictions}, {Combustion
+Science and Technology} 012022~(676) (2019) 1--17.
+\newblock \href {http://dx.doi.org/10.1080/00102202.2019.1678907}
+  {\path{doi:10.1080/00102202.2019.1678907}}.
+
+\bibitem{Coelho_2017}
+P.~J. Coelho,
+\href{https://link-springer-com.erl.lib.byu.edu/referenceworkentry/10.1007/978-3-319-32003-8_61-1}{{Radiative
+Transfer in Combustion Systems}}, in: F.~A. Kulacki (Ed.), {Handbook of
+Thermal Science and Engineering}, {Springer International Publishing}, Cham,
+2017, pp. 1--27.
+\newblock \href {http://dx.doi.org/10.1007/978-3-319-32003-8{\textunderscore
+  }61-1} {\path{doi:10.1007/978-3-319-32003-8{\textunderscore }61-1}}.
+\newline\urlprefix\url{https://link-springer-com.erl.lib.byu.edu/referenceworkentry/10.1007/978-3-319-32003-8_61-1}
+
+\bibitem{FDS}
+K.~McGrattan, R.~McDermott, C.~Weinschenk, G.~Forney, Fire dynamics simulator,
+technical reference guide, sixth edition (2013-11-04 2013).
+\newblock \href {http://dx.doi.org/https://doi.org/10.6028/NIST.sp.1018}
+  {\path{doi:https://doi.org/10.6028/NIST.sp.1018}}.
+
+\bibitem{Solovjov_2001}
+V.~P. Solovjov, B.~W. Webb, {An Efficient Method for Modeling Radiative
+Transfer in Multicomponent Gas Mixtures With Soot}, {Transactions of the
+ASME} 123 (2001) 450--457.
+
+\bibitem{Solovjov_2001b}
+V.~P. Solovjov, B.~W. Webb, {An Efficient Method for Modeling Radiative
+Transfer in Multicomponent Gas Mixtures With Soot}, {Journal of Heat
+Transfer} 123~(3) (2001) 450--457.
+\newblock \href {http://dx.doi.org/10.1115/1.1350824}
+  {\path{doi:10.1115/1.1350824}}.
+
+\bibitem{Solovjov_2011}
+V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, {The {SLW}-1 model for efficient
+prediction of radiative transfer in high temperature gases}, {Journal of
+Quantitative Spectroscopy and Radiative Transfer} 112~(7) (2011) 1205--1212.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2010.08.009}
+  {\path{doi:10.1016/j.jqsrt.2010.08.009}}.
+
+\bibitem{Solovjov_2020}
+V.~P. Solovjov, B.~W. Webb, F.~Andr{\'e}, D.~Lemonnier, {Locally correlated
+{SLW} model for prediction of gas radiation in non-uniform media and its
+relationship to other global methods}, {Journal of Quantitative Spectroscopy
+{\&} Radiative Transfer} 245 (2020) 106857.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2020.106857}
+  {\path{doi:10.1016/j.jqsrt.2020.106857}}.
+
+\bibitem{Solovjov_2000}
+V.~P. Solovjov, B.~W. Webb, {{SLW} modeling of radiative transfer in
+multicomponent gas mixtures}, {Journal of Quantitative Spectroscopy and
+Radiative Transfer} 65 (2000) 655--672.
+
+\bibitem{Solovjov_2008}
+V.~P. Solovjov, B.~W. Webb, {Multilayer modeling of radiative transfer by {SLW}
+and {CW} methods in non-isothermal gaseous medium}, {Journal of Quantitative
+Spectroscopy and Radiative Transfer} 109~(2) (2008) 245--257.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2007.08.015}
+  {\path{doi:10.1016/j.jqsrt.2007.08.015}}.
+
+\bibitem{Solovjov_2014}
+V.~P. Solovjov, D.~Lemonnier, B.~W. Webb, {Extension of the exact {SLW} model
+to non-isothermal gaseous media}, {Journal of Quantitative Spectroscopy and
+Radiative Transfer} 143 (2014) 83--91.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2013.10.008}
+  {\path{doi:10.1016/j.jqsrt.2013.10.008}}.
+
+\bibitem{Webb_2018}
+B.~W. Webb, V.~P. Solovjov, F.~Andr{\'e}, {An exploration of the influence of
+spectral model parameters on the accuracy of the rank correlated SLW model},
+{Journal of Quantitative Spectroscopy and Radiative Transfer} 218 (2018)
+161--170.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2018.06.023}
+  {\path{doi:10.1016/j.jqsrt.2018.06.023}}.
+
+\bibitem{Pearson_2014}
+J.~T. Pearson, B.~W. Webb, V.~P. Solovjov, J.~Ma, {Efficient representation of
+the absorption line blackbody distribution function for H2O, CO2, and CO at
+variable temperature, mole fraction, and total pressure}, {Journal of
+Quantitative Spectroscopy {\&} Radiative Transfer} 138 (2014) 82--96.
+\newblock \href {http://dx.doi.org/10.1016/j.jqsrt.2014.01.019}
+  {\path{doi:10.1016/j.jqsrt.2014.01.019}}.
+
+\bibitem{Solovjov_2014b}
+V.~P. Solovjov, J.~T. Pearson, \href{https://albdf.byu.edu/}{{ALBDF: Absorption
+Line Blackbody Distribution Function}} (2014).
+\newline\urlprefix\url{https://albdf.byu.edu/}
+
+\bibitem{Brewster_1992}
+M.~Q. Brewster, {Thermal Radiative Transfer and Properties}, 1992.
+
+\bibitem{Lee_1981}
+S.~C. Lee, C.~L. Tien, {Optical constants of soot in hydrocarbon flames},
+{Symposium (International) on Combustion} 18~(1) (1981) 1159--1166.
+\newblock \href {http://dx.doi.org/10.1016/S0082-0784(81)80120-8}
+  {\path{doi:10.1016/S0082-0784(81)80120-8}}.
+
+\bibitem{Stull_1960}
+V.~R. Stull, G.~N. Plass, {Emissivity of Dispersed Carbon Particles}, {Journal
+of the Optical Society of America} 50~(2) (1960) 121.
+\newblock \href {http://dx.doi.org/10.1364/JOSA.50.000121}
+  {\path{doi:10.1364/JOSA.50.000121}}.
+
+\bibitem{Dalzell_1969}
+W.~H. Dalzell, A.~F. Sarofim, {Optical Constants of Soot and Their Application
+to Heat-Flux Calculations}, {Journal of Heat Transfer} 91~(1) (1969)
+100--104.
+\newblock \href {http://dx.doi.org/10.1115/1.3580063}
+  {\path{doi:10.1115/1.3580063}}.
+
+\bibitem{Howarth_1966}
+C.~R. Howarth, P.~J. Foster, M.~W. Thring (Eds.), {The Effect of Temperature on
+the Extinction of Radiation By Soot Particles}, Begellhouse, 1966.
+\newblock \href {http://dx.doi.org/10.1615/IHTC3.1210}
+  {\path{doi:10.1615/IHTC3.1210}}.
+
+\bibitem{Chang_1990}
+H.-c. Chang, T.~T. Charalampopoulos, {Determination of the wavelength
+dependence of refractive indices of flame soot}, {Proceedings of the Royal
+Society of London. Series A: Mathematical and Physical Sciences} 430~(1880)
+(1990) 577--591.
+\newblock \href {http://dx.doi.org/10.1098/rspa.1990.0107}
+  {\path{doi:10.1098/rspa.1990.0107}}.
+
+\bibitem{Felske_1984}
+J.~D. Felske, T.~T. Charalampopoulos, H.~S. Hura, {Determination of the
+Refractive Indices of Soot Particles from the Reflectivities of Compressed
+Soot Pellets}, {Combustion Science and Technology} 37~(5-6) (1984) 263--283.
+\newblock \href {http://dx.doi.org/10.1080/00102208408923757}
+  {\path{doi:10.1080/00102208408923757}}.
+
+\bibitem{Williams_2007}
+T.~C. Williams, C.~R. Shaddix, K.~A. Jensen, J.~M. Suo-Anttila, {Measurement of
+the dimensionless extinction coefficient of soot within laminar diffusion
+flames}, {International Journal of Heat and Mass Transfer} 50~(7-8) (2007)
+1616--1630.
+\newblock \href {http://dx.doi.org/10.1016/j.ijheatmasstransfer.2006.08.024}
+  {\path{doi:10.1016/j.ijheatmasstransfer.2006.08.024}}.
+
+\bibitem{Felske_1977}
+J.~D. Felske, C.~L. Tien, {The Use of the Milne-Eddington Absorption
+Coefficient for Radiative Heat Transfer in Combustion Systems}, {Journal of
+Heat Transfer} 99~(3) (1977) 458--465.
+\newblock \href {http://dx.doi.org/10.1115/1.3450718}
+  {\path{doi:10.1115/1.3450718}}.
+
+\bibitem{Bordbar_personal}
+H.~Bordbar, {personal communication RE: WSGG model implementation}.
+
+\bibitem{Chang_1984}
+S.~L. Chang, K.~T. Rhee, {Blackbody radiation functions}, {International
+Communications in Heat and Mass Transfer} 11~(5) (1984) 451--455.
+\newblock \href {http://dx.doi.org/10.1016/0735-1933(84)90051-4}
+  {\path{doi:10.1016/0735-1933(84)90051-4}}.
+
+\end{thebibliography}
 

### 2021-09-09 manuscript/manuscript.tex
DOL: responses to reviewers, second revision

--- 2021-07-25 manuscript/manuscript.tex
@@
     \end{tabular}
-    \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}.}
+    \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}.
+In Examples S2 and S5, ``RCSLW n=1'', or ``n=2'', etc.
+refer to the number of gray gases considered in the RCSLW model.
+}
     \label{f:examples}

### 2021-09-09 submissions/CPC_response_to_reviewers_revision2.md

# Response to Reviewers: CPC initial submission

Note, reviewer comments are included with responses in **bold** text.

## Reviewer 2

The authors have adequately addressed the reviewer's concern and significantly improved the quality of the manuscript
and the software. The reviewer recommends acceptance for publication.

**The authors thank the reviewer for their time and contributions.**

-------------------------------------

## Reviewer 3

The authors have responded to this reviewer's comments and have revised the manuscript substantially. There are still a
few issues that need to be resolved before it is accepted for publication.

**The authors thank the reviewer for their time and contributions.**

1) The capabilities and limitations of RadLib should be more clearly articulated. For example, different property models
   have different temperature ranges of applicability. While the authors specified what happens if the simulation
   temperature goes beyond the appropriate temperature range, they should comment or provide some recommendations on the
   appropriateness of the choice of the property model. For example, WSGG model has a valid temperature range of
   300-2400 K, and RadLib caps the absorption coefficient values at the respective bound if the simulation temperature
   is beyond this range. Can the authors provide some guidance on what is the error expected from such a strategy of
   allowing simulation to continue at ranges beyond the valid range of the property model? If the user knows that the
   simulation temperature is beyond 2400 K, is it recommended to use WSGG? Also, what is the applicable range of
   pressure in the models implemented? Related to this, on repeated readings, this reviewer felt a table to list the
   range of applicability for each model may be useful for understanding the capabilities of RadLib at-a-glance for an
   user.

   **Valid temperature ranges for the WSGG and RCSLW models were noted in their respective sections, and the applicable
   temperature range for the PM model has been added to its section. Additionally, the RCSLW model section specifies the
   range of pressures under which the RCSLW model can be applied. A table summarizing these conditions has been added to
   the beginning of Section 2.**

2) Please rephrase and, if possible, simplify the sentence on lines 82-86 ("Radiation property models, including those
   implemented in RadLib, are typically developed using ... correlations and modeling assumptions [4].") It is difficult
   to understand what exactly the authors are trying to convey in this sentence.

   **Sentence has been revised for clarity.**

3) Line 92 - 95: "Modern band models .. cant lose accuracy when applied to nonhomogeneous media and may still require
   large numbers of RTE evaluations [1]." Should this be "<can> lose accuracy when applied …"?

   **Yes, it should. Typo has been fixed.**

4) In Figure 2, Example S5: Do "n=2" "n=4", etc mean the number of bands in RCSLW? It needs to be clarified.
   Furthermore, can the authors comment on the physical significance of RCSLW n =1 and how is this different from PM
   which uses a spectral average value?

   **The figure's caption has been updated to clarify this. The main difference between the PM model and RCSLW (or WSGG) with n=1 
is that the RCSLW model always considers one transparent gas (representing gaps in the absorption spectrum) in addition 
to some number of gray gases, whereas the PM model uses an average over the entire spectrum, gaps included. The "clear gas" 
concept is discussed on page 4 during the derivation of the gray gas spectral RTE (Eq. 5), but the PM model description 
did not indicate its deviation from this and has been revised to clarify that it does not consider a transparent gas in 
addition to its single gray gas.**

5) In Figure 2: This is a kind of cosmetic request, but still if the legends and symbols can be made consistent it will
   be easier to read.

6) In lines 499-501: Please clarify the sentence, "The PM absorption coefficient is 27.4 atm−1 m−1 , which results in a
   calculated optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively." Optical thickness is a
   dimensionless quantity, it cannot be 0.36 m. The thicknesses of layers are changing in S2, so what do these 0.09 and
   0.36 refer to?

   **Those numbers are intended to be optical thicknesses and should not have units. This has been fixed. The layer thicknesses in 
Example S2 are physical lengths, as indicated.**

7) In Section 5.1, please clarify which files and functions belong to FDS and which to RadLib. For example, in line
   544, "This was done by editing the radi.f90 file." By looking at the f90 extension the readers can guess that
   radi.f90 is part of FDS and not RadLib. But then in the next sentence, there are references to A_WSGG and KAPPA_WSGG
   functions. Are these part of FDS?

   **Sentence has been revised to clarify which files and functions belong to FDS.**

8) In lines 562-564: "The FDS default model uses a single gray gas with a composition and temperature dependent
   absorption coefficient computed from RADCAL." Is this equivalent to the PM model in RadLib? If so, a comparison with
   PM from RadLib and FDS default will be a good validation. Also, what RTE solver does FDS default use?

   **No, they are not equivalent. FDS uses a finite-volume discrete ordinates RTE solver, as specified in the first paragraph of Section 5.1.**

9) In Section 5.2 can the author comment on the computational cost of RadLib-coupled FDS runs? Some quantitative
   information on the computational cost of using RadLib for a coupled run will be very useful. For example, the authors
   can compare the cost of the same FDS configuration simulated without any radiation, with RadLib, and with the
   FDS-default model.

10) Line 624: "At present, it includes three major radiation property models - Planck Mean (PM) absorption coefficients
    using the optically thin approximation, the weighted sum of gray gases (WSGG) model,..." PM can be used with any RTE
    solver in principle, not just with optically thin approximation. Is there any limitation within RadLib of using PM
    only with optically thin approximation?

   **This is an error; the reference to the optically thin approximation has been removed. It is true that the PM model can 
be used with any RTE solver. There is no limitation within RadLib that prevents its use with other RTE solvers.**

### 2021-09-13 manuscript/manuscript.tex
Grammar, usage, and proofreading edits for clarity in Sections 1, 2, and 2.1

--- 2021-09-08 manuscript/manuscript.tex
@@
         \begin{abstract}
-            RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations.
-RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
-RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
-A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS).
-The computational cost of the models is compared.
-RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
+            RadLib is a C++ library of radiation property models that can be applied to a variety of systems involving
+            radiative heat transfer, including CFD simulations. RadLib includes three major radiation property
+            models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the
+            rank-correlation spectral line-weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and
+            Fortran interfaces and can be expanded to include additional models. Several example cases illustrate the
+            use of the models with an included ray-tracing solver, compare their accuracy relative to
+            line-by-line (LBL) solutions, and compare their computational costs. Finally, RadLib is coupled with Fire
+            Dynamics Simulator (FDS) in an ethylene burner flame example case to demonstrate its use with existing
+            CFD software. RadLib provides researchers with convenient access to validated radiation property models
+            and a framework for further development.
         \end{abstract}
@@
         {\em Nature of problem(approx. 50-250 words):} \\
-        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations.
-Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations.
+        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in
+        significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a
+        high degree of specialization due to its complexity and the challenges associated with implementation in
+        existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies
+        introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
+        {\em Solution method(approx. 50-250 words):}\\
+        We present RadLib, an open-source C++ library of validated radiation property models that can be applied
+        alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for
+        combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with
+        a provided ray-tracing solver, and an integrated example using Fire Dynamics Simulator (FDS). RadLib can also
+        be expanded to include additional radiative property models and interfaces. \\
+        {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
+        The RadLib library is intended to be used in Linux-like terminal applications.
         \\
-        {\em Solution method(approx. 50-250 words):}\\
-        We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD.
-The package includes C++, Fortran, and Python interfaces, several illustrative examples with a provided ray-tracing solver, and possibility for expansion to include additional radiation property models and interfaces.\\
-        {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
-        The library is intended to be used in Linux-like terminal applications.
-        \\
 
@@
 
-    Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem.
-Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
-Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
-Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures \citep{Modest_2016}.
-Additionally, some late-stage flame phenomena, particularly soot behavior and flamesheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
-These problems motivated development of the RadLib library, which implements three radiation property models, with C++, Python, and Fortran interfaces, and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.
-
-    The core mechanisms of radiative phenomena are physically and mathematically complex.
-Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
-Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model.
-    Complexity, implementation, and computational costs of these two parts can vary widely, depending on the models chosen.
-The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and Reverse Monte Carlo Ray Tracing (RMCRC) model, among others, are significantly more involved.
-Similarly for radiation property models, which range from simple correlations for mean absorption coefficients, to gray gas models such as the weighted sum of gray gas model (WSGG), to the more advanced Spectral Line WSGG (SLW) family of model, to full line-by-line (LBL) treatment.
-In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models, such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
-    RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
-
-    For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
+    Modeling radiative heat transfer in high temperature participating media systems is challenging, particularly in
+    combustion systems.
+    Combustion CFD is uniquely challenging because
+    it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and
+    radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction
+    kinetics---that span many orders of magnitude in both length and time scales.
+    Radiation modeling often complicates combustion simulations because accurate models can be difficult to
+    implement and
+    computationally expensive relative to overall simulation costs.
+    Radiative heat transfer modeling in combustion systems
+    is frequently neglected or oversimplified, resulting in significant flame temperature prediction errors~\citep{Modest_2016}.
+    Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough,
+    increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate
+    accurately without robust radiation modeling~\cite{Modest_2013}. These problems motivated development of the
+    RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and
+    provides a framework for additional models and further development, providing researchers with convenient access to
+    advanced radiation property modeling tools.
+
+    The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat
+    transfer, radiation is governed by a set of directionally and spectrally dependent integro-differential equations
+    known as the radiative transfer
+    equations (RTEs). Computational radiation solvers require two distinct
+    but interconnected parts: (1) a solution approach for the radiative transfer equations (RTEs) and (2) a radiative
+    property model.
+    The complexity, implementation, and computational costs of these two parts can vary widely depending on the models
+    chosen. For example, the optically thin approximation for solution of the RTE is trivial, while the discrete
+    ordinates model (DOM) and
+    reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved. Similarly,
+    radiation property models range from simple correlations for computing mean absorption coefficients to gray gas
+    models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral
+    line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
+    In practical engineering simulations, solving the RTE is
+    often the most complex and costly part of radiative simulation, but advanced property models such as the
+    rank-correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and
+    validate.
+    RadLib addresses this second radiative property model part of radiation simulation by providing a set of
+    implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
+
+    Consider an absorbing, emitting, and non-scattering medium. The RTE describes the radiative intensity $I$ at a
+    specified wavenumber $\eta$ in unit direction $\mathbf{s}$ as
 % 
@@
 %
-    where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity
+    where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity
     (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
-    along direction $\mathbf{s}$.
-    Solving the RTE requires information about the radiative properties of the materials and media in the system.
-    Radiative property data typically takes the form of radiation absorption
+    along direction $\mathbf{s}$. Solving the RTE requires information about the radiative properties of the
+    materials and media in the system. Radiative property data typically takes the form of radiation absorption
     coefficients $\kappa$, which are provided by a radiation property model.
-    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, and depends
+    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend
     on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
@@
     spectral databases, reducing the huge amount of spectral data and
-    simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.
-
-    The direct solution of the spectral RTE using so-called line-by-line calculations in which the RTE is solved for each
-    individual spectral line is computationally prohibitive for most practical configurations and is used primarily for model
-    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
-    incorporated into the RTE.
-
-    Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
-    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
-    RTE evaluations \citep{Modest_2016}.
-
-    Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}.
-Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
+    simplifying evaluation of radiation absorption coefficients~\cite{Zhang_2002b}.
+
+    The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations---in which the RTE is solved
+    for each individual spectral line---is computationally prohibitive for most practical configurations and used
+    primarily for model validation. In contrast, simple ``band'' models rely on estimated or averaged ``line-of-sight''
+    property values that cannot be directly incorporated into the RTE solution.
+    Modern band models, which require access to high-resolution spectral databases, tend to reorder spectral emission
+    levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to
+    nonhomogeneous media and may still require large numbers of RTE evaluations~\citep{Modest_2016}.
+
+    Global models are an important class of radiation property models that use spectrally-integrated radiation
+    properties~\cite{Hottel_1967,Modest_2013,Modest_2016}. Assuming spectrally uniform (gray) properties over a
+    wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to
+    obtain
 %
@@
 %
-    where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
+    where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray
+    gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
 %
@@
 %
-    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases.
-Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$.
-This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
+    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray
+    gases. Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the
+    spectrum for which $\kappa_0=0$. This gray gas approach allows calculation of the total radiative intensity $I$
+    by summing the individual gray gas intensities:
 %
@@
 %
-
-    The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
-%
-    \begin{linenomath}
-        \begin{equation}
-            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
+    The heat flux $\mathbf{q}$ (kW/m$^2$) can be calculated by integrating over the directional solid
+    angles $\mathbf{s}\Omega$ on the sphere, and the volumetric radiative heat source $Q$ (kW/m$^3$) can be found by
+    computing the divergence of the resulting vector field:
+%
+    \begin{linenomath}
+        \begin{equation}
+            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega,
         \end{equation}
@@
 
-    With RadLib, we aim to provide researchers with a convenient access point for radiative property models that
-    can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a C++ library with optional
-    Python and Fortran interfaces. RadLib calculates radiation absorption coefficients and weighting factors for use in global
-    radiation models. Expansion to other radiative properties and model types is possible. Three models are fully implemented
-    and validated.
+    RadLib calculates radiation absorption coefficients and weighting factors for use in global
+    radiation models. It can interface with various RTE solution approaches suitable for CFD applications and serves
+    as a convenient access point for radiative property modeling.
+    The RadLib library includes three property models that are fully implemented
+    and validated, but it can also be expanded to include other radiative properties and model types.
 
@@
 
-    At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption
-    coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG)
-    model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model.
-These models were chosen for their relevance to practical radiative heat transfer simulations.
+    At present, RadLib includes three radiation property models of varying complexity: the Planck Mean (PM) absorption
+    coefficients model, a weighted sum of gray gases (WSGG)
+    model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model. These models were chosen
+    for their relevance to practical radiative heat transfer simulations.
 They represent increasing levels of complexity, computational cost, and accuracy.
@@
 
-    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITRAN, and HITEMP \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
+    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution
+    spectral databases like RADCAL, HITRAN, and HITEMP~\citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
 At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot.
 The property models implemented in RadLib apply only to non-scattering media.
-
     Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
@@
     \begin{table}
-        \caption{Summary of radiative property models in RadLib.}
+        \caption{Summary of radiative property models in RadLib and the range of conditions under which they can be
+        applied.}
         \label{t:models}
@@
                 \hline
-                Model & T range (K) & P range (atm) & Refs.   \\
+                Model & T range & P range & Refs.   \\
                 \hline
-                PM      & 300\textendash 2500 & 1                   & \cite{TNF} \\
-                WSGG    & 300\textendash 2400 & 1                   & \cite{Bordbar_2020,Bordbar_2014} \\
-                RCSLW   & 300\textendash 3000 & 0.1\textendash 50   &  \cite{Solovjov_2017} \\
+                PM      & 300\textendash 2500 K & 1 atm               & \cite{TNF} \\
+                WSGG    & 300\textendash 2400 K & 1 atm               & \cite{Bordbar_2020,Bordbar_2014} \\
+                RCSLW   & 300\textendash 3000 K & 0.1\textendash 50 atm &  \cite{Solovjov_2017} \\
                 \hline
@@
     \end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     (with no transparent gas)
-    and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
-
-    The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}.
-This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
-The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models.
-The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
-
-    For each species, the PM model provides the absorption coefficient as fourth or fifth order polynomial fits in one
-    or two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
-    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
-    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
-    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
-    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
-    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
-
-    The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
-    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
-    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration.
-Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.
-
-    The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation.
-Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss.
-It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%.
-At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.
+    and computes the absorption coefficient as a function of temperature and gas composition.
+
+    The particular version of the model implemented comes from the Turbulent Nonpremixed Flames (TNF)
+    workshop~\cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent
+    combustion~\citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been
+    extensively characterized---including temperature, velocity, and composition profiles---and which serve as target
+    flames for computational scientists validating simulations and models. The PM model implemented in RadLib is the
+    one recommended by the TNF workshop and is widely used in turbulent combustion simulation research.
+
+    For each gas species considered, the PM model provides the absorption coefficient $\kappa(T)$ as a fourth or fifth order
+    polynomial fit in one of two temperature ranges to values computed from the RADCAL spetral database~\cite{Grosshandler_1993}.
+    It considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, and \ce{CH4} at temperatures between 300 K and 2500 K.
+    \ce{CO} and \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and
+    \ce{H2O} do, but are included here because of their strong presence in the TNF workshop flames, several of which
+    use methane (\ce{CH4}) or syngas (mixture of \ce{CO} and \ce{H2}) fuels. For more details on the TNF workshop
+    flames and the TNF radiation model, see \cite{TNF}.
+
+    The PM model is not as accurate as the other two models considered; this is illustrated by the examples cases
+    presented in Sections~\ref{s:Examples} and~\ref{s:discussion}.
+    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models
+    because it is commonly used in combustion simulations.
+    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100
+    K or more~\cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the simulation geometry. Accurate
+    results have been reported for hydrogen jet flames~\cite{Barlow_1999}.
+
+    The PM model is most often used in conjunction with the optically-thin approximation for solving the RTE; in this
+    case, the radiative source term of the energy transport equation is particularly simple, and the overall
+    computational cost of the radiative treatment is negligible compared to other aspects of reacting flow
+    simulations. Many combustion applications with relatively low radiative heat loss can be considered optically
+    thin with respect to radiation; non-sooting laboratory-scale research jet flames, for example, tend to experience
+    radiative losses of about 5\%. In such cases, when radiative losses are relatively small, the accuracy of the
+    radiative property model is not as crucial to simulation results, and simpler radiative treatments like the PM model
+    may be appropriate.
 
@@
             \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}. In Examples S2 and S5, $n$
-                refers to the number of gray gases considered.}
+                refers to the number of gray gases considered in the RCSLW model.}
             \label{f:examples}

### 2021-09-14 manuscript/manuscript.tex
Grammar, usage, and proofreading edits for clarity in Sections 2.2, 2.3, 2.4, and 3

@@
         \resizebox{\textwidth}{!}{
-            \begin{tabular}{l l l l}
+            \begin{tabular}{l l l l l}
                 \hline
-                Model & T range & P range & Refs.   \\
+                Model & T range & P range & Gas species & Refs.   \\
                 \hline
-                PM      & 300\textendash 2500 K & 1 atm               & \cite{TNF} \\
-                WSGG    & 300\textendash 2400 K & 1 atm               & \cite{Bordbar_2020,Bordbar_2014} \\
-                RCSLW   & 300\textendash 3000 K & 0.1\textendash 50 atm &  \cite{Solovjov_2017} \\
+                PM    & 300\textendash 2500 K & 1 atm & \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4} & \cite{TNF} \\
+                WSGG  & 300\textendash 2400 K & 1 atm & \ce{CO2}, \ce{H2O} & \cite{Bordbar_2014,Bordbar_2020} \\
+                RCSLW & 300\textendash 3000 K & 0.1\textendash 50 atm & \ce{CO2}, \ce{H2O}, \ce{CO} & \cite{Solovjov_2017} \\
                 \hline
@@
 
-    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
-    RadLib implements the WSGG model presented by Bordbar et al.
-\citep{Bordbar_2014,Bordbar_2020}.
-This model computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010 database \cite{Rothman_2010}.
-The $k_j$ and $a_j$ are then correlated to these results using polynomial fits summarized below.
-The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas.
+    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally
+    integrated RTE (Eq.~\ref{e:RTE_wsgg}).
+    RadLib implements the WSGG model presented by Bordbar et al.~\citep{Bordbar_2014,Bordbar_2020}. This model
+    computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010
+    database~\cite{Rothman_2010}. The $k_j$ and $a_j$ values are correlated to these results using polynomial fits as
+    summarized below. The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant
+    radiatively participating species in most combustion environments, using four gray gases and one clear gas.
     Absorption coefficients are calculated by
@@
 %
-    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$.
-The weight factors are calculated by
+    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and
+    $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$. The weight factors are calculated by
 %
@@
 %
-    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K.
-The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound.
-The value of $b_{i,j}$ is calculated by
+    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled
+    temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K. The value of $b_{i,j}$ is calculated by
 %
@@
 %
-    where $C_{j,k,i}$ is a correlated model coefficient.
-The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al.
-\citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.
-
-    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility.
-Most WSGG models are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values.
-This is true of Bordbar et al.'s 2014 model \cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$.
-That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG model versions.
-    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of the correlated range, and that is the model implemented here.
+    where $C_{j,k,i}$ is a correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are
+    provided by Bordbar~et~al.~\citep{Bordbar_2014,Bordbar_2020}; RadLib uses updated values
+    in~\cite{Bordbar_2020}. The model is valid for temperatures between 300 K and 2400 K; temperatures outside this range use the value at the respective bound.
+
+    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility. Most WSGG models
+    are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values. This is
+    true of Bordbar et al.'s 2014 model~\cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$.
+    That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG
+    model versions.
+    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values of $M_r$ by interpolating
+    $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of
+    the correlated range. RadLib implements this extended version of the model.
 
@@
 
-    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed.
-In traditional WSGG models, the component gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}.
+    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases,
+    but differ in the way that the gray gases are constructed. In traditional WSGG models, the component gases are only
+    conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}.
 In SLW approaches, however, the gases are gray in a given spectral band by construction.
@@
 
-    For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}.
-The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
+    For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of
+    its component absorption cross sections \cite{Solovjov_2000}. RadLib's RCSLW implementation considers \ce{H2O},
+    \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
 %
@@
 %
-    Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
+    Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
 
@@
 %That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$. 
-    Hence, a spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and $\tilde{C}_j$.
+    Hence, a spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and
+    $\tilde{C}_j$.
     The RCSLW model uses the notion of rank correlation to handle this spatial variation in the ALBDF.
-    Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ with corresponding absorption cross section spectra $C_\eta(\eta,\BS{\phi}_1)$, and $C_\eta(\eta,\BS{\phi}_2)$ and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some wavenumber $\hat{\eta}$.
-For each spectrum, we define the set of wavenumbers that give cross sections less than $\hat{C}$ as
+    Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ with corresponding absorption
+    cross section spectra $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$, and let $\hat{C}_1\equiv C_\eta
+    (\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some
+    wavenumber $\hat{\eta}$. For each spectrum, we define the set of wavenumbers that give cross sections less than
+    $\hat{C}$ as
 %
@@
 
-    In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient.
+    In the PM model, which treats a gas mixture as a single gray gas, the soot absorption coefficient
+    calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient.
 Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ with units of \si{m^{-1}}.
@@
 
-    RadLib installation is automated with CMake as follows.
-Inside the downloaded \texttt{radlib} folder, the user creates and enters a \texttt{build} directory, then enters the commands \texttt{cmake ..}, followed by \texttt{make}, followed by \texttt{make install}.
-Project options are specified by editing the top-level \texttt{CMakeLists.txt} file where the options are clearly marked.
-These can also be specified at the command line.
-Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and an option to build the documentation.
-Included \texttt{Readme.md} files provide additional information.
-
-    The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, \texttt{lib} containing library files for each interface, \texttt{cmake} with relocatable CMake files for downstream usage, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model.
-These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name.
-The \texttt{include} directory contains the following interface header and module (Fortran) files:
+    RadLib installation is automated with CMake. Inside the downloaded \texttt{radlib} folder, the user must create a
+    \texttt{build} directory and navigate into it. From there, the user executes the following commands in order:
+    \begin{enumerate}
+        \item \texttt{cmake ..}
+        \item \texttt{make}
+        \item \texttt{make install}
+    \end{enumerate}
+    Project options can specified by editing the top-level
+    \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command
+    line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed};
+    options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and
+    an option to build the documentation. Refer to the included \texttt{README} files for additional information.
+
+    Following successful installation, the installation folder will contain four directories:
+    \texttt{cmake} contains relocatable CMake files for downstream developer use;
+    \texttt{include} contains the C++ header files and a Fortran module file;
+    \texttt{lib} contains library files for each interface, including the python module files;
+    and \texttt{rcslw\textunderscore data} contains the binary data files used by the RCSLW model, each of which
+    contains the tabulated ALBDF functions for a given species at a given pressure (in units of atm) as indicated by
+    the file name. If the Python interface is built, the location of the installed Python package must be added
+    to the \texttt{PYTHONPATH} environment variable. A command instructing the user how to do this is provided at the end of
+    the installation. The following outline further illustrates the organization of the installation folder and file
+    locations therein:
 %
     \begin{itemize}
-        \item \texttt{rad\textunderscore planck\textunderscore mean.h},
-        \item \texttt{rad\textunderscore wsgg.h},
-        \item \texttt{rad\textunderscore rcslw.h},
-        \item \texttt{rad\textunderscore module.mod}.
+        \item \texttt{cmake}
+        \begin{itemize}
+            \item \texttt{radlib}
+            \begin{itemize}
+                \item \texttt{radlib.cmake}
             \end{itemize}
-%
-    The C++ and Fortran libraries in the \texttt{lib} folder are
+            \item \texttt{radlib\textunderscore fortran}
             \begin{itemize}
-        \item \texttt{libradlib.a},
-        \item \texttt{libradlib\textunderscore fortran.a}.
+                \item \texttt{radlib\textunderscore fortran.cmake}
             \end{itemize}
-%
-    This folder also contains the Python module.
-If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable.
-A command to do this is provided at the end of the installation.
-
-    To use RadLib in C++, a user code includes the header file for the desired radiation model, e.g., \texttt{\#include "rad\textunderscore rcslw.h"}.
-For Fortran, a \texttt{use rad\textunderscore module} statement provides access to the required interface functions.
-The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}.
-Such usage is demonstrated in the code listing for the examples discussed below.
-Compilation of C++ and Fortran programs requires specification of the header/module and library directory locations and linking against the installed libraries (\texttt{libradlib.a} for C++ and both \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a} for Fortran).
-
-    Figure \ref{fig:flowchart} illustrates the basic structure of using RadLib in a generic one-dimensional RTE solution.
-The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver.
-A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()}, or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
-    These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}.
-The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}.
-A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters so that these do not need to be specified for models that do not make use of them.
-The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first).
-The PM model only considers one gas and the vectors are of unity size.
-The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument.
-This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}.
-The absorption coefficients and weights are set through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface.
-Additional details are included in the program documentation and code listing.
+        \end{itemize}
+        \item \texttt{include}
+        \begin{itemize}
+            \item \texttt{rad\textunderscore planck\textunderscore mean.h}
+            \item \texttt{rad\textunderscore wsgg.h}
+            \item \texttt{rad\textunderscore rcslw.h}
+            \item \texttt{rad\textunderscore module.mod}
+        \end{itemize}
+        \item \texttt{lib}
+        \begin{itemize}
+            \item \texttt{libradlib.a}
+            \item \texttt{libradlib\textunderscore fortran.a}
+            \item \texttt{python[version]}
+            \begin{itemize}
+                \item \texttt{site-packages}
+                \begin{itemize}
+                    \item \texttt{pyrad.cpython-[system architecture].so}
+                \end{itemize}
+            \end{itemize}
+        \end{itemize}
+        \item \texttt{rcslw\textunderscore data}
+    \end{itemize}
+%
+    To use RadLib in C++ code, the user must include the header file for the desired radiation model, e.g.,
+    \texttt{\#include "rad\textunderscore rcslw.h"}, in their code. Compilation requires specification of the header
+    and library directory locations and linking against the installed library (\texttt{libradlib.a}). In Fortran,
+    a \texttt{use rad\textunderscore module} statement provides access to the required interface functions. To
+    compile, the module and library locations must be specified and the code linked against both
+    \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a}. The Python interface functions are loaded
+    from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}. The examples
+    included with the RadLib package and discussed in Section~\ref{s:Examples} demonstrate these usages.
+
+    Figure \ref{fig:flowchart} illustrates the basic structure of RadLib in the context of a generic, one-dimensional
+    RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an
+    appropriate RTE solver. To use it, a user first creates a \texttt{radiation} object and then makes calls to
+    one of two primary functions: \texttt{get\textunderscore k\textunderscore a()} or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
+    These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole
+    fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The \ce{CO} and \ce{CH4} mole fraction
+    parameters have default values of zero and do not need to be specified for models that do not make use of them
+    (see Table~\ref{t:models}). The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of
+    absorption coefficients and a vector of weight factors in which each element corresponds to one of the gray gases
+    considered in the model (with the clear gas in the first position). The PM model only considers one gray gas and
+    thus returns vectors containing one element each.
+    The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} function computes the
+    absorption coefficient and weight factor as scalar values for a single gray gas whose index
+    (starting at zero for all interfaces) is provided as an additional argument. This option to compute the
+    properties for a single gray gas can be important for efficient implementation in some solvers, including Fire
+    Dynamics Simulator (FDS), discussed below~\cite{FDS}.
+    In C++ and Fortran, the absorption coefficients and weights are set through the function argument list; in
+    Python, they appear as return values from the functions. For additional details, refer to the software
+    documentation.
 %
@@
 
-    The RadLib source code is build around a base class called \texttt{rad} from which the individual property models, e.g., \texttt{rad\textunderscore rcslw}, inherit.
-    To extend RadLib to include new radiative property models, a user would create a new derived class for the model that inherits from the \texttt{rad} base class.
-The interface functions \texttt{get\textunderscore k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} would be reimplemented in the new model.
-Additional functions and capabilities could be added as desired.
-The Fortran and Python interface codes consist of wrapper functions to the underlying C++.
-These can be easily extended by paralleling the existing interface functions.
+    To extend RadLib to include new radiative property models, a user would create a new derived class
+    that inherits from the \texttt{rad} base class. The interface functions \texttt{get\textunderscore
+    k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} must be
+    reimplemented for the new model. Additional functions and capabilities could be added as desired. The Fortran and
+    Python interface codes consist of wrapper functions to the underlying C++ that can be easily extended in parallel
+    to the existing interface functions.
 

### 2021-09-15 manuscript/manuscript.tex
Rolling back purely stylistic edits. Finished edits to remainder of paper. Added section to reviewer response document with summary of revisions made.

@@
         \begin{abstract}
-            RadLib is a C++ library of radiation property models that can be applied to a variety of systems involving
-            radiative heat transfer, including CFD simulations. RadLib includes three major radiation property
-            models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the
-            rank-correlation spectral line-weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and
-            Fortran interfaces and can be expanded to include additional models. Several example cases illustrate the
-            use of the models with an included ray-tracing solver, compare their accuracy relative to
-            line-by-line (LBL) solutions, and compare their computational costs. Finally, RadLib is coupled with Fire
-            Dynamics Simulator (FDS) in an ethylene burner flame example case to demonstrate its use with existing
-            CFD software. RadLib provides researchers with convenient access to validated radiation property models
-            and a framework for further development.
+            RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations.
+RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
+RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
+A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS).
+The computational cost of the models is compared.
+RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
         \end{abstract}
@@
         {\em Nature of problem(approx. 50-250 words):} \\
-        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in
-        significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a
-        high degree of specialization due to its complexity and the challenges associated with implementation in
-        existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies
-        introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
+        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations.
+Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations.
+\\
         {\em Solution method(approx. 50-250 words):}\\
@@
         combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with
-        a provided ray-tracing solver, and an integrated example using Fire Dynamics Simulator (FDS). RadLib can also
-        be expanded to include additional radiative property models and interfaces. \\
+        a provided ray-tracing solver and an integrated example using Fire Dynamics Simulator (FDS).
+        RadLib can also be expanded to include additional radiation property models and interfaces.\\
         {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
-        The RadLib library is intended to be used in Linux-like terminal applications.
+        The library is intended to be used in Linux-like terminal applications.
         \\
@@
 
-    Modeling radiative heat transfer in high temperature participating media systems is challenging, particularly in
-    combustion systems.
-    Combustion CFD is uniquely challenging because
+    Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem.
+    Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because
     it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and
     radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction
-    kinetics---that span many orders of magnitude in both length and time scales.
-    Radiation modeling often complicates combustion simulations because accurate models can be difficult to
-    implement and
-    computationally expensive relative to overall simulation costs.
-    Radiative heat transfer modeling in combustion systems
-    is frequently neglected or oversimplified, resulting in significant flame temperature prediction errors~\citep{Modest_2016}.
+    kinetics---that span many orders of magnitude in both length and time scales. Combustion simulations are often
+    complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally
+    expensive relative to overall simulation cost. Frequently, radiative heat transfer modeling in combustion systems
+    is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
     Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough,
     increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate
-    accurately without robust radiation modeling~\cite{Modest_2013}. These problems motivated development of the
+    accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the
     RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and
-    provides a framework for additional models and further development, providing researchers with convenient access to
+    provides a framework for additional models and further development, giving researchers convenient access to
     advanced radiation property modeling tools.
@@
     The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat
-    transfer, radiation is governed by a set of directionally and spectrally dependent integro-differential equations
-    known as the radiative transfer
-    equations (RTEs). Computational radiation solvers require two distinct
-    but interconnected parts: (1) a solution approach for the radiative transfer equations (RTEs) and (2) a radiative
+    transfer, radiation is governed by a set of integro-differential equations that depend on both direction and
+    wavelength, known as the radiative transfer equations (RTE). Computational radiation solvers require two distinct
+    but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative
     property model.
-    The complexity, implementation, and computational costs of these two parts can vary widely depending on the models
-    chosen. For example, the optically thin approximation for solution of the RTE is trivial, while the discrete
-    ordinates model (DOM) and
-    reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved. Similarly,
-    radiation property models range from simple correlations for computing mean absorption coefficients to gray gas
-    models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral
-    line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
-    In practical engineering simulations, solving the RTE is
-    often the most complex and costly part of radiative simulation, but advanced property models such as the
-    rank-correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and
-    validate.
+    Complexity, implementation, and computational cost of these two parts can vary widely depending on the models
+    chosen. The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and
+    reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved. Similarly, radiation
+    property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted
+    sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full
+    line-by-line (LBL) treatment. In practical engineering simulations, the solution of the RTE is
+    often the most complex and costly part of radiative simulation, but advanced property models such as the Rank
+    Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
     RadLib addresses this second radiative property model part of radiation simulation by providing a set of
@@
 
-    Consider an absorbing, emitting, and non-scattering medium. The RTE describes the radiative intensity $I$ at a
-    specified wavenumber $\eta$ in unit direction $\mathbf{s}$ as
+    For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
 % 
@@
 %
-    where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity
+    where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity
     (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
-    along direction $\mathbf{s}$. Solving the RTE requires information about the radiative properties of the
-    materials and media in the system. Radiative property data typically takes the form of radiation absorption
+    along direction $\mathbf{s}$.
+    Solving the RTE requires information about the radiative properties of the materials and media in the system.
+    Radiative property data typically takes the form of radiation absorption
     coefficients $\kappa$, which are provided by a radiation property model.
-    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend
+    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical
+    energy levels of gas molecules and depend
     on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
@@
     spectral databases, reducing the huge amount of spectral data and
-    simplifying evaluation of radiation absorption coefficients~\cite{Zhang_2002b}.
-
-    The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations---in which the RTE is solved
-    for each individual spectral line---is computationally prohibitive for most practical configurations and used
-    primarily for model validation. In contrast, simple ``band'' models rely on estimated or averaged ``line-of-sight''
-    property values that cannot be directly incorporated into the RTE solution.
-    Modern band models, which require access to high-resolution spectral databases, tend to reorder spectral emission
-    levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to
-    nonhomogeneous media and may still require large numbers of RTE evaluations~\citep{Modest_2016}.
-
-    Global models are an important class of radiation property models that use spectrally-integrated radiation
-    properties~\cite{Hottel_1967,Modest_2013,Modest_2016}. Assuming spectrally uniform (gray) properties over a
-    wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to
-    obtain
+    simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.
+
+    The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for
+    each
+    individual spectral line, is computationally prohibitive for most practical configurations and is used primarily
+    for model
+    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
+    incorporated into the RTE. Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
+    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
+    RTE evaluations \citep{Modest_2016}.
+
+    Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}.
+Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
 %
@@
 %
-    where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray
-    gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
+    where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
 %
@@
 %
-    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray
-    gases. Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the
-    spectrum for which $\kappa_0=0$. This gray gas approach allows calculation of the total radiative intensity $I$
-    by summing the individual gray gas intensities:
+    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases.
+Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$.
+This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
 %
@@
 %
-    The heat flux $\mathbf{q}$ (kW/m$^2$) can be calculated by integrating over the directional solid
-    angles $\mathbf{s}\Omega$ on the sphere, and the volumetric radiative heat source $Q$ (kW/m$^3$) can be found by
-    computing the divergence of the resulting vector field:
-%
-    \begin{linenomath}
-        \begin{equation}
-            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega,
+
+    The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
+%
+    \begin{linenomath}
+        \begin{equation}
+            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
         \end{equation}
@@
 
-    RadLib calculates radiation absorption coefficients and weighting factors for use in global
-    radiation models. It can interface with various RTE solution approaches suitable for CFD applications and serves
-    as a convenient access point for radiative property modeling.
-    The RadLib library includes three property models that are fully implemented
-    and validated, but it can also be expanded to include other radiative properties and model types.
+    RadLib calculates radiation absorption coefficients and weighting factors
+    for use in global radiation models. It can interface with various RTE solution
+    approaches suitable for CFD applications and serves as a convenient access
+    point for radiative property modeling. The RadLib library includes three
+    property models that are fully implemented and validated, but it can also be
+    expanded to include other radiative properties and model types.
 
@@
 
-    At present, RadLib includes three radiation property models of varying complexity: the Planck Mean (PM) absorption
-    coefficients model, a weighted sum of gray gases (WSGG)
+    At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption
+    coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG)
     model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model. These models were chosen
@@
 
-    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution
-    spectral databases like RADCAL, HITRAN, and HITEMP~\citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
+    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITRAN, and HITEMP \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}.
 At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot.
@@
     \begin{table}
-        \caption{Summary of radiative property models in RadLib and the range of conditions under which they can be
-        applied.}
+        \caption{Summary of radiative property models in RadLib.}
         \label{t:models}
@@
                 \hline
-                Model & T range & P range & Gas species & Refs.   \\
+                Model & T range (K) & P range (atm) & Gas species & Refs.   \\
                 \hline
-                PM    & 300\textendash 2500 K & 1 atm & \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4} & \cite{TNF} \\
-                WSGG  & 300\textendash 2400 K & 1 atm & \ce{CO2}, \ce{H2O} & \cite{Bordbar_2014,Bordbar_2020} \\
-                RCSLW & 300\textendash 3000 K & 0.1\textendash 50 atm & \ce{CO2}, \ce{H2O}, \ce{CO} & \cite{Solovjov_2017} \\
+                PM      & 300\textendash 2500 & 1                 & \ce{H2O}, \ce{CO2}, \ce{CO}, \ce{CH4}  &
+                \cite{TNF} \\
+                WSGG    & 300\textendash 2400 & 1                 & \ce{H2O}, \ce{CO2} & \cite{Bordbar_2020,
+                    Bordbar_2014} \\
+                RCSLW   & 300\textendash 3000 & 0.1\textendash 50 & \ce{H2O}, \ce{CO2}, \ce{CO} &
+                \cite{Solovjov_2017} \\
                 \hline
@@
     \end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     (with no transparent gas)
-    and computes the absorption coefficient as a function of temperature and gas composition.
-
-    The particular version of the model implemented comes from the Turbulent Nonpremixed Flames (TNF)
-    workshop~\cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent
-    combustion~\citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been
-    extensively characterized---including temperature, velocity, and composition profiles---and which serve as target
-    flames for computational scientists validating simulations and models. The PM model implemented in RadLib is the
-    one recommended by the TNF workshop and is widely used in turbulent combustion simulation research.
-
-    For each gas species considered, the PM model provides the absorption coefficient $\kappa(T)$ as a fourth or fifth order
-    polynomial fit in one of two temperature ranges to values computed from the RADCAL spetral database~\cite{Grosshandler_1993}.
-    It considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, and \ce{CH4} at temperatures between 300 K and 2500 K.
-    \ce{CO} and \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and
-    \ce{H2O} do, but are included here because of their strong presence in the TNF workshop flames, several of which
-    use methane (\ce{CH4}) or syngas (mixture of \ce{CO} and \ce{H2}) fuels. For more details on the TNF workshop
-    flames and the TNF radiation model, see \cite{TNF}.
-
-    The PM model is not as accurate as the other two models considered; this is illustrated by the examples cases
-    presented in Sections~\ref{s:Examples} and~\ref{s:discussion}.
-    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models
-    because it is commonly used in combustion simulations.
-    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100
-    K or more~\cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the simulation geometry. Accurate
-    results have been reported for hydrogen jet flames~\cite{Barlow_1999}.
-
-    The PM model is most often used in conjunction with the optically-thin approximation for solving the RTE; in this
-    case, the radiative source term of the energy transport equation is particularly simple, and the overall
-    computational cost of the radiative treatment is negligible compared to other aspects of reacting flow
-    simulations. Many combustion applications with relatively low radiative heat loss can be considered optically
-    thin with respect to radiation; non-sooting laboratory-scale research jet flames, for example, tend to experience
-    radiative losses of about 5\%. In such cases, when radiative losses are relatively small, the accuracy of the
-    radiative property model is not as crucial to simulation results, and simpler radiative treatments like the PM model
-    may be appropriate.
+    and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
+
+    The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}.
+This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
+The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models.
+The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
+
+    For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one
+    of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
+    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
+    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
+    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
+    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
+    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
+
+    The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
+    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
+    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration.
+Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.
+
+    The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation.
+Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss.
+It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%.
+At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.
 
@@
 
-    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally
-    integrated RTE (Eq.~\ref{e:RTE_wsgg}).
-    RadLib implements the WSGG model presented by Bordbar et al.~\citep{Bordbar_2014,Bordbar_2020}. This model
-    computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010
-    database~\cite{Rothman_2010}. The $k_j$ and $a_j$ values are correlated to these results using polynomial fits as
-    summarized below. The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant
-    radiatively participating species in most combustion environments, using four gray gases and one clear gas.
+    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
+    RadLib implements the WSGG model presented by Bordbar et al.
+\citep{Bordbar_2014,Bordbar_2020}.
+This model computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010 database \cite{Rothman_2010}.
+The $k_j$ and $a_j$ are then correlated to these results using polynomial fits summarized below.
+The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas.
 Absorption coefficients are calculated by
@@
 %
-    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and
-    $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$. The weight factors are calculated by
+    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$.
+The weight factors are calculated by
 %
@@
 %
-    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled
-    temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K. The value of $b_{i,j}$ is calculated by
+    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K.
+The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound.
+The value of $b_{i,j}$ is calculated by
 %
@@
 %
-    where $C_{j,k,i}$ is a correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are
-    provided by Bordbar~et~al.~\citep{Bordbar_2014,Bordbar_2020}; RadLib uses updated values
-    in~\cite{Bordbar_2020}. The model is valid for temperatures between 300 K and 2400 K; temperatures outside this range use the value at the respective bound.
-
-    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility. Most WSGG models
-    are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values. This is
-    true of Bordbar et al.'s 2014 model~\cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$.
-    That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG
-    model versions.
-    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values of $M_r$ by interpolating
-    $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of
-    the correlated range. RadLib implements this extended version of the model.
+    where $C_{j,k,i}$ is a correlated model coefficient.
+The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al.
+\citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.
+
+    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility.
+Most WSGG models are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values.
+This is true of Bordbar et al.'s 2014 model \cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$.
+That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG model versions.
+    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of the correlated range, and that is the model implemented here.
 
@@
 
-    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases,
-    but differ in the way that the gray gases are constructed. In traditional WSGG models, the component gases are only
-    conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}.
+    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed.
+In traditional WSGG models, the component gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}.
 In SLW approaches, however, the gases are gray in a given spectral band by construction.
@@
 
-    For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of
-    its component absorption cross sections \cite{Solovjov_2000}. RadLib's RCSLW implementation considers \ce{H2O},
-    \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
+    For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}.
+The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
 %
@@
 %
-    Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
+    Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
 
@@
 %That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$. 
-    Hence, a spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and
-    $\tilde{C}_j$.
+    Hence, a spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and $\tilde{C}_j$.
     The RCSLW model uses the notion of rank correlation to handle this spatial variation in the ALBDF.
-    Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ with corresponding absorption
-    cross section spectra $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$, and let $\hat{C}_1\equiv C_\eta
-    (\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some
-    wavenumber $\hat{\eta}$. For each spectrum, we define the set of wavenumbers that give cross sections less than
-    $\hat{C}$ as
+    Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ with corresponding absorption cross section spectra $C_\eta(\eta,\BS{\phi}_1)$, and $C_\eta(\eta,\BS{\phi}_2)$ and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some wavenumber $\hat{\eta}$.
+For each spectrum, we define the set of wavenumbers that give cross sections less than $\hat{C}$ as
 %
@@
 
-    In the PM model, which treats a gas mixture as a single gray gas, the soot absorption coefficient
-    calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient.
+    In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient.
 Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ with units of \si{m^{-1}}.
@@
 %
+
     To use RadLib in C++ code, the user must include the header file for the desired radiation model, e.g.,
@@
 
-    Figure \ref{fig:flowchart} illustrates the basic structure of RadLib in the context of a generic, one-dimensional
-    RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an
-    appropriate RTE solver. To use it, a user first creates a \texttt{radiation} object and then makes calls to
-    one of two primary functions: \texttt{get\textunderscore k\textunderscore a()} or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
+    Figure \ref{fig:flowchart} illustrates the basic structure of using RadLib in a generic one-dimensional RTE
+    solution. The RadLib library generates absorption coefficients and their weighting factors for use within an
+    appropriate RTE solver. A user first creates a radiation object, and then makes calls to one of two primary
+    functions: \texttt{get\textunderscore k\textunderscore a()} or \texttt{get\textunderscore k\textunderscore
+    a\textunderscore oneband()}.
     These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole
@@
     (starting at zero for all interfaces) is provided as an additional argument. This option to compute the
-    properties for a single gray gas can be important for efficient implementation in some solvers, including Fire
-    Dynamics Simulator (FDS), discussed below~\cite{FDS}.
-    In C++ and Fortran, the absorption coefficients and weights are set through the function argument list; in
-    Python, they appear as return values from the functions. For additional details, refer to the software
-    documentation.
+    properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire
+    Dynamics Simulation (FDS), discussed below \cite{FDS}. The absorption coefficients and weights are set through
+    the function argument list for the C++ and Fortran interfaces and as return values for the Python interface.
+    Additional details are included in the program documentation and code listing.
 %
@@
 
-    To extend RadLib to include new radiative property models, a user would create a new derived class
-    that inherits from the \texttt{rad} base class. The interface functions \texttt{get\textunderscore
-    k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} must be
-    reimplemented for the new model. Additional functions and capabilities could be added as desired. The Fortran and
-    Python interface codes consist of wrapper functions to the underlying C++ that can be easily extended in parallel
-    to the existing interface functions.
+    The RadLib source code is build around a base class called \texttt{rad} from which the individual property models, e.g., \texttt{rad\textunderscore rcslw}, inherit.
+    To extend RadLib to include new radiative property models, a user would create a new derived class for the model that inherits from the \texttt{rad} base class.
+The interface functions \texttt{get\textunderscore k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} would be reimplemented in the new model.
+Additional functions and capabilities could be added as desired.
+The Fortran and Python interface codes consist of wrapper functions to the underlying C++.
+These can be easily extended by paralleling the existing interface functions.
 
@@
 
-    The examples are provided with the RadLib code and implemented in both C++ and Python.
-A Juptyer notebook is provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files.
-Python and Cython versions of the one-dimensional solver \texttt{parallel\textunderscore planes.py} are provided for convenience.
-
-    These cases are intended to illustrate the use of the RadLib library and are not exhaustive.
-Details about these examples and their motivations can be found in their respective references.
-Comparison of these results to the LBL data, shown here, serve as model validation.
-For WSGG and RCSLW, direct comparison (not shown) of RadLib was made to examples presented in the model references with identical results (up to the resolution of the available data), which serves as verification of the implementation.
+    The examples are provided with the RadLib code and implemented in both C++ and Python. A Juptyer notebook is
+    provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files.
+    Python and Cython versions of the one-dimensional solver \texttt{parallel\textunderscore planes.py} are provided
+    for convenience.
+
+    These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these
+    examples and their motivations can be found in their respective references. Comparison of these results to the
+    LBL data, shown here, serve as model validation. For the WSGG and RCSLW models, direct comparison (not shown) of
+    RadLib was
+    made to examples presented in the model references with identical results (up to the resolution of the available
+    data), which serves as verification of the implementation.
 
@@
 
-    Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}.
-These plots are included to demonstrate the examples that are provided with the code, and to compare the models to give an indication of their relative accuracy.
-In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied.
-The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature.
+    Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models
+    implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}. These plots are
+    included to demonstrate the examples that are provided with the code, and to compare the models to give an
+    indication of their relative accuracy. In all examples, the RCSLW model data is computed using four gray gases
+    ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Examples S2 and S5, in
+    which
+    the number of gray gases in the RCSLW model is varied. The RCSLW model is initialized using the mean temperature
+    and composition on the domain for all cases except Example S5, which uses the maximum temperature.
 %
@@
 
-    In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data.
-The results show that the PM model tends to exaggerate the trends displayed by the other models.
-The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity.
-For the PM model in Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100 kW/m$^3$ at $x=2$~m.
-    In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity.
-The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36 in the thick and thin layers, respectively.
-These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
-    Example S3 illustrates that the PM model tends to overpredict radiative heat loss at hight temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-
-    The WSGG model closely follows the trends of the LBL data for all examples, and in most examples gives reasonable quantitative agreement.
-This is especially true for Example S2, S4, and B3.
-For example S5, the WSGG model shows peak errors of around 50\%, and somewhat higher in Example S1.
-The heat flux near the boundaries in Example B3 is low by around 30\%.
-The RCSLW model gives results in very close agreement to the LBL data for all examples.
-A notable exception is example S2, where the heat flux at the right boundary is not well-predicted for four gray gases.
-The heat flux does converge to the LBL results when the number of gray gases increases.
-This behavior was not discussed in \cite{Solovjov_2017} where 24 gray gases were used.
-The WSGG model is very close to the LBL data for this case.
-The good agreement is likely a result of the simplicity of this case that is isothermal with pure \ce{CO2} at uniform concentration in either of the two adjacent gas slabs.
-    The RCSLW model is sensitive to the number of gray gases used, as illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
-The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases (not shown) and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
+    In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data. The results show
+    that the PM model tends to exaggerate the trends displayed by the other models. The PM data mimics the shape of
+    the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity. For the PM model in
+    Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100
+    kW/m$^3$ at $x=2$~m.
+    In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity. The
+    PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in calculated optical thicknesses of 0.09
+    and 0.36 in the thick and thin layers, respectively. These values are small compared to the domain sizes greater
+    than 0.5 m considered in Example S2.
+    Example S3 illustrates that the PM model tends to overpredict radiative heat loss at high temperatures, which
+    has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.
+
+    The WSGG model closely follows the trends of the LBL data for all examples, and in most examples gives reasonable
+    quantitative agreement. This is especially true for Examples S2, S4, and B3. For example S5, the WSGG model shows
+    peak errors of around 50\%, and somewhat higher in Example S1. The heat flux near the boundaries in Example B3 is
+    low by around 30\%. The RCSLW model gives results in very close agreement to the LBL data for all examples. A
+    notable exception is Example S2, where the heat flux at the right boundary is not well-predicted with four gray
+    gases. The heat flux does converge to the LBL results when the number of gray gases increases. This behavior was
+    not discussed in \cite{Solovjov_2017} where 24 gray gases were used. The WSGG model is very close to the LBL data
+    for this case. The good agreement is likely a result of the simplicity of this case, which is isothermal with pure
+    \ce{CO2} at uniform concentration in either of the two adjacent gas slabs.
+    The RCSLW model is sensitive to the number of gray gases used, as illustrated in Figure~\ref{f:examples} by
+    Examples S2 and S5. The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example
+    cases (not shown) and typically falls within the margin of error represented by the WSGG model's deviation from
+    the LBL data.
     The RCSLW model also depends on the value of the chosen reference temperature that is used to set the ALBDF grid.
-In Example S5, the RCSLW model does not converge to the LBL data at $x>0.5$ m when the domain average temperature is used.
-
-    Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume fraction in addition to the radiating gas.
-Both the WSGG and RCSLW models perform accurately in all three cases, but the PM model displays significant deviations from the LBL data.
-In sooting flames, soot acts as a significant source and sink of radiation, and its radiative properties differ significantly from those of the participating gaseous species.
-Soot reactions and transport are both sensitive to, and strongly influence local variations in, flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
+    In Example S5, the RCSLW model does not converge to the LBL data at $x>0.5$ m when the domain average temperature
+    is used.
+
+    Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume
+    fraction in addition to the radiating gas. Both the WSGG and RCSLW models perform accurately in all three cases,
+    but the PM model displays significant deviations from the LBL data. In sooting flames, soot acts as a significant
+    source and sink of radiation, and its radiative properties differ significantly from those of the participating
+    gaseous species. Soot reactions and transport are both sensitive to, and strongly influence local variations in,
+    flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot
+    radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame
+    phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes. As such,
+    simpler models such as the PM model may fail to capture important subtleties in soot's radiative behavior.
 
@@
             \end{tabular}
-            \caption{Radial profiles of mean temperature at two heights (a), and height versus radiative emission (b) for FDS simulations of the FM Burner validation case comparing three models to experimental data.}
+            \caption{Radial profiles of mean temperature at two heights (a) and height versus radiative emission (b) for FDS simulations of the FM Burner validation case comparing three models to experimental data.}
             \label{f:fds}
@@
 
-    Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver.
-This is relevant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evaluations alone.
-This is consistent with the results of the figure and as follows.
-Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.
+    Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties
+    and solution of the RTE using the provided ray-tracing solver. This is relevant because radiative property
+    calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost
+    differences may be smaller than those of the property evaluations alone. This is consistent with the results of
+    Figure~\ref{f:cost}b and as follows. Relative to the WSGG model, which required 0.0079 s, the model costs for the
+    PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.
 
@@
 
-    Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to their high level of conceptual and mathematical complexity and potentially large computational cost.
-Many combustion CFD studies either neglect radiative heat transfer or employ oversimplified models that do not accurately represent combustion systems.
-Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation to yield accurate results.
-
-    RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations.
-At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
-Each of the implemented models has been validated and the library's structure and functionality has been outlined.
-The library can be expanded to include additional property models.
-
-    In addition to the library itself, RadLib includes several illustrative example cases in a one-dimensional parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model implementation.
-Results are compared to line-by-line (LBL) solutions.
-In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy at the expense of computational cost.
-
-    RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for relatively high temperature CFD applications, such as combustion, but could potentially be applied to research problems involving radiative heat transfer in other fields as well.
-RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models.
-Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions.
-By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations.
+    Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to
+    their high level of conceptual and mathematical complexity and potentially large computational cost. Many
+    combustion CFD studies either neglect radiative heat transfer or employ oversimplified models that do not
+    accurately represent combustion systems. Most combustion processes of interest to engineers and researchers,
+    however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which
+    includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield
+    accurate results.
+
+    RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property
+    models in CFD simulations. At present, it includes three major radiation property models---Planck Mean (PM)
+    absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line
+    weighted-sum-of-gray-gases (RCSLW) model. Each of the implemented models has been validated and the library's
+    structure and functionality has been outlined. The library can be expanded to include additional property models.
+
+    In addition to the library itself, RadLib includes several illustrative example cases in a one-dimensional
+    parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model
+    implementation. Results are compared to line-by-line (LBL) solutions. In general, the RCSLW model outperforms
+    both the PM and WSGG models in terms of accuracy at the expense of computational cost.
+
+    RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for
+    relatively high temperature CFD applications such as combustion but could potentially be applied to research
+    problems involving radiative heat transfer in other fields as well. RadLib is designed to facilitate and simplify
+    the process of implementing and using radiative property models; it consolidates various model types into a
+    single library with a consistent framework, reducing some of the overhead associated with choosing, implementing,
+    and testing radiation property models. Its framework can be used to implement and validate new models as well as
+    compare existing models under consistent conditions. By facilitating model comparison through a common interface,
+    RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by
+    large-scale CFD simulations.
 
@@
 \bibitem{Modest_2013}
-M.~F. Modest, {Radiative Heat Transfer}, third edition Edition, {Academic
+M.~F. Modest, {Radiative Heat Transfer}, Third Edition, {Academic
 Press}, New York, 2013.
@@
 \newblock \href {http://dx.doi.org/10.1007/978-3-319-32003-8{\textunderscore
-  }61-1} {\path{doi:10.1007/978-3-319-32003-8{\textunderscore }61-1}}.
+  }61-1} {\path{doi:10.1007/978-3-319-32003-8_61-1}}.
 \newline\urlprefix\url{https://link-springer-com.erl.lib.byu.edu/referenceworkentry/10.1007/978-3-319-32003-8_61-1}

### 2021-09-28 manuscript/manuscript.tex
fixing whitespace issues to allow comparison with previous revision

@@
 {\em Solution method(approx. 50-250 words):}\\
-        We present RadLib, an open-source C++ library of validated radiation property models that can be applied
-        alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for
-        combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with
-        a provided ray-tracing solver and an integrated example using Fire Dynamics Simulator (FDS).
+We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD.
+The package includes C++, Fortran, and Python interfaces, several illustrative examples with a provided ray-tracing solver and an integrated example using Fire Dynamics Simulator (FDS).
 RadLib can also be expanded to include additional radiation property models and interfaces.\\
@@
 Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem.
-    Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because
-    it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and
-    radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction
-    kinetics---that span many orders of magnitude in both length and time scales. Combustion simulations are often
-    complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally
-    expensive relative to overall simulation cost. Frequently, radiative heat transfer modeling in combustion systems
-    is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
-    Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough,
-    increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate
-    accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the
-    RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and
-    provides a framework for additional models and further development, giving researchers convenient access to
-    advanced radiation property modeling tools.
-
-    The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat
-    transfer, radiation is governed by a set of integro-differential equations that depend on both direction and
-    wavelength, known as the radiative transfer equations (RTE). Computational radiation solvers require two distinct
-    but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative
-    property model.
-    Complexity, implementation, and computational cost of these two parts can vary widely depending on the models
-    chosen. The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and
-    reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved. Similarly, radiation
-    property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted
-    sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full
-    line-by-line (LBL) treatment. In practical engineering simulations, the solution of the RTE is
-    often the most complex and costly part of radiative simulation, but advanced property models such as the Rank
-    Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
-    RadLib addresses this second radiative property model part of radiation simulation by providing a set of
-    implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
+Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
+Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
+Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
+Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
+These problems motivated development of the RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.
+
+The core mechanisms of radiative phenomena are physically and mathematically complex.
+Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
+Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model.
+Complexity, implementation, and computational cost of these two parts can vary widely depending on the models chosen.
+The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
+Similarly, radiation property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
+In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
+RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
 
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:RTE_general}
+\begin{equation} \label{e:RTE_general}
     \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
@@
 %
-    where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity
-    (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
-    along direction $\mathbf{s}$.
+where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
 Solving the RTE requires information about the radiative properties of the materials and media in the system.
-    Radiative property data typically takes the form of radiation absorption
-    coefficients $\kappa$, which are provided by a radiation property model.
-    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical
-    energy levels of gas molecules and depend
-    on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
-    Radiation property models typically consist of correlations between radiative properties and high-resolution
-    spectral databases, reducing the huge amount of spectral data and
-    simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.
-
-    The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for
-    each
-    individual spectral line, is computationally prohibitive for most practical configurations and is used primarily
-    for model
-    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
-    incorporated into the RTE. Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
-    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
-    RTE evaluations \citep{Modest_2016}.
+Radiative property data typically takes the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model.
+Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
+Radiation property models typically consist of correlations between radiative properties and high-resolution spectral databases, reducing the huge amount of spectral data and simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.
+
+The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and is used primarily for model validation.
+Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
+%dol
+Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.
 
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:RTE_wsgg}
+\begin{equation} \label{e:RTE_wsgg}
     \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
@@
 %
-    Global models are especially attractive in computational heat transfer applications because they can provide good accuracy
-    while limiting computational costs.
-
-    RadLib calculates radiation absorption coefficients and weighting factors
-    for use in global radiation models. It can interface with various RTE solution
-    approaches suitable for CFD applications and serves as a convenient access
-    point for radiative property modeling. The RadLib library includes three
-    property models that are fully implemented and validated, but it can also be
-    expanded to include other radiative properties and model types.
+Global models are especially attractive in computational heat transfer applications because they can provide good accuracy while limiting computational costs.
+
+RadLib calculates radiation absorption coefficients and weighting factors for use in global radiation models.
+It can interface with various RTE solution approaches suitable for CFD applications and serves as a convenient access point for radiative property modeling.
+The RadLib library includes three property models that are fully implemented and validated, but it can also be expanded to include other radiative properties and model types.
 
@@
 
-    At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption
-    coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG)
-    model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model. These models were chosen
-    for their relevance to practical radiative heat transfer simulations.
+At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
+These models were chosen for their relevance to practical radiative heat transfer simulations.
 They represent increasing levels of complexity, computational cost, and accuracy.
@@
 The property models implemented in RadLib apply only to non-scattering media.
-    Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
-    which they apply.
+Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under which they apply.
 
@@
 
-    The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas
-    (with no transparent gas)
-    and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
+The Planck Mean (PM) model is the simplest of the three models implemented.
+This model assumes a single gray gas (with no transparent gas) and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
 
@@
 The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
-
-    For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one
-    of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
-    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
-    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
-    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
-    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
-    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
+For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
+Ultimately, the model accommodates temperatures between 300 K and 2500 K.
+See \cite{TNF} for details and references.
+The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
+The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream.
+(\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
 
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:albdf}
+\begin{equation} \label{e:albdf}
 F(C,\BS{\phi},T) = \frac{1}{\sigma T^4}\int_{\{\eta:\,C_\eta(\eta,\BS{\phi})<C\}}E_b(\eta,T)d\eta,
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:aj}
+\begin{equation} \label{e:aj}
 a_j = F(\tilde{C}_j,\BS{\phi}, T) - F(\tilde{C}_{j-1}, \BS{\phi},T).
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:multiC}
+\begin{equation} \label{e:multiC}
 C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:multiF}
+\begin{equation} \label{e:multiF}
 F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right).
@@
 \begin{linenomath}
-        \begin{align}
-            \label{e:albdf2}
+\begin{align} \label{e:albdf2}
 F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:FeqF}
+\begin{equation} \label{e:FeqF}
 F(\hat{C}_1,\BS{\phi}_1,T_r)=F(\hat{C}_2,\BS{\phi}_2,T_r).
@@
 \begin{linenomath}
-        \begin{equation}
-            \label{e:soot2}
+\begin{equation} \label{e:soot2}
 \kappa_{soot}=3.72\frac{f_vC_0T}{C_2},
@@
 
-    RadLib installation is automated with CMake. Inside the downloaded \texttt{radlib} folder, the user must create a
-    \texttt{build} directory and navigate into it. From there, the user executes the following commands in order:
+RadLib installation is automated with CMake.
+Inside the downloaded \texttt{radlib} folder, the user must create a \texttt{build} directory and navigate into it.
+From there, the user executes the following commands in order:
+%
 \begin{enumerate}
@@
 \end{enumerate}
-    Project options can specified by editing the top-level
-    \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command
-    line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed};
-    options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and
-    an option to build the documentation. Refer to the included \texttt{README} files for additional information.
+%
+Project options can specified by editing the top-level \texttt{CMakeLists.txt} file where the options are clearly marked.
+These can also be specified at the command line.
+Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and an option to build the documentation.
+Refer to the included \texttt{README} files for additional information.
 
@@
 and \texttt{rcslw\textunderscore data} contains the binary data files used by the RCSLW model, each of which
-    contains the tabulated ALBDF functions for a given species at a given pressure (in units of atm) as indicated by
-    the file name. If the Python interface is built, the location of the installed Python package must be added
-    to the \texttt{PYTHONPATH} environment variable. A command instructing the user how to do this is provided at the end of
-    the installation. The following outline further illustrates the organization of the installation folder and file
-    locations therein:
+contains the tabulated ALBDF functions for a given species at a given pressure (in units of atm) as indicated by the file name.
+If the Python interface is built, the location of the installed Python package must be added to the \texttt{PYTHONPATH} environment variable.
+A command instructing the user how to do this is provided at the end of the installation.
+The following outline further illustrates the organization of the installation folder and file locations therein:
 %
@@
 
-    To use RadLib in C++ code, the user must include the header file for the desired radiation model, e.g.,
-    \texttt{\#include "rad\textunderscore rcslw.h"}, in their code. Compilation requires specification of the header
-    and library directory locations and linking against the installed library (\texttt{libradlib.a}). In Fortran,
-    a \texttt{use rad\textunderscore module} statement provides access to the required interface functions. To
-    compile, the module and library locations must be specified and the code linked against both
-    \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a}. The Python interface functions are loaded
-    from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}. The examples
-    included with the RadLib package and discussed in Section~\ref{s:Examples} demonstrate these usages.
-
-    Figure \ref{fig:flowchart} illustrates the basic structure of using RadLib in a generic one-dimensional RTE
-    solution. The RadLib library generates absorption coefficients and their weighting factors for use within an
-    appropriate RTE solver. A user first creates a radiation object, and then makes calls to one of two primary
-    functions: \texttt{get\textunderscore k\textunderscore a()} or \texttt{get\textunderscore k\textunderscore
-    a\textunderscore oneband()}.
-    These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole
-    fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The \ce{CO} and \ce{CH4} mole fraction
-    parameters have default values of zero and do not need to be specified for models that do not make use of them
-    (see Table~\ref{t:models}). The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of
-    absorption coefficients and a vector of weight factors in which each element corresponds to one of the gray gases
-    considered in the model (with the clear gas in the first position). The PM model only considers one gray gas and
-    thus returns vectors containing one element each.
-    The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} function computes the
-    absorption coefficient and weight factor as scalar values for a single gray gas whose index
-    (starting at zero for all interfaces) is provided as an additional argument. This option to compute the
-    properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire
-    Dynamics Simulation (FDS), discussed below \cite{FDS}. The absorption coefficients and weights are set through
-    the function argument list for the C++ and Fortran interfaces and as return values for the Python interface.
+To use RadLib in C++ code, the user must include the header file for the desired radiation model, e.g., \texttt{\#include "rad\textunderscore rcslw.h"}, in their code.
+Compilation requires specification of the header and library directory locations and linking against the installed library (\texttt{libradlib.a}).
+In Fortran, a \texttt{use rad\textunderscore module} statement provides access to the required interface functions.
+To compile, the module and library locations must be specified and the code linked against both \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a}.
+The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}.
+The examples included with the RadLib package and discussed in Section~\ref{s:Examples} demonstrate these usages.
+
+Figure \ref{fig:flowchart} illustrates the basic structure of using RadLib in a generic one-dimensional RTE solution.
+The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver.
+A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()} or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
+These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}.
+The \ce{CO} and \ce{CH4} mole fraction parameters have default values of zero and do not need to be specified for models that do not make use of them (see Table~\ref{t:models}).
+The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors in which each element corresponds to one of the gray gases considered in the model (with the clear gas in the first position).
+The PM model only considers one gray gas and thus returns vectors containing one element each.
+The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} function computes the absorption coefficient and weight factor as scalar values for a single gray gas whose index (starting at zero for all interfaces) is provided as an additional argument.
+This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}.
+The absorption coefficients and weights are set through the function argument list for the C++ and Fortran interfaces and as return values for the Python interface.
 Additional details are included in the program documentation and code listing.
@@
 
-    The examples are provided with the RadLib code and implemented in both C++ and Python. A Juptyer notebook is
-    provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files.
-    Python and Cython versions of the one-dimensional solver \texttt{parallel\textunderscore planes.py} are provided
-    for convenience.
-
-    These cases are intended to illustrate the use of the RadLib library and are not exhaustive. Details about these
-    examples and their motivations can be found in their respective references. Comparison of these results to the
-    LBL data, shown here, serve as model validation. For the WSGG and RCSLW models, direct comparison (not shown) of
-    RadLib was
-    made to examples presented in the model references with identical results (up to the resolution of the available
-    data), which serves as verification of the implementation.
+The examples are provided with the RadLib code and implemented in both C++ and Python.
+A Juptyer notebook is provided with the Python examples that runs the examples, displays the plots, and saves the plots to PDF files.
+Python and Cython versions of the one-dimensional solver \texttt{parallel\textunderscore planes.py} are provided for convenience.
+
+These cases are intended to illustrate the use of the RadLib library and are not exhaustive.
+Details about these examples and their motivations can be found in their respective references.
+Comparison of these results to the LBL data, shown here, serve as model validation.
+For the WSGG and RCSLW models, direct comparison (not shown) of RadLib was made to examples presented in the model references with identical results (up to the resolution of the available data), which serves as verification of the implementation.
 
@@
 
-    Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models
-    implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}. These plots are
-    included to demonstrate the examples that are provided with the code, and to compare the models to give an
-    indication of their relative accuracy. In all examples, the RCSLW model data is computed using four gray gases
-    ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Examples S2 and S5, in
-    which
-    the number of gray gases in the RCSLW model is varied. The RCSLW model is initialized using the mean temperature
-    and composition on the domain for all cases except Example S5, which uses the maximum temperature.
+Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}.
+These plots are included to demonstrate the examples that are provided with the code, and to compare the models to give an indication of their relative accuracy.
+In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Examples S2 and S5, in which the number of gray gases in the RCSLW model is varied.
+The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature.
 %
@@
         \end{tabular}
-            \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}. In Examples S2 and S5, $n$
-                refers to the number of gray gases considered in the RCSLW model.}
+        \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}. In Examples S2 and S5, $n$ refers to the number of gray gases considered in the RCSLW model.}
         \label{f:examples}
@@
 
-    In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data. The results show
-    that the PM model tends to exaggerate the trends displayed by the other models. The PM data mimics the shape of
-    the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity. For the PM model in
-    Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100
-    kW/m$^3$ at $x=2$~m.
-    In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity. The
-    PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in calculated optical thicknesses of 0.09
-    and 0.36 in the thick and thin layers, respectively. These values are small compared to the domain sizes greater
-    than 0.5 m considered in Example S2.
-    Example S3 illustrates that the PM model tends to overpredict radiative heat loss at high temperatures, which
-    has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.
-
-    The WSGG model closely follows the trends of the LBL data for all examples, and in most examples gives reasonable
-    quantitative agreement. This is especially true for Examples S2, S4, and B3. For example S5, the WSGG model shows
-    peak errors of around 50\%, and somewhat higher in Example S1. The heat flux near the boundaries in Example B3 is
-    low by around 30\%. The RCSLW model gives results in very close agreement to the LBL data for all examples. A
-    notable exception is Example S2, where the heat flux at the right boundary is not well-predicted with four gray
-    gases. The heat flux does converge to the LBL results when the number of gray gases increases. This behavior was
-    not discussed in \cite{Solovjov_2017} where 24 gray gases were used. The WSGG model is very close to the LBL data
-    for this case. The good agreement is likely a result of the simplicity of this case, which is isothermal with pure
-    \ce{CO2} at uniform concentration in either of the two adjacent gas slabs.
-    The RCSLW model is sensitive to the number of gray gases used, as illustrated in Figure~\ref{f:examples} by
-    Examples S2 and S5. The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example
-    cases (not shown) and typically falls within the margin of error represented by the WSGG model's deviation from
-    the LBL data.
+In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data.
+The results show that the PM model tends to exaggerate the trends displayed by the other models.
+The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity.
+For the PM model in Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100 kW/m$^3$ at $x=2$~m.
+In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity.
+The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in calculated optical thicknesses of 0.09 and 0.36 in the thick and thin layers, respectively.
+These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
+Example S3 illustrates that the PM model tends to overpredict radiative heat loss at high temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.
+
+The WSGG model closely follows the trends of the LBL data for all examples, and in most examples gives reasonable quantitative agreement.
+This is especially true for Examples S2, S4, and B3.
+For example S5, the WSGG model shows peak errors of around 50\%, and somewhat higher in Example S1.
+The heat flux near the boundaries in Example B3 is low by around 30\%.
+The RCSLW model gives results in very close agreement to the LBL data for all examples.
+A notable exception is Example S2, where the heat flux at the right boundary is not well-predicted with four gray gases.
+The heat flux does converge to the LBL results when the number of gray gases increases.
+This behavior was not discussed in \cite{Solovjov_2017} where 24 gray gases were used.
+The WSGG model is very close to the LBL data for this case.
+The good agreement is likely a result of the simplicity of this case, which is isothermal with pure \ce{CO2} at uniform concentration in either of the two adjacent gas slabs.
+The RCSLW model is sensitive to the number of gray gases used, as illustrated in Figure~\ref{f:examples} by Examples S2 and S5.
+The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases (not shown) and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data.
 The RCSLW model also depends on the value of the chosen reference temperature that is used to set the ALBDF grid.
-    In Example S5, the RCSLW model does not converge to the LBL data at $x>0.5$ m when the domain average temperature
-    is used.
-
-    Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume
-    fraction in addition to the radiating gas. Both the WSGG and RCSLW models perform accurately in all three cases,
-    but the PM model displays significant deviations from the LBL data. In sooting flames, soot acts as a significant
-    source and sink of radiation, and its radiative properties differ significantly from those of the participating
-    gaseous species. Soot reactions and transport are both sensitive to, and strongly influence local variations in,
-    flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot
-    radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame
-    phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes. As such,
-    simpler models such as the PM model may fail to capture important subtleties in soot's radiative behavior.
+In Example S5, the RCSLW model does not converge to the LBL data at $x>0.5$ m when the domain average temperature is used.
+
+Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume fraction in addition to the radiating gas.
+Both the WSGG and RCSLW models perform accurately in all three cases, but the PM model displays significant deviations from the LBL data.
+In sooting flames, soot acts as a significant source and sink of radiation, and its radiative properties differ significantly from those of the participating gaseous species.
+Soot reactions and transport are both sensitive to, and strongly influence local variations in, flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
+As such, simpler models such as the PM model may fail to capture important subtleties in soot's radiative behavior.
 
@@
 
-    The RadLib model was coupled to the Fire Dynamics Simulator (FDS) code developed at NIST \cite{FDS}. FDS is
-    written in Fortran, and the Fortran interface of Radlib was used for simulations. FDS includes several radiative
-    models, but the spectral WSGG model coupled to a finite volume discrete ordinates model is used here. This was
-    done by editing the \texttt{radi.f90} file in FDS. A \texttt{use rad\textunderscore module} statement is included
-    and the FDS functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} are replaced with calls
-    to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}. The \texttt{oneband} version was
-    used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.
+The RadLib model was coupled to the Fire Dynamics Simulator (FDS) code developed at NIST \cite{FDS}.
+FDS is written in Fortran, and the Fortran interface of Radlib was used for simulations.
+FDS includes several radiative models, but the spectral WSGG model coupled to a finite volume discrete ordinates model is used here.
+This was done by editing the \texttt{radi.f90} file in FDS.
+A \texttt{use rad\textunderscore module} statement is included and the FDS functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} are replaced with calls to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}.
+The \texttt{oneband} version was used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.
 
@@
 \begin{tabular}{c c}
-            (a)
-                & (b) \\
+(a) & (b) \\
 \includegraphics[width=2.5 in]{fig_fds_T_mean.pdf} &
@@
 \begin{tabular}{c c}
-            (a)
-                & (b) \\
+(a) & (b) \\
 \includegraphics[width=2.5 in]{fig_getka_c++.pdf} &
@@
 \end{tabular}
-            \caption{Relative computational cost to (a) evaluate gas properties only and (b) run Example S3, including the ray-tracing solver.
-Results are normalized by the cost of the WSSG model for each case.}
+\caption{Relative computational cost to (a) evaluate gas properties only and (b) run Example S3, including the ray-tracing solver. Results are normalized by the cost of the WSSG model for each case.}
 \label{f:cost}
@@
 
-    Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties
-    and solution of the RTE using the provided ray-tracing solver. This is relevant because radiative property
-    calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost
-    differences may be smaller than those of the property evaluations alone. This is consistent with the results of
-    Figure~\ref{f:cost}b and as follows. Relative to the WSGG model, which required 0.0079 s, the model costs for the
-    PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.
+Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver.
+This is relevant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evaluations alone.
+This is consistent with the results of Figure~\ref{f:cost}b and as follows.
+Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.
 
@@
 
-    Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to
-    their high level of conceptual and mathematical complexity and potentially large computational cost. Many
-    combustion CFD studies either neglect radiative heat transfer or employ oversimplified models that do not
-    accurately represent combustion systems. Most combustion processes of interest to engineers and researchers,
-    however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which
-    includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield
-    accurate results.
-
-    RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property
-    models in CFD simulations. At present, it includes three major radiation property models---Planck Mean (PM)
-    absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line
-    weighted-sum-of-gray-gases (RCSLW) model. Each of the implemented models has been validated and the library's
-    structure and functionality has been outlined. The library can be expanded to include additional property models.
-
-    In addition to the library itself, RadLib includes several illustrative example cases in a one-dimensional
-    parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model
-    implementation. Results are compared to line-by-line (LBL) solutions. In general, the RCSLW model outperforms
-    both the PM and WSGG models in terms of accuracy at the expense of computational cost.
-
-    RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for
-    relatively high temperature CFD applications such as combustion but could potentially be applied to research
-    problems involving radiative heat transfer in other fields as well. RadLib is designed to facilitate and simplify
-    the process of implementing and using radiative property models; it consolidates various model types into a
-    single library with a consistent framework, reducing some of the overhead associated with choosing, implementing,
-    and testing radiation property models. Its framework can be used to implement and validate new models as well as
-    compare existing models under consistent conditions. By facilitating model comparison through a common interface,
-    RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by
-    large-scale CFD simulations.
+Radiative heat transfer phenomena are historically difficult to model and implement in CFD calculations due to their high level of conceptual and mathematical complexity and potentially large computational cost.
+Many combustion CFD studies either neglect radiative heat transfer or employ oversimplified models that do not accurately represent combustion systems.
+Most combustion processes of interest to engineers and researchers, however, involve significant radiative heat transfer, and simulations require robust radiative modeling, which includes both radiation property modeling and solution approaches for the radiative transfer equation, to yield accurate results.
+
+RadLib is a C++ library of radiation property models developed to facilitate implementing radiative property models in CFD simulations.
+At present, it includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
+Each of the implemented models has been validated and the library's structure and functionality has been outlined.
+The library can be expanded to include additional property models.
+
+In addition to the library itself, RadLib includes several illustrative example cases in a one-dimensional parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model implementation.
+Results are compared to line-by-line (LBL) solutions.
+In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy at the expense of computational cost.
+
+RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for relatively high temperature CFD applications such as combustion but could potentially be applied to research problems involving radiative heat transfer in other fields as well.
+RadLib is designed to facilitate and simplify the process of implementing and using radiative property models; it consolidates various model types into a single library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models.
+Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions.
+By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations.
 
@@
 The authors extend special thanks to Hadi Bordbar for assistance with the WSGG model and to Vladimir Solovjov and Brent Webb for their insights and assistance with the RCSLW model.
-    This research did not receive any specific grant from funding agencies in the public, commercial, or
-    not-for-profit sectors.
+This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors.
 

### 2021-09-29 submissions/CPC_response_to_reviewers_revision2.md
DOL edits mostly done; todo: R3 comment 1, 9

@@
 
+<font color='green'>
+
 2) Please rephrase and, if possible, simplify the sentence on lines 82-86 ("Radiation property models, including those
@@
 
-   **Sentence has been revised for clarity.**
+   **This sentence has been rephrased as requested.**
 
@@
 
-   **Yes, it should. Typo has been fixed.**
+   **Yes, it should, this typo has been fixed.**
 
@@
 
-   **The figure's caption has been updated to clarify this. The main difference between the PM model and RCSLW (or WSGG) with n=1 
-is that the RCSLW model always considers one transparent gas (representing gaps in the absorption spectrum) in addition 
-to some number of gray gases, whereas the PM model uses an average over the entire spectrum, gaps included. The "clear gas" 
-concept is discussed on page 4 during the derivation of the gray gas spectral RTE (Eq. 5), but the PM model description 
-did not indicate its deviation from this and has been revised to clarify that it does not consider a transparent gas in 
-addition to its single gray gas.**
+   **The "n=2", etc.
+refer to the number of gray gases in the RCLSW model.
+The figure's caption has been updated to clarify this.
+The figure legend has also been modified to add "n=" to the number listed in Example S2.
+The PM model differs from the $n=1$ RCSLW model as follows.
+The PM model gives a Planck-function-weighted average absorption coefficient, which is not true for the RCSLW model.
+That statement is now added to the paper in Section 2.1.
+For n=1, the RCSLW model considers one gray gas as well as a clear gas representing windows in the distribution, discussed on page 4 during the derivation of the gray gas spectral RTE (Eq.
+5).
+We have revised the paper to note that the PM model does not include a clear gas. 
+The PM model uses a linear mixing of partial-pressure-weighted components for the absorption coefficients, whereas the RCSLW model uses the multiplication method to get the mixture ALBDF from the product of species ALBDF values (Eq.
+14), which is then used to compute the absorption coefficient and weight.
+The method of calculation of the gas absorption coefficient and weight for RCSLW follows from the summary description near the end of section 2.3.**
+</font>
+
+<font color='green'>
 
@@
    be easier to read.
+
+   **We have revised the figure as requested. All subplots now use consistent line styles. Figure 3 is also made consistent with Fig. 2.**
 
@@
 
-   **Those numbers are intended to be optical thicknesses and should not have units. This has been fixed. The layer thicknesses in 
-Example S2 are physical lengths, as indicated.**
+    **These numbers are the inverse of the PM absorption coefficient times the partial pressures of the radiating gas (CO2) in the two regions and could be considered optical path lengths.
+We have corrected this issue in the paper and reword to "The PM absorption coefficient is 27.4 (1/atm*m), which results in optical thicknesses greater than 5.5
+for the domain sizes considered in Example S2."**
+</font>
+
+<font color='green'>
 
@@
 
-   **Sentence has been revised to clarify which files and functions belong to FDS.**
+   **This sentence has been revised to clarify which files and functions belong to FDS.**
 
@@
 
-   **No, they are not equivalent. FDS uses a finite-volume discrete ordinates RTE solver, as specified in the first paragraph of Section 5.1.**
+   **No, they are not equivalent.
+FDS uses the RadCal narrow-band model that depends on a user-specified radiative path length with a default value of 0.1 m.
+This is a geometry-dependent property that is different than a PM coefficient.
+For the radiative solver, FDS uses a finite-volume discrete ordinates RTE solver.
+That is noted in the paper in the first paragraph of Section 5.1.
+We added a note of the path length variable in the revised manuscript.**
+</font>
 
@@
    FDS-default model.
+
+<font color='green'>
 
@@
 be used with any RTE solver. There is no limitation within RadLib that prevents its use with other RTE solvers.**
+</font>

### 2021-09-29 manuscript/manuscript.tex
DOL edits mostly done; todo: R3 comment 1, 9

@@
 Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
-Radiation property models typically consist of correlations between radiative properties and high-resolution spectral databases, reducing the huge amount of spectral data and simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.
+Radiation property models are typically developed as correlations from high-resolution spectral databases, reducing the huge amount of spectral data contained in those databases and simplifying the evaluation of absorption coefficients \cite{Zhang_2002b}.
 
@@
 This model assumes a single gray gas (with no transparent gas) and computes the absorption coefficient as a function of temperature, pressure, and gas composition.
+The PM absorption coefficient is a Planck-function-weighted average absorption coefficient.
 
@@
 In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity.
-The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in calculated optical thicknesses of 0.09 and 0.36 in the thick and thin layers, respectively.
+%
+%DOL: old: The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in calculated optical thicknesses of 0.09 and 0.36 in the thick and thin layers, respectively.
 These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
+%DOL: revised: The PM absorption coefficient is $k_{PM}=27.4$~atm$^{-1}$m$^{-1}$.
+The quantity $(k_{PM}P_{CO_2})^{-1}$ is an optical pathlength with values of 0.09~m and 0.36~m in the thick and thin layers, respectively, which are small compared to the domain sizes greater than 0.5~m that are considered in Example S2.
+%DOL: preferred, below
+The PM absorption coefficient is 27.4~atm$^{-1}$m$^{-1}$, which results in optical thicknesses greater than 5.5
+for the domain sizes considered in Example S2.
+%
+
 Example S3 illustrates that the PM model tends to overpredict radiative heat loss at high temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.
@@
 This was done by editing the \texttt{radi.f90} file in FDS.
-A \texttt{use rad\textunderscore module} statement is included and the FDS functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} are replaced with calls to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}.
+A \texttt{use rad\textunderscore module} statement is included there and the FDS functions \texttt{A\textunderscore WSGG} and \texttt{KAPPA\textunderscore WSGG} are replaced with calls to RadLib's \texttt{get\textunderscore k\textunderscore a\textunderscore oneband}.
 The \texttt{oneband} version was used because FDS does an outer iteration over the bands/gases, computing properties at a given band for each grid point.
@@
 The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL.
+The calculation depends on a user-specified radiation path length variable with a default value of 0.1 m, which is used in the FM Burner validation case.
 Further details are provided in the FDS user guide \cite{FDS}.

### 2021-09-30 submissions/CPC_response_to_reviewers_revision2.md
DOL: comment 1: updating correct p ranges, and discussion

@@
 
+<font color='green'>
 1) The capabilities and limitations of RadLib should be more clearly articulated. For example, different property models
@@
    temperature range for the PM model has been added to its section. Additionally, the RCSLW model section specifies the
-   range of pressures under which the RCSLW model can be applied. A table summarizing these conditions has been added to
-   the beginning of Section 2.**
-
-<font color='green'>
+   range of pressures under which the RCSLW model can be applied.
+The WSGG model has pressure ranges given as the pressure-path length product, which are now    noted in the paper.
+A table summarizing these conditions has been added to the beginning of Section 2 as requested.
+   The models included cannot be used reliably outside the temperature and pressure bounds for which the models were developed.
+In the WSGG model, only the a weights have temperature dependence.
+The model gives a continuing trend as the temperature crosses above the 2400 K bound, up to at least 3000 K, suggesting use of the model up to 3000 K.
+This is true for the applicable range of Mr.
+However, some of the a weights are slightly negative above 2800 K as the upper Mr bound is approached.
+A statement is added to the paper.**
 

### 2021-09-30 manuscript/manuscript.tex
DOL: comment 1: updating correct p ranges, and discussion

@@
 \begin{table}
-\caption{Summary of radiative property models in RadLib.}
+    \caption{Summary of radiative property models and ranges of applicability. For the WSGG model the pressure range is given in terms of the pressure-path length product.}
 \label{t:models}
@@
         \hline
-        Model & T range (K) & P range (atm) & Gas species & Refs.   \\
+        Model & T range                 & P range               & Gas species                            & Refs.   \\
         \hline
-        PM      & 300\textendash 2500 & 1                 & \ce{H2O}, \ce{CO2}, \ce{CO}, \ce{CH4}  &
-        \cite{TNF} \\
-        WSGG    & 300\textendash 2400 & 1                 & \ce{H2O}, \ce{CO2} & \cite{Bordbar_2020,
-            Bordbar_2014} \\
-        RCSLW   & 300\textendash 3000 & 0.1\textendash 50 & \ce{H2O}, \ce{CO2}, \ce{CO} &
-        \cite{Solovjov_2017} \\
+        PM      & 300\textendash 2500 K & 1 atm                 & \ce{H2O}, \ce{CO2}, \ce{CO}, \ce{CH4}  & \cite{TNF} \\
+        WSGG    & 300\textendash 2400 K & 0.01-60 atm$\cdot$m   & \ce{H2O}, \ce{CO2}                     & \cite{Bordbar_2020, Bordbar_2014} \\
+        RCSLW   & 300\textendash 3000 K & 0.1\textendash 50 atm & \ce{H2O}, \ce{CO2}, \ce{CO}            & \cite{Solovjov_2017} \\
         \hline
@@
 For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
-Ultimately, the model accommodates temperatures between 300 K and 2500 K.
+The model accommodates temperatures between 300 K and 2500 K.
 See \cite{TNF} for details and references.
@@
 The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound.
+The $\kappa_j$ values are not temperature dependent.
+The $a_j$ values show a continuing trend as the temperature increases past 2400 K up to 3000 K, suggesting possible use of the model at these temperatures.
+However, some of the $a_j$ become slightly negative above $\sim$2800 K as the upper $M_r$ bound is approached.
+The pressure range of the model is given in terms of the pressure-path length product with values from 0.01-60 atm$\cdot$m.
 The value of $b_{i,j}$ is calculated by

### 2021-10-06 manuscript/manuscript.tex
VBS clarity/style revisions---abstract

@@
 RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
-RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
+RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.
+Several example cases illustrate use of the models with an included ray-tracing solver, compare their accuracy relative to line-by-line (LBL) solutions, and examine their computational costs.
+Additionally, an integrated CFD example of an ethylene burner configuration using Fire Dynamics Simulator (FDS) is provided.
+%Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
 A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS).

### 2021-10-06 manuscript/manuscript.tex
VBS clarity/style revisions---introduction

@@
 Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales.
-Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
-Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
+Accurate radiation modeling often complicates combustion simulations because it can be difficult to implement and computationally expensive relative to the overall simulation cost.
+%Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
+Radiative heat transfer modeling in combustion systems is frequently neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
+%Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
 Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
@@
 The core mechanisms of radiative phenomena are physically and mathematically complex.
-Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
+Unlike other modes of heat transfer, radiation is governed by the radiative transfer equations (RTE), a set of integro-differential equations that depend on both direction and wavelength.
+%Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
 Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model.
-Complexity, implementation, and computational cost of these two parts can vary widely depending on the models chosen.
-The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
+The complexity, implementation, and computational cost of these two parts can vary widely depending on the models chosen.
+For example, the optically thin approximation for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
+%The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
 Similarly, radiation property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
-In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
-RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
-
-For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
+In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and validate.
+%In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
+RadLib addresses the second part of the radiation solver requirements by providing a set of implemented and validated radiation property models that can be applied alongside various solution approaches for the RTE.
+%RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
+
+For an absorbing, emitting, and non-scattering medium (considered here), the RTE solved for the intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
+%For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
 %
@@
 %
-where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
+where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
+%where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
 Solving the RTE requires information about the radiative properties of the materials and media in the system.
-Radiative property data typically takes the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model.
+Radiative property data typically take the form of radiation absorption coefficients $\kappa$, which are provided by a radiation property model.
 Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
@@
 
-The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and is used primarily for model validation.
-Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
+The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and used primarily for model validation.
+%The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and is used primarily for model validation.
+Simple band models rely on estimated or averaged line-of-sight property values that cannot be directly incorporated into the RTE.
+%Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
 %dol
@@
 Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}.
-Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
+Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to obtain
+%Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
 %
@@
 %
-where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
+where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
+%where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
 %
@@
 Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases.
+Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the spectrum for which $\kappa_0=0$.
+%Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases.
 Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$.
-This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
+This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas intensities:
+%This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
 %
@@
 
-The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
+The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field, respectively:
+%The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
 %

### 2021-10-07 manuscript/manuscript.tex
VBS clarity/style revisions---section 2

@@
 
-At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
+At present, RadLib includes three radiation property models of varying complexity: a Planck Mean (PM) absorption coefficients model, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
+%At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
 These models were chosen for their relevance to practical radiative heat transfer simulations.
@@
 
-The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}.
+The version of the PM model implemented in RadLib comes from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
+The workshop includes a number of laboratory jet flames that have been extensively characterized\textemdash including temperature, velocity, and composition profiles\textemdash and serve as target flames against which computational scientists can validate models and simulations.
+%The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}.
 This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
 The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models.
-The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
-For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
-The model accommodates temperatures between 300 K and 2500 K.
-See \cite{TNF} for details and references.
-The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
-The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream.
+The PM model implemented in RadLib is the model advocated by the TNF workshop and, as a result, widely used in turbulent combustion research.
+%The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
+For each chemical species considered, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
+%For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
+The model accommodates temperatures between 300 K and 2500 K and considers the chemical species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
+%The model accommodates temperatures between 300 K and 2500 K. See \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
+\ce{CO}, \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and \ce{H2O}, but the TNF Workshop radiation model includes them because \ce{CH4} and syngas (which consists of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in high concentrations in the fuel streams of several TNF target flames.
+Additionally, \ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.
+%The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream.
 (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
 
-The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
-It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
-The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration.
+The PM model is not as accurate as the other two models considered, as illustrated by the example cases in Section~\ref{s:discussion}.
+%The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
+It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in combustion simulations.
+%It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
+The PM model reportedly overpredicts radiative losses and underpredicts flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the geometric configuration of the simulation.
+%The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration.
 Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.
 
-The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation.
+The PM model is most often used in conjunction with the optically thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation reduces to an algebraic expression and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of reacting flow simulations.
+Many smaller combustion configurations are radiatively thin and experience minimal radiative heat loss; non-sooting laboratory-scale research jet flames, for example, tend to exhibit radiative losses of around 5\%.
+At low levels of radiative heat loss, the accuracy of the radiation model is not as crucial, and simpler radiative property models like the PM model may be appropriate.
+%The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation.
 Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss.
@@
 The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al.
-\citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.
+\citep{Bordbar_2014,Bordbar_2020}, but updated values are used in RadLib.
 
@@
 
-SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed.
+SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases, but differ in the way that the gray gases are constructed.
 In traditional WSGG models, the component gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}.
@@
 For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}.
-The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
+In RadLib, the RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
+%The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
 %
@@
 %
-Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
+Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
+%Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
 

### 2021-10-11 manuscript/manuscript.tex
DOL timing: might also add a norad case later

--- 2021-10-06 manuscript/manuscript.tex
@@
 RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model.
-RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.
-Several example cases illustrate use of the models with an included ray-tracing solver, compare their accuracy relative to line-by-line (LBL) solutions, and examine their computational costs.
-Additionally, an integrated CFD example of an ethylene burner configuration using Fire Dynamics Simulator (FDS) is provided.
-%Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
+RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
 A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS).
@@
 Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions.
-The models produce centerline temperature differences of about 80 K (7\%) between the RCSLW and the WSGG at z=2.5D, and 90 K (12\%) at z=3.5D.
-The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative.
-Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 1.3 kW/m (11\%).
+The models produce maximum radial temperature differences at 1.5R of about 70 K (6\%) between the RCSLW and the WSGG at z=2.5D, and 50 K (6\%) at z=3.5D.
+%The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative. 
+Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 0.94 kW/m (8\%).
 %
@@
 
+The computational cost of the FDS simulations, relative to the default model are 1, 1.68, and 1.71 for the default, WSGG, and RCSLW model, respectively.
+This indicates that the cost is dominated by the radiative solver and not the computation of the radiative properties.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-10-11 notes/fm_burner/plot_T.py

@@ -1,0 +1,60 @@
+
+import numpy as np
+import matplotlib
+matplotlib.use('PDF')       
+import matplotlib.pyplot as plt
+
+########################################################################
+
+#-------------- DEFINE THE DATA TO PLOT (or get it from somewhere)
+
+git = np.loadtxt('fds_test_line_T.csv', delimiter=',')
+wsgg = np.loadtxt('fds_wsgg_line_T.csv', delimiter=',')
+rcslw = np.loadtxt('fds_rcslw_line_T.csv', delimiter=',')
+exp_m_1p5D = np.loadtxt('exp/T_mean_1p5D_exp.csv', delimiter=',')
+exp_m_2p5D = np.loadtxt('exp/T_mean_2p5D_exp.csv', delimiter=',')
+exp_m_3p5D = np.loadtxt('exp/T_mean_3p5D_exp.csv', delimiter=',')
+
+#-------------- SET UP SOME PLOT BOILERPLATE
+
+matplotlib.rcParams.update({'font.size':20, 'figure.autolayout': True}) 
+fig, ax = plt.subplots()
+ax.tick_params(direction='in', top=True, right=True)
+
+########################################################################
+
+
+#-------------- MAKE THE PLOT
+
+plt.cla()
+
+
+
+ax.plot(rcslw[:,0], rcslw[:,6], '-',  color='black', linewidth=1) 
+ax.plot(wsgg[:,0],  wsgg[:,6],  '--', color='black',  linewidth=1) 
+ax.plot(git[:,0],   git[:,6],   ':',  color='black', linewidth=1) 
+ax.plot(exp_m_3p5D[:,0], exp_m_3p5D[:,1], '^',  color='black', ms=5, linewidth=1, fillstyle='none') 
+plt.text(0.5, 1210, "z=2.5D", color='blue')
+
+ax.plot(rcslw[:,0], rcslw[:,4], '-',  color='blue', linewidth=1) 
+ax.plot(wsgg[:,0],  wsgg[:,4],  '--', color='blue',  linewidth=1) 
+ax.plot(git[:,0],   git[:,4],   ':',  color='blue', linewidth=1) 
+ax.plot(exp_m_2p5D[:,0], exp_m_2p5D[:,1], 's',  color='blue', ms=5, linewidth=1, fillstyle='none') 
+plt.text(0.5, 600, "z=3.5D", color='black')
+
[…]

### 2021-10-11 notes/fm_burner/plot_rad.py

@@ -1,0 +1,66 @@
+
+import numpy as np
+import matplotlib
+matplotlib.use('PDF')       
+import matplotlib.pyplot as plt
+
+########################################################################
+
+#-------------- DEFINE THE DATA TO PLOT (or get it from somewhere)
+
+git = np.loadtxt('fds_test_line.csv', delimiter=',')
+wsgg = np.loadtxt('fds_wsgg_line.csv', delimiter=',')
+rcslw = np.loadtxt('fds_rcslw_line.csv', delimiter=',')
+exp_m = np.loadtxt('exp/rad_mean_exp.csv', delimiter=',')
+exp_r = np.loadtxt('exp/rad_rms_exp.csv', delimiter=',')
+
+#-------------- SET UP SOME PLOT BOILERPLATE
+
+matplotlib.rcParams.update({'font.size':20, 'figure.autolayout': True}) 
+fig, ax = plt.subplots()
+ax.tick_params(direction='in', top=True, right=True)
+
+########################################################################
+
+
+#-------------- MAKE THE PLOT
+
+plt.cla()
+
+ax.plot(rcslw[:,1], rcslw[:,0], '-',  color='black', linewidth=1) 
+ax.plot(wsgg[:,1],  wsgg[:,0],  '--', color='black',  linewidth=1) 
+ax.plot(git[:,1],   git[:,0],   ':',  color='black', linewidth=1) 
+ax.plot(exp_m[:,0], exp_m[:,1], 'o',  color='black', linewidth=1, fillstyle='none') 
+
+ax.set_xlabel("Radiative Emission (kW/m)", fontsize=22)
+ax.set_ylabel("Height (cm)",               fontsize=22)
+ax.set_xlim([0,15])
+ax.set_ylim([0,90])
+
+ax.legend(['RCSLW', 'WSGG', 'FDS default', 'Exp'], loc='upper right', frameon=False, fontsize=16)
+
+#-------------- SAVE PLOT TO FILE CALLED plot.pdf (the ".pdf" is left off below)
+
+plt.savefig("plot_rad_mean")
+
+########################################################################
+
+plt.cla()
+
+#-------------- MAKE THE PLOT
+
+ax.plot(rcslw[:,2], rcslw[:,0], '-',  color='black', linewidth=1) 
+ax.plot(wsgg[:,2],  wsgg[:,0],  '--', color='black',  linewidth=1) 
[…]

### 2021-10-11 submissions/CPC_response_to_reviewers_revision2.md

@@
 
+   **FDS simulations were rerun.
+The cost of the FDS simulations relative to the FDS default radiative case is 1, 1.68, and 1.71, for the default, WSGG, and RCSLW, respectively.
+This has been added to the paper with a note that the small difference between the WSGG and RCSLW costs imply that the cost is dominated by the solver rather than the property model.
+The corresponding results plots were updated.**
+
 <font color='green'>

### 2021-10-18 manuscript/manuscript.tex
DOL: accepting VBS edits, deleting commented old version

@@
 Additionally, an integrated CFD example of an ethylene burner configuration using Fire Dynamics Simulator (FDS) is provided.
-%Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions.
-A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS).
-The computational cost of the models is compared.
 RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
@@
 Accurate radiation modeling often complicates combustion simulations because it can be difficult to implement and computationally expensive relative to the overall simulation cost.
-%Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost.
 Radiative heat transfer modeling in combustion systems is frequently neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
-%Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures~\citep{Modest_2016}.
 Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}.
@@
 The core mechanisms of radiative phenomena are physically and mathematically complex.
-Unlike other modes of heat transfer, radiation is governed by the radiative transfer equations (RTE), a set of integro-differential equations that depend on both direction and wavelength.
-%Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE).
+Unlike other modes of heat transfer, radiation is governed by the radiative transfer equation (RTE), an integro-differential equation that depend on both direction and wavelength.
 Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model.
@@
 For example, the optically thin approximation for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
-%The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved.
 Similarly, radiation property models range from simple correlations for computing mean absorption coefficients to gray gas models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
 In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and validate.
-%In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
 RadLib addresses the second part of the radiation solver requirements by providing a set of implemented and validated radiation property models that can be applied alongside various solution approaches for the RTE.
-%RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.
 
 For an absorbing, emitting, and non-scattering medium (considered here), the RTE solved for the intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
-%For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
 %
@@
 where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
-%where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length along direction $\mathbf{s}$.
 Solving the RTE requires information about the radiative properties of the materials and media in the system.
@@
 The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and used primarily for model validation.
-%The direct solution of the spectral RTE using so-called line-by-line calculations, in which the RTE is solved for each individual spectral line, is computationally prohibitive for most practical configurations and is used primarily for model validation.
 Simple band models rely on estimated or averaged line-of-sight property values that cannot be directly incorporated into the RTE.
-%Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly incorporated into the RTE.
-%dol
 Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of RTE evaluations \citep{Modest_2016}.
@@
 Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to obtain
-%Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
 %
@@
 where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
-%where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
 %
@@
 Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the spectrum for which $\kappa_0=0$.
-%Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases.
-Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$.
 This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas intensities:
-%This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
 %
@@
 The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field, respectively:
-%The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
 %
@@
 At present, RadLib includes three radiation property models of varying complexity: a Planck Mean (PM) absorption coefficients model, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
-%At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model.
 These models were chosen for their relevance to practical radiative heat transfer simulations.
@@
 The version of the PM model implemented in RadLib comes from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
-The workshop includes a number of laboratory jet flames that have been extensively characterized\textemdash including temperature, velocity, and composition profiles\textemdash and serve as target flames against which computational scientists can validate models and simulations.
-%The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}.
-This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}.
-The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models.
+The workshop includes a number of laboratory jet flames that have been extensively characterized\textemdash including temperature, velocity, and composition profile measurements\textemdash and serve as target flames against which models and simulations can be validated.
 The PM model implemented in RadLib is the model advocated by the TNF workshop and, as a result, widely used in turbulent combustion research.
-%The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.
 For each chemical species considered, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
-%For each species, the PM model provides the absorption coefficient as a fourth or fifth order polynomial fit in one of two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
 The model accommodates temperatures between 300 K and 2500 K and considers the chemical species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
-%The model accommodates temperatures between 300 K and 2500 K. See \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
-\ce{CO}, \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and \ce{H2O}, but the TNF Workshop radiation model includes them because \ce{CH4} and syngas (which consists of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in high concentrations in the fuel streams of several TNF target flames.
-Additionally, \ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.
-%The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames in high concentrations in the fuel stream.
-(\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)
+\ce{CO} and \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and \ce{H2O}, but the TNF Workshop radiation model includes them because \ce{CH4} and syngas (which consists of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in high concentrations in the fuel streams of several TNF target flames.
+\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.
 
 The PM model is not as accurate as the other two models considered, as illustrated by the example cases in Section~\ref{s:discussion}.
-%The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
 It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in combustion simulations.
-%It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
 The PM model reportedly overpredicts radiative losses and underpredicts flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the geometric configuration of the simulation.
-%The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration.
 Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.
@@
 The PM model is most often used in conjunction with the optically thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation reduces to an algebraic expression and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of reacting flow simulations.
-Many smaller combustion configurations are radiatively thin and experience minimal radiative heat loss; non-sooting laboratory-scale research jet flames, for example, tend to exhibit radiative losses of around 5\%.
+Many smaller combustion configurations are radiatively thin and experience low radiative heat loss; non-sooting laboratory-scale research jet flames, for example, tend to exhibit radiative losses of around 5\%.
 At low levels of radiative heat loss, the accuracy of the radiation model is not as crucial, and simpler radiative property models like the PM model may be appropriate.
-%The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation.
-Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss.
-It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%.
-At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.
 
@@
 In RadLib, the RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
-%The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
 %
@@
 Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
-%Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.
 

### 2021-10-23 submissions/revision_2/manuscript.tex
revision_2 submitted; radlib code used is in submissions/revision_2

--- 2021-10-18 manuscript/manuscript.tex
@@
 Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib (both using four gray gases and one clear gas).
+A case with no radiative model is also included.
 The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL.
@@
 Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions.
-The models produce maximum radial temperature differences at 1.5R of about 70 K (6\%) between the RCSLW and the WSGG at z=2.5D, and 50 K (6\%) at z=3.5D.
+The models produce maximum radial temperature differences at 1.5R of 86 K (7\%) at z=2.5D, and 71 K (9\%) at z=3.5D.
 %The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative. 
-Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 0.94 kW/m (8\%).
+Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 1.4 kW/m (10\%).
 %
@@
 
-The computational cost of the FDS simulations, relative to the default model are 1, 1.68, and 1.71 for the default, WSGG, and RCSLW model, respectively.
-This indicates that the cost is dominated by the radiative solver and not the computation of the radiative properties.
+The computational costs of the FDS simulations, relative to the case with no radiation are 1, 1.04, 1.62, and 2.18 for the no radiation, default, WSGG, and RCSLW model, respectively. 
+%This indicates that the cost is dominated by the radiative solver and not the computation of the radiative properties.
 

### 2021-10-23 notes/fm_burner/revision_2/plot_T.py

@@ -1,60 +1,0 @@
-
-import numpy as np
-import matplotlib
-matplotlib.use('PDF')       
-import matplotlib.pyplot as plt
-
-########################################################################
-
-#-------------- DEFINE THE DATA TO PLOT (or get it from somewhere)
-
-git = np.loadtxt('default_line_T.csv', delimiter=',')
-wsgg = np.loadtxt('wsgg_line_T.csv', delimiter=',')
-rcslw = np.loadtxt('rcslw_line_T.csv', delimiter=',')
-exp_m_1p5D = np.loadtxt('T_mean_1p5D_exp.csv', delimiter=',')
-exp_m_2p5D = np.loadtxt('T_mean_2p5D_exp.csv', delimiter=',')
-exp_m_3p5D = np.loadtxt('T_mean_3p5D_exp.csv', delimiter=',')
-
-#-------------- SET UP SOME PLOT BOILERPLATE
-
-matplotlib.rcParams.update({'font.size':20, 'figure.autolayout': True}) 
-fig, ax = plt.subplots()
-ax.tick_params(direction='in', top=True, right=True)
-
-########################################################################
-
-
-#-------------- MAKE THE PLOT
-
-plt.cla()
-
-
-
-ax.plot(rcslw[:,0], rcslw[:,6], '-',  color='black', linewidth=1) 
-ax.plot(wsgg[:,0],  wsgg[:,6],  '--', color='black',  linewidth=1) 
-ax.plot(git[:,0],   git[:,6],   ':',  color='black', linewidth=1) 
-ax.plot(exp_m_3p5D[:,0], exp_m_3p5D[:,1], '^',  color='black', ms=5, linewidth=1, fillstyle='none') 
-plt.text(0.5, 1220, "z=2.5D", color='blue')
-
-ax.plot(rcslw[:,0], rcslw[:,4], '-',  color='blue', linewidth=1) 
-ax.plot(wsgg[:,0],  wsgg[:,4],  '--', color='blue',  linewidth=1) 
-ax.plot(git[:,0],   git[:,4],   ':',  color='blue', linewidth=1) 
-ax.plot(exp_m_2p5D[:,0], exp_m_2p5D[:,1], 's',  color='blue', ms=5, linewidth=1, fillstyle='none') 
-plt.text(0.5, 600, "z=3.5D", color='black')
-
[…]

### 2021-10-23 notes/fm_burner/revision_2/plot_rad.py

@@ -1,66 +1,0 @@
-
-import numpy as np
-import matplotlib
-matplotlib.use('PDF')       
-import matplotlib.pyplot as plt
-
-########################################################################
-
-#-------------- DEFINE THE DATA TO PLOT (or get it from somewhere)
-
-git = np.loadtxt('default_line.csv', delimiter=',')
-wsgg = np.loadtxt('wsgg_line.csv', delimiter=',')
-rcslw = np.loadtxt('rcslw_line.csv', delimiter=',')
-exp_m = np.loadtxt('rad_mean_exp.csv', delimiter=',')
-exp_r = np.loadtxt('rad_rms_exp.csv', delimiter=',')
-
-#-------------- SET UP SOME PLOT BOILERPLATE
-
-matplotlib.rcParams.update({'font.size':20, 'figure.autolayout': True}) 
-fig, ax = plt.subplots()
-ax.tick_params(direction='in', top=True, right=True)
-
-########################################################################
-
-
-#-------------- MAKE THE PLOT
-
-plt.cla()
-
-ax.plot(rcslw[:,1], rcslw[:,0], '-',  color='black', linewidth=1) 
-ax.plot(wsgg[:,1],  wsgg[:,0],  '--', color='black',  linewidth=1) 
-ax.plot(git[:,1],   git[:,0],   ':',  color='black', linewidth=1) 
-ax.plot(exp_m[:,0], exp_m[:,1], 'o',  color='black', linewidth=1, fillstyle='none') 
-
-ax.set_xlabel("Radiative Emission (kW/m)", fontsize=22)
-ax.set_ylabel("Height (cm)",               fontsize=22)
-ax.set_xlim([0,15])
-ax.set_ylim([0,90])
-
-ax.legend(['RCSLW', 'WSGG', 'FDS default', 'Exp'], loc='upper right', frameon=False, fontsize=16)
-
-#-------------- SAVE PLOT TO FILE CALLED plot.pdf (the ".pdf" is left off below)
-
-plt.savefig("plot_rad_mean")
-
-########################################################################
-
-plt.cla()
-
-#-------------- MAKE THE PLOT
-
-ax.plot(rcslw[:,2], rcslw[:,0], '-',  color='black', linewidth=1) 
-ax.plot(wsgg[:,2],  wsgg[:,0],  '--', color='black',  linewidth=1) 
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Build/mpi_intel_linux_64_db/make_fds.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+dir=`pwd`
+target=${dir##*/}
+
+../Scripts/save_fdsinfo.sh
+echo Building $target
+make -j4 VPATH="../../Source" -f ../makefile $target

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/cons.f90

@@ -1,0 +1,791 @@
+!> \brief Global constants, parameters, variables
+!>
+!> \details Each MPI process stores a copy of the GLOBAL_CONSTANTS. It cannot be
+!> assumed that these values are same for each MPI process.
+
+MODULE GLOBAL_CONSTANTS
+
+USE PRECISION_PARAMETERS
+USE MPI_F08
+USE ISO_FORTRAN_ENV, ONLY: ERROR_UNIT
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+INTEGER, PARAMETER :: DNS_MODE=1                 !< Flag for SIM_MODE: Direct Numerical Simulation
+INTEGER, PARAMETER :: LES_MODE=2                 !< Flag for SIM_MODE: Large Eddy Simulation
+INTEGER, PARAMETER :: VLES_MODE=3                !< Flag for SIM_MODE: Very Large Eddy Simulation
+INTEGER, PARAMETER :: SVLES_MODE=4               !< Flag for SIM_MODE: Simple Very Large Eddy Simulation
+
+INTEGER, PARAMETER :: GAS_SPECIES=2              !< Flag for SPECIES\%MODE indicating a gaseous species
+INTEGER, PARAMETER :: AEROSOL_SPECIES=3          !< Flag for SPECIES\%MODE indicating an aerosol species
+
+INTEGER, PARAMETER :: EXPLICIT_EULER=1           !< Flag for COMBUSTION_ODE_SOLVER: explicit first-order Euler
+INTEGER, PARAMETER :: RK2=2                      !< Flag for COMBUSTION_ODE_SOLVER: second-order Runge-Kutta
+INTEGER, PARAMETER :: RK3=3                      !< Flag for COMBUSTION_ODE_SOLVER: third-order Runge-Kutta
+INTEGER, PARAMETER :: RK2_RICHARDSON=4           !< Flag for COMBUSTION_ODE_SOLVER: second-order Runge-Kutta, Richardson extrap.
+
+INTEGER, PARAMETER :: EXTINCTION_1=1             !< Flag for EXTINCT_MOD (EXTINCTION MODEL 1)
+INTEGER, PARAMETER :: EXTINCTION_2=2             !< Flag for EXTINCT_MOD (EXTINCTION MODEL 2)
+
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/ctrl.f90

@@ -1,0 +1,803 @@
+!> Routines for evaluating control functions
+   
+MODULE CONTROL_FUNCTIONS
+
+USE PRECISION_PARAMETERS
+USE CONTROL_VARIABLES
+USE GLOBAL_CONSTANTS, ONLY : DO_EVACUATION,EVACUATION_ONLY,UPDATE_DEVICES_AGAIN
+USE DEVICE_VARIABLES
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+CONTAINS
+
+!> Updates the state of all control functions followed by DEVC where QUANTITY is CONTROL or CONTROL VALUE   
+!>
+!> \param T Current time (s)
+!> \param DT Current time step (s)
+!> \param CTRL_STOP_STATUS Flag for a contorl function stopping the FDS calculation
+!> \param RUN_START Flag indicating subroutine call is during initialization
+
+SUBROUTINE UPDATE_CONTROLS(T,DT,CTRL_STOP_STATUS,RUN_START)
+
+REAL(EB), INTENT(IN) :: T,DT
+INTEGER :: NC,N
+LOGICAL :: CTRL_STOP_STATUS
+LOGICAL, INTENT(IN) :: RUN_START
+TYPE(DEVICE_TYPE), POINTER :: DV=>NULL()
+
+CTRL_STOP_STATUS = .FALSE.
+
+CONTROL_LOOP_1: DO NC=1,N_CTRL
+   IF (.NOT. RUN_START .AND. CONTROL(NC)%LATCH .AND. (CONTROL(NC)%INITIAL_STATE .NEQV. CONTROL(NC)%CURRENT_STATE)) THEN
+      CONTROL(NC)%UPDATED = .TRUE.
+      CONTROL(NC)%PRIOR_STATE = CONTROL(NC)%CURRENT_STATE
+   ELSE
+      CONTROL(NC)%UPDATED = .FALSE.
+   ENDIF
+END DO CONTROL_LOOP_1
+CONTROL_LOOP_2: DO NC=1,N_CTRL
+   IF (CONTROL(NC)%UPDATED) CYCLE CONTROL_LOOP_2
+   IF (DO_EVACUATION) CYCLE CONTROL_LOOP_2
+   CALL EVALUATE_CONTROL(T,NC,DT,CTRL_STOP_STATUS)
+END DO CONTROL_LOOP_2
+
+! Update devices that are used to print out control function results only for devices that require an 'INSTANT VALUE';
+! that is, a value from this current time step.
+
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/data.f90

@@ -1,0 +1,4574 @@
+MODULE OUTPUT_DATA
+
+! Output quantity arrays
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS, ONLY: CELL_CENTER
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+INTEGER, PARAMETER :: N_Q_DOT=8
+INTEGER :: PLOT3D_QUANTITY_INDEX(5),PLOT3D_Y_INDEX(5)=0,PLOT3D_Z_INDEX(5)=0,PLOT3D_PART_INDEX(5),&
+           SMOKE3D_QUANTITY_INDEX(4),SMOKE3D_Y_INDEX(4)=0,SMOKE3D_Z_INDEX(4)=0,PLOT3D_VELO_INDEX(5)=0
+CHARACTER(LABEL_LENGTH) :: PLOT3D_QUANTITY(5),PLOT3D_SPEC_ID(5),PLOT3D_PART_ID(5),PLOT3D_SMOKEVIEW_BAR_LABEL(5),&
+                 SMOKE3D_QUANTITY(4),SMOKE3D_SPEC_ID(4),SMOKE3D_SMOKEVIEW_BAR_LABEL(4)
+CHARACTER(LABEL_LENGTH) :: PLOT3D_SMOKEVIEW_LABEL(5),SMOKE3D_SMOKEVIEW_LABEL(4)
+INTEGER :: N_BNDF,N_ISOF,N_PROF,N_SLCF_MAX=0
+REAL(EB) :: T_LAST_DUMP_HRR,T_LAST_DUMP_MASS,T_LAST_DUMP_MOM
+REAL(EB),ALLOCATABLE, DIMENSION(:) :: ENTHALPY_SUM
+REAL(EB),ALLOCATABLE, DIMENSION(:,:) :: MASS_DT,Q_DOT,Q_DOT_SUM,M_DOT,M_DOT_SUM
+
+TYPE OUTPUT_QUANTITY_TYPE
+   CHARACTER(LABEL_LENGTH) :: NAME='null',OLD_NAME='null',SHORT_NAME='null',UNITS='null'
+   REAL(EB) :: AMBIENT_VALUE=0._EB
+   INTEGER :: IOR=0,CELL_POSITION=CELL_CENTER
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/devc.f90

@@ -1,0 +1,203 @@
+!> \brief Derived variable types for devices
+
+MODULE DEVICE_VARIABLES
+
+USE PRECISION_PARAMETERS
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+INTEGER, ALLOCATABLE, DIMENSION(:) :: DEVC_PIPE_OPERATING
+
+!> \brief Derived type storing inputs for the PROP namelist group
+
+TYPE PROPERTY_TYPE
+   REAL(EB) :: DENSITY,DIAMETER,EMISSIVITY,HEAT_TRANSFER_COEFFICIENT,SPECIFIC_HEAT,RTI, &
+               ACTIVATION_TEMPERATURE,ACTIVATION_OBSCURATION, &
+               ALPHA_E,ALPHA_C,BETA_E,BETA_C,CHARACTERISTIC_VELOCITY,PARTICLE_VELOCITY,MASS_FLOW_RATE,FLOW_RATE,FLOW_TAU, &
+               GAUGE_EMISSIVITY,GAUGE_TEMPERATURE,INITIAL_TEMPERATURE,K_FACTOR,C_FACTOR,OPERATING_PRESSURE,OFFSET,&
+               SPRAY_ANGLE(2,2),P0=0._EB,PX(3)=0._EB,PXX(3,3)=0._EB
+   INTEGER  :: PDPA_M=0,PDPA_N=0,N_SMOKEVIEW_PARAMETERS=0,N_SMOKEVIEW_IDS=0,N_INSERT,I_VEL=0,PARTICLES_PER_SECOND
+   LOGICAL  :: PDPA_INTEGRATE=.TRUE.,PDPA_NORMALIZE=.TRUE.,HISTOGRAM_NORMALIZE=.TRUE.,HISTOGRAM=.FALSE., &
+               HISTOGRAM_CUMULATIVE=.FALSE.
+   REAL(EB) :: PDPA_START=0._EB,PDPA_END=1.E6_EB,PDPA_RADIUS=0.1_EB
+   REAL(EB), ALLOCATABLE, DIMENSION(:) :: TABLE_ROW, V_FACTOR
+   INTEGER  :: PART_INDEX=-1,FLOW_RAMP_INDEX,SPRAY_PATTERN_INDEX,Z_INDEX=-999,Y_INDEX=-999,PRESSURE_RAMP_INDEX
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/divg.f90

@@ -1,0 +1,1804 @@
+MODULE DIVG
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+
+PUBLIC DIVERGENCE_PART_1,DIVERGENCE_PART_2,CHECK_DIVERGENCE
+
+CONTAINS
+
+SUBROUTINE DIVERGENCE_PART_1(T,DT,NM)
+
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME
+USE MATH_FUNCTIONS, ONLY: EVALUATE_RAMP,INTERPOLATE1D_UNIFORM,SCALAR_FACE_VALUE
+USE PHYSICAL_FUNCTIONS, ONLY: GET_CONDUCTIVITY,GET_SPECIFIC_HEAT,GET_SENSIBLE_ENTHALPY_Z,GET_SENSIBLE_ENTHALPY,&
+                              GET_VISCOSITY,GET_MOLECULAR_WEIGHT
+USE GEOMETRY_FUNCTIONS, ONLY: ASSIGN_PRESSURE_ZONE
+USE MANUFACTURED_SOLUTIONS, ONLY: DIFF_MMS,UF_MMS,WF_MMS,VD2D_MMS_Z_SRC !,RHO_0_MMS,RHO_1_MMS
+USE EVAC, ONLY: EVAC_EMESH_EXITS_TYPE, EMESH_EXITS, EMESH_NFIELDS, N_EXITS, N_CO_EXITS, N_DOORS
+USE COMPLEX_GEOMETRY, ONLY : IBM_CGSC, IBM_IDCC, IBM_IDCF, IBM_SOLID, IBM_CUTCFE
+USE CC_SCALARS_IBM, ONLY : SET_EXIMDIFFLX_3D,SET_DOMAINDIFFLX_3D,SET_EXIMRHOHSLIM_3D,SET_EXIMRHOZZLIM_3D,&
+                           CCREGION_DIVERGENCE_PART_1,CFACE_PREDICT_NORMAL_VELOCITY
+
+! Compute contributions to the divergence term
+
+INTEGER, INTENT(IN) :: NM
+REAL(EB), INTENT(IN) :: T,DT
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/fire.f90

@@ -1,0 +1,1349 @@
+MODULE FIRE
+
+! Compute combustion
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME
+USE SOOT_ROUTINES, ONLY: SOOT_SURFACE_OXIDATION
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+PRIVATE
+
+PUBLIC COMBUSTION,COMBUSTION_BC,CONDENSATION_EVAPORATION
+
+CONTAINS
+
+SUBROUTINE COMBUSTION(T,DT,NM)
+
+INTEGER, INTENT(IN) :: NM
+REAL(EB), INTENT(IN) :: T,DT
+REAL(EB) :: TNOW
+
+IF (EVACUATION_ONLY(NM)) RETURN
+
+TNOW=CURRENT_TIME()
+
+CALL POINT_TO_MESH(NM)
+
+Q     = 0._EB
+CHI_R = 0._EB
+
+! Call combustion ODE solver
+
+CALL COMBUSTION_GENERAL(T,DT)
+
+! Combustion in cut-cells:
+! Time used for combustion in cut-cells is added to GEOM timing T_USED(14) in CCREGION_COMBUSTION.
+
+IF (CC_IBM) CALL CCREGION_COMBUSTION(T,DT,NM)
+
+! Soot oxidation routine
+
+IF (DEPOSITION .AND. SOOT_OXIDATION) CALL SOOT_SURFACE_OXIDATION(DT,NM)
+
+T_USED(10)=T_USED(10)+CURRENT_TIME()-TNOW
+END SUBROUTINE COMBUSTION
+
+
+SUBROUTINE COMBUSTION_GENERAL(T,DT)
+
+! Generic combustion routine for multi-step reactions
+
+USE PHYSICAL_FUNCTIONS, ONLY: GET_SPECIFIC_GAS_CONSTANT,GET_MASS_FRACTION_ALL,GET_SPECIFIC_HEAT,GET_MOLECULAR_WEIGHT, &
+                              GET_SENSIBLE_ENTHALPY_Z,IS_REALIZABLE,LES_FILTER_WIDTH_FUNCTION
+USE COMPLEX_GEOMETRY, ONLY : IBM_CGSC, IBM_GASPHASE
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/func.f90

@@ -1,0 +1,4989 @@
+#ifndef GITHASH_PP
+#define GITHASH_PP "unknown"
+#endif
+#ifndef GITDATE_PP
+#define GITDATE_PP "unknown"
+#endif
+#ifndef BUILDDATE_PP
+#define BUILDDATE_PP "unknown"
+#endif
+
+!> \brief A collection of utility routines used throughout FDS.
+
+MODULE COMP_FUNCTIONS
+
+USE PRECISION_PARAMETERS
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+CONTAINS
+
+
+!> \brief Returns the wall clock time in seconds.
+
+REAL(EB) FUNCTION CURRENT_TIME()
+USE MPI_F08
+CURRENT_TIME = MPI_WTIME()
+END FUNCTION CURRENT_TIME
+
+!> \brief Return the current time and date in ISO_8601 format.
+!> \param DATE A character string containing the date and time of day.
+
+SUBROUTINE GET_DATE_ISO_8601(DATE)
+
+INTEGER :: VALUES(8)
+CHARACTER(LABEL_LENGTH), INTENT(OUT) :: DATE
+INTEGER :: HOURS_TZ
+INTEGER :: MINUTES_TZ
+
+CALL DATE_AND_TIME(VALUES=VALUES)
+
+HOURS_TZ = VALUES(4)/60
+MINUTES_TZ = MOD(VALUES(4),60)
+
+WRITE(DATE,'(I4.4,"-",I2.2,"-",I2.2,"T",I2.2,":",I2.2,":",I2.2,".",I3.3,SP,I3.2,":",SS,I2.2)') &
+        VALUES(1), &
+        VALUES(2), VALUES(3), VALUES(5), VALUES(6), VALUES(7), &
+        VALUES(8), HOURS_TZ, ABS(MINUTES_TZ)
+
+END SUBROUTINE GET_DATE_ISO_8601
+
+
+!> \brief Return the current time and date
+!> \param DATE A character string containing the date and time of day
+
+SUBROUTINE GET_DATE(DATE)
+
+INTEGER :: DATE_TIME(8)
+CHARACTER(10) :: BIG_BEN(3),MONTH
+CHARACTER(LABEL_LENGTH), INTENT(OUT) :: DATE
+
+CALL DATE_AND_TIME(BIG_BEN(1),BIG_BEN(2),BIG_BEN(3),DATE_TIME)
+
+SELECT CASE(DATE_TIME(2))
+   CASE(1)
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/hvac.f90

@@ -1,0 +1,3483 @@
+!> \brief Compute the HVAC mass and energy transport
+!> \details Module contains routines to read the HVAC namelist inputs, intialize the HVAC solver, and solve
+!> the flow for each timestep. Note that the HVAC solver is only called for the first MPI process. This requires
+!> that HVAC boundary conditions at VENTs be aggregated over MPI processes and that the HVAC solution 
+!> be shared with all MPI processes.
+   
+MODULE HVAC_ROUTINES
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+USE DEVICE_VARIABLES
+USE CONTROL_VARIABLES
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME, CHECKREAD, SHUTDOWN
+USE MEMORY_FUNCTIONS, ONLY: ChkMemErr
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+PRIVATE
+
+REAL(EB) :: DT_HV !< Size of subtimestep used in HVAC solver
+REAL(EB) :: DT_MT !< Size of subtimestep used in 1D mass+energy transport solver
+CHARACTER(LABEL_LENGTH), ALLOCATABLE, DIMENSION(:,:) :: NODE_DUCT_A  !< Temporary array storing DUCT_ID inputs for NODEs
+CHARACTER(LABEL_LENGTH), ALLOCATABLE, DIMENSION(:,:) :: DUCT_NODE_A  !< Temporary array storing NODE_ID inputs for DUCTs
+CHARACTER(LABEL_LENGTH), ALLOCATABLE, DIMENSION(:) :: NODE_FILTER_A  !< Temporary array storing FILTER_ID inputs for NODEs
+CHARACTER(LABEL_LENGTH), ALLOCATABLE, DIMENSION(:) :: DUCT_FAN_A     !< Temporary array storing FAN_ID inputs for DUCTs
+CHARACTER(LABEL_LENGTH), ALLOCATABLE, DIMENSION(:) :: DUCT_AIRCOIL_A !< Temporary array storing AIRCOIL_ID inputs for DUCTS
+INTEGER :: LEAK_DUCTS = 0 !< Number of ducts used for leakage
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/init.f90

@@ -1,0 +1,3819 @@
+MODULE INIT
+
+! Allocate numerous arrays and perform miscellaneous initializations
+
+USE PRECISION_PARAMETERS
+USE MESH_VARIABLES
+USE MESH_POINTERS
+USE GLOBAL_CONSTANTS
+USE OUTPUT_DATA
+USE TRAN
+USE MEMORY_FUNCTIONS, ONLY : CHKMEMERR
+USE DEVICE_VARIABLES
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+PRIVATE
+
+PUBLIC INITIALIZE_MESH_VARIABLES_1,INITIALIZE_MESH_VARIABLES_2,INITIALIZE_GLOBAL_VARIABLES, &
+       OPEN_AND_CLOSE,INITIAL_NOISE,UVW_INIT,INITIALIZE_DEVICES,INITIALIZE_PROFILES,REASSIGN_WALL_CELLS
+
+CONTAINS
+
+
+SUBROUTINE INITIALIZE_MESH_VARIABLES_1(DT,NM)
+
+USE PHYSICAL_FUNCTIONS, ONLY: GET_VISCOSITY,GET_SPECIFIC_GAS_CONSTANT,GET_SPECIFIC_HEAT,LES_FILTER_WIDTH_FUNCTION,&
+                              COMPUTE_WIND_COMPONENTS
+USE MEMORY_FUNCTIONS, ONLY: COMPUTE_ONE_D_STORAGE_DIMENSIONS,COMPUTE_BOUNDARY_PROPERTY_STORAGE_DIMENSIONS,&
+                            COMPUTE_PARTICLE_STORAGE_DIMENSIONS,COMPUTE_WALL_STORAGE_DIMENSIONS,&
+                            COMPUTE_CFACE_STORAGE_DIMENSIONS,COMPUTE_BOUNDARY_COORD_STORAGE_DIMENSIONS
+USE GEOMETRY_FUNCTIONS, ONLY: ASSIGN_HT3D_WALL_INDICES
+USE RADCONS, ONLY: UIIDIM
+USE CONTROL_VARIABLES
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/main.f90

@@ -1,0 +1,4427 @@
+!> \brief FDS is a computational fluid dynamics (CFD) code designed to model
+!> fire and other thermal phenomena.
+
+PROGRAM FDS
+
+! Fire Dynamics Simulator, Main Program, Multiple CPU version.
+
+USE PRECISION_PARAMETERS
+USE MESH_VARIABLES
+USE GLOBAL_CONSTANTS
+USE TRAN
+USE DUMP
+USE READ_INPUT
+USE INIT
+USE DIVG
+USE PRES
+USE MASS
+USE PART
+USE VEGE
+USE VELO
+USE RAD
+USE RADCONS, ONLY : DLN
+USE OUTPUT_DATA
+USE MEMORY_FUNCTIONS
+USE HVAC_ROUTINES
+USE COMP_FUNCTIONS, ONLY : CURRENT_TIME
+USE DEVICE_VARIABLES
+USE WALL_ROUTINES
+USE FIRE
+USE CONTROL_FUNCTIONS
+USE EVAC
+USE TURBULENCE, ONLY: NS_ANALYTICAL_SOLUTION,INIT_TURB_ARRAYS,COMPRESSION_WAVE,&
+                      TWOD_VORTEX_CERFACS,TWOD_VORTEX_UMD,TWOD_SOBOROT_UMD, &
+                      SYNTHETIC_TURBULENCE,SYNTHETIC_EDDY_SETUP,SANDIA_DAT
+USE MANUFACTURED_SOLUTIONS, ONLY: SHUNN_MMS_3,SAAD_MMS_1
+USE CC_SCALARS_IBM,   ONLY: CCIBM_SET_DATA,CCIBM_END_STEP,CCREGION_DENSITY,CCIBM_TARGET_VELOCITY, &
+                            CHECK_SPEC_TRANSPORT_CONSERVE,MASS_CONSERVE_INIT,CCIBM_RHO0W_INTERP,  &
+                            CCCOMPUTE_RADIATION,CCIBM_NO_FLUX,CCIBM_COMPUTE_VELOCITY_ERROR,       &
+                            FINISH_CCIBM,INIT_CUTCELL_DATA,LINEARFIELDS_INTERP_TEST,              &
+                            MESH_CC_EXCHANGE,ROTATED_CUBE_ANN_SOLN
+USE OPENMP
+USE MPI_F08
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/mass.f90

@@ -1,0 +1,768 @@
+MODULE MASS
+
+! Compute the mass equation differences
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+
+REAL(EB), POINTER, DIMENSION(:,:,:) :: UU,VV,WW,RHOP
+
+PUBLIC MASS_FINITE_DIFFERENCES,DENSITY
+
+CONTAINS
+
+
+SUBROUTINE MASS_FINITE_DIFFERENCES(NM)
+
+! Compute spatial differences for density equation
+
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME
+USE GLOBAL_CONSTANTS, ONLY: N_TOTAL_SCALARS,PREDICTOR,DO_EVACUATION,SOLID_PHASE_ONLY,T_USED
+USE MATH_FUNCTIONS, ONLY: SCALAR_FACE_VALUE
+
+INTEGER, INTENT(IN) :: NM
+REAL(EB) :: TNOW,ZZZ(1:4)
+REAL(EB), PARAMETER :: DUMMY=0._EB
+INTEGER  :: I,J,K,N,IOR,IW,IIG,JJG,KKG,II,JJ,KK
+REAL(EB), POINTER, DIMENSION(:,:,:,:) :: ZZP=>NULL()
+REAL(EB), POINTER, DIMENSION(:,:,:) :: RHO_Z_P=>NULL()
+LOGICAL :: THIN_OBSTRUCTION
+TYPE(WALL_TYPE), POINTER :: WC=>NULL()
+
+IF (DO_EVACUATION .OR. SOLID_PHASE_ONLY) RETURN
+
+TNOW=CURRENT_TIME()
+CALL POINT_TO_MESH(NM)
+
+IF (PREDICTOR) THEN
+   UU => U
+   VV => V
+   WW => W
+   RHOP => RHO
+   ZZP => ZZ
+ELSE
+   UU => US
+   VV => VS
+   WW => WS
+   RHOP => RHOS
+   ZZP => ZZS
+ENDIF
+
+! Reset counter for CLIP_RHOMIN, CLIP_RHOMAX
+! Done here so DT_RESTRICT_COUNT will persist until WRITE_DIAGNOSTICS is called
+
+IF (PREDICTOR) DT_RESTRICT_COUNT = 0
+
+! Species face values
+
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/mesh.f90

@@ -1,0 +1,853 @@
+!> \brief Variables that are defined on each mesh.
+
+MODULE MESH_VARIABLES
+
+USE PRECISION_PARAMETERS
+USE TYPES
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+!> \brief Derived type containing the bulk of the variables defined on each mesh.
+!>
+!> \details The variables listed in this module are defined on each mesh that is
+!> owned by a given MPI process. For example, MESHES(NM)%U(I,J,K) is the \f$u\f$
+!> component of velocity at the forward \f$x\f$ face of grid cell (I,J,K) and
+!> mesh NM.
+
+TYPE MESH_TYPE
+
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: U  !< Velocity component at current time step, \f$u_{ijk}^n\f$
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: V  !< Velocity component at current time step, \f$v_{ijk}^n\f$
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: W  !< Velocity component at current time step, \f$w_{ijk}^n\f$
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: US !< Velocity component estimated at next time step, \f$u_{ijk}^*\f$
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: VS !< Velocity component estimated at next time step, \f$v_{ijk}^*\f$
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: WS !< Velocity component estimated at next time step, \f$w_{ijk}^*\f$
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: DDDT    !< \f$(\partial D/\partial t)_{ijk}\f$ where \f$D_{ijk}\f$ is the divergence
+   REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: D       !< Divergence at current time step, \f$D_{ijk}^n\f$
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/part.f90

@@ -1,0 +1,3967 @@
+!> \brief Variables and subroutines pertaining to Lagrangian particles
+
+MODULE PART
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+USE TRAN
+USE MEMORY_FUNCTIONS, ONLY: ALLOCATE_STORAGE
+USE COMP_FUNCTIONS, ONLY : CURRENT_TIME
+USE SOOT_ROUTINES, ONLY: DROPLET_SCRUBBING
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+PRIVATE
+
+PUBLIC INSERT_ALL_PARTICLES,UPDATE_PARTICLES,REMOVE_PARTICLES,GENERATE_PARTICLE_DISTRIBUTIONS,PARTICLE_MOMENTUM_TRANSFER
+
+CONTAINS
+
+
+!> \brief Generate size distribution statistics for all particles classes
+
+SUBROUTINE GENERATE_PARTICLE_DISTRIBUTIONS
+
+USE MATH_FUNCTIONS, ONLY: EVALUATE_RAMP
+USE PHYSICAL_FUNCTIONS, ONLY : PARTICLE_SIZE_DISTRIBUTION
+
+REAL(EB) :: LL,UL,BIN_SIZE,TNOW,DD,DI
+INTEGER  :: I,J,IL,IU,ILPC
+TYPE (LAGRANGIAN_PARTICLE_CLASS_TYPE), POINTER :: LPC=>NULL()
+TYPE (RAMPS_TYPE), POINTER :: RM=>NULL()
+
+IF (N_LAGRANGIAN_CLASSES==0) RETURN ! Don't waste time if no particles
+
+TNOW=CURRENT_TIME()
+
+PART_CLASS_LOOP: DO ILPC=1,N_LAGRANGIAN_CLASSES
+
+   LPC=>LAGRANGIAN_PARTICLE_CLASS(ILPC)
+
+   IF_SIZE_DISTRIBUTION: IF (.NOT.LPC%MONODISPERSE .AND. (LPC%DIAMETER>0._EB) .OR. LPC%CNF_RAMP_INDEX>=0) THEN
+      IF (LPC%CNF_RAMP_INDEX<0) THEN
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/pois.f90

@@ -1,0 +1,7491 @@
+MODULE POIS
+
+! CODE CONVERTED USING TO_F90 BY ALAN MILLER
+! DATE: 2006-01-18  TIME: 13:48:46
+
+! POISSON SOLVER ROUTINES
+
+USE PRECISION_PARAMETERS
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+REAL(EB) SCALE
+INTEGER :: KAPPA,NMAX,IKPWR
+LOGICAL :: TPOSE,NOCOPY,OUTARY
+
+PUBLIC H3CZIS,H3CZSS,H2CZSS,H2CYSS,H3CSSS,H2CZIS,H3CSIS,H2CYIS
+
+CONTAINS
+
+SUBROUTINE H3CZIS(XS,XF,L,LBDCND,YS,YF,M,MBDCND,ZS,ZF,N,NBDCND,  &
+    H,ELMBDA,LDIMF,MDIMF,IERROR,SAVE)
+
+! +--------------------------------------------------------------------+
+! |                                                                    |
+! |                       COPYRIGHT (C) 1989 BY                        |
+! |                          ROLAND A. SWEET                           |
+! |                        ALL RIGHTS RESERVED                         |
+! |                                                                    |
+! +--------------------------------------------------------------------+
+
+REAL(EB)::  XS, XF, YS, YF, ZS, ZF, ELMBDA, DLZSQR
+INTEGER:: L, LBDCND, M, MBDCND, N, NBDCND, LDIMF, MDIMF, IERROR, LPEROD
+REAL(EB) SAVE(-3:*),H(0:*)
+
+REAL(EB) :: DX, DY, DZ, DLXSQR, DLYSQR, HM, HP
+INTEGER :: LP, MP, NP, IA, IB, IC, ID, IS, I, IR
+
+!                               CHECK FOR INVALID INPUT
+
+IERROR = 0
+
+IF (XS>XF) THEN
+  IERROR = IERROR + 1
+  SAVE(IERROR) = 1._EB
+END IF
+
+IF (L<3) THEN
+  IERROR = IERROR + 1
+  SAVE(IERROR) = 2._EB
+END IF
+
+IF (LBDCND<0 .OR. LBDCND>4) THEN
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/prec.f90

@@ -1,0 +1,47 @@
+!> \brief Set important parameters having to do with variable precision and array allocations
+
+MODULE PRECISION_PARAMETERS
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+INTEGER, PARAMETER :: FB = SELECTED_REAL_KIND(6)     !< Precision of "Four Byte" reals
+INTEGER, PARAMETER :: EB = SELECTED_REAL_KIND(12)    !< Precision of "Eight Byte" reals
+INTEGER, PARAMETER :: MAX_LPC=20                     !< Maximum number of declared particle classes
+INTEGER, PARAMETER :: MAX_SPECIES=20                 !< Maximum number of declared species
+INTEGER, PARAMETER :: MAX_LAYERS=20                  !< Maximum number of solid material layers
+INTEGER, PARAMETER :: MAX_MATERIALS=20               !< Maximum number of solid material components
+INTEGER, PARAMETER :: MAX_MATERIALS_TOTAL=400        !< Dimension of material work array
+INTEGER, PARAMETER :: MAX_REACTIONS=10               !< Maximum number of chemical reactions
+INTEGER, PARAMETER :: MAX_STEPS=20                   !< Maximum steps in processing of material residues
+INTEGER, PARAMETER :: MAX_NUMBER_SPECTRAL_BANDS=9    !< Maximum number of radiation spectral bands
+INTEGER, PARAMETER :: MAX_NUMBER_FSK_POINTS=32
+INTEGER, PARAMETER :: MAX_TERRAIN_IMAGES=10          !< Maximum number of images to paste onto complex terrain
+INTEGER, PARAMETER :: MAX_INPUT_ID=40                !< Maximum number of CTRL INPUT_IDs
+INTEGER, PARAMETER :: N_ZONE_POINTS=100              !< Maximum number of declared ZONE points (deprecated)
+INTEGER, PARAMETER :: MAX_AIT_EXCLUSION_ZONES=10     !< Maximum number of AUTO_IGNITION_TEMPERATURE exclusion zones
+INTEGER, PARAMETER :: SMOKEVIEW_OBJECTS_DIMENSION=20 !< Number of parameters that can be passed to Smokeview to describe objects
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/pres.f90

@@ -1,0 +1,3548 @@
+MODULE PRES
+
+! Find the perturbation pressure by solving Poisson's Equation
+
+USE PRECISION_PARAMETERS
+USE MESH_POINTERS
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+
+PUBLIC PRESSURE_SOLVER_COMPUTE_RHS,PRESSURE_SOLVER_FFT,PRESSURE_SOLVER_CHECK_RESIDUALS,COMPUTE_VELOCITY_ERROR
+
+CONTAINS
+
+SUBROUTINE PRESSURE_SOLVER_COMPUTE_RHS(T,DT,NM)
+
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME
+USE MATH_FUNCTIONS, ONLY: EVALUATE_RAMP
+USE COMPLEX_GEOMETRY, ONLY: IBM_IDCF
+USE GLOBAL_CONSTANTS
+
+INTEGER, INTENT(IN) :: NM
+REAL(EB), INTENT(IN) :: T,DT
+REAL(EB), POINTER, DIMENSION(:,:,:) :: UU,VV,WW,HP,RHOP
+INTEGER :: I,J,K,IW,IOR,NOM,N_INT_CELLS,IIO,JJO,KKO,ICF
+REAL(EB) :: TRM1,TRM2,TRM3,TRM4,H_OTHER,TNOW, &
+            TSI,TIME_RAMP_FACTOR,DX_OTHER,DY_OTHER,DZ_OTHER,P_EXTERNAL, &
+            VEL_EDDY,DUNDT
+TYPE (VENTS_TYPE), POINTER :: VT
+TYPE (WALL_TYPE), POINTER :: WC
+TYPE (EXTERNAL_WALL_TYPE), POINTER :: EWC
+
+IF (SOLID_PHASE_ONLY) RETURN
+IF (FREEZE_VELOCITY)  RETURN
+
+TNOW=CURRENT_TIME()
+CALL POINT_TO_MESH(NM)
+
+IF (PREDICTOR) THEN
+   UU => U
+   VV => V
+   WW => W
+   HP => H
+   RHOP => RHO
+ELSE
+   UU => US
+   VV => VS
+   WW => WS
+   HP => HS
+   RHOP => RHOS
+ENDIF
+
+! Apply pressure boundary conditions at external cells.
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/radi.f90

@@ -1,0 +1,4802 @@
+MODULE SPECDATA
+
+USE PRECISION_PARAMETERS
+IMPLICIT NONE (TYPE,EXTERNAL)
+INTEGER ::  I,J
+INTEGER, PARAMETER :: NWATERK=183
+REAL(EB) :: CPLXREF_WATER(NWATERK,2)
+INTEGER, PARAMETER :: NFUELK=94
+REAL(EB) :: CPLXREF_FUEL(NFUELK,3)
+
+! HALE, G.M. AND QUERRY, M.R., "OPTICAL CONSTANTS OF WATER IN THE 200-NM TO 200-\MU M WAVELENGTH REGION",
+! APPLIED OPTICS, 12(3), 555-63 (1973)
+
+DATA ((CPLXREF_WATER(I,J), J = 1,2), I = 1,10)  &
+/ 1.0000000E-6_EB,  2.8647890E-6_EB,&
+1.0200000E-6_EB,  2.1915636E-6_EB,&
+1.0400000E-6_EB,  1.3241691E-6_EB,&
+1.0600000E-6_EB,  1.0122254E-6_EB,&
+1.0800000E-6_EB,  1.1172677E-6_EB,&
+1.1000000E-6_EB,  1.4880987E-6_EB,&
+1.1200000E-6_EB,  4.6345919E-6_EB,&
+1.1400000E-6_EB,  5.9874090E-6_EB,&
+1.1600000E-6_EB,  8.2155782E-6_EB,&
+1.1800000E-6_EB,  9.7657473E-6_EB /
+DATA ((CPLXREF_WATER(I,J), J = 1,2), I =11,20)  &
+/ 1.2000000E-6_EB,  9.9312684E-6_EB,&
+1.2200000E-6_EB,  9.2230290E-6_EB,&
+1.2400000E-6_EB,  8.6834937E-6_EB,&
+1.2600000E-6_EB,  8.9238177E-6_EB,&
+1.2800000E-6_EB,  9.9821980E-6_EB,&
+1.3000000E-6_EB,  1.1483029E-5_EB,&
+1.3200000E-6_EB,  1.1953809E-5_EB,&
+1.3400000E-6_EB,  1.2614780E-5_EB,&
+1.3600000E-6_EB,  2.9978533E-5_EB,&
+1.3800000E-6_EB,  6.6988316E-5_EB /
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/smvv.f90

@@ -1,0 +1,1062 @@
+MODULE ISOSMOKE
+!> \brief Collection of routines to output data to smokeview.
+
+USE PRECISION_PARAMETERS
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+PRIVATE
+PUBLIC ISO_TO_FILE,SMOKE3D_TO_FILE, SLICE_TO_RLEFILE
+
+CONTAINS
+
+! ----------------------- ISO_TO_FILE -------------------------
+
+
+!> \brief Routine to output compute an isosurface and output it to a file.
+
+SUBROUTINE ISO_TO_FILE(LU_ISO,LU_ISO2, NM,IBAR, JBAR, KBAR, T,VDATA, VDATA2, HAVE_ISO2, LEVELS, NLEVELS, IBLANK, SKIP, DELTA, &
+                       XPLT, NX, YPLT, NY, ZPLT, NZ)
+  USE TRAN, ONLY : GET_IJK
+  USE BOXTETRA_ROUTINES, ONLY : DECIMATE_FB
+
+  INTEGER, INTENT(IN) :: NX, NY, NZ, NM, IBAR, JBAR, KBAR
+  INTEGER, INTENT(INOUT) :: LU_ISO, LU_ISO2
+  REAL(FB), INTENT(IN) :: T
+  REAL(FB), INTENT(IN), DIMENSION(0:NX,0:NY,0:NZ) :: VDATA, VDATA2
+  INTEGER, INTENT(IN), DIMENSION(NX-1,NY-1,NZ-1) :: IBLANK
+  INTEGER, INTENT(IN) :: HAVE_ISO2
+  INTEGER, INTENT(IN) :: SKIP
+  REAL(FB), INTENT(IN) :: DELTA
+  INTEGER, INTENT(IN) :: NLEVELS
+  REAL(FB), INTENT(IN), DIMENSION(NLEVELS) :: LEVELS
+  REAL(FB), INTENT(IN), DIMENSION(NX) :: XPLT
+  REAL(FB), INTENT(IN), DIMENSION(NY) :: YPLT
+  REAL(FB), INTENT(IN), DIMENSION(NZ) :: ZPLT
+
+  INTEGER :: I, J, K, IJK
+  INTEGER :: NXYZVERTS, NTRIANGLES, NXYZVERTS_ALL, NTRIANGLES_ALL
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/soot.f90

@@ -1,0 +1,739 @@
+MODULE SOOT_ROUTINES
+
+USE PRECISION_PARAMETERS
+USE MESH_POINTERS
+USE GLOBAL_CONSTANTS, ONLY: N_PARTICLE_BINS, MIN_PARTICLE_DIAMETER, MAX_PARTICLE_DIAMETER, K_BOLTZMANN, &
+                            N_TRACKED_SPECIES, GRAV, AGGLOMERATION_SMIX_INDEX, AGGLOMERATION_SPEC_INDEX, N_AGGLOMERATION_SPECIES
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+PUBLIC CALC_AGGLOMERATION, INITIALIZE_AGGLOMERATION,SETTLING_VELOCITY,PARTICLE_RADIUS, SOOT_SURFACE_OXIDATION
+
+REAL(EB) :: MIN_AGGLOMERATION=1.E-4_EB
+REAL(EB), ALLOCATABLE, DIMENSION(:) :: BIN_S
+REAL(EB), ALLOCATABLE, DIMENSION(:,:) :: BIN_M, BIN_X,MOBILITY_FAC,A_FAC,PARTICLE_RADIUS
+REAL(EB), ALLOCATABLE, DIMENSION(:,:,:) :: PHI_B_FAC,PHI_G_FAC,PHI_S_FAC,PHI_I_FAC,FU1_FAC,FU2_FAC,PARTICLE_MASS
+REAL(EB), ALLOCATABLE, DIMENSION(:,:,:,:) :: BIN_ETA
+INTEGER, ALLOCATABLE, DIMENSION(:,:,:,:) :: BIN_ETA_INDEX
+
+CONTAINS
+
+SUBROUTINE SETTLING_VELOCITY(NM)
+! Routine for gravitational sedimentation and
+! thermophoretic movement in gas phase.
+
+USE PHYSICAL_FUNCTIONS, ONLY: GET_VISCOSITY,GET_CONDUCTIVITY,CUNNINGHAM
+USE GLOBAL_CONSTANTS, ONLY: PREDICTOR,GVEC,SOLID_BOUNDARY,NULL_BOUNDARY,OPEN_BOUNDARY,INTERPOLATED_BOUNDARY,&
+                            GRAVITATIONAL_SETTLING,THERMOPHORETIC_SETTLING
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/turb.f90

@@ -1,0 +1,3942 @@
+! This module is useful for verification tests and development of
+! turbulence models.
+
+MODULE TURBULENCE
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+USE MESH_VARIABLES
+USE COMP_FUNCTIONS
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+
+PUBLIC :: INIT_TURB_ARRAYS, VARDEN_DYNSMAG, &
+          WALL_MODEL, COMPRESSION_WAVE, VELTAN2D,VELTAN3D, &
+          SYNTHETIC_TURBULENCE, SYNTHETIC_EDDY_SETUP, TEST_FILTER, EX2G3D, &
+          TWOD_VORTEX_CERFACS, TWOD_VORTEX_UMD, TWOD_SOBOROT_UMD, &
+          LOGLAW_HEAT_FLUX_MODEL, &
+          NS_ANALYTICAL_SOLUTION, NS_U_EXACT, NS_V_EXACT, NS_H_EXACT, SANDIA_DAT, SPECTRAL_OUTPUT, SANDIA_OUT, &
+          FILL_EDGES, NATURAL_CONVECTION_MODEL, FORCED_CONVECTION_MODEL, RAYLEIGH_HEAT_FLUX_MODEL, YUAN_HEAT_FLUX_MODEL, &
+          WALE_VISCOSITY, TAU_WALL_IJ, ABL_WALL_MODEL, RAYLEIGH_MASS_FLUX_MODEL
+
+CONTAINS
+
+
+SUBROUTINE INIT_TURB_ARRAYS(NM)
+
+USE MEMORY_FUNCTIONS, ONLY: ChkMemErr
+INTEGER, INTENT(IN) :: NM
+INTEGER :: IZERO
+TYPE (MESH_TYPE), POINTER :: M
+
+IF (DO_EVACUATION) RETURN
+CALL POINT_TO_MESH(NM)
+M => MESHES(NM)
+
+!IF (PERIODIC_TEST==2 .OR. TURB_MODEL==DYNSMAG) THEN
+!   ! real work arrays
+!   ALLOCATE(M%TURB_WORK1(0:IBP1,0:JBP1,0:KBP1),STAT=IZERO)
+!   CALL ChkMemErr('INIT_TURB_ARRAYS','TURB_WORK1',IZERO)
+!   M%TURB_WORK1 = 0._EB
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/type.f90

@@ -1,0 +1,1435 @@
+!> \brief A collection of major derived types used in FDS.
+
+MODULE TYPES
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS, ONLY : IAXIS,JAXIS,KAXIS,MAX_DIM,LOW_IND,HIGH_IND
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+
+!> \brief Parameters associated with an entire class of Lagrangian particles
+
+TYPE LAGRANGIAN_PARTICLE_CLASS_TYPE
+
+   CHARACTER(LABEL_LENGTH) :: ID                                               !< Name of particle class
+   CHARACTER(LABEL_LENGTH) :: SPEC_ID='null'                                   !< Name of evaporating gas species
+   CHARACTER(LABEL_LENGTH) :: DEVC_ID='null'                                   !< Name of controlling device
+   CHARACTER(LABEL_LENGTH) :: CTRL_ID='null'                                   !< Name of control function
+   CHARACTER(LABEL_LENGTH) :: SURF_ID='null'                                   !< Name of SURFace type
+   CHARACTER(LABEL_LENGTH) :: PROP_ID='null'                                   !< Name of PROPerty type
+   CHARACTER(LABEL_LENGTH) :: RADIATIVE_PROPERTY_TABLE_ID='null'               !< Name of radiative property table
+   CHARACTER(LABEL_LENGTH) :: CNF_RAMP_ID='null'                     !< Cumulative Number Fraction (CNF) function
+   CHARACTER(LABEL_LENGTH) :: BREAKUP_CNF_RAMP_ID='null'             !< User-defined cumulative number fraction after break-up
+   CHARACTER(LABEL_LENGTH) :: DISTRIBUTION='ROSIN-RAMMLER-LOGNORMAL'           !< Droplet size distribution
+   CHARACTER(LABEL_LENGTH) :: BREAKUP_DISTRIBUTION='ROSIN-RAMMLER-LOGNORMAL'   !< Droplet size distribution after break-up
+   CHARACTER(LABEL_LENGTH) :: QUANTITIES(10)                                   !< Names of output quantities.
+   CHARACTER(LABEL_LENGTH) :: SMOKEVIEW_LABEL(10)                              !< Smokeview file label for output quantities
+   CHARACTER(LABEL_LENGTH) :: SMOKEVIEW_BAR_LABEL(10)                          !< Short Smokeview label for output quantities
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/vege.f90

@@ -1,0 +1,1205 @@
+!> \brief Level set model of fire spread across terrain
+
+MODULE VEGE
+
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+USE MEMORY_FUNCTIONS, ONLY: CHKMEMERR
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+PUBLIC INITIALIZE_LEVEL_SET_FIRESPREAD_1,INITIALIZE_LEVEL_SET_FIRESPREAD_2,LEVEL_SET_FIRESPREAD
+INTEGER :: IZERO
+INTEGER  :: LIMITER_LS
+REAL(EB) :: B_ROTH,BETA_OP_ROTH,C_ROTH,E_ROTH,T_NOW
+REAL(EB), POINTER, DIMENSION(:,:) :: PHI_LS_P
+REAL(EB), PARAMETER :: PHI_LS_MIN=-1._EB, PHI_LS_MAX=1._EB
+
+CONTAINS
+
+
+!> \brief Set up the major level set arrays
+!>
+!> \param NM Mesh number
+!> \details Set up the array for level set value PHI_LS, and determine terrain height on each 2D mesh, Z_LS(I,J).
+!> After this routine, go back to main, exchange Z_LS, and return for more initialization.
+
+SUBROUTINE INITIALIZE_LEVEL_SET_FIRESPREAD_1(NM)
+
+USE COMPLEX_GEOMETRY, ONLY : IBM_IDCF
+INTEGER, INTENT(IN) :: NM
+INTEGER :: ICF,IW,I,J,SURF_INDEX
+TYPE (MESH_TYPE),    POINTER :: M
+TYPE (WALL_TYPE),    POINTER :: WC
+TYPE (CFACE_TYPE),   POINTER :: CFA
+TYPE (SURFACE_TYPE), POINTER :: SF
+
+T_NOW = CURRENT_TIME()
+
+CALL POINT_TO_MESH(NM)
+
+M => MESHES(NM)
+
+! Loop through all SURFace types and find level set cases that need a calculated RoS
+
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/velo.f90

@@ -1,0 +1,3359 @@
+!> \brief Collection of velocity routines.
+!> Computes the velocity flux terms, baroclinic torque correction terms, and performs the CFL check.
+
+MODULE VELO
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+
+PUBLIC VELOCITY_PREDICTOR,VELOCITY_CORRECTOR,NO_FLUX,BAROCLINIC_CORRECTION,MATCH_VELOCITY,MATCH_VELOCITY_FLUX,&
+       VELOCITY_BC,COMPUTE_VISCOSITY,VISCOSITY_BC,VELOCITY_FLUX,VELOCITY_FLUX_CYLINDRICAL
+
+
+CONTAINS
+
+
+!> \brief Compute the viscosity of the gas.
+!> \callergraph
+!> \callgraph
+!> \param T Current time (s).
+!> \param NM Mesh number.
+!> \param APPLY_TO_ESTIMATED_VARIABLES Flag indicating \f$\mu(T,\mathbf{u})\f$ or \f$\mu(T^*,\mathbf{u}^*)\f$
+
+SUBROUTINE COMPUTE_VISCOSITY(T,NM,APPLY_TO_ESTIMATED_VARIABLES)
+
+USE PHYSICAL_FUNCTIONS, ONLY: GET_VISCOSITY,LES_FILTER_WIDTH_FUNCTION,GET_POTENTIAL_TEMPERATURE,GET_CONDUCTIVITY,GET_SPECIFIC_HEAT
+USE TURBULENCE, ONLY: VARDEN_DYNSMAG,TEST_FILTER,FILL_EDGES,WALL_MODEL,WALE_VISCOSITY,ABL_WALL_MODEL
+USE MATH_FUNCTIONS, ONLY:EVALUATE_RAMP
+USE CC_SCALARS_IBM, ONLY : CCREGION_COMPUTE_KRES,CCREGION_COMPUTE_VISCOSITY
+REAL(EB), INTENT(IN) :: T
+INTEGER, INTENT(IN) :: NM
+LOGICAL, INTENT(IN) :: APPLY_TO_ESTIMATED_VARIABLES
+REAL(EB), ALLOCATABLE, DIMENSION(:) :: ZZ_GET
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/Source/wall.f90

@@ -1,0 +1,4482 @@
+!> \brief Collection of routines to compute boundary conditions
+
+MODULE WALL_ROUTINES
+
+USE PRECISION_PARAMETERS
+USE GLOBAL_CONSTANTS
+USE MESH_POINTERS
+USE DEVICE_VARIABLES, ONLY : PROPERTY,PROPERTY_TYPE
+
+IMPLICIT NONE (TYPE,EXTERNAL)
+PRIVATE
+
+PUBLIC WALL_BC,TGA_ANALYSIS
+
+TYPE(WALL_TYPE), POINTER :: WC
+TYPE(CFACE_TYPE), POINTER :: CFA
+TYPE(EXTERNAL_WALL_TYPE), POINTER :: EWC
+TYPE(LAGRANGIAN_PARTICLE_TYPE), POINTER :: LP
+TYPE(LAGRANGIAN_PARTICLE_CLASS_TYPE), POINTER :: LPC
+TYPE(ONE_D_M_AND_E_XFER_TYPE), POINTER :: ONE_D,ONE_D_BACK
+TYPE(BOUNDARY_PROPERTY_TYPE), POINTER :: BP,BP_BACK
+TYPE(BOUNDARY_COORD_TYPE), POINTER :: BC,BC_BACK
+TYPE(SURFACE_TYPE), POINTER :: SF
+TYPE(VENTS_TYPE), POINTER :: VT
+TYPE(OMESH_TYPE), POINTER :: OM
+TYPE(MESH_TYPE), POINTER :: MM
+TYPE(MATERIAL_TYPE), POINTER :: ML
+TYPE(PROPERTY_TYPE), POINTER :: PY
+LOGICAL :: CALL_HT_1D
+
+CONTAINS
+
+
+!> \brief Main control routine for applying boundary conditions.
+!>
+!> \param T Current time (s)
+!> \param DT Current time step (s)
+!> \param NM Mesh number
+ 
+SUBROUTINE WALL_BC(T,DT,NM)
+
+USE COMP_FUNCTIONS, ONLY: CURRENT_TIME
+USE SOOT_ROUTINES, ONLY: DEPOSITION_BC
+REAL(EB) :: TNOW
+REAL(EB), INTENT(IN) :: T,DT
+INTEGER, INTENT(IN) :: NM
+
+IF (DO_EVACUATION) RETURN
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/fm_burner_runs/default/go.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+date
+
+mpiexec -np 64 --hostfile hostfile --oversubscribe /Users/dol4/Desktop/radlib_fds/Build/mpi_gnu_osx_64/fdsradlib default.fds
+
+date

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/fm_burner_runs/norad/go.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+date
+
+mpiexec -np 64 --hostfile hostfile --oversubscribe /Users/dol4/Desktop/radlib_fds/Build/mpi_gnu_osx_64/fdsradlib norad.fds
+
+date

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/fm_burner_runs/plots/plot_T.py

@@ -1,0 +1,61 @@
+
+import numpy as np
+import matplotlib
+matplotlib.use('PDF')       
+import matplotlib.pyplot as plt
+
+########################################################################
+
+#-------------- DEFINE THE DATA TO PLOT (or get it from somewhere)
+
+norad   = np.loadtxt('norad_fds_line_T.csv',   delimiter=',')
+default = np.loadtxt('default_fds_line_T.csv', delimiter=',')
+wsgg    = np.loadtxt('wsgg_fds_line_T.csv',    delimiter=',')
+rcslw   = np.loadtxt('rcslw_fds_line_T.csv',   delimiter=',')
+exp_m_1p5D = np.loadtxt('../plots/T_mean_1p5D_exp.csv', delimiter=',')
+exp_m_2p5D = np.loadtxt('../plots/T_mean_2p5D_exp.csv', delimiter=',')
+exp_m_3p5D = np.loadtxt('../plots/T_mean_3p5D_exp.csv', delimiter=',')
+
+#-------------- SET UP SOME PLOT BOILERPLATE
+
+matplotlib.rcParams.update({'font.size':20, 'figure.autolayout': True}) 
+fig, ax = plt.subplots()
+ax.tick_params(direction='in', top=True, right=True)
+
+########################################################################
+
+
+#-------------- MAKE THE PLOT
+
+plt.cla()
+
+ax.plot(norad[:,0],   norad[:,6],   ':',  color='black', linewidth=1) 
+ax.plot(default[:,0], default[:,6], '-.', color='black', linewidth=1) 
+ax.plot(wsgg[:,0],    wsgg[:,6],    '--', color='black', linewidth=1) 
+ax.plot(rcslw[:,0],   rcslw[:,6],   '-',  color='black', linewidth=1) 
+ax.plot(exp_m_3p5D[:,0], exp_m_3p5D[:,1], '^',  color='black', ms=5, linewidth=1, fillstyle='none') 
+plt.text(2.5, 1300, "z=2.5D", color='blue')
+
+ax.plot(norad[:,0],   norad[:,4],   ':',  color='blue', linewidth=1) 
+ax.plot(default[:,0], default[:,4], '-.', color='blue', linewidth=1) 
+ax.plot(wsgg[:,0],    wsgg[:,4],    '--', color='blue', linewidth=1) 
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/fm_burner_runs/plots/plot_rad.py

@@ -1,0 +1,66 @@
+
+import numpy as np
+import matplotlib
+matplotlib.use('PDF')       
+import matplotlib.pyplot as plt
+
+########################################################################
+
+#-------------- DEFINE THE DATA TO PLOT (or get it from somewhere)
+
+git   = np.loadtxt('default_fds_line_rad.csv', delimiter=',')
+wsgg  = np.loadtxt('wsgg_fds_line_rad.csv',    delimiter=',')
+rcslw = np.loadtxt('rcslw_fds_line_rad.csv',   delimiter=',')
+exp_m = np.loadtxt('rad_mean_exp.csv', delimiter=',')
+exp_r = np.loadtxt('rad_rms_exp.csv',  delimiter=',')
+
+#-------------- SET UP SOME PLOT BOILERPLATE
+
+matplotlib.rcParams.update({'font.size':20, 'figure.autolayout': True}) 
+fig, ax = plt.subplots()
+ax.tick_params(direction='in', top=True, right=True)
+
+########################################################################
+
+
+#-------------- MAKE THE PLOT
+
+plt.cla()
+
+ax.plot(rcslw[:,1], rcslw[:,0], '-',  color='black', linewidth=1) 
+ax.plot(wsgg[:,1],  wsgg[:,0],  '--', color='black',  linewidth=1) 
+ax.plot(git[:,1],   git[:,0],   '-.',  color='black', linewidth=1) 
+ax.plot(exp_m[:,0], exp_m[:,1], 'o',  color='black', linewidth=1, fillstyle='none') 
+
+ax.set_xlabel("Radiative Emission (kW/m)", fontsize=22)
+ax.set_ylabel("Height (cm)",               fontsize=22)
+ax.set_xlim([0,15])
+ax.set_ylim([0,90])
+
+ax.legend(['RCSLW', 'WSGG', 'FDS default', 'Exp'], loc='upper right', frameon=False, fontsize=16)
+
+#-------------- SAVE PLOT TO FILE CALLED plot.pdf (the ".pdf" is left off below)
+
+plt.savefig("plot_rad_mean")
+
+########################################################################
+
+plt.cla()
+
+#-------------- MAKE THE PLOT
+
+ax.plot(rcslw[:,2], rcslw[:,0], '-',  color='black', linewidth=1) 
[…]

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/fm_burner_runs/rcslw/go.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+date
+
+mpiexec -np 64 --hostfile hostfile --oversubscribe /Users/dol4/Desktop/radlib_fds/Build/mpi_gnu_osx_64/fdsradlib rcslw.fds
+
+date

### 2021-10-23 notes/fm_burner/revision_2/radlib_fds/fm_burner_runs/wsgg/go.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+date
+
+mpiexec -np 64 --hostfile hostfile --oversubscribe /Users/dol4/Desktop/radlib_fds/Build/mpi_gnu_osx_64/fdsradlib wsgg.fds
+
+date
